---
title: "Waterbird building"
format: html
editor: visual
---

This doc is to make sure we do things correctly for the main analyses.

## Understanding the spatial layers

```{r}
library(CC2)
library(sf)
library(ggplot2)
```

```{r}
source('directorySet.R')
```

We should only use the complexes defined as contributing to breeding in Asset_site_list.xlsx.

```{r}
asset_list <- readxl::read_xlsx(path = file.path(datDir, 'MDBA_complex', 'Asset_site_list.xlsx'), sheet = 'Waterbird Assets')
```

That needs to have its names cleaned up. And the 'MDBA Environmental Assets' col seems to match the wrpa names.

```{r}
asset_list <- asset_list |> 
  dplyr::select(-1) |> 
  dplyr::rename(SWWRPAName = 'MDBA Environmental Assets') |> 
  dplyr::rename(hab_function = 'Habitat function')
```

Filter to just the breeding assets

```{r}
breeding_assets <- asset_list |> 
  dplyr::filter(grepl('breed', hab_function))
```

Now, do the SWWRAPAnames actually match, and do the wetlands match the mdba_bird_complexes?

Fix some things so they do

```{r}
breeding_assets <- breeding_assets |> 
  dplyr::mutate(SWWRPAName = dplyr::case_when(SWWRPAName == 'Victoria Murray' ~ 'Victorian Murray',
                   SWWRPAName == 'Intersecting streams' ~ 'Intersecting Streams',
                   SWWRPAName == 'NSW Lower Murray and Lower Darling' ~ 'New South Wales Murray and Lower Darling',
                   SWWRPAName == 'Wimmera-Mallee' ~ 'Wimmera-Mallee (surface water)',
                   SWWRPAName == 'River Murray' ~ 'South Australian River Murray',
                   .default = SWWRPAName))
```

Any that don't match?

```{r}
nowrpamatch <- which(!breeding_assets$SWWRPAName %in% unique(wrpa$SWWRPAName))

breeding_assets$SWWRPAName[nowrpamatch]
```

For the most part, the wetland differences are just typos, but Lake Alex is a subwetland. So I think when we build the polygons to use, pull that one in separatelty.

```{r}
breeding_assets <- breeding_assets |> 
  dplyr::mutate(Wetland = dplyr::case_when(Wetland == 'Gwydir wetlands' ~ 'Gwydir Wetlands',
                   Wetland == 'Macquarie-Marshes' ~ 'Macquarie Marshes',
                   Wetland == 'Fivebough and Tuckerbil swamps' ~ 'Fivebough Swamp',
                   Wetland == 'Koondrook–Perricoota Forest' ~ 'Gunbower-Koondrook-Perricoota',
                   Wetland == 'Gunbower–Koondrook–Perricoota Forest' ~ 'Gunbower-Koondrook-Perricoota',
                   Wetland == 'Corop Wetlands' ~ 'Corop Wetlands Complex',
                   # There is a sub-wetland for just Lake Alex. I wonder if we should use that.
                   # Wetland == 'Lake Alexandrina' ~ 'Coorong, Lower Lakes and Murray Mouth', 
                   Wetland == 'Lindsay–Walpolla–Chowilla Floodplain' ~ 'Lindsay-Walpolla-Chowilla',
                   .default = Wetland))
```

```{r}
nowetmatch <- which(!breeding_assets$Wetland %in% unique(mdba_bird_wetlands$Wetland))
breeding_assets$Wetland[nowetmatch]
```

Make the polygons we want to use for the breeding assets

```{r}
breeding_polys <- mdba_bird_wetlands |> 
  dplyr::filter(Wetland %in% breeding_assets$Wetland)

subalex <- mdba_bird_subwetlands |> 
  dplyr::filter(SubWetland == 'Lake Alexandrina') |> 
  dplyr::select(Wetland = SubWetland)

breeding_polys <- breeding_polys |> 
  dplyr::bind_rows(subalex)
```

Those overlap the actual wrpas

```{r}

ggplot() +
  geom_sf(data = wrpa) +
  geom_sf(data = breeding_polys, aes(fill = Wetland), alpha = 0.6) +
  theme(legend.position = 'none')
```

```{r}
# How which of those hit > 1 WRPA?
bird_wrpa <- st_intersection(breeding_polys, wrpa)
nintersects <- table(bird_wrpa$Wetland, bird_wrpa$SWWRPAName) > 0

nintersects |> rowSums() |> knitr::kable()
```

So, how should we assign condition at a complex to the wrpas?

-   Use the assignment in `breeding_assets`, rather than do it spatially.
-   If we did it spatially, we could intersect or assign ANAEs separately, but the best move is just to use the mapping in the assets.

Get those SWWRPANames on the assets.

```{r}
breeding_polys <- breeding_polys |> 
  dplyr::left_join(dplyr::select(breeding_assets, -hab_function))
```

There is duplication in Gunbower because it matches to two states and SWWRPANames.

```{r}
gunbower <- breeding_polys |> 
  filter(grepl('Gunbower', Wetland))

gunbower
```

What should we do with that? Give it to one, or split it? It's the same polygon, we just duplicated it with the join. Let's look at a spatial join and see if that makes it clearer.

```{r}
gunstate <- st_intersection(gunbower |> slice(1) |> select(Wetland), wrpa |> select(-Area, -Dams)) |> mutate(area = st_area(geometry))
gunstate
```

```{r}
ggplot(gunstate, aes(fill = SWWRPAName)) + geom_sf()
```

That's pretty even. We don't want to actually divide gunbower though, because we want to treat it as a polygon. So, can we either give it to one state/SWWRPA or the other and divide in half later, or let it duplicate as above? I think the duplication is more dangerous than the dividing.

So, let's give it to Vic, the area is a bit larger there than NSW, and we'll just have to make sure we give credit to NSW when we do state-based analyses.

```{r}
breeding_polys <- breeding_polys |> 
  filter(!(Wetland == 'Gunbower-Koondrook-Perricoota' & State == 'NSW'))
```

For this particular analysis we can JUST deal with the ANAEs in the `breeding_polys` and ignore all those outside them.

Do we want to actually cut the ANAEs, or just grab the ones that are entirely or partially within the complexes and go with that. That seems easiest.

### overlapping complexes

Do any of the complexes overlap? No

```{r}
overcomplex <- st_intersection(breeding_polys, breeding_polys)

nrow(overcomplex) == nrow(breeding_polys)
```

Several of the scripts and directory structures don't like spaces, so have a no-space name

```{r}
breeding_polys <- breeding_polys |> 
  dplyr::mutate(wetland_clean = stringr::str_remove_all(Wetland, ' '))
```

Save those out- they're not canonical, but we don't want to have to make them over and over.

```{r}
outDir <- file.path(datOut, 'waterbird_breeding')
if (!dir.exists(outDir)) {dir.create(outDir, recursive = TRUE)}
saveRDS(breeding_polys, file = file.path(outDir, 'breeding_polys.rds'))
```
