---
title: "Bird responses"
format: html
editor: visual
---

```{r}
source('directorySet.R')
library(CC2)
library(foreach)
library(doFuture)
library(progressr)
doFuture::registerDoFuture()
```

```{r}
if (parset == 'local') {
  plan(multisession)
}

if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 60,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'bird_breeding')),
          multicore))
}
```

Calculate the strictures for each asset. Do we want to do the aggregation to the asset *inside* here? I'm tempted not to, but it is part of the requirements, so I might. I'm not sure I like the dataname/summaryfun here, since we might want several and do different htings with them- it is inherently bespoke, and that's OK.

I could do that future in a function, but I might just do it here- unlike the raster data, it's not clear to me that these will be consistent enough to allow a single parallel_responses function like with `parallel_data`. So, I'll basically go back to calling the setup and runs myself here. And maybe I'll see a way forward after doing it a couple times.

```{r}
breeding_polys <- readRDS(file.path(datOut, 'waterbird_breeding', 'breeding_polys.rds'))
```

```{r}
runlist <- chunks_to_process(out_dir = datOut,
                               dataname = '',# Short circuit, just test the full list
                               summaryFun = 'waterbirds', 
                               nchunks = 1,
                               catchment = breeding_polys$wetland_clean,
                               returnForR = TRUE,
                               filetype = '.rds')
```

```{r}
source('R/bird_breeding.R')

with_progress({
  p <- progressor(steps = nrow(runlist))
  bird_all <- foreach(nl = 1:nrow(runlist),
                    .combine = rbind,
                    .errorhandling = 'remove',
                    .options.future = list(
                      seed = TRUE)) %dofuture% {
                      
                            # get the looplevels
    w <- runlist$catchment[nl]
    
    bird_responses <- bird_breeding(out_dir = datOut, 
                                strictname = 'waterbirds',
                          dataname = 'inundation',
                          summaryFun = 'areaBirdBreed',
                          catchment = w,
                          thischunk = 1, 
                          nchunks = 1,
                          saveout = TRUE, 
                          returnForR = FALSE)
    
    p(glue::glue('catchment {w}'))
                    }
})


```

```{r}
bird_all
```

## On to analysis

How should we concatenate across the catchments/assets? It's not the same problem as concatenating chunks of a standard stars-index list. One option would be to just read everything in, and have a function that combined as appropriate if it detected stars or sf. Another would be to save out into separate files instead of a list, and then read in. It probably doesn't matter much here, but will if we're basin-wide.

See `catchAggW` and the `*CatchmentAggregate` functions in `Scripts/DataProcessing`. Again, I think largely irrelevant here, and might not work for sf anyway. I think the best option here would be to have a flexible auto-detect function. Or just save out separately.
