---
title: "Bird breeding inundation"
format: html
editor: visual
---

## Calculating breeding inundation in each ANAE

Set directories and set up for parallel

```{r}
source('directorySet.R')
# library(stars)
# library(dplyr)
library(CC2)
# library(sf)
library(foreach)
library(doFuture)
library(progressr)
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per node, I think.

```{r}
if (parset == 'local') {
  plan(multisession)
}

if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 60,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'bird_breeding')),
          multicore))
}
```

## Set the function

Water needs to be between 0.5 and 1.5m deep. The data comes in in mm, but gets changed to m for consistency inside process_data. Following new conventions (dplyr \> 1.1), we hardcode area in not as an argument.

```{r}
 areaBirdBreed <- function(x, limitShallow = 0.5, limitDeep = 1.5) {
      sum(ifelse(x >= limitShallow & x <= limitDeep, area, 0))
 }
```

There is a stricture here about time of year. I suppose for speed, I could only read in those inundation files. But it will be much more flexible to get the inundation assessment in all of them, and then use the breeding period as a stricture in the next step.

### Set up the chunks

The following is typically indexed to catchments, but we should be able to use any set of polygon-based groupings. Use the breeding polys created in [waterbird_breeding_polys.qmd](waterbird_breeding_polys.qmd).

```{r}
breeding_polys <- readRDS(file.path(datOut, 'waterbird_breeding', 'breeding_polys.rds'))
```

I now have a function that can find the chunks, process them, check, and return.

Send it the ANAEs we've cut down to the breeding polys (in ANAE_birdbreeding.qmd)

```{r}
# with runlist as a tibble, this could actually be furrr_imap.
with_progress({
  birdout <- process_with_checks(dataname = 'inundation',
                          data_dir = file.path(datDir,
                                               'Inundation_new',
                                               'data',
                                               'MDB_Water_Depth_v3.6_4326'),
                          poly_path = file.path(datOut, 'ANAEbirdbreed'),
                          summaryFun = 'areaBirdBreed',
                          catchment = breeding_polys$wetland_clean,
                          out_dir = datOut,
                          nchunks = 100)
})

```

### Timings and check results

The timings and check results are returned

```{r}
birdout$timings
```

### Error checks

```{r}
birdout$failures
```
