---
title: "Waterbird analyses"
format: html
editor: visual
---

```{r}
source('directorySet.R')
library(CC2)
library(ggplot2)
library(foreach)
library(patchwork)
```

## Analyses to do

-   How much breeding area in each year in each wetland?

    -   Attributable to each ANAE type

-   How much breeding area in each WRPA?

    -   Don't forget to split Gunbower-Koondrook-Perricoota with st_intersects

-   Do we want to do anything with the sub-strictures? e.g. pre-area cutoffs, etc?

-   Do we want anything at the ANAE level?

-   The things in the workplan basically build on the above- the range/total range stuff, and the timeseries analysis

### Data

Data for each ANAE as stars

-   bird_season_year

    -   Season stricture

-   bird_season_anae

    -   Season and anae type

Indexed to the larger wetland asset as sf object

-   bird_asset

    -   Summary of area inundated for each anae type within the asset

-   bird_asset_anae

    -   Same, but limited to only the relevant anae types

-   bird_asset_anae_amount

    -   Same, but now only those anae types given they're over the thresholds.

-   bird_breed_area

    -   Final amount- total area in the wetland (in given ANAE types above threshold)

### Relevant information

Set the anae types and thresholds here too in case we need them.

```{r}
  breedtypes <- c('Freshwater meadow', 
                  'Temporary tall emergent marsh',
                  'River cooba woodland riparian zone or floodplain', 
                  'Temporary stream')
  
    areathreshold <- tibble::tibble(ANAE_DESC = breedtypes,
                                  area_min_hectares = c(10.67, 0.98, 5.57, 0.04),
                                  area_min_m2 = area_min_hectares*10000)
    
    breeding_polys <- readRDS(file.path(datOut, 'waterbird_breeding', 'breeding_polys.rds'))
    
# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')
preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')
```

## Analyses

I think I can do much of what I need with just these two datasets.

```{r}
# Should I make this a function in eFlowEval? It's conceptually similar to catchAggW, but it's really just reading and glueing sfs, not doing an agg.

bird_asset_anae_amount <- foreach(i = breeding_polys$wetland_clean,
                                  .combine = dplyr::bind_rows,
                                  .multicombine = TRUE) %do% {
  thiscatch <- readRDS(file.path(datOut, 'waterbirds', 'bird_asset_anae_amount', 
                                 paste0(i, '_', 'bird_asset_anae_amount.rds')))
                                  }

bird_breed_area <- foreach(i = breeding_polys$wetland_clean,
                                  .combine = dplyr::bind_rows,
                                  .multicombine = TRUE) %do% {
  thiscatch <- readRDS(file.path(datOut, 'waterbirds', 'bird_breed_area', 
                                 paste0(i, '_', 'bird_breed_area.rds')))
                                  }

```

### Breeding in each year in each wetland

Breeding in each Wetland

```{r}
wetland_breeding <- ggplot(bird_breed_area, 
                           aes(x = time, y = breeding_area/10000, color = Wetland)) +
  geom_line() + geom_point() +
  labs(y = 'Breeding area\n(hectares)')

wetland_breeding
```

A table would be possible, would just want timeframes to summarise probably.

```{r}

```

A map

```{r}

bba_timecut <- bird_breed_area |>
  filter((time > currenttimestart & time < currenttimeend) | 
                                 (time > preBPtimestart & 
                                    time < preBPtimeend))

wetland_breeding_map <- ggplot(bba_timecut, 
                           aes(fill = (breeding_area/10000) + 1)) +
  geom_sf(data = basin, fill = 'cornsilk') +
  geom_sf() + 
  facet_wrap('time') + 
  scale_fill_viridis_c(trans = 'log10') +
  labs(fill = 'Breeding area\nlog(hectares + 1)')
  

wetland_breeding_map
```

### Pre-post BP

This makes display easier, especially when looking at contribution of different ANAE types. But we could certainly look at that in a more analytical way.

I'm not spending a ton of time making these pretty.

```{r}
ggplot(bird_asset_anae_amount, aes(x = time, y = area_given_threshold/10000, color = ANAE_DESC)) +
  geom_line() + geom_point() +
  labs('Breeding area\n(hectares)') +
  facet_wrap('Wetland')
```

Summarise that into a table over a couple timeperiods.

```{r}
bird_asset_anae_summary <- bird_asset_anae_amount |> 
  mutate(timeperiod = case_when((time > currenttimestart & 
                                   time < currenttimeend) ~ 'Current',
                                (time > preBPtimestart & 
                                    time < preBPtimeend) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ANAE_DESC, Wetland, timeperiod) |> 
  summarise(breeding_area = mean(area_given_threshold)) |> 
  ungroup()
```

Over all wetlands, in hectares

```{r}
bird_asset_anae_summary |> 
  st_drop_geometry() |> 
  group_by(ANAE_DESC, timeperiod) |> 
  summarise(breeding_area = sum(breeding_area)/10000) |> 
  ungroup() |> 
  tidyr::pivot_wider(id_cols = ANAE_DESC, names_from = timeperiod, values_from = breeding_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  mutate(across(where(is.numeric), round, 2)) |> 
  select(ANAE_DESC, `Pre-BP`, Current, Difference, `Percent of pre`) |> 
  knitr::kable()
```

Over all anaes, per wetland

```{r}
bird_asset_anae_summary |> 
  st_drop_geometry() |> 
  group_by(Wetland, timeperiod) |> 
  summarise(breeding_area = sum(breeding_area)/10000) |> 
  ungroup() |> 
  tidyr::pivot_wider(id_cols = Wetland, names_from = timeperiod, 
                     values_from = breeding_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  mutate(across(where(is.numeric), round, 2)) |> 
  select(Wetland, `Pre-BP`, Current, Difference, `Percent of pre`) |> 
  knitr::kable()
```

A map, pre-post bp

```{r}
bird_asset_anae_summary |> 
  group_by(Wetland, timeperiod) |> 
  summarise(breeding_area = sum(breeding_area)/10000) |> 
  ungroup() |> 
  tidyr::pivot_wider(id_cols = c(Wetland, geometry), names_from = timeperiod, 
                     values_from = breeding_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  ggplot(aes(fill = Difference)) + 
  geom_sf(data = basin, fill = 'cornsilk')+
  geom_sf() +
  scale_fill_viridis_c() +
  labs(fill = 'Change in breeding area\n(hectares)')
```

## WRPA scale

We can mostly just join to the wrpas by name, but gunbower should be split.

Just do it with the full wetland dataset; would be easy enough to do with the ANAE-level

```{r}
wrpa_birds <- bird_breed_area |> 
  st_drop_geometry() |> 
  select(-State) |> # gets confusing
  filter(!grepl('Gunbower', Wetland)) |> # Drop, will add later
  left_join(wrpa, by = 'SWWRPAName') |> 
  st_as_sf()

wrpa_gunbower <- bird_breed_area |> 
  select(-State, -SWWRPAName) |> # gets confusing
  filter(grepl('Gunbower', Wetland)) |> 
  mutate(gunarea = st_area(geometry)) |> # set up to modify areas
  st_intersection(wrpa) |> 
  filter(SWWRPAName != 'Northern Victoria') |> # This is tiny
  mutate(newarea = st_area(geometry),
         adjustment = newarea/gunarea,
         breeding_area = as.numeric(breeding_area * adjustment)) |> 
  select(-newarea, -gunarea, -adjustment)

wrpa_birds <- bind_rows(wrpa_birds, wrpa_gunbower)

wrpa_birds_total <- wrpa_birds |> 
  group_by(SWWRPAName, time) |> 
  summarise(breeding_area = sum(breeding_area)) |> 
  ungroup()

wrpa_birds_prepost <- wrpa_birds_total |> 
  mutate(timeperiod = case_when((time > currenttimestart & 
                                   time < currenttimeend) ~ 'Current',
                                (time > preBPtimestart & 
                                    time < preBPtimeend) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
    mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 

  group_by(SWWRPAName, timeperiod) |> 
  summarise(breeding_area = mean(breeding_area)) |> 
  ungroup()
```

```{r}
ggplot(wrpa_birds_total, 
                           aes(x = time, y = breeding_area/10000, color = SWWRPAName)) +
  geom_line() + geom_point() +
  labs(y = 'Breeding area\n(hectares)')
```

Table

```{r}
wrpa_birds_prepost |> 
  st_drop_geometry() |> 
  group_by(SWWRPAName, timeperiod) |> 
  summarise(breeding_area = sum(breeding_area)/10000) |> 
  ungroup() |> 
  tidyr::pivot_wider(id_cols = SWWRPAName, names_from = timeperiod, 
                     values_from = breeding_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  mutate(across(where(is.numeric), round, 2)) |> 
  select(SWWRPAName, `Pre-BP`, Current, Difference, `Percent of pre`) |> 
  knitr::kable()
```

And a couple maps

```{r}
wrpa_map <- ggplot(wrpa_birds_prepost, aes(fill = (breeding_area/10000) + 1)) +
  geom_sf(data = basin, fill = 'cornsilk') +
  geom_sf() +
  scale_fill_viridis_c(trans = 'log10') +
  facet_wrap('timeperiod') +
  labs(fill = 'Breeding area\n(hectares+1)')

wrpa_map
```

```{r}
wrpachange_map <- wrpa_birds_prepost |> 
  group_by(SWWRPAName, timeperiod) |> 
  summarise(breeding_area = sum(breeding_area)/10000) |> 
  ungroup() |> 
  tidyr::pivot_wider(id_cols = c(SWWRPAName, geometry), names_from = timeperiod, 
                     values_from = breeding_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  ggplot(aes(fill = Difference)) +
  geom_sf(data = basin, fill = 'cornsilk') +
  geom_sf() +
  scale_fill_viridis_c() +
  labs(fill = 'Change in breeding area\n(hectares)')

wrpachange_map
```

```{r}
wrpa_map / wrpachange_map + plot_layout(guides = 'collect')
```

## Basin scale

I'll just do this basically like the WRPAs, using `bird_breed_area`. That uses the Wetland (asset) as the base unit, not ANAE, because that's where we assess things like sufficient area.

```{r}
basin_birds <- basin |> 
  bind_cols(bird_breed_area |> st_drop_geometry()) |> 
  group_by(time, LEVEL2NAME) |> 
  summarise(breeding_area = sum(breeding_area)) |> 
  ungroup()

basin_birds_prepost <- basin_birds |> 
  mutate(timeperiod = case_when((time > currenttimestart & 
                                   time < currenttimeend) ~ 'Current',
                                (time > preBPtimestart & 
                                    time < preBPtimeend) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
    mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 

  group_by(LEVEL2NAME, timeperiod) |> 
  summarise(breeding_area = mean(breeding_area)) |> 
  ungroup()
```

```{r}
basin_birds_prepost |> 
  st_drop_geometry() |> 
  mutate(breeding_area = breeding_area/10000) |> 
  tidyr::pivot_wider(id_cols = LEVEL2NAME, names_from = timeperiod, 
                     values_from = breeding_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  mutate(across(where(is.numeric), round, 2)) |> 
  select(' ' = LEVEL2NAME, `Pre-BP`, Current, Difference, `Percent of pre`) |> 
  knitr::kable()
```

```{r}
ggplot(basin_birds, aes(x = time, y = breeding_area/10000)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
  labs(y = 'Breeding area\n(hectares)')
```

```{r}
bbdiff <- basin_birds_prepost
bbdiff$timeperiod <- as.character(bbdiff$timeperiod)
bbdiff[3, ] <- bbdiff[1, ]
bbdiff[3, 2] <- 'Difference'
bbdiff[3, 3] <- bbdiff$breeding_area[2] - bbdiff$breeding_area[3]

bbdiff$timeperiod <- factor(bbdiff$timeperiod, levels = c('Pre-BP', 'Current', 'Difference'))


  
basin_map <- ggplot(bbdiff, aes(fill = breeding_area/10000)) +
  geom_sf() +
  scale_fill_viridis_c(trans = 'log10') +
  facet_wrap('timeperiod') +
  labs(fill = 'Breeding area\n(hectares)')

basin_map
```
