---
title: "Wetland diversity analyses"
format: html
editor: visual
---

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
source('directorySet.R')
library(CC2)
library(ggplot2)
library(foreach)
library(patchwork)
```

```{r}
# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')
preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')

# Need a clean name to bring in data
catchments <- ltimNoNorth |> 
  mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

cleancatch <- catchments$name_clean
```

A read-in function

```{r}
catch_cat_sf <- function(which_strict, catchments = cleancatch, outerdir = 'diversity') {
  foreach(i = catchments,
          .combine = dplyr::bind_rows,
          .multicombine = TRUE) %do% {
            thiscatch <- readRDS(file.path(datOut, outerdir, which_strict, 
                                           paste0(i, '_', which_strict, '.rds')))
          }
}
```

I'm making myself crazy with all the copy-pasting and not writing functions to do a lot of the data manipulations, but just trying to make sure everything works.

And I'm not putting any time into writing figure captions or cross-referencing. Easy to do in quarto though.

## What is the diversity of wetlands inundated?

Splitting that up into a few analyses:

-   Richness (# of ANAE types)

-   Diversity (shannon, either on number of wetlands per type or area per type)

-   The ANAE types themselves

-   Scales

    -   In each catchment

    -   Basin-wide

    -   Temporal diversity- are different wetlands inundated in different years? Or always the same ones?

        -   Crudely done with beta diversity, but likely needs more thought.

-   Wetland groupings? Is there a way to group the ANAEs?

-   The things in the workplan basically build on the above- the range/total range stuff, and the timeseries analysis

## Data read-in

```{r}
diversity_anae_summary <- catch_cat_sf('diversity_anae_summary')
```

```{r}
diversity_richness <- catch_cat_sf('diversity_richness')
```

```{r}
diversity_shannon_area <- catch_cat_sf('diversity_shannon_area')
```

```{r}
diversity_temporal_abgamma <- catch_cat_sf('diversity_temporal_abgamma')

```

To get the total inundated area, we can just sum `diversity_anae_summary`.

```{r}
total_inun_area <- diversity_anae_summary |> 
  sf::st_drop_geometry() |> 
  summarise(area_inundated = sum(area_inundated),
            total_area = sum(total_area),
            n_inundated = sum(n_inundated),
            n_anaes = sum(n_anaes),
            .by = c(time, name_clean, ValleyName)) |> 
  mutate(prop_wetland_inundated = area_inundated/total_area) |> 
  left_join(werptoolkitr::cewo_valleys, by = 'ValleyName') |> 
  st_as_sf()
```

Check

```{r}
ggplot(total_inun_area, aes(x = time, y = prop_wetland_inundated)) + geom_point() + geom_line() + facet_wrap('ValleyName')
```

### Basin versions

Diversity_anae_summary should have what we need- it has the anae types and their inundation are, so we can just make these here.

Basically steal these from the catchment-scale analyses in anae_diversity.R

```{r}
basin_anae_richness <- diversity_anae_summary |> 
  st_drop_geometry() |> 
    mutate(n_anaes = dplyr::n_distinct(ANAE_DESC),
           .by = time) |>
    filter(area_inundated > 0) |>
    summarise(anae_diversity_richness = dplyr::n_distinct(ANAE_DESC),
              diversity_richness_proportion = anae_diversity_richness/unique(n_anaes),
              .by = time) |>
    arrange(time) |> 
  bind_cols(basin) |> 
  st_as_sf()
```

Shannon should be better- more opportunity for variation. Again, ripped straight out of anae_diversity. This should all just be functioned, but I need to get it done.

```{r}
  # a function to get it from a vector of values, each of which corresponds to some measure of an anae type (number or area)
  calc_shan <- function(x) {
    px <- x/sum(x)
    shan <- -sum(px*log(px))
    return(shan)
  }
```

```{r}

  # Shannon (based on number)
  basin_shannon_number <- diversity_anae_summary |>
    st_drop_geometry() |>
    mutate(area_binary = area_inundated > 0) |> # just whether it's area or not
    summarise(n_anaes_type = sum(area_binary), .by = c(ANAE_DESC, time)) |> # the 'abundance', e.g. number of wetlands of each type
    filter(n_anaes_type > 0) |> # otherwise the log dies, and they don't count anyway.
    summarise(shannon_binary = calc_shan(n_anaes_type), .by = c(time)) |>
    arrange(time)|> 
  bind_cols(basin) |> 
  st_as_sf()

  # Shannon (based on area)
  basin_shannon_area <- diversity_anae_summary |>
    st_drop_geometry() |>
    summarise(total_area = sum(area_inundated), .by = c(ANAE_DESC, time)) |> # the 'abundance', e.g. number of wetlands of each type
    filter(total_area > 0) |> # otherwise the log dies, and they don't count anyway.
    summarise(diversity_shannon_area = calc_shan(total_area), .by = c(time)) |>
    arrange(time)|> 
  bind_cols(basin) |> 
  st_as_sf()
```

## Expected and max

These are for the catchment, but we sometimes need to reference basin, so do it here once we have basin info

```{r}
total_basin_anae <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  summarise(basin_anae = n_distinct(ANAE_DESC)) |> 
  pull()

shannon_expectations <- diversity_anae_summary |>
  sf::st_drop_geometry() |> 
  summarise(n_anae_types = n_distinct(ANAE_DESC),
            max_shannon_catchment = log(n_anae_types),
            max_shannon_basin = log(total_basin_anae),
            .by = c(ValleyName, name_clean))
```

Getting the expected shannon given the basin p's depends on the vector of regional probabilities

```{r}
expected_shannon <- function(N, regional_probs, 
                             n_boots = 1000, returntype = 'mean') {
  
  H <- matrix(NA, ncol = length(N), nrow = n_boots)
  colnames(H) <- paste0('N_', as.character(N))
  
  for (i in 1:length(N)) {
    for (j in 1:n_boots) {
      # This loses the names, but that doesn't matter.
      localcomp <- extraDistr::rcat(N[i], regional_probs)
      localprops <- table(localcomp)/N[i]
      H[j,i] <- -sum(localprops*log(localprops))
    }
  }
  
  if (returntype == 'dist') {return(H)}
  
  if (returntype == 'mean') {return(apply(H, 2, mean))}
  
}
```

Get basin-level probabilities

```{r}
basin_probs <- diversity_anae_summary |>
    st_drop_geometry() |>
    summarise(basin_inun_area = sum(area_inundated),
              .by = c(ANAE_DESC)) |> # If we include time here, it gives a different set of p's each year
    mutate(wetland_area = sum(basin_inun_area),
           prob = basin_inun_area/wetland_area)
```

The overall basin-scale shannon

```{r}
basin_shan_overall <- calc_shan(basin_probs$basin_inun_area[basin_probs$basin_inun_area > 0])
```

Get the expected shannon given the basin composition and the number of local ANAEs

```{r}
shannon_expectations <- shannon_expectations |> 
  mutate(basin_shannon_overall = basin_shan_overall,
         expected_shannon = expected_shannon(N = n_anae_types, 
                                             regional_probs = basin_probs$prob))
```

Save

```{r}
saveRDS(shannon_expectations,
        file.path(datOut, 'diversity', 'shannon_expectations.rds'))
```

## Analyses

I'm going to try to avoid actually reading in any stars, but it might be unavoidable.

### Inundation in each ANAE type

make a couple quick plots. Not worrying too much about making them pretty, just mostly making sure the data is there.

Could also make this plot as the area fraction or number fraction with appropriate columns. Likely we'll want to collapse these down or look at some reasonable subset.

```{r}
ggplot(diversity_anae_summary, 
       aes(x = time, y = area_inundated/10000, color = ValleyName)) +
  geom_line() + geom_point() +
  facet_wrap('ANAE_DESC')
```

*Maybe not for SRA, but this is primed for a spatio-temporal Bray-Curtis --\> NMDS analysis comparing the sets of inundated wetland types through time and across catchments*

### Richness in each catchment

The number of anae types

```{r}
ggplot(diversity_richness, aes(x = time, y = anae_diversity_richness, color = ValleyName)) +
  geom_line() + geom_point()
```

And since valleys differ in the number of ANAE types, the proportion of ANAEs that exist in each valley

```{r}
ggplot(diversity_richness, aes(x = time, y = diversity_richness_proportion, color = ValleyName)) +
  geom_line() + geom_point()
```

And we can look at individual wetlands rather than type- what proportion of the wetlands in each catchment get inundated?

```{r}
ggplot(diversity_richness, aes(x = time, y = UID_proportion, color = ValleyName)) +
  geom_line() + geom_point()
```

Make a pre-post BP map

```{r}
richness_prepost <- diversity_richness |> 
  mutate(timeperiod = case_when((time > currenttimestart & 
                                   time < currenttimeend) ~ 'Current',
                                (time > preBPtimestart & 
                                    time < preBPtimeend) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, timeperiod) |> 
  summarise(diversity_richness_proportion = mean(diversity_richness_proportion),
            UID_proportion = mean(UID_proportion)) |> 
  ungroup()
```

A table

```{r}
richness_prepost |> 
  st_drop_geometry() |> 
  tidyr::pivot_wider(id_cols = ValleyName, 
                     names_from = timeperiod, 
                     values_from = diversity_richness_proportion) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  mutate(across(where(is.numeric), \(x) round(x, 2))) |> 
  select(ValleyName, `Pre-BP`, Current, Difference, `Percent of pre`) |> 
  knitr::kable()
```

```{r}
ggplot(richness_prepost, aes(fill = diversity_richness_proportion)) +
  geom_sf() +
  facet_wrap('timeperiod') +
  scale_fill_viridis_c(option = 'magma')
```

### Diversity in each catchment

I did this with number and with area, just doing area as a demo

```{r}
ggplot(diversity_shannon_area, aes(x = time, y = diversity_shannon_area, 
                                   color = ValleyName)) +
  geom_line() + geom_point()
```

```{r}
shannon_area_prepost <- diversity_shannon_area |> 
  mutate(timeperiod = case_when((time > currenttimestart & 
                                   time < currenttimeend) ~ 'Current',
                                (time > preBPtimestart & 
                                    time < preBPtimeend) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, timeperiod) |> 
  summarise(diversity_shannon_area = mean(diversity_shannon_area)) |> 
  ungroup()
```

```{r}
shannon_area_prepost |> 
  st_drop_geometry() |> 
  tidyr::pivot_wider(id_cols = ValleyName, 
                     names_from = timeperiod, 
                     values_from = diversity_shannon_area) |> 
  mutate(Difference = Current - `Pre-BP`,
         'Percent of pre' = (Current/`Pre-BP`) * 100) |> 
  mutate(across(where(is.numeric), \(x) round(x, 2))) |> 
  select(ValleyName, `Pre-BP`, Current, Difference, `Percent of pre`) |> 
  knitr::kable()
```

```{r}
ggplot(shannon_area_prepost, aes(fill = diversity_shannon_area)) +
  geom_sf() +
  facet_wrap('timeperiod') +
  scale_fill_viridis_c(option = 'magma')
```

### Temporal turnover

This is about temporal turnover, so doesn't work as a timeseries; it's an analysis of the timeseries, fundamentally. I'm mostly interested in beta diversity here; alpha is basically done above.

```{r}

ggplot(diversity_temporal_abgamma, aes(x = ValleyName, y = beta_diversity_anae)) +
  geom_col()
```

### Richness and diversity in the basin

This will be a big analysis, need to think about it.

How can we summarise at the basin scale in a way the data is small enough to read in?

That's boring. Wondering if I stuffed something up. I don't think so, I think it might just be boring- by the time we're at the basin, maybe there's just always 61 anae types that get inundated? Tracing back, we don't ever do anything silly like dropping all the zeros (and they are in there if we check).

```{r}
ggplot(basin_anae_richness, aes(x = time, y = diversity_richness_proportion)) + 
  geom_point() + geom_line()
```

### Shannon

```{r}
ggplot(basin_shannon_number, aes(x = time, y = shannon_binary)) + 
  geom_point() + geom_line()

```

```{r}
ggplot(basin_shannon_area, aes(x = time, y = diversity_shannon_area)) + 
  geom_point() + geom_line()
```

Make a map

```{r}
basin_shannon_prepost <- basin_shannon_area |> 
  mutate(timeperiod = case_when((time > currenttimestart & 
                                   time < currenttimeend) ~ 'Current',
                                (time > preBPtimestart & 
                                    time < preBPtimeend) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |> 
  summarise(diversity_shannon_area = mean(diversity_shannon_area)) |> 
  ungroup()
```

A bit silly

```{r}
ggplot(basin_shannon_prepost, aes(fill = diversity_shannon_area)) +
  geom_sf() +
  facet_wrap('timeperiod') +
  scale_fill_viridis_c(option = 'mako')
```

