---
title: "Wetland diversity analyses"
format: html
editor: visual
---

```{r}
source('directorySet.R')
library(CC2)
library(ggplot2)
library(foreach)
library(patchwork)
```

```{r}
# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')
preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')
```

## What is the diversity of wetlands inundated?

Splitting that up into a few analyses:

-   In each catchment

    -   `catchAggW` in eFlowEval (but might need modifications?)

-   A plot of inundation (%?) in each wetland type

-   Basin-wide

-   Wetland groupings?

-   Temporal diversity- are different wetlands inundated in different years? Or always the same ones?

    -   `tempaggregate` in eFlowEval (but might need modifications)

-   For each:

    -   Just use binary is inundated? Or use area or proportional area?

    -   Temporal scale? If we want yearly, will want to `tempaggregate` everything.

## Analyses

I'm going to try to avoid actually reading in any stars, but it might be unavoidable.

```{r}

```
