---
title: "Wetland diversity analyses"
format: html
editor: visual
---

```{r}
source('directorySet.R')
library(CC2)
library(ggplot2)
library(foreach)
library(patchwork)
```

```{r}
# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')
preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')

# Need a clean name to bring in data
catchments <- ltimNoNorth |> 
  mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))
```

## What is the diversity of wetlands inundated?

Splitting that up into a few analyses:

-   In each catchment

-   A plot of inundation (%?) in each wetland type

-   Basin-wide

-   Wetland groupings?

-   Temporal diversity- are different wetlands inundated in different years? Or always the same ones?

-   The things in the workplan basically build on the above- the range/total range stuff, and the timeseries analysis

-   For each:

    -   Just use binary is inundated? Or use area or proportional area?

    -   Temporal scale? If we want yearly, will want to `tempaggregate` everything.

## Analyses

I'm going to try to avoid actually reading in any stars, but it might be unavoidable.

### Inundation in each ANAE type

```{r}
diversity_anae_summary <- foreach(i = catchments$name_clean,
                                  .combine = dplyr::bind_rows,
                                  .multicombine = TRUE) %do% {
  thiscatch <- readRDS(file.path(datOut, 'diversity', 'diversity_anae_summary', 
                                 paste0(i, '_', 'diversity_anae_summary.rds')))
                                  }
```

make a couple quick plots. Not worrying too much about making them pretty

```{r}
ggplot(diversity_anae_summary, 
       aes(x = time, y = area_inundated/10000, color = ValleyName)) +
  geom_line() + geom_point() +
  facet_wrap('ANAE_DESC')
```
