---
title: "Report Data Updates"
format: html
editor: visual
---

We need to update some analyses for the report. I need to extract some data that has already been processed and summarise it in different ways than before. I don't want to re-run the analyses, and instead use the original data outputs, just process them a bit differently or extract thigns we hadn't extracted previously.

```{r}
library(sf)
library(dplyr)
library(foreach)
source('directorySet.R')
```

```{r}
# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20170701') # last day is 2022-07-01, so 5 years back
currenttimeend <- lubridate::ymd('20240301')

# Centered on BP date?
preBPtimestart <- lubridate::ymd('20060701')
preBPtimeend <- lubridate::ymd('20110701')

# Need a clean name to bring in data
catchments <- eFlowEval::ltimNoNorth |> 
  mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

cleancatch <- catchments$name_clean
```


## 'Lateral connectivity'

Here, we want the area of inundation in ANAE polygons assigned to Red Gum (lower) and Black Box (upper). That's already been calculated, and is in the rds files in `file.path(datOut, 'red_gum', 'anae_inun_anae_name_catchment')`

We will need to extract the total area of wetlands of each named type. We have it, but never aggregated it that way.

```{r}
allwets <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))
```


```{r}
# veg_name <- 'red_gum'
# veg_grep <- dplyr::case_when(veg_name == 'black_box' ~ 'black box',
#                                veg_name == 'red_gum' ~ 'red gum',
#                                veg_name == 'coolabah' ~ 'cool',
#                                veg_name == 'lignum' ~ 'lignum')

  # Filter the polygons
rgwets <- allwets |> 
  dplyr::filter(grepl('red gum', ANAE_DESC, ignore.case = TRUE)) # the name filter

# Add up their areas
rgwets <- rgwets |> 
  dplyr::mutate(area = sf::st_area(geometry)) |> 
  st_drop_geometry() |> 
  summarise(ValleyName = unique(ValleyName), area = sum(as.numeric(area)), 
            .by = ValleyName) |> 
  mutate(species = 'red_gum')

bbwets <- allwets |> 
  dplyr::filter(grepl('black box', ANAE_DESC, ignore.case = TRUE)) # the name filter

# Add up their areas
bbwets <- bbwets |> 
  dplyr::mutate(area = sf::st_area(geometry)) |> 
  st_drop_geometry() |> 
  summarise(ValleyName = unique(ValleyName), area = sum(as.numeric(area)), 
            .by = ValleyName) |> 
  mutate(species = 'black_box')

named_areas <- dplyr::bind_rows(rgwets, bbwets)

named_areas <- left_join(named_areas, eFlowEval::ltimNoNorth) |> 
  st_as_sf()
saveRDS(named_areas, file.path(datOut, 'report_updates', 'named_wetland_areas.rds'))
```

## 'Extent'

Here, we want to get the ANAE polygons with ALA records for each species, as well as the adult favourability in those specific polygons.

```{r}
bb <- readRDS(file.path(datOut, 'vegmapping','black_box_anae_records.rds'))
```

```{r}
# are the UIDs enough?
all(unique(bb$UID) %in% allwets$UID)
```
So, first we want all the ANAE polygons where there are records; the '_records.rds' files have hte records themselves, but have been joined to anaes, so we can select those UIDs. I might save a few useful things there too.

Sort it out with black box

```{r}
bb_all_wetlands <- bb |> 
  st_drop_geometry() |> 
  summarise(n_records = n(), .by = c(UID)) |> 
  mutate(species = 'black_box') |> 
  left_join(allwets, by = 'UID') |> 
  st_as_sf() |> 
  mutate(area = as.numeric(st_area(geometry)))
```

```{r}
bb_all_wetlands_catchment <- 
  bb_all_wetlands |> 
  st_drop_geometry() |> 
  summarise(species = unique(species), 
            area = sum(area), n_records = sum(n_records),
            .by = ValleyName) |> 
  left_join(eFlowEval::ltimNoNorth) |> 
  st_as_sf()
```

Now, where are the adult favourabilities for *just those anaes*?

I think everythign we save out might be the summaries. 

In woody_general, it looks like bare_stricts are raw, and yearstricts are year-aggregated but still in ANAEs.

```{r}
ads <- readRDS(file.path(datOut, 'black_box', 'adult_area', 'Avoca_adult_area.rds'))
```


