---
title: "Strictures and diversity methods"
echo: false
format:
  html:
    embed-resources: true
    toc: true
    comments:
      hypothesis: true
  docx:
    toc: true
    toc-depth: 2
    prefer-html: true
    # setting these to the html defaults so they don't get jumbled between format
    fig-width: 7
    fig-height: 5
    reference-doc: ../default_word_template.docx
bibliography: ../HabProcessPaper/references.bib
---

```{r}
#| include: false
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
#| include: false
library(dplyr)
library(ggplot2)
library(eFlowEval)
library(foreach)
library(kableExtra)
source('directorySet.R')

```

```{r}
#| label: background-data
#| include: false

ausoutline <- rnaturalearth::ne_countries(country = 'australia',
                                          type = 'countries', scale = 'medium') |> 
  st_transform(st_crs(ltimNoNorth))

cities <- rnaturalearth::ne_download(type="populated_places_simple", scale = 'small') |> 
  filter(name %in% c("Canberra", "Adelaide", "Brisbane", "Melbourne", "Sydney"))

# just get the east
eastbox <- sf::st_bbox(ausoutline)
eastbox <- c(xmin = 550000, ymin = -4300000, xmax = 2122000, ymax = -1158000)

aucut <- sf::st_crop(ausoutline, eastbox)
```

## Vegetation

We assess favourable area for Red Gum (*Eucalyptus camaldulensis*), Black Box (*Eucalyptus largiflorens*), Coolabah (*Eucalyptus coolabah*), and Lignum (*Muehlenbeckia florulenta*) using a strictures-and-promoters framework (@lester2020). This framework asks if there are favourable conditions for each of several sequential life stages. This approach captures the major known limitations and requirements of species, including the necessity of completing a life cycle.

### Strictures

Three primary life stages for each species were modeled; adults, regeneration (germination or sprouting), and seedling survival. For each species, we identified major environmental requirements for each life stage from the literature, each with several environmental requirements @tbl-env-reqs. Favourability for adult condition and survival depends on inundation, with strictures arising from excessive inundation (continuous inundation can waterlog or drown roots), the interval between inundation events (most species require inundation at some frequency), and the season in which those events occur. For regeneration, some species have a favourable season, likely due to temperatures, and all require preceding inundation followed by sustained moisture duration over several days. The seedling stage then extends this requirement for soil moisture over months to allow growth past the cotyledon stage and establishment of robust root systems. While these plants need recurrent flooding for establishment and persistence, the seedling stages tend to be sensitive to excessive flooding, and so we also include seedling failure with prolonged inundation.

+-----------+-----------------------------------------------------------------------------+---------------------------------------+--------------------------+----------------------------------------------------------------------------+-------------------------------------------+--------------------------------------------+---------------------------------------------------+
| Species   | Regeneration season                                                         | Regeneration moisture duration (days) | Seedling period (months) | Seedling excessive inundation (months)                                     | Adult excessive inundation (months)       | Adult inundation interval (months)         | Adult inundation season                           |
+===========+=============================================================================+=======================================+==========================+============================================================================+===========================================+============================================+===================================================+
| Red gum   | Sept-Dec ('Spring to early summer') [@rogers2011; @johns2009]               | 14 [@casanova2015]                    | 4.5 [@roberts2011]       | \>2, 'several months' [@johns2009; @dexter1978]                            | 24 [@rogers2011]                          | 48 [@rogers2011]                           | July-Dec ('winter to early summer') [@rogers2011] |
+-----------+-----------------------------------------------------------------------------+---------------------------------------+--------------------------+----------------------------------------------------------------------------+-------------------------------------------+--------------------------------------------+---------------------------------------------------+
| Black box | May-October (Northern basin), November-March (Southern basin) [@rogers2011] | 10 [@jensen2008]                      | 6 [@roberts2011]         | \>2, '70 days' [@johns2009]                                                | 5 [@rogers2011]                           | 96 (8 years) [@rogers2011]                 | year-round [@rogers2011]                          |
+-----------+-----------------------------------------------------------------------------+---------------------------------------+--------------------------+----------------------------------------------------------------------------+-------------------------------------------+--------------------------------------------+---------------------------------------------------+
| Coolabah  | Jan-April 'late summer' 'high temperature' [@rogers2011; @roberts2011]      | 14 [@casanova2015]                    | 6                        | No information [@rogers2011; @durant2016]                                  | No information [@rogers2011; @durant2016] | 240 (20 years) [@rogers2011; @roberts2011] | No data, year-round                               |
|           |                                                                             |                                       |                          |                                                                            |                                           |                                            |                                                   |
|           |                                                                             |                                       |                          |                                                                            |                                           |                                            | [@rogers2011]                                     |
+-----------+-----------------------------------------------------------------------------+---------------------------------------+--------------------------+----------------------------------------------------------------------------+-------------------------------------------+--------------------------------------------+---------------------------------------------------+
| Lignum    | Sept-April 'spring to autumn' [@rogers2011; @casanova2015]                  | 14 [@casanova2015]                    | 3 [@capon2009]           | \>1 (any inundation during the seedling period) [@roberts2011; @capon2009] | 12 [@rogers2011]                          | 120 (10 years) [@rogers2011]               | Sept-Dec 'spring- early summer' [@rogers2011]     |
+-----------+-----------------------------------------------------------------------------+---------------------------------------+--------------------------+----------------------------------------------------------------------------+-------------------------------------------+--------------------------------------------+---------------------------------------------------+

: Inundation and soil moisture requirements for four species of wetland-dependent woody vegetation in the Murray-Darling Basin, with references. Because inundation data is bimonthly, seasonality has been approximated as closely as possible given the limitations of those two-month units, and statements such as 'several months of inundation' have been translated to \> 2 months. {#tbl-env-reqs}

For the results presented here, the final outcome (i.e. favourable conditions for adults, followed by regeneration and recruitment) is reported. So conditions may be favourable for seedling survival, but if there was no preceding germination, then we would say that conditions were not favourable for overall recruitment. These species can be very long-lived as adults (hundreds of years) and do not have persistent soil seed banks [@roberts2011].

### Environmental data

We used two publicly-available datasets to establish environmental conditions for each model type- a two-monthly inundation depth layer @teng2023 and a daily soil moisture layer @frost2018, chosen to capture environmental requirements of the species, with inundation also being a common hydrological proxy of favourability. Both of these datasets are raster timeseries, and were processed into a set of 287,680 wetland polygons comprising the Australian National Aquatic Ecosystem Classification (ANAE, @brooks2021) spanning the entire Murray-Darling Basin. We processed the rasters into the polygons using the eFlowEval R package @holt2024 , yielding inundation and soil moisture timeseries in each polygon. For inundation, the area inundated \> 5mm depth was calculated for each polygon, while for soil moisture, the area of each polygon with soil moisture between 10% and 30% was calculated, reflecting soil moisture requirements for recruitment and seedling survival @jensen2008.

### Assessing favourability

To assess favourability, we calculated the area of favourable conditions in each ANAE polygon at each timestep, as determined by the relevant conditions in @tbl-env-reqs using the eFlowEval R package @holt2024 . These conditions were assessed at each timestep in each ANAE polygon for each species. The requirements necessarily include not just the current conditions on each day or bimonthly period, but also preceding conditions, e.g. soil moisture must be maintained for some number of days. Thus, in this example, the favourability of each day was determined by whether the preceding required number of days had all met the soil moisture requirement. In addition to assessing favourability to each life stage independently, conditional results were assessed as well. So, for conditional germination to be successful, the germination conditions must be favourable, but there also must have been favourable conditions for adults preceding that germination (typically 10-14 days, @tbl-env-reqs), as these species tend to regenerate from an aerial seedbank or sprouting (@roberts2011). Likewise, successful recruitment requires not only conditions favourable for seedling survival, but also favourable adult and germination conditions at the start of the seedling period so there are seedlings to survive. In these cases, the eFlowEval framework looks back to the start of the stage's period for the favourable area in the preceding stage. The favourable area for the stage conditional on preceding stages is the minimum of this preceding stage area and the area of favourability for the target stage. From these analyses, we return the area of favourability from each stage independently, as well as the area of favourability from regeneration following adults, and for recruitment as the full sequence from adults to regeneration to seedling survival.

## Diversity

Understanding how inundation is distributed across different wetland types can provide critical information about the impacts on different components of the ecosystem. For example, are only a small subset of wetland types being inundated, or is inundation happening to a wide range of wetland types? Within an area such as a catchment or the basin, inundation of many wetland types suggests a greater opportunity for diverse and complex ecosystem processes, while inundation of few types prioritises those few at the detriment of others and the benefits that accrue from a diverse ecosystem. Shannon diversity is a measure of how many different \'things\' there are and their relative proportions. Here, we use Shannon diversity to measure the diversity of inundated wetland types, with high diversity equating to inundation of appreciable amounts of many different wetland types (and so contributing to a diverse overall aquatic ecosystem in that catchment) and low diversity equating to inundation of few wetland types.

To assess the diversity of inundated wetland types, a two-monthly inundation depth layer @teng2023 provided raster data across the basin. This was processed into a set of 287,680 wetland polygons comprising the Australian National Aquatic Ecosystem Classification (ANAE, @brooks2021) spanning the entire Murray-Darling Basin, each of which is given a particular wetland type classification. We processed the rasters into the polygons using the eFlowEval R package @holt2024 , yielding a value for the area of inundation \> 5mm for each polygon.

To calculate the diversity of wetland types inundated in each catchment, we took the set of ANAE polygons in that catchment and calculated the Shannon diversity, which quantifies diversity in terms of the proportion $p_x$ of each type present,

$$H=-\sum_x p(x)ln[p(x)]$$

This approach provides information about both how many wetland types are inundated, but also how their relative areas of inundation vary, and so is more nuanced than a simple count of the number of types with inundation. The *x* here are each of the 70 ANAE types and the $p_x$ are the area inundated of that type divided by the total area of wetland inundation in the catchment.

These calculations then yielded a timeseries of Shannon diversity of the types of wetlands inundated in each catchment.
