---
title: "Mean soil temp"
format: html
editor: visual
---

## Calculating soil moisture data for veg

First, set directories and set up for parallel

```{r}
source('directorySet.R')
library(eFlowEval)
```

```{r}
library(sf)
library(foreach)
library(doFuture)
library(progressr)
# make the handlers call in the console.
# handlers(global = TRUE)
# Not supposed to need this, but it seems to help
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per node, I think.

```{r}
if (parset == 'local') {
  plan(multisession)
}

# There's a couple in the condamine that time out at 60. Nearly everything else finishes in 10-30.
if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 600,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'daily1030')),
          multicore))
}
```

## Set functions

We need to do a few things here. And so may want to break this notebook up.

For soil temp, let's just get the area-weighted mean for each polygon. `eFlowEval::weightedMean` does this.

## Run and check

```{r}
# 10 days > 10%
with_progress({
  tempmean <- process_with_checks(dataname = 'soiltemp',
                          data_dir = file.path(datDir,
                                               'soil_temp_02_23'),
                          poly_path = file.path(datOut, 'ANAEcatchment'),
                          summaryFun = 'weightedMean',
                          catchment = 'all',
                          out_dir = datOut,
                          nchunks = 100)
})
```

```{r}
tempmean$timings
tempmean$failures
```

This gets done in the above, but it's handy to past in to a terminal

```{r}
#| eval: false
library(eFlowEval)
source('directorySet.R')
ct <- chunks_to_process(dataname = 'soiltemp',
                        summaryFun = 'weightedMean',
                          catchment = 'all',
                          out_dir = datOut,
                          nchunks = 100)
```
