---
title: "Veg soil moisture"
format: html
editor: visual
---

## Calculating soil moisture data for veg

First, set directories and set up for parallel

```{r}
source('directorySet.R')
library(CC2)
```

```{r}
library(sf)
library(foreach)
library(doFuture)
library(progressr)
# make the handlers call in the console.
# handlers(global = TRUE)
# Not supposed to need this, but it seems to help
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per node, I think.

```{r}
if (parset == 'local') {
  plan(multisession)
}

# There's a couple in the condamine that time out at 60. Nearly everything else finishes in 10-30.
if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 1200,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'daily1030')),
          multicore))
}
```

## Set functions

We need to do a few things here. And so may want to break this notebook up.

Unlike the other veg1\_ notebooks, this one is not going to roll the raster, but instead get the daily area in the moisture band and then we'll roll the polygons later. That's a bit cruder than the rolling calculations, but should yield a massive speedup, and is less crude than operating on mean soil moisture in the polygons.

The stricture is a moisture band from 10-30%

```{r}
areamoist_10_30 <- function(x) {
  sum(ifelse(x >= 0.1 & x <= 0.3, area, 0), na.rm = TRUE)
}
```

## Run and check

This is shared between red gum and black box, and is needed for germ and seedlings

```{r}
# 10 days > 10%
with_progress({
  out1030 <- process_with_checks(dataname = 'soilmoisture',
                          data_dir = file.path(datDir,
                                               'soil_moisture_more'),
                          poly_path = file.path(datOut, 'ANAEcatchment'),
                          process_function = 'areamoist_10_30',
                          catchment = 'all',
                          out_dir = datOut,
                          poly_per_chunk = 10)
})
```

```{r}
out1030$timings
out1030$failures
```

This gets done in the above, but it's handy to paste in to a terminal

```{r}
#| eval: false
source('directorySet.R')
library(CC2)
ct <- chunks_to_process(dataname = 'soilmoisture',
                        summaryFun = 'areamoist_10_30',
                          catchment = 'all',
                          out_dir = datOut,
                          poly_per_chunk = 10)
```
