---
title: "Veg ANAE type mapping"
format: html
editor: visual
---

Here, we want to get the ANAE types with records for each veg species in the [ALA](https://www.ala.org.au/).

```{r}
source('directorySet.R')
# ALA package
library(galah)
library(sf)
library(ggplot2)

vegdir <- file.path(datOut, 'vegmapping')
galah_config(email = "g.holt@deakin.edu.au", atlas = "Australia")

```

## Download from ALA

### Black box

```{r}
black_box <- galah_call() |>
  galah_identify("Eucalyptus largiflorens") |>
  atlas_occurrences()
```

### Red gum

```{r}
red_gum <- galah_call() |>
  galah_identify("Eucalyptus camaldulensis") |>
  atlas_occurrences()
```

### Coolabah

```{r}
coolabah <- galah_call() |>
  galah_identify(c("Eucalyptus coolabah", 'Eucalyptus microtheca')) |>
  atlas_occurrences()
```

### Lignum

```{r}
lignum <- galah_call() |>
  galah_identify(c("Muehlenbeckia florulenta")) |>
  atlas_occurrences()
```

## Make geographic

We need *all* the anaes

```{r}
all_anaes <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))
```

We need to make the data we just read in geographic

```{r}

make_geo <- function(x) {
   x |> 
  tidyr::drop_na(decimalLongitude, decimalLatitude) |> 
  st_as_sf(coords = c('decimalLongitude', 'decimalLatitude'))  |>  
  st_set_crs("WGS84") |>  
  st_transform(st_crs(all_anaes))
}

black_box <- make_geo(black_box)
red_gum <- make_geo(red_gum)
coolabah <- make_geo(coolabah)
lignum <- make_geo(lignum)
```

### Maps

```{r}
base_aus <- rnaturalearth::ne_countries(country = 'australia') |> 
  st_transform(st_crs(black_box))
```

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = black_box) + 
  ggtitle('Black Box')
```

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = red_gum) + 
  ggtitle('Red Gum')
```

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = coolabah) + 
  ggtitle('Coolabah')
```

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = lignum) + 
  ggtitle('Lignum')
```

## Geointersections

My notes say these take about 10 minutes each for lippia and centipeda, which have roughly the same order of magnitude as here. But I wonder if they'll be faster if I crop to the basin first? They only take 13 seconds though, so maybe it's moot.

```{r}
red_gum_mdb <- st_join(red_gum, basin, left = FALSE)
black_box_mdb <- st_join(black_box, basin, left = FALSE)
coolabah_mdb <- st_join(coolabah, basin, left = FALSE)
lignum_mdb <- st_join(lignum, basin, left = FALSE)
```

I could obviously do this as a single run, just \|\> the basin to the anaes, but this lets me check intermediately.

### To ANAEs

```{r}
system.time(
red_gum_anae <- st_join(red_gum_mdb, all_anaes, left = FALSE)
)
system.time(
black_box_anae <- st_join(black_box_mdb, all_anaes, left = FALSE)
)
system.time(
coolabah_anae <- st_join(coolabah_mdb, all_anaes, left = FALSE)
)
system.time(
lignum_anae <- st_join(lignum_mdb, all_anaes, left = FALSE)
)
```

### To catchment

We also want to limit those not just to ANAE type, but to catchments where there are records.

This is straight to catchment- records don't have to be in an ANAE

```{r}
system.time(
red_gum_catchment <- st_join(red_gum_mdb, ltimNoNorth, left = FALSE)
)
system.time(
black_box_catchment <- st_join(black_box_mdb, ltimNoNorth, left = FALSE)
)
system.time(
coolabah_catchment <- st_join(coolabah_mdb, ltimNoNorth, left = FALSE)
)
system.time(
lignum_catchment <- st_join(lignum_mdb, ltimNoNorth, left = FALSE)
)
```

And this says they have to be in an anae wetland to count.

```{r}

# don't assume the ValleyNames in the ANAE are exactly the same (though they should be)
system.time(
red_gum_anae_catchment <- st_join(red_gum_anae |> 
                                    select(scientificName),
                                  ltimNoNorth, left = FALSE)
)
system.time(
black_box_anae_catchment <- st_join(black_box_anae |> 
                                    select(scientificName),
                                  ltimNoNorth, left = FALSE)
)
system.time(
coolabah_anae_catchment <- st_join(coolabah_anae |> 
                                    select(scientificName),
                                  ltimNoNorth, left = FALSE)
)
system.time(
lignum_anae_catchment <- st_join(lignum_anae |> 
                                    select(scientificName),
                                  ltimNoNorth, left = FALSE)
)
```

Gut check maps anae

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = red_gum_anae) + 
  ggtitle('red_gum')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = black_box_anae) + 
  ggtitle('Black box')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = coolabah_anae) + 
  ggtitle('Coolabah')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = basin) +
  geom_sf(data = lignum_anae) + 
  ggtitle('Lignum')
```

catchment

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = red_gum_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('red_gum')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = black_box_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('Black box')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = coolabah_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('Coolabah')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = lignum_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('Lignum')
```

ANAE and then catchment

```{r}
ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = red_gum_anae_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('red_gum')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = black_box_anae_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('Black box')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = coolabah_anae_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('Coolabah')

ggplot() + 
  geom_sf(data = base_aus) +
  geom_sf(data = ltimNoNorth) +
  geom_sf(data = lignum_anae_catchment, mapping = aes(color = ValleyName)) + 
  theme(legend.position = 'none') +
  ggtitle('Lignum')
```

## Extract unique ANAE types

```{r}
red_gum_type <- red_gum_anae |> 
  st_drop_geometry() |> 
  # drop subspecies
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ANAE_CODE, ANAE_DESC))

black_box_type <- black_box_anae |> 
  st_drop_geometry() |> 
  # no subspecies here anyway
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ANAE_CODE, ANAE_DESC))

coolabah_type <- coolabah_anae |> 
   st_drop_geometry() |> 
  # Some are Eucalyptus microtheca, just change to make standard
  mutate(species = "Eucalyptus coolabah") |> 
  summarise(n_records = n(),
            .by = c(species, ANAE_CODE, ANAE_DESC))

lignum_type <- lignum_anae |> 
  st_drop_geometry() |> 
  # no subspecies here anyway
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ANAE_CODE, ANAE_DESC))
```

Save that. I think it'd be entirely reasonable to cut off the rare occurrences (\<10, \<0.5%, etc), but that should be an analysis/use decision.

```{r}
#| eval: false
if (!dir.exists(vegdir)) {dir.create(vegdir, recursive = TRUE)}
saveRDS(red_gum_type, file = file.path(vegdir, 'red_gum_anae_type.rds'))
saveRDS(black_box_type, file = file.path(vegdir, 'black_box_anae_type.rds'))
saveRDS(coolabah_type, file = file.path(vegdir, 'coolabah_anae_type.rds'))
saveRDS(lignum_type, file = file.path(vegdir, 'lignum_anae_type.rds'))

```

## Extract catchments

Straight to catchments

```{r}
red_gum_catch <- red_gum_catchment |> 
  st_drop_geometry() |> 
  # drop subspecies
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))

black_box_catch <- black_box_catchment |> 
  st_drop_geometry() |> 
  # no subspecies here anyway
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))

coolabah_catch <- coolabah_catchment |> 
   st_drop_geometry() |> 
  # Some are Eucalyptus microtheca, just change to make standard
  mutate(species = "Eucalyptus coolabah") |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))

lignum_catch <- lignum_catchment |> 
  st_drop_geometry() |> 
  # no subspecies here anyway
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))
```

anae and then catchments

```{r}
red_gum_anae_catch <- red_gum_anae_catchment |> 
  st_drop_geometry() |> 
  # drop subspecies
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))

black_box_anae_catch <- black_box_anae_catchment |> 
  st_drop_geometry() |> 
  # no subspecies here anyway
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))

coolabah_anae_catch <- coolabah_anae_catchment |> 
   st_drop_geometry() |> 
  # Some are Eucalyptus microtheca, just change to make standard
  mutate(species = "Eucalyptus coolabah") |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))

lignum_anae_catch <- lignum_anae_catchment |> 
  st_drop_geometry() |> 
  # no subspecies here anyway
  mutate(species = stringr::str_remove_all(scientificName, ' subsp.*')) |> 
  summarise(n_records = n(),
            .by = c(species, ValleyName))
```

Join those together, allow analysis-time decisions

```{r}

red_gum_catch <- red_gum_catch |> 
  left_join(red_gum_anae_catch |> rename(in_anae = n_records))

black_box_catch <- black_box_catch |> 
  left_join(black_box_anae_catch |> rename(in_anae = n_records))

coolabah_catch <- coolabah_catch |> 
  left_join(coolabah_anae_catch |> rename(in_anae = n_records))

lignum_catch <- lignum_catch |> 
  left_join(lignum_anae_catch |> rename(in_anae = n_records))
```

Save

```{r}
#| eval: false
if (!dir.exists(vegdir)) {dir.create(vegdir, recursive = TRUE)}
saveRDS(red_gum_catch, file = file.path(vegdir, 'red_gum_catchment.rds'))
saveRDS(black_box_catch, file = file.path(vegdir, 'black_box_catchment.rds'))
saveRDS(coolabah_catch, file = file.path(vegdir, 'coolabah_catchment.rds'))
saveRDS(lignum_catch, file = file.path(vegdir, 'lignum_catchment.rds'))
```

## Raw records

Save out the records themselves too, I keep wanting them

```{r}
#| eval: false
saveRDS(red_gum_mdb, file = file.path(vegdir, 'red_gum_mdb_records.rds'))
saveRDS(black_box_mdb, file = file.path(vegdir, 'black_box_mdb_records.rds'))
saveRDS(coolabah_mdb, file = file.path(vegdir, 'coolabah_mdb_records.rds'))
saveRDS(lignum_mdb, file = file.path(vegdir, 'lignum_mdb_records.rds'))

saveRDS(red_gum_anae, file = file.path(vegdir, 'red_gum_anae_records.rds'))
saveRDS(black_box_anae, file = file.path(vegdir, 'black_box_anae_records.rds'))
saveRDS(coolabah_anae, file = file.path(vegdir, 'coolabah_anae_records.rds'))
saveRDS(lignum_anae, file = file.path(vegdir, 'lignum_anae_records.rds'))
```
