---
title: "Veg soil moisture"
format: html
editor: visual
---

## Calculating soil moisture data for veg

First, set directories and set up for parallel

```{r}
source('directorySet.R')
library(CC2)
```

```{r}
library(sf)
library(foreach)
library(doFuture)
library(progressr)
# make the handlers call in the console.
# handlers(global = TRUE)
# Not supposed to need this, but it seems to help
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per node, I think.

```{r}
if (parset == 'local') {
  plan(multisession)
}

# These take a REALLY long time
if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 1200,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'daily1030')),
          multicore))
}
```

## Set functions

We need to do a few things here. And so may want to break this notebook up.

Unlike the other veg1\_ notebooks, this one is not going to roll the raster, but instead get the daily area in the moisture band and then we'll roll the polygons later. That's a bit cruder than the rolling calculations, but should yield a massive speedup, and is less crude than operating on mean soil moisture in the polygons.

The stricture is a moisture band from 10-30%

```{r}
areamoist_10_30 <- function(x) {
  sum(ifelse(x >= 0.1 & x <= 0.3, area, 0), na.rm = TRUE)
}
```

## Run and check

This is shared between red gum and black box, and is needed for germ and seedlings

```{r}
# 10 days > 10%
with_progress({
  out1030 <- process_with_checks(dataname = 'soilmoisture',
                          data_dir = file.path(datDir,
                                               'soil_moisture_22_23'),
                          poly_path = file.path(datOut, 'ANAEcatchment'),
                          process_function = 'areamoist_10_30',
                          catchment = 'all',
                          out_dir = datOut,
                          poly_per_chunk = 12,
                          extraname = 'yr2223')
})
```

```{r}
out1030$timings
out1030$failures
```

This gets done in the above, but it's handy to paste in to a terminal

```{r}
#| eval: false
source('directorySet.R')
library(CC2)
ct <- chunks_to_process(dataname = 'soilmoisture',
                        summaryFun = 'areamoist_10_30',
                          catchment = 'all',
                          out_dir = datOut,
                          poly_per_chunk = 12,
                        extraname = 'yr2223')
```

## Date smash

The first round through left off 2022. I've now run 2022-23 and need to glue it on. Ideally, this would have all happened in one go, but we're on a time crunch to fully re-do the processing.

And hopefully this will get us a long way towards time-parallelising

```{r}
catchment <- 'Avoca'
out_dir <- datOut

# The big ones without 2022
soilmoist_polys <- readRDS(file.path(out_dir, 'soilmoisture',
                                       'areamoist_10_30', 'no_roll',
                                       paste0(catchment, '_areamoist_10_30', '.rds'))) |>
    setNames(c('aggdata', 'indices'))

soilmoist_2223 <- readRDS(file.path(out_dir, 'soilmoisture',
                                       'areamoist_10_30', 'yr2223',
                                       paste0(catchment, '_areamoist_10_30', '.rds'))) |>
    setNames(c('aggdata', 'indices'))

# check they match
all(soilmoist_2223$indices$UID == soilmoist_polys$indices$UID)

# Get the common times
sametimes <- which(st_get_dimension_values(soilmoist_polys$aggdata, 'time') %in% st_get_dimension_values(soilmoist_2223$aggdata, 'time'))

# Using concat_star_index machinery
sm21 <- soilmoist_polys
sm21$aggdata <- soilmoist_polys$aggdata[,,-sametimes]

time_cat <- concat_star_index(list(sm21, soilmoist_2223), dimension = 'time')


# From concat_anae_chunks
extraname = NULL
summaryFun = 'areamoist_10_30'
dataname = 'soilmoisture'
thiscatch = catchment
# There are some that were NOT chunked- leave them alone, and just look in the chunked folder
  if (!is.null(extraname)) {
    sumextra <- paste0(summaryFun, '/', extraname)
  } else {
    sumextra <- summaryFun
  }
    fundir <- file.path(out_dir, dataname, sumextra)
    
saveRDS(time_cat, 
        file = file.path(fundir, paste0(thiscatch, '_', summaryFun, '.rds')))


```

Can I just use concat_anae_chunks with geometry changed to time? If I'm careful? I think otherwise it'll jumble them. Probably safest to do that explicitly with a time-parallel function tbd. Especially since this has the issue that we didnt time-parallel at the outset so need to clip the input times.

Turn the above into an ad-hoc function just for this, but use the same infrastructure as concat_chunks for future inclusion

```{r}
concat_time_chunks <- function(out_dir,
                          dataname,
                          summaryFun,
                          catchment = 'all',
                          poly_path = file.path(out_dir, 'ANAEprocessed'),
                          extraname = NULL,
                          rebuild = FALSE,
                          filetype = '.rds') {
  # loop over summary functions- deprecated, this was never used in practice, and could be done outside the code
  # for (su in 1:length(summaryFuns)) {
  #   summaryFun <- summaryFuns[su]

    # There are some that were NOT chunked- leave them alone, and just look in the chunked folder
  if (!is.null(extraname)) {
    sumextra <- paste0(summaryFun, '/', extraname)
  } else {
    sumextra <- summaryFun
  }
    fundir <- file.path(out_dir, dataname, sumextra)
    chunkdir <- file.path(fundir, 'chunked')

    if ('all' %in% catchment) {
      # get the names of the catchments
      catchment <- c("Avoca", "BarwonDarling", "BorderRivers", "Broken", "Campaspe",
                     "Castlereagh", "CentralMurray", "CondamineBalonne",
                     "EdwardWakool", "Goulburn", "Gwydir", "Kiewa", "Lachlan",
                     "Loddon", "LowerDarling", "LowerMurray", "Macquarie", "MittaMitta",
                     "Murrumbidgee", "Namoi", "Ovens", "Paroo", "UpperMurray", "Warrego", "Wimmera")
    }

    # # Usually only rebuild new data
    # # This looks in the concatenated folder and finds the catchments already there and removes them from the list to do.
    # if (!rebuild) {
    #   filespresent <- list.files(fundir)
    #   catchespresent <- stringr::str_remove(filespresent, '_[A-z].*')
    #   catchment <- catchment[!(catchment %in% catchespresent)]
    # }
    # 
    # if (length(catchment) == 0) {
    #   rlang::inform("No catchments to combine, likely because `rebuild = FALSE` and they're all done")
    #   return()
    # }

    # set up progress bar
    p <- progressor(steps = length(catchment))

    # Loop over catchments that were chunked. I do not understand why, but if
    # this is %dofuture%, concat_star_index can't use c.stars or bind_rows on an
    # sf. I've tried passing in packages in options.future and nothing is working.
      allcatch <- foreach(cn = 1:length(catchment),
                          .options.future = list(seed = TRUE)) %dofuture% {
        # Get a single catchment
        thiscatch <- catchment[cn]

        # This is the new ad-hoc bit
        # The big ones without 2022
soilmoist_polys <- readRDS(file.path(out_dir, dataname,
                                       summaryFun, 'no_roll',
                                       paste0(thiscatch, '_', summaryFun, '.rds'))) |>
    setNames(c('aggdata', 'indices'))

soilmoist_2223 <- readRDS(file.path(out_dir, dataname,
                                       summaryFun, 'yr2223',
                                       paste0(thiscatch, '_', summaryFun, '.rds'))) |>
    setNames(c('aggdata', 'indices'))

# check they match
all(soilmoist_2223$indices$UID == soilmoist_polys$indices$UID)

# Get the common times
sametimes <- which(st_get_dimension_values(soilmoist_polys$aggdata, 'time') %in% st_get_dimension_values(soilmoist_2223$aggdata, 'time'))

# Cut to the right set of times- this is particularly specific
sm21 <- soilmoist_polys
sm21$aggdata <- soilmoist_polys$aggdata[,,-sametimes]

# Use concat_star_index, just on time
time_cat <- concat_star_index(list(sm21, soilmoist_2223), dimension = 'time')


      # Could just use thisInunName for the rdata, since there's a folder structure, but this is more explicit
      saveRDS(time_cat, 
        file = file.path(fundir, paste0(thiscatch, '_', summaryFun, '.rds')))

      # just kick the catchment name to the foreach output
      p(glue::glue("catchment {thiscatch} concatenated"))
      thiscatch
    }
  # }

      return(invisible())
}
```

```{r}
tc <- concat_time_chunks(out_dir = datOut,
                         summaryFun = 'areamoist_10_30',
                         dataname = 'soilmoisture',
                         catchment = 'all',
                         extraname = NULL)
```
