---
title: "Veg soil moisture"
format: html
editor: visual
---

## Calculating soil moisture data for veg

First, set directories and set up for parallel

```{r}
source('directorySet.R')
library(eFlowEval)
```

```{r}
library(sf)
library(foreach)
library(doFuture)
library(progressr)
# make the handlers call in the console.
# handlers(global = TRUE)
# Not supposed to need this, but it seems to help
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per node, I think.

```{r}
if (parset == 'local') {
  plan(multisession)
}

# There's a couple in the condamine that time out at 60. Nearly everything else finishes in 10-30.
if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 600,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'min_10d')),
          multicore))
}
```

## Set functions

We need to do a few things here. And so may want to break this notebook up.

### Soil moisture for germ

Both black box and red gum need soil moisture between 10 and 30% for 10 days for germination. Lets do that by rolling the raster and then getting the area that meets that condition. That means we need to set up a rolling arglist. I can't actually do conditionals if I rely on RcppRoll, so will do this from both ends- get the minimum and the maximum over the 10-day span. These will then be checked in the strictures.

Seedlings require 1 (red gum) or 2 (black box) years above 10% for survival and establishment.

These rolling functions will return the min or max over the previous x days at each day, and so give whether success had been possible up to that day.

```{r}
# The 10-day min and max for germ
min10day <- list(attribute_number = 1, 
                  tDim = 3, 
                  FUN = RcppRoll::roll_min,
                  rolln = 10,
                  align = 'right',
                  na.rm = TRUE)

max10day <- list(attribute_number = 1, 
                  tDim = 3, 
                  FUN = RcppRoll::roll_max,
                  rolln = 10,
                  align = 'right',
                  na.rm = TRUE)

# the one and two-year mins for seedlings
min1yr <- list(attribute_number = 1, 
                  tDim = 3, 
                  FUN = RcppRoll::roll_min,
                  rolln = 365,
                  align = 'right',
                  na.rm = TRUE)

min2yr <- list(attribute_number = 1, 
                  tDim = 3, 
                  FUN = RcppRoll::roll_min,
                  rolln = 730,
                  align = 'right',
                  na.rm = TRUE)
```

And the stricture functions. These will return the area for which the rolling conditions are met. The first can be used for any of the timespans of 10% mins above.

```{r}
areamoistgreater10 <- function(x) {
  sum(ifelse(x > 0.1, area, 0), na.rm = TRUE)
}
```

```{r}
areamoistless30 <- function(x) {
  sum(ifelse(x <= 0.30, area, 0), na.rm = TRUE)
}
```

## Run and check

### Germination

This is shared between red gum and black box

10-day minimum 10%

```{r}
# 10 days > 10%
with_progress({
  min10dayout <- process_with_checks(dataname = 'soilmoisture',
                          data_dir = file.path(datDir,
                                               'soil_moisture_more'),
                          poly_path = file.path(datOut, 'ANAEcatchment'),
                          summaryFun = 'areamoistgreater10',
                          catchment = 'all',
                          out_dir = datOut,
                          nchunks = 100,
                          rastRollArgs = min10day,
                          extraname = 'min10day')
})
```

```{r}
min10dayout$timings
min10dayout$failures
```
