---
title: "Black box analyses"
format: html
editor: visual
---

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
source('directorySet.R')
library(CC2)
library(ggplot2)
library(foreach)
library(patchwork)
```

Borrowing a lot from diversity analyses for the boilerplate

```{r}
# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')
preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')

# Need a clean name to bring in data
catchments <- ltimNoNorth |> 
  mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

cleancatch <- catchments$name_clean
```

Bring in data. I really wanted a read and concat function for this in diversity, write it here. It doesn't save a lot of typing, but will be cleaner. I've made it here with specific defaults, but I think it likely generalises to all strictures that return sf as I'm currently doing, which is why I included the other arguments.

```{r}
catch_cat_sf <- function(which_strict, catchments = cleancatch, outerdir = 'black_box') {
  foreach(i = catchments,
          .combine = dplyr::bind_rows,
          .multicombine = TRUE) %do% {
            thiscatch <- readRDS(file.path(datOut, outerdir, which_strict, 
                                           paste0(i, '_', which_strict, '.rds')))
          }
}
```

## Step through strictures

Will need to clean figures up, obviously.

Adults are not connected to the rest of the life stages because the persistence time is too long- regeneration during the period considered is not likely to be the dominant driver of adult numbers.

### Germination

The first step in the life cycle is germination. It requires

```{r}
germ <- catch_cat_sf('germ_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germ')
```

```{r}
ggplot(germ, aes(x = date, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

Is log scale better? not necessarily

```{r}
ggplot(germ, aes(x = date, y = (area+1), color = ValleyName)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
ggplot(germ, aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

**WHY DO WE GET A HUGE GERM SPIKE AT THE END- IS THAT REAL**? It sometimes goes higher than inundation\_?

How about basin-scale? we can just sum up the catchments here, since they're area passing.

```{r}
germ_basin <- germ |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()
  
```

```{r}
ggplot(germ_basin, aes(x = date, y = area)) +
  geom_line() +
  geom_point()
```

```{r}
ggplot(germ_basin, aes(fill = area)) +
  geom_sf() +
  facet_wrap('date')
```

### Seedling survival

The second step in the life cycle is survival of seedlings post-germination. When considered on its own (i.e. were conditions right for seedling survival), we get the following.

```{r}
seed <- catch_cat_sf('seed_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seed')
```

```{r}
ggplot(seed, aes(x = date, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
ggplot(seed, aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

```{r}
seed_basin <- seed |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

ggplot(seed_basin, aes(x = date, y = area)) +
  geom_line() +
  geom_point()
```

And these are actually much more permissive seedling strictures than typical. 6 mo instead of 2 years.

### Germination and seedlings

The life cycle is sequential, and so what we are interested in ultimately is regeneration success; that is, germination and subsequent survival. Here, we as whether conditions supported seedling survival *after successful germination conditions*. Thus, this is not simply the minimum of the upper two, it actually takes sequencing into account, and we lose some areas of successful seedling conditions because they were not preceded by germination.

```{r}
germ_and_seed <- catch_cat_sf('germ_and_seed_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germ_and_seed')
```

```{r}
ggplot(germ_and_seed, aes(x = date, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
ggplot(germ_and_seed, aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

```{r}
germ_and_seed_basin <- germ_and_seed |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

ggplot(germ_and_seed_basin, aes(x = date, y = area)) +
  geom_line() +
  geom_point()
```

### Adult condition

Here, we assess area of favourable adult condition, primarily as a consequence of inundation duration and periods between events. This is not connected to the regeneration due to the length of available data and tree life spans.

```{r}
adult <- catch_cat_sf('adult_catch') |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19950101)) |> 
  mutate(stage = 'adult')
```

```{r}
ggplot(adult, aes(x = date, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
ggplot(adult, aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

```{r}
adult_basin <- adult |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

ggplot(adult_basin, aes(x = date, y = area)) +
  geom_line() +
  geom_point()
```

So, ignoring habitat information, we can see that seedling survival is the limiting factor. We haven't connected adults with the earlier stages, so we sort of have two measures of condition- regeneration and persistence, where regeneration is germ and subsequent seedling survival. Note also that the germ and seedling survival is smaller than just seedling survival, because there has to have been germination first.

### Comparison

We can compare these areas of favourability for each life stage

```{r}
all_stages <- bind_rows(germ, seed, germ_and_seed, adult)
```

The adults swamp the others.

```{r}
ggplot(all_stages, aes(x = date, y = area, color = stage)) +
  geom_line() + 
  facet_wrap('ValleyName')
```

Ignoring adults is still not very informative. Just draw attention to the scales above.

```{r}
ggplot(all_stages |> filter(stage != 'adult'), 
       aes(x = date, y = area, color = stage)) +
  geom_line() + 
  facet_wrap('ValleyName')
```

at the basin scale

```{r}
all_stages_basin <- bind_rows(germ_basin, seed_basin, germ_and_seed_basin, adult_basin)

ggplot(all_stages_basin, aes(x = date, y = area, color = stage)) +
  geom_line() +
  geom_point()
```

## Habitat

```{r}
# all_anaes <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))
bbala <- readRDS(file.path(datOut, 'vegmapping', 'black_box_anae_type.rds'))

# we could pull the names out of all_anaes, but they're all in the ala set, and that's much faster
bbnames <- bbala |> 
  sf::st_drop_geometry() |> 
  filter(grepl('black|box', ANAE_DESC)) |> 
  select(ANAE_DESC) |> 
  distinct()
```

We can also include habitat information, and do so in two ways: First, some of the ANAE types are explicitly 'Black box', `r pull(bbnames)`. There are also ALA records of black box that we have intersected with the ANAE to get a list of ANAE types with records. In the analysis, only those types with \> 0.5% of the total records were used. *should indicate here which were cut off*.

```{r}
bbala |> select(ANAE_DESC, n_records) |> arrange(desc(n_records)) |> knitr::kable()
```

See veg1_anae_mapping.qmd for a map of the ALA records if we want to include that.

### Only habitat

The above asks about whether conditions favour the biology of the plants. At the simplest, the habitat ignores the biology, and asks if there was inundation in the "correct" habitat type. We also have just straight up inundation area, but that seems like it would go in an appendix, if anywhere.

```{r}
inun_anae_name <- catch_cat_sf('inun_anae_name_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'inun_anae_name')
```

```{r}
ggplot(inun_anae_name, aes(x = date, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
ggplot(inun_anae_name, aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

```{r}
inun_anae_ala <- catch_cat_sf('inun_anae_ala_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'inun_anae_ala')
```

```{r}
ggplot(inun_anae_ala, aes(x = date, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
ggplot(inun_anae_ala, aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

These are a bit different to just the strictures above- what would we get if we just look at inundation in 'black box' anae types? What about ANAE types where there are ALA records? How does that compare to what we get above? Though the habitat and biological strictures aren't orthogonal, we can compare hwo they differin terms of what they tell us when considered separately. In other words, what is the effect of actually having strictures?

There are a couple very interesting comparisons to do here- what area do we get from the germ, adult, and these habitat requirements? Could put germ_and_seed in there, but we know it's basically 0.

```{r}
gahab <- bind_rows(germ, germ_and_seed, adult, inun_anae_name, inun_anae_ala)
```

Need to work on scales, but putting on log helps. Basically, adult is highest, ala is MUCH larger than name, and germ tends to be on the same order as name, though there's quite a lot of (particularly spatial) variation around that statement- some catchments have a lot more germ than 'Black Box' ANAE types, and others have a lot less.

```{r}
ggplot(gahab, aes(x = date, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName')
```

Then, we ask what happens if we have both- ie there are biological strictures, but also requirements for habitat?

Can make maps for all of this too, but not sure how useful they'll be.

### Germination and habitat

Do I want to include the inundated area as above? It's largely covered above, and the main question here is how the habitat further restricts the biology. But it does give another (two) baseline(s), where we can ask how the biology restricts the habitat. I guess include, and maybe drop later.

```{r}
germ_anae_name <- catch_cat_sf('germ_anae_name_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germ_anae_name')

germ_anae_ala <- catch_cat_sf('germ_anae_ala_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germ_anae_ala')

# Set up the comparison
germ_hab <- bind_rows(germ, germ_anae_name, germ_anae_ala, 
                      inun_anae_name, inun_anae_ala)
```

Inun_ala is almost always highest, so we're not losing much if any germ habitat to the ala restriction. But see avoca, it does happen- the red is higher than the beige. We lose a LOT to the habitat name.

```{r}
ggplot(germ_hab, aes(x = date, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName')
```

I should be able to summarise these, both yearly and over the whole period. How much area do we lose from germ to germ_anae_ala and anae_name? How much do we lose from the inuns to the germ_anaes?

Do I want relative or the actual area?

```{r}
germ_compare_r <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germ', 'germ_anae_ala', 'germ_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germ',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')

germ_compare_d <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germ', 'germ_anae_ala', 'germ_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germ',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'difference')
```

What fraction of the area of the process-based strictures is lost with the habitat strictures? Well, this shows the proportion that remains.

```{r}
ggplot(germ_compare_r, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

```{r}
ggplot(germ_compare_d, aes(x = date, y = difference_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

And, flipping that around to the inuns as baseline, what proportion of the inundated habitat is lost when we consider the biological processes?

```{r}
germ_inun_name_compare <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('inun_anae_name', 'germ_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'inun_anae_name',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')
germ_inun_ala_compare <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('inun_anae_ala', 'germ_anae_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'inun_anae_ala',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')
```

Kind of annoying this is two plots, but they are different comparisons

**How does germ_anae_ala get higher than inun_anae_ala and anae_name at the end**??? Seems like a data problem- limiting to anae_name or anae_ala should put a cap on at those levels.

```{r}
ggplot(germ_inun_name_compare, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

```{r}
ggplot(germ_inun_ala_compare, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

### Germ and seedling

I could look at just seedling too, but this is already a TON

```{r}
germ_and_seed_anae_name <- catch_cat_sf('germ_and_seed_anae_name_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germ_and_seed_anae_name')

germ_and_seed_anae_ala <- catch_cat_sf('germ_and_seed_anae_ala_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germ_and_seed_anae_ala')

# Set up the comparison
germ_and_seed_hab <- bind_rows(germ_and_seed, germ_and_seed_anae_name, germ_and_seed_anae_ala, 
                      inun_anae_name, inun_anae_ala)
```

Inun_ala is almost always highest, so we're not losing much if any germ_and_seed habitat to the ala restriction. But see avoca, it does happen- the red is higher than the beige. We lose a LOT to the habitat name.

```{r}
ggplot(germ_and_seed_hab, aes(x = date, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName')
```

I should be able to summarise these, both yearly and over the whole period. How much area do we lose from germ_and_seed to germ_and_seed_anae_ala and anae_name? How much do we lose from the inuns to the germ_and_seed_anaes?

Do I want relative or the actual area?

```{r}
germ_and_seed_compare_r <- germ_and_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germ_and_seed', 'germ_and_seed_anae_ala', 'germ_and_seed_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germ_and_seed',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')

germ_and_seed_compare_d <- germ_and_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germ_and_seed', 'germ_and_seed_anae_ala', 'germ_and_seed_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germ_and_seed',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'difference')
```

What fraction of the area of the process-based strictures is lost with the habitat strictures? Well, this shows the proportion that remains.

```{r}
ggplot(germ_and_seed_compare_r, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

```{r}
ggplot(germ_and_seed_compare_d, aes(x = date, y = difference_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

And, flipping that around to the inuns as baseline, what proportion of the inundated habitat is lost when we consider the biological processes?

```{r}
germ_and_seed_inun_name_compare <- germ_and_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('inun_anae_name', 'germ_and_seed_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'inun_anae_name',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')
germ_and_seed_inun_ala_compare <- germ_and_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('inun_anae_ala', 'germ_and_seed_anae_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'inun_anae_ala',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')
```

Kind of annoying this is two plots, but they are different comparisons

**How does germ_and_seed_anae_ala get higher than inun_anae_ala and anae_name at the end**??? Seems like a data problem- limiting to anae_name or anae_ala should put a cap on at those levels.

```{r}
ggplot(germ_and_seed_inun_name_compare, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

```{r}
ggplot(germ_and_seed_inun_ala_compare, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

### Adults

```{r}
adult_anae_name <- catch_cat_sf('adult_anae_name_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_anae_name')

adult_anae_ala <- catch_cat_sf('adult_anae_ala_catch') |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_anae_ala')

# Set up the comparison
adult_hab <- bind_rows(adult, adult_anae_name, adult_anae_ala, 
                      inun_anae_name, inun_anae_ala)
```

Inun_ala is almost always highest, so we're not losing much if any adult habitat to the ala restriction. But see avoca, it does happen- the red is higher than the beige. We lose a LOT to the habitat name.

```{r}
ggplot(adult_hab, aes(x = date, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName')
```

I should be able to summarise these, both yearly and over the whole period. How much area do we lose from adult to adult_anae_ala and anae_name? How much do we lose from the inuns to the adult_anaes?

Do I want relative or the actual area?

```{r}
adult_compare_r <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('adult', 'adult_anae_ala', 'adult_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'adult',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')

adult_compare_d <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('adult', 'adult_anae_ala', 'adult_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'adult',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'difference')
```

What fraction of the area of the process-based strictures is lost with the habitat strictures? Well, this shows the proportion that remains.

```{r}
ggplot(adult_compare_r, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

```{r}
ggplot(adult_compare_d, aes(x = date, y = difference_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

And, flipping that around to the inuns as baseline, what proportion of the inundated habitat is lost when we consider the biological processes?

```{r}
adult_inun_name_compare <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('inun_anae_name', 'adult_anae_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'inun_anae_name',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')
adult_inun_ala_compare <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('inun_anae_ala', 'adult_anae_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'inun_anae_ala',
                                 group_cols = c('date', 'ValleyName'),
                                 values_col = 'area', comp_fun = 'relative')
```

Kind of annoying this is two plots, but they are different comparisons

**How does adult_anae_ala get higher than inun_anae_ala and anae_name at the end**??? Seems like a data problem- limiting to anae_name or anae_ala should put a cap on at those levels.

```{r}
ggplot(adult_inun_name_compare, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

```{r}
ggplot(adult_inun_ala_compare, aes(x = date, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  facet_wrap('ValleyName')
```

## Discussion

Biological processes are important- they're what determine where species actually can persist.

In some cases, habitat, particularly around key species, can be a useful shorthand. And put bounds on reasonable places to assess the biological processes, picking up covariates we might have missed, especially in something simple like strictures.

But relying solely on habitat is particularly dangerous- it does not capture whether conditions were actually favourable, particularly for sequential life cycles. And misses things like a major limitation of seedling survival.

Moreover, with climate change, 'habitat type' as defined statically, will not stay the same, and we run the risk of missing and mis-modeling shifts.

Here, we see areas of congruence and areas of major discrepancy between process-based strictures and habitat-based locations, though they can inform each other. This leads to hypothesis generation (where might 'black box' wetlands shift in the future, where should we loook for black box), and identifies critical periods for condition, whether or not they occur in the proper wetland type (seedling survival) that can be targeted by management.
