---
title: "Red gum analyses"
editor: visual
echo: false
# setting fig-width: 7 and fig-height: 5 are the defaults, changing here to be more standard ms sizes
format:
  html:
    embed-resources: true
    toc: true
    fig-width: 9
    fig-height: 6
    comments:
      hypothesis: true
  docx:
    toc: true
    toc-depth: 2
    prefer-html: true
    fig-width: 9
    fig-height: 6
    reference-doc: ../default_word_template.docx
bibliography: references.bib
---

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
#| include: false
library(CC2)
library(sf)
source('directorySet.R')
source('R/catch_cat_sf.R')
library(dplyr)
library(ggplot2)
library(foreach) # needed internally for some funs
library(patchwork)
library(kableExtra)
```

```{r}

figpath <- file.path(datOut, 'habprocesspaper', 'Figures')
tspath <- file.path(datOut, 'habprocesspaper', 'Figures', 'timeseries')
barpath <- file.path(datOut, 'habprocesspaper', 'Figures', 'bar')
mappath <- file.path(datOut, 'habprocesspaper', 'Figures', 'map')

if (!dir.exists(figpath)) {
  dir.create(figpath)
}

if (!dir.exists(tspath)) {
  dir.create(tspath)
}

if (!dir.exists(barpath)) {
  dir.create(barpath)
}

if (!dir.exists(mappath)) {
  dir.create(mappath)
}
```

## Data read-in

I'm leading with this because we're tweaking the data, but it could all be offloaded to a script to focus on the ms. Or just collapse the section.

I'm splitting this up into a few sections since the process and anae-clipped (2 ways) gets confusing to do in one go.

### Background

First, a few useful background pieces- which species, what are the anae types and a bit of a summary, etc

```{r}
#| label: which-data
species <- c('black_box', 'red_gum', 'coolabah', 'lignum')
species_names <- species |> 
  stringr::str_replace('_', ' ') |> 
  stringr::str_to_sentence()
```

```{r}
valleys <- ltimNoNorth |> 
  select(-ValleyID, -ValleyCode) |> 
  mutate(name_orig = ValleyName,
         ValleyName = stringr::str_remove_all(ValleyName, ' '))
```

What are the anae types?

```{r}
# this dataset generated in the diversity analysis is really useful to get overall info about what got inundated and the wetland areas, but it's massive. I need it here though to get assorted areas and the full set of anae types
diversity_anae_summary <- catch_cat_sf('diversity_anae_summary', 'diversity')
```

```{r}
# all_anaes <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))
# bbala <- readRDS(file.path(datOut, 'vegmapping', 'black_box_anae_type.rds'))

alatypes <- foreach(i = species,
                    .combine = bind_rows, .multicombine = TRUE) %do% {
  readRDS(file.path(datOut, 'vegmapping', paste0(i, '_anae_type.rds'))) |> 
                        mutate(species = i)
                    }

# That's useful to have in a dataframe, but in a few places I want a list too
type_list <- vector(mode = 'list', length = length(species)) |> setNames(species)
for (s in species) {
  
  # stolen from woody_general
    veg_grep <- dplyr::case_when(s == 'black_box' ~ 'black box',
                               s == 'red_gum' ~ 'red gum',
                               s == 'coolabah' ~ 'cool',
                               s == 'lignum' ~ 'lignum')
    
    
  spalatypes <- alatypes |> 
    filter(species == s) |> 
    pull(ANAE_DESC)
  
  # Use the full set of ANAEs, not just those that show up in the alas.
  spnametypes <- diversity_anae_summary |> 
    filter(grepl(veg_grep, ANAE_DESC, ignore.case = TRUE)) |> 
    pull(ANAE_DESC) |> 
    unique()
  
  type_list[[s]] <- list(alatype = spalatypes, nametype = spnametypes)
}

# Double check we pick up all the 'name's in the alas
# for (i in species) {
#   stype <- alatypes |> 
#     filter(species == i) |> 
#     select(ANAE_DESC) |> 
#     pull() |> 
#     unique()
#   
#   print(all(tl$nametype[[i]] %in% stype))
# }
# We do, so comment that out.


# We get the area in the different types below.
```

Where are the ala records?

```{r}
# use the anae overlap records, not the mdb, since the anae match the rest.
alarecords <- foreach(i = species,
                    .combine = bind_rows, .multicombine = TRUE) %do% {
  readRDS(file.path(datOut, 'vegmapping', paste0(i, '_anae_records.rds'))) |> 
                        mutate(species = i)
                    }

alarecords <- alarecords |> 
  mutate()
```

### Process-only

These are the strictures for just biological processes.

```{r}
adult <- purrr::map(species, \(x) 
                    catch_cat_sf('adult_area', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult',
         species = x)) |> 
  bind_rows()

germ <- purrr::map(species, \(x) 
                   catch_cat_sf('germ_area', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination',
         species = x)) |> 
  bind_rows()

seed <- purrr::map(species, \(x) 
                   catch_cat_sf('seedling_area',
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling',
         species = x)) |> 
  bind_rows()

# Two step
adult_germ <- purrr::map(species, \(x) 
                            catch_cat_sf('adult_germ_area',
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_regen',
         species = x)) |> 
  bind_rows()

adult_germ_seed <- purrr::map(species, \(x) 
                            catch_cat_sf('adult_germ_seed_area',
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment',
         species = x)) |> 
  bind_rows()


```

### Habitat only

```{r}
# Keep using 'stage' as the name of the data, since it makes joining for comparison easier.

inun_anae_all <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun',
                                outerdir = paste0('habprocesspaper/', x)) |> 
                                 # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'all_wetlands',
         species = x)) |> 
  bind_rows()

inun_anae_name <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun_anae_name',
                                outerdir = paste0('habprocesspaper/', x)) |> 
                                 # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'anae_name',
         species = x)) |> 
  bind_rows()
  
inun_anae_ala <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
                                # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'anae_ala',
         species = x)) |> 
  bind_rows()

```

There are also two other sorts of baselines we might want for the habitat- the total amount of inundation in *any* wetland type, and the total amount of area in each set of habitats, ignoring inundation. I had been doing this in the appendix, but think I'll move the data extraction here, anyway.

```{r}
# One use- total area of wetland habitat regardless of inundation for each species in various ways
# First, get rid of the yearly since total area doesn't change and simplify

typearea <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  summarise(total_area = unique(total_area), .by = c(ANAE_DESC, name_clean))

# Now I want to get the total area attributable to each species' types. This seems like it should be a grouped operation, but they aren't mutually exclusive, so it's actually better to work with type_list and filter

# using the same stage names lets us use the same colors
total_wetland_area <- foreach(s = species, .combine = bind_rows, .multicombine = TRUE) %do% {
  alaarea <- typearea |> 
    # set area of non-matching types to 0, then sum over the catchment
    mutate(total_area = ifelse(ANAE_DESC %in% type_list[[s]]$alatype, total_area, 0)) |> 
    summarise(total_area = sum(total_area), .by = name_clean) |> 
    mutate(species = s, stage = 'anae_ala')
  
  namearea <- typearea |> 
    mutate(total_area = ifelse(ANAE_DESC %in% type_list[[s]]$nametype, total_area, 0)) |> 
    summarise(total_area = sum(total_area), .by = name_clean) |> 
    mutate(species = s, stage = 'anae_name')
  
  bind_rows(alaarea, namearea) |> 
    rename(ValleyName = name_clean)
}

total_wetland_area <- total_wetland_area |> 
  rename(area = total_area)


total_wetland_area_basin <- total_wetland_area |> 
  summarise(area = sum(area), .by = c(species, stage))

total_wetland_area <- total_wetland_area |> 
  left_join(valleys, by = 'ValleyName') |> 
  st_as_sf()
```

```{r}
#| eval: false
# a check of that, probably delete if passes- does that actually have all the anae wetlands?
all_anae <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))

all_anae <- all_anae |> 
  mutate(area = st_area(geometry))

all(unique(all_anae$ANAE_DESC) %in% typearea$ANAE_DESC)

# Yes, so no need for both.
```

```{r}

# First, simplify
# There's no species differences here
inun_area <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  rename(date = time) |> 
  mutate(ValleyName = name_clean) |> 
  summarise(area = sum(area_inundated, na.rm = TRUE),
            stage = 'wetland_inundation',
            .by = c(date, ValleyName)) |>
    left_join(valleys) |> 
    st_as_sf() |> 
  select(-name_orig)

```

### Interactive

Include independent and full for the stages. Skip the adult_germ, it's not very interesting

```{r}
# ALA records

adult_ala <- purrr::map(species, \(x) catch_cat_sf('adult_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_ala',
         species = x)) |> 
  bind_rows()

germ_ala <- purrr::map(species, \(x) catch_cat_sf('germ_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination_ala',
         species = x)) |> 
  bind_rows()

seed_ala <- purrr::map(species, \(x) catch_cat_sf('seedling_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling_ala',
         species = x)) |> 
  bind_rows()

adult_germ_ala <- purrr::map(species, \(x) catch_cat_sf('adult_germ_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration_ala',
         species = x)) |> 
  bind_rows()

adult_germ_seed_ala <- purrr::map(species, \(x) catch_cat_sf('adult_germ_seed_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment_ala',
         species = x)) |> 
  bind_rows()

# Name

adult_name <- purrr::map(species, \(x) catch_cat_sf('adult_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_name',
         species = x)) |> 
  bind_rows()

germ_name <- purrr::map(species, \(x) catch_cat_sf('germ_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination_name',
         species = x)) |> 
  bind_rows()

seed_name <- purrr::map(species, \(x) catch_cat_sf('seedling_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling_name',
         species = x)) |> 
  bind_rows()

adult_germ_name <- purrr::map(species, \(x) catch_cat_sf('adult_germ_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration_name',
         species = x)) |> 
  bind_rows()

adult_germ_seed_name <- purrr::map(species, \(x) catch_cat_sf('adult_germ_seed_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment_name',
         species = x)) |> 
  bind_rows()
```

### Concatenate

```{r}
all_data <- bind_rows(adult, germ, seed, 
                         adult_germ, adult_germ_seed, 
                         adult_ala, germ_ala, seed_ala,
                      adult_germ_ala, adult_germ_seed_ala,
                         adult_name, germ_name, seed_name,
                      adult_germ_name,
                      adult_germ_seed_name,
                         inun_anae_name, inun_anae_ala,
                      inun_area)

# To make data line up, we need a numeric year sometimes
all_data <- all_data |> 
  mutate(year = lubridate::year(date))

# Sum to the basin
all_data_basin <- all_data |>
  sf::st_drop_geometry() |>
  summarise(area = sumna(area),
            .by = c(date, year, stage, species)) |>
  bind_cols(basin) |>
  st_as_sf()

# average over time
all_data_time <- all_data |>
  group_by(ValleyName, stage, species) |> 
  summarise(area = meanna(area)) |>
  ungroup()

# sum to basin and average over time
all_data_basin_time <- all_data_basin |>
  group_by(stage, species) |> 
 summarise(area = meanna(area)) |> 
  ungroup()

rm(adult, germ, seed,
   adult_germ, adult_germ_seed,
   adult_ala, germ_ala, seed_ala,
   adult_germ_ala,
   adult_germ_seed_ala,
   adult_name, germ_name, seed_name,
   adult_germ_name,
   adult_germ_seed_name,
   inun_anae_name, inun_anae_ala, inun_area)

```

Set up a standard color palette for the types. Could do the same for species if we every plot those, and should choose a standard ramp for things like maps. Could do it for catchments too, but there's a million. This is ugly, but changing it is easy.

Clean up the names

```{r}
# Set up various groupings
# the different types
anae_stages <- c('Named wetland types', 'Recorded wetland types', 'All wetlands')
process_stages <- c('Adult', 'Germination', 'Seedling',
                    'Regeneration', 'Recruitment')
combo_stages <- c('Adult and Named', 'Germination and Named',
                  'Seedling and Named', 'Regeneration and Named', 'Recruitment and Named',
                  'Adult and Recorded', 'Germination and Recorded',
                  'Seedling and Recorded', 'Regeneration and Recorded',
                  'Recruitment and Recorded')

sequential_stages <- c('Adult', 'Regeneration', 'Recruitment',
                       'Recruitment and Named', 'Recruitment and Recorded')

sequential_hab <- c('Named wetland types', 'Recorded wetland types', 'All wetlands',
                       'Recruitment and Named', 'Recruitment and Recorded')

# The different comparisons across type
hab_all <- c('All wetlands', process_stages)
hab_named <- c('Named wetland types', combo_stages[grepl('Named', combo_stages)])
hab_record <- c('Recorded wetland types', combo_stages[grepl('Recorded', combo_stages)])

proc_adult <- c('Adult', combo_stages[grepl('Adult', combo_stages)])
proc_germ <- c('Germination', combo_stages[grepl('Germination', combo_stages)])
proc_seed <- c('Seedling', combo_stages[grepl('Seed', combo_stages)])
proc_regen <- c('Regeneration', combo_stages[grepl('Regeneration', combo_stages)])
proc_recruit <- c('Recruitment', combo_stages[grepl('Recruitment', combo_stages)])

```

```{r}
clean_stages <- function(x) {
  x <- x |> 
    mutate(stage_name = case_when(
      stage == 'adult' ~ 'Adult',
      stage == 'germination' ~ 'Germination',
      stage == 'seedling' ~ 'Seedling',
      stage == 'adult_regen' ~ 'Regeneration',
      stage == 'recruitment' ~ 'Recruitment',
      stage == 'adult_ala' ~ 'Adult and Recorded',
      stage == 'germination_ala' ~ 'Germination and Recorded',
      stage == 'seedling_ala' ~ 'Seedling and Recorded',
      stage == 'regeneration_ala' ~ 'Regeneration and Recorded',
      stage == 'recruitment_ala' ~ 'Recruitment and Recorded',
      stage == 'adult_name' ~ 'Adult and Named',
      stage == 'germination_name' ~ 'Germination and Named',
      stage == 'seedling_name' ~ 'Seedling and Named',
      stage == 'regeneration_name' ~ 'Regeneration and Named',
      stage == 'recruitment_name' ~ 'Recruitment and Named',
      stage == 'anae_name' ~ 'Named wetland types',
      stage == 'anae_ala' ~ 'Recorded wetland types',
      stage == 'wetland_inundation' ~ 'All wetlands',
      .default = 'FAIL'
    ),
    stage_name = factor(stage_name,
                        levels = c('All wetlands',
                                   'Recorded wetland types',
                                   'Named wetland types',
                                   'Adult', 'Germination', 'Seedling',
                                   'Regeneration', 'Recruitment',
                                   'Adult and Recorded',
                                   'Germination and Recorded',
                                   'Seedling and Recorded',
                                   'Regeneration and Recorded',
                                   'Recruitment and Recorded',
                                   'Adult and Named',
                                   'Germination and Named',
                                   'Seedling and Named',
                                   'Regeneration and Named',
                                   'Recruitment and Named')),
    # create an independent stage flag. don't includ adults, since they're both
    is_independent_proc = case_when(
      stage %in% c('germination', 'seedling',
                                                 'germination_ala', 'seedling_ala',
                                                 'germination_name', 'seedling_name') ~
                                      'independent',
                                    stage %in% c('adult', 'adult_regen', 'recruitment',
                                                 'adult_ala', 'adult_regen_ala',
                                                 'recruitment_ala',
                                                 'adult_name', 'adult_regen_name',
                                                 'recruitment_name') ~ 'sequential',
                                    .default = NA
      ),
    is_independent_proc = factor(is_independent_proc, levels = c('sequential', 'independent'))) |> 
    mutate(hab_type = case_when(
      stage_name %in% hab_all ~ "All wetlands",
                                stage_name %in% hab_named ~ "Named wetland types",
                                stage_name %in% hab_record ~ "Recorded wetland types",
                                .default = NA
      ),
           hab_type = factor(hab_type, levels = c('All wetlands',
                                                  'Recorded wetland types',
                                                  'Named wetland types')),
           proc_type = case_when(
             stage_name %in% proc_adult ~ "Adult",
                                 stage_name %in% proc_germ ~ "Germination",
                                 stage_name %in% proc_seed ~ "Seedling",
                                 stage_name %in% proc_regen ~ "Regeneration",
                                 stage_name %in% proc_recruit ~ "Recruitment",
                                 .default = NA
             ),
           model_type = case_when(
             stage_name %in% anae_stages ~ 'Wetland type',
                                  stage_name %in% process_stages ~ "Process",
                                  stage_name %in% combo_stages ~ "Process within\nwetland type", 
                                  .default = NA),
           model_type = factor(model_type, levels = c('Wetland type', 'Process', 'Process within\nwetland type')),
           proc_type = factor(proc_type, levels = c('Adult', 'Germination', 'Seedling', 'Regeneration', 'Recruitment')))
  
}
```

Use that to clean data

```{r}
all_data <- clean_stages(all_data)
all_data_basin <- clean_stages(all_data_basin)
all_data_time <- clean_stages(all_data_time)
all_data_basin_time <- clean_stages(all_data_basin_time)

# the wetland type area regardless of inundation
total_wetland_area <- clean_stages(total_wetland_area)
```

```{r}
# just to make it easy to access
stages <- unique(all_data$stage)
stagenames <- unique(all_data$stage_name)



#  "palettetown::surskit"
# "RColorBrewer::Set3"
# This worked pretty well with 12, but is a mess with 15.
# stage_pal <- werptoolkitr::make_pal(stages, "rcartocolor::Safe")

# This is going to take some tweaking to get right.
# having hte names in separate vectors can make some filtering easier
# "beyonce::X41" "ggprism::plasma" "rcartocolor::ag_Sunset" "RColorBrewer::RdPu", direction = -1 "PNWColors::Sunset2"
anae_cols <- werptoolkitr::make_pal(anae_stages, "rcartocolor::ag_Sunset")

process_stages <- c('Adult', 'Germination', 'Seedling',
                    'Regeneration', 'Recruitment')

process_cols <- werptoolkitr::make_pal(process_stages,
                                       "calecopal::superbloom1")
# that last one is just barely too purple
process_cols[names(process_cols) == 'Recruitment'] <- '#527E87FF' # '#477173FF'

combo_cols <- werptoolkitr::make_pal(combo_stages, "rcartocolor::Safe")

stage_pal <- c(anae_cols, process_cols, combo_cols)
class(stage_pal) <- 'colors'

# probably need to change this
type_pal <- werptoolkitr::make_pal(c('Wetland type', 'Process', 'Process within\nwetland type'), "trekcolors::starfleet")


# make a consistent set of shapes that allows patchworking
shape_type <- scales::shape_pal()(3) |> 
  setNames(names(type_pal))

# make an alpha scale for that too
alpha_type <- c('Wetland type' = 1, 'Process' = 1, 'Process within\nwetland type' = 0.75)

# make an alpha scale for that too
line_type <- c('Wetland type' = 'solid', 'Process' = 'solid', 'Process within\nwetland type' = 'dashed')
```

# PLOT BUILDING

The order these are easiest to build in is not necessarily the best presentation order.

## Basin-scale bar graphs over time

### Habitat alone

```{r}
#| label: habitat-bar-function
make_habitat_bar <- function(species) {
  
  hab_basin_bar <- all_data_basin |>
  filter((species == {{species}} | 
            is.na(species)) & 
           stage_name %in% anae_stages) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
  ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
  scale_fill_manual(values = stage_pal) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)', fill = 'Model')

  
  return(hab_basin_bar)
}

# Individual per-species plots
hab_basin_bar <- purrr::map(species, make_habitat_bar) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-bar-function
make_process_bar <- function(species) {
  
  proc_basin_bar <- all_data_basin |>
    filter((species == {{species}} |
              is.na(species)) & 
             stage_name %in% process_stages) |>
    sf::st_drop_geometry() |>
    summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
              sd_area = sd(log10(area + 1), na.rm = TRUE),
              is_independent_proc = unique(is_independent_proc),
              .by = stage_name) |>
    mutate(base_stage = case_when(
      stage_name == 'Adult' ~ 'Adult',
      stage_name %in% c('Germination', 'Regeneration') ~ 'Regeneration',
      stage_name %in% c('Seedling', 'Recruitment') ~ 'Recruitment'
      ),
      base_stage = factor(base_stage, levels = levels(stage_name))) |>
    ggplot(aes(x = base_stage, y = mean_area, fill = stage_name, color = is_independent_proc)) +
    geom_col(position = position_dodge()) +
    geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                   position = position_dodge(width = 0.9)) +
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = c(sequential = 'black', independent = 'grey70')) +
    werptoolkitr::theme_werp_toolkit() +
    labs(y = 'Mean log(area + 1)', x = 'Step',
         fill = 'Life stage', color = 'Stage type')
  
  
  return(proc_basin_bar)
}

# Individual per-species plots
proc_basin_bar <- purrr::map(species, make_process_bar) |> 
  setNames(species)
```

### Interactive

Sequence through life cycle and then a habitat filter

```{r}
#| label: interact-sequential-function
make_interact_seq_bar <- function(species) {
  
 seq_proc_basin_bar <- all_data_basin |>
  filter((species == {{species}} |
            is.na(species)) & 
           stage_name %in% sequential_stages) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
  ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
  scale_fill_manual(values = stage_pal) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)',
       fill = 'Life stage')

  
  return(seq_proc_basin_bar)
}

# Individual per-species plots
interact_seq_basin_bar <- purrr::map(species, make_interact_seq_bar) |> 
  setNames(species)
```

What is the effect of process occurring within each habitat type?

```{r}
#| label: interact-sequential-hab-function
make_interact_hab_bar <- function(species) {
  
new_basin_bar_hab <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, hab_type, model_type)) |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
  ggplot(aes(x = hab_type, y = mean_area, fill = stage_name, color = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)',
       fill = 'Model', color = 'Model type')

  
  return(new_basin_bar_hab)
}

# Individual per-species plots
interact_hab_basin_bar <- purrr::map(species, make_interact_hab_bar) |> 
  setNames(species)
```

How much does habitat restrict each stage?

```{r}
#| label: interact-sequential-proc-function
make_interact_proc_bar <- function(species) {
  
new_basin_bar_proc <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           !is.na(proc_type)) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, model_type)) |>
  ggplot(aes(x = proc_type, y = mean_area, fill = stage_name, color = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)',
       fill = 'Model', color = 'Model type')

  
  return(new_basin_bar_proc)
}

# Individual per-species plots
interact_proc_basin_bar <- purrr::map(species, make_interact_proc_bar) |> 
  setNames(species)
```

### Stacked fig for paper

Make the simplified versions that accentuate what we want for the ms.

```{r}
#| label: interact-for-stacking
make_interact_hab2proc_bar <- function(species) {
  
basin_bar_hab2proc <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |>
  mutate(hab_comp = ifelse(grepl('Recruit', stage_name),
                           'Recruitment', as.character(hab_type)),
         hab_comp = factor(hab_comp, levels = levels(stage_name))) |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, hab_type, model_type, hab_comp)) |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
  ggplot(aes(x = hab_type, y = mean_area, fill = hab_comp,
             color = model_type,
             alpha = model_type,
             linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model",
       color = "Model type", linetype = "Model type",
       alpha = 'Model type')

  
  return(basin_bar_hab2proc)
}

make_interact_proc2hab_bar <- function(species) {
  
basin_bar_proc2hab <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           !is.na(proc_type) &
           !grepl('Germ|Seed', stage_name)) |>
  mutate(hab_comp = ifelse(as.character(hab_type) == 'All wetlands',
                           as.character(proc_type), as.character(hab_type)),
         hab_comp = factor(hab_comp, levels = c(levels(proc_type), "Recorded wetland types","Named wetland types"))) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, hab_comp, model_type)) |>
  ggplot(aes(x = proc_type, y = mean_area,
             fill = hab_comp,
             color = model_type,
             alpha = model_type,
             linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model",
       color = "Model type", linetype = "Model type",
       alpha = 'Model type')

  
  return(basin_bar_proc2hab)
}

# Individual per-species plots
interact_basin_bar_hab2proc <- purrr::map(species, make_interact_hab2proc_bar) |> 
  setNames(species)
interact_basin_bar_proc2hab <- purrr::map(species, make_interact_proc2hab_bar) |> 
  setNames(species)
```

Make a legend for the barplot

```{r}
#| label: make-bar-legend
bar_legend_plot <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           stage_name %in% c(sequential_stages, anae_stages) &
           !grepl('Germ|Seed', stage_name)) |>
  sf::st_drop_geometry() |> 
  mutate(stage_fake = ifelse(grepl(' and ', as.character(stage_name)), 
                             as.character(hab_type),
                             as.character(stage_name)),
         stage_fake = factor(stage_fake, levels = levels(stage_name))) |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_fake, proc_type, model_type)) |>
ggplot(aes(x = proc_type, y = mean_area, 
           fill = stage_fake, 
           color = model_type, 
           alpha = model_type,
           linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model", 
       color = "Model type", linetype = "Model type", 
       alpha = 'Model type')

barbottom <- bar_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(fill = guide_legend(nrow = 3), color = guide_legend(nrow = 3))


bar_legend <- ggpubr::get_legend(bar_legend_plot)
bar_bottom_legend <- ggpubr::get_legend(barbottom)
```

```{r}
#| label: stacked-bar

# Save these out by default
make_stacked_bars <- function(species, print = TRUE) {
  
  bar_layout_stack <- "
AAA#C
BBB#C
"
  compare_bar <- (interact_basin_bar_hab2proc[[species]] +
                  scale_x_discrete(labels = \(x)
                                   stringr::str_wrap(x, width = 100)) +
                  theme(legend.position = 'none')) +
  (interact_basin_bar_proc2hab[[species]] + scale_x_discrete(labels = \(x)
                                        stringr::str_wrap(x, width = 100)) +
     theme(legend.position = 'none'))  +
  wrap_plots(ggpubr::as_ggplot(bar_legend), plot_spacer()) +
  plot_layout(design = bar_layout_stack)


  if (print) {
    thispath <- file.path(barpath, paste0(species, '_bar'))
    galenR::ggsave_multi(filename = thispath, plot = compare_bar, 
                         device = c('png', 'svg'),
                         width = 12, height = 9, units = "cm")
  }

  return(compare_bar)

}

all_stacked_bars <- purrr::map(species, make_stacked_bars) |> 
  setNames(species)
```

## Basin-scale timeseries

### Habitat alone

```{r}
#| label: habitat-ts-function
make_habitat_timeseries <- function(species) {
  
  hab_basin_ts <- all_data_basin |> 
  filter((species %in% {{species}} | is.na(species)) & 
           stage_name %in% anae_stages) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  # Seems like a good idea, but the 'All wetlands' isn't duplicated over species.
  # if (length(species) > 1) {
  #   hab_basin_ts <- hab_basin_ts +
  #     facet_wrap('species')
  # } 
  
  return(hab_basin_ts)
}

# Individual per-species plots
hab_basin_ts <- purrr::map(species, make_habitat_timeseries) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-ts-fun-allstages

make_all_process_ts <- function(species) {
  proc_basin_ts <- all_data_basin |> 
    filter(species == {{species}} & stage_name %in% process_stages) |> 
    ggplot(aes(x = year, y = log10(area + 1), color = stage_name,
           linetype = is_independent_proc, shape = model_type)) +
    geom_line(show.legend = TRUE) +
    geom_point(show.legend = TRUE) +
    scale_shape_manual(values = shape_type) +
    scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
    werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
    labs(y = "log(area + 1)", color = "Model",
       linetype = "Stage type", shape = "Model type")
  
  return(proc_basin_ts)
}

all_proc_basin_ts <- purrr::map(species, make_all_process_ts) |> 
  setNames(species)
```

Sequential

```{r}

make_seq_process_ts <- function(species) {
  proc_basin_seq_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           # both process and sequential
           stage_name %in% process_stages &
           stage_name %in% sequential_stages) |> 
    ggplot(aes(x = year, y = log10(area + 1), 
               color = stage_name, 
               shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(proc_basin_seq_ts)
}


seq_proc_basin_ts <- purrr::map(species, make_seq_process_ts) |> 
  setNames(species)
```

### Interactive

Here, we decided the easiest is to do the relevant wetland types in separate panels

```{r}


make_named_process_interact_ts <- function(species) {
  
  inter_basin_named_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           stage_name %in% c('Named wetland types', 'Recruitment and Named', 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(inter_basin_named_ts)
  
}



make_recorded_process_interact_ts <- function(species) {
  
  inter_basin_recorded_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           stage_name %in% c('Recorded wetland types', 
                             'Recruitment and Recorded', 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1),
           color = stage_name, shape = model_type)) +
  geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
      scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  scale_y_continuous() +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(inter_basin_recorded_ts)
}

interact_named_basin_ts <- purrr::map(species, 
                                      make_named_process_interact_ts) |> 
  setNames(species)
interact_recorded_basin_ts <- purrr::map(species,
                                         make_recorded_process_interact_ts) |> 
  setNames(species)
```

Construct Venn diagrams. I guess go ahead and do it for both recorded and named

```{r}
#| label: make-venn-data

# I think I will split this into data prep and plot construction

recorded_venn_data <- function(species) {
  # First, extract and organise the data into the right format (a col with the two main things with the interaction as 'overlap')
  venncheck <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(species == {{species}} & 
             stage_name %in% c('Recorded wetland types',
                               'Recruitment and Recorded',
                               'Recruitment')) |> 
    mutate(area = log10(area + 1)) |>
    mutate(area = area/max(area, na.rm = TRUE)) |> 
    # need to do a funny flip-flop here to get overlap in its own column
    tidyr::pivot_wider(id_cols = date,
                       names_from = stage_name,
                       values_from = area) |> 
    tidyr::pivot_longer(cols = c(Recruitment, `Recorded wetland types`),
                        names_to = 'stage_name',
                        values_to = 'area') |> 
    rename(overlap = `Recruitment and Recorded`)
  
  # Now calculate the radii and centers we need to plot with geom_circle
  venncheck <- venncheck |> 
    mutate(radius = sqrt(area/pi)) |> 
    mutate(d = galenR::find_d(unique(overlap),
                              radii = radius),
           .by = date) |> 
    mutate(centers = d*c(-0.5, 0.5)) |> 
    mutate(year = lubridate::year(date))
  
  return(venncheck)
}

named_venn_data <- function(species) {
  # First, extract and organise the data into the right format (a col with the two main things with the interaction as 'overlap')
  venncheck <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(species == {{species}} & 
             stage_name %in% c('Named wetland types',
                               'Recruitment and Named',
                               'Recruitment')) |> 
    mutate(area = log10(area + 1)) |>
    mutate(area = area/max(area, na.rm = TRUE)) |> 
    # need to do a funny flip-flop here to get overlap in its own column
    tidyr::pivot_wider(id_cols = date,
                       names_from = stage_name,
                       values_from = area) |> 
    tidyr::pivot_longer(cols = c(Recruitment, `Named wetland types`),
                        names_to = 'stage_name',
                        values_to = 'area') |> 
    rename(overlap = `Recruitment and Named`)
  
  # Now calculate the radii and centers we need to plot with geom_circle
  venncheck <- venncheck |> 
    mutate(radius = sqrt(area/pi)) |> 
    mutate(d = galenR::find_d(unique(overlap),
                              radii = radius),
           .by = date) |> 
    mutate(centers = d*c(-0.5, 0.5)) |> 
    mutate(year = lubridate::year(date))
  
  return(venncheck)
}

venndata_recorded <- purrr::map(species, recorded_venn_data) |> 
  setNames(species)
venndata_named <- purrr::map(species, named_venn_data) |> 
  setNames(species)
```

Create a legend that has all the levels. We could do something with limits and breaks, but it's terrible

```{r}
#| label: make-ts-legend
ts_legend_plot <- all_data_basin |>
  filter(is.na(is_independent_proc) | is_independent_proc == 'sequential') |>
  filter(!stage_name %in% c('Adult and Recorded', 'Regeneration and Recorded',
                            'Adult and Named', 'Regeneration and Named')) |>
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point() +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")

# Some other legend orientations for testing
ts_legend_plot_bottom <- ts_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = guide_legend(nrow = 3), color = guide_legend(nrow = 3))

ts_legend_plot_bottom_notype <- ts_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = 'none', color = guide_legend(nrow = 3))

ts_legend <- ggpubr::get_legend(ts_legend_plot)
ts_legend_bottom <- ggpubr::get_legend(ts_legend_plot_bottom)
ts_legend_bottom_notype <- ggpubr::get_legend(ts_legend_plot_bottom_notype)

```

```{r}
#| label: venn-plot-funs

# this takes data, not species, as an argument
make_venn_plots <- function(venn_data) {
  vennplot <- ggplot(venn_data) + 
  ggforce::geom_circle(mapping = aes(x0 = year, y0 = centers, 
                            r = radius, 
                            fill = factor(stage_name)),
              alpha = 0.7) + 
   scale_fill_manual(values = stage_pal) +
  coord_fixed() + 
  lims(x = c(1988, NA)) +
  werptoolkitr::theme_werp_toolkit(axis.ticks.y = element_blank(),
                                   axis.text.y = element_blank(),
                                   legend.position = 'none')
  return(vennplot)
}

vennplots_recorded <- purrr::map(venndata_recorded, make_venn_plots)
vennplots_named <- purrr::map(venndata_named, make_venn_plots)
```

### Stacked fig for paper

```{r}
#| label: stacked-fig

# Save these out by default
make_stacked_fig <- function(species, print = TRUE) {
  
  topplot <- (hab_basin_ts[[species]] + theme(legend.position = 'none')) + 
    (seq_proc_basin_ts[[species]] + theme(legend.position = 'none'))

ts_plot <-  topplot /
  (interact_named_basin_ts[[species]] + 
     theme(legend.position = 'none',
           axis.text.x = element_blank())) /
     (interact_recorded_basin_ts[[species]]  + 
        theme(legend.position = 'none',
              axis.text.x = element_blank(),
              plot.margin = unit(c(5,5,0,5), 'points'))) /
  wrap_plots(vennplots_recorded[[species]] + 
               theme(plot.margin = unit(c(0,5,5,5), 'points'))) /
  wrap_plots(ggpubr::as_ggplot(ts_legend_bottom)) + #ts_legend_bottom_notype
  plot_layout(heights = c(5,5,5,1,3)) +
  plot_annotation(tag_levels = list(c('a', 'b', 'c', 'd', 'e', '')))

  if (print) {
    thispath <- file.path(tspath, paste0(species, '_timeseries'))
    galenR::ggsave_multi(filename = thispath, plot = ts_plot, 
                         device = c('png', 'svg'),
                         width = 16, height = 22, units = "cm")
  }

  return(ts_plot)

}

all_stacked_ts <- purrr::map(species, make_stacked_fig) |> 
  setNames(species)
```

## Maps

### Background- ala records

The raw records

```{r}
#| label: ala-function
make_ala_record_map <- function(species) {
  
  # just species-facet, so no need to filter
  ala_maps <- alarecords |>
    mutate(species_name = stringr::str_replace(species, '_', ' ') |>
                                 stringr::str_to_sentence()) |> 
  # filter(species == {{species}}) |>
  ggplot() +
    geom_sf(data = valleys, fill = 'azure', color = 'grey80') +
    geom_sf(alpha = 0.3) +
  facet_wrap("species_name") +
  werptoolkitr::theme_werp_toolkit()

  
  return(ala_maps)
}

# Individual per-species plots
ala_records_map <- make_ala_record_map(NULL)
```

summed by catchment (the sum by type is done in making the tables)

```{r}
#| label: ala-catch-function
make_ala_catch_map <- function() {
  
  catch_ala <- st_join(valleys, select(alarecords, species)) |>
  summarise(n_records = n(),
            .by = c(geometry, species, ValleyName)) |> 
  filter(!is.na(species))

# That drops the non-matches, which is super annoying
allpairs <- tidyr::expand_grid(species, ValleyName = unique(valleys$ValleyName))
joinpairs <- catch_ala |>
  st_drop_geometry() |>
  select(species, ValleyName)
missingpairs <- setdiff(allpairs, joinpairs) |>
  mutate(n_records = 0)

missingpairs <- left_join(missingpairs, valleys, by = 'ValleyName')

catch_ala <- bind_rows(catch_ala, missingpairs)

ala_catch_maps <- catch_ala |>
  mutate(species_name = stringr::str_replace(species, '_', ' ') |>
           stringr::str_to_sentence()) |>
  # filter(species == {{species}}) |>
  ggplot() +
  # geom_sf(data = basin, fill = 'azure') +
  geom_sf(aes(fill = log10(n_records))) +
  facet_wrap("species_name") +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  return(ala_catch_maps)
}

# Individual per-species plots
ala_catch_map <- make_ala_catch_map()
```

### Habitat alone

```{r}
#| label: habitat-map-function
make_habitat_map <- function(species) {
  
  hab_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in% anae_stages) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(hab_maps)
}

# Individual per-species plots
hab_basin_map <- purrr::map(species, make_habitat_map) |> 
  setNames(species)
```

The baseline- how much area is there in each habitat type?

We could make this for the other plots too; it is the ultimate baseline for the habitat analyses.

```{r}
#| label: totalhabitat-area-function
make_totalhabitat_map <- function(species) {
  
  hab_maps <- total_wetland_area |>
  filter(species == {{species}} & stage_name %in% anae_stages) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(hab_maps)
}

# Individual per-species plots
totalhab_basin_map <- purrr::map(species, make_totalhabitat_map) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-map-function
make_process_indep_map <- function(species) {
  
  pi_maps <- all_data_time |>
  filter(species == {{species}} &
           stage_name %in% c('Adult', 'Germination', 'Seedling')) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(pi_maps)
}

make_process_seq_map <- function(species) {
  
  ps_maps <- all_data_time |>
  filter(species == {{species}} & 
           stage_name %in% c('Adult', 'Regeneration', 'Recruitment')) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(ps_maps)
}

# Individual per-species plots
proc_indep_basin_map <- purrr::map(species, make_process_indep_map) |> 
  setNames(species)
proc_seq_basin_map <- purrr::map(species, make_process_seq_map) |> 
  setNames(species)
```

A joined version of the above. I had been using patchwork, but I think it's probably cleaner to just duplicate adults and facet

```{r}
#| label: process-indepseq-map-function
make_process_indepseq_map <- function(species) {
  
  # there's a lot of data cleaning, so just do it first
  adult_indep <- all_data_time |>
    filter(stage_name == "Adult") |>
    mutate(is_independent_proc = 'independent') |>
    bind_rows(all_data_time) |>
    mutate(base_stage = case_when(
      stage_name == 'Adult' ~ 'Adult',
      stage_name %in% c('Germination', 'Regeneration') ~ 'Regeneration',
      stage_name %in% c('Seedling', 'Recruitment') ~ 'Recruitment'
    ),
    base_stage = factor(base_stage, levels = levels(stage_name))) |>
    filter(species == {{species}} &
             base_stage %in% c('Adult', 'Regeneration', 'Recruitment'))
  
  # I was trying to label panels with their specific name, but it didn't work well
  # label_data <- adult_indep |>
  #   filter(species == 'red_gum' &
  #            base_stage %in% c('Adult', 'Regeneration', 'Recruitment')) |>
  #   filter(ValleyName == 'Warrego') |>
  #   reframe(stage_name = unique(stage_name), .by = geometry) |>
  #   st_as_sf()
  
  bio_both_maps <-
    ggplot() +
    geom_sf(data = adult_indep, aes(fill = log10(area + 1))) +
    # geom_sf_text(data = label_data,
    #              aes(label = stage_name), nudge_x = 1, nudge_y = 1) +
    scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
    facet_grid(is_independent_proc~base_stage) +
    werptoolkitr::theme_werp_toolkit() +
    labs(fill = "log(area + 1)")
  
  
  
  return(bio_both_maps)
}

# Individual per-species plots
proc_indepseq_basin_map <- purrr::map(species, make_process_indepseq_map) |> 
  setNames(species)
```

### Interactive

Just interactive- I don't think we'll actually use this anywhere.

```{r}
#| label: interactive-alone-map-function
#| eval: false
make_interact_alone_map <- function(species) {
  
inter_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in%
           c('Recruitment and Named', 'Recruitment and Recorded')) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(inter_maps)
}

# Individual per-species plots
interact_alone_map <- purrr::map(species, make_interact_alone_map) |> 
  setNames(species)
```

Sequenced off process

```{r}
#| label: interactive-procseq-map-function
make_interact_procseq_map <- function(species) {
  
inter_seq_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in%
           sequential_stages) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(inter_seq_maps)
}

# Individual per-species plots
interact_procseq_map <- purrr::map(species, make_interact_procseq_map) |> 
  setNames(species)
```

Sequenced off habitat

```{r}
#| label: interactive-habseq-map-function
make_interact_habseq_map <- function(species) {
  
  # Change the names here from the standard set to make the comparison clearer
habseqdata <- total_wetland_area |>
  mutate(stage_name = ifelse(grepl('Recorded', stage_name),
                             'Total Recorded', 'Total Named'),
         stage_name = factor(stage_name,
                             levels = c('Total Recorded', 'Total Named',
                                        levels(all_data_time$stage_name)))) |>
  bind_rows(all_data_time) |>
  mutate(stage_name = case_when(stage_name == 'Recorded wetland types' ~ 'Recorded and inundated',
                                stage_name == 'Named wetland types' ~ 'Named and inundated',
                                .default = stage_name),
         stage_name = factor(stage_name,
                             levels = c('Total Recorded', 'Total Named',
                                        'Recorded and inundated','Named and inundated',
                                        levels(all_data_time$stage_name)))) |>
  filter(species == {{species}} &
           stage_name %in% c(sequential_hab, 'Total Recorded', 'Total Named',
                             'Recorded and inundated','Named and inundated'))

inter_habseq_maps <- habseqdata |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_wrap('stage_name', nrow = 3) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")
  
  return(inter_habseq_maps)
}

# Individual per-species plots
interact_habseq_map <- purrr::map(species, make_interact_habseq_map) |> 
  setNames(species)
```

The plot for the paper

```{r}
#| label: map-for-paper

# Save these out by default
make_interact2d_fig <- function(species, print = TRUE) {
  
  inter_matrix_maps <- all_data_time |>
  filter((species == {{species}} | 
            is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment')) |>
  mutate(stage_name = forcats::fct_drop(stage_name)) |>
  # filter(!is.na(species)) |> #
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_wrap('stage_name', nrow = 2, drop = FALSE) +
  # facet_wrap('stage_name', ncol = 3) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = 'log(area + 1)')



  if (print) {
    thispath <- file.path(mappath, paste0(species, '_map'))
    galenR::ggsave_multi(filename = thispath, 
                         plot = inter_matrix_maps, 
                         device = c('png', 'svg'),
                         width = 16, height = 9, units = "cm")
  }

  return(inter_matrix_maps)

}

all_interactmap <- purrr::map(species, make_interact2d_fig) |> 
  setNames(species)
```

# Appendix: ALA records and ANAE

The Recorded wetland types were extracted from the ALA (Atlas of Living Australia). Those records were intersected with ANAE polygons to determine the ANAE wetland types where there were records. The records that intersect with ANAE wetlands are shown in @fig-ala-records. The number of records for each species in each catchment is shown in @fig-ala-catch, which is on the log scale due to the wide range of values. Grey catchments had no records.

```{r}
anaes <- readRDS(file.path(datOut, 'anae_simplify', 'all_anae_simplify.rds'))
```

```{r}
#| label: fig-anae-locations
#| fig-cap: ANAE wetlands across the Murray-Darling Basin
anae_map <- 
ggplot() +
  geom_sf(data = werptoolkitr::basin, fill = 'azure') +
  geom_sf(data = anaes, fill = 'grey20', color = NA,
          linewidth = 0.1, stroke = 0.1) +
  werptoolkitr::theme_werp_toolkit()

anae_map
```

```{r}
#| label: fig-ala-records
#| fig-cap: ALA records for each species that intersect with ANAE wetlands. This is the vast majority of ALA records in the Murray-Darling Basin for these species, though there are a small number that fall outside the ANAE polygons.
ala_records_map
```

```{r}
#| label: fig-ala-catch
#| fig-cap: ALA records for each species that intersect with ANAE wetlands. This is the vast majority of ALA records in the Murray-Darling Basin for these species, though there are a small number that fall outside the ANAE polygons.
ala_records_map
```

The number of ALA records is highly variable across wetland type and varies between species (@tbl-ala-records-rg, black box @tbl-ala-records-bb, coolabah @tbl-ala-records-cool, and lignum @tbl-ala-records-l). Strikingly, the *Named* wetland types are not always the wetland types with the most records, and in some cases are even excluded from the *Recorded* set because they contain < 0.05% of the total records. 

```{r}
#| label: tbl-ala-records-rg
#| tbl-cap: Habitat types with red gum records in Atlas of Living Australia, with number of records. ANAE_DESC is the wetland type from the ANAE. Bold rows with green background are the *Named* records (with the species name in the type). Those in light grey are < 0.5% of the total, and were not included in the set of ANAE wetland types used.

rgtab <- alatypes |> 
  filter(species == 'red_gum') |> 
  select(ANAE_DESC, Records = n_records) |> 
  arrange(desc(Records))

cutoff <- which(rgtab$Records < sum(rgtab$Records)*0.005)
named <- which(grepl('red gum', rgtab$ANAE_DESC, ignore.case = TRUE))

rgtab |> 
  knitr::kable() |> 
  kable_styling() |> 
  row_spec(named, bold = TRUE, background = 'lightgreen') |> 
  row_spec(cutoff, color = 'grey')
```

```{r}
#| label: tbl-ala-records-bb
#| tbl-cap: Habitat types with black box records in Atlas of Living Australia, with number of records. ANAE_DESC is the wetland type from the ANAE. Bold rows with green background are the *Named* records (with the species name in the type). Those in light grey are < 0.5% of the total, and were not included in the set of ANAE wetland types used.
#| 
bbtab <- alatypes |> 
  filter(species == 'black_box') |> 
  select(ANAE_DESC, Records = n_records) |> 
  arrange(desc(Records))

cutoff <- which(bbtab$Records < sum(bbtab$Records)*0.005)
named <- which(grepl('black box', bbtab$ANAE_DESC, ignore.case = TRUE))

bbtab |> 
  knitr::kable() |> 
  kable_styling() |> 
  row_spec(named, bold = TRUE, background = 'lightgreen') |> 
  row_spec(cutoff, color = 'grey')
```

```{r}
#| label: tbl-ala-records-cool
#| tbl-cap: Habitat types with coolabah records in Atlas of Living Australia, with number of records. ANAE_DESC is the wetland type from the ANAE. Bold rows with green background are the *Named* records (with the species name in the type). Those in light grey are < 0.5% of the total, and were not included in the set of ANAE wetland types used.
#| 
ctab <- alatypes |> 
  filter(species == 'coolabah') |> 
  select(ANAE_DESC, Records = n_records) |> 
  arrange(desc(Records))

cutoff <- which(ctab$Records < sum(ctab$Records)*0.005)
named <- which(grepl('cool', ctab$ANAE_DESC, ignore.case = TRUE))

ctab |> 
  knitr::kable() |> 
  kable_styling() |> 
  row_spec(named, bold = TRUE, background = 'lightgreen') |> 
  row_spec(cutoff, color = 'grey')
```

```{r}
#| label: tbl-ala-records-l
#| tbl-cap: Habitat types with lignum records in Atlas of Living Australia, with number of records. ANAE_DESC is the wetland type from the ANAE. Bold rows with green background are the *Named* records (with the species name in the type). Those in light grey are < 0.5% of the total, and were not included in the set of ANAE wetland types used.
#| 
ltab <- alatypes |> 
  filter(species == 'lignum') |> 
  select(ANAE_DESC, Records = n_records) |> 
  arrange(desc(Records))

cutoff <- which(ltab$Records < sum(ltab$Records)*0.005)
named <- which(grepl('lignum', ltab$ANAE_DESC, ignore.case = TRUE))

ltab |> 
  knitr::kable() |> 
  kable_styling() |> 
  row_spec(named, bold = TRUE, background = 'lightgreen') |> 
  row_spec(cutoff, color = 'grey')
```

The area of wetlands in each wetland type group is highly variable across the basin, with some species not having any named wetland types in entire catchments, or even nearly the entire southern basin in the case of Coolabah @fig-habitattype-map. There are also Recorded habitat types in areas where there are no ALA records ( @fig-ala-records).

```{r}
#| label: fig-habitattype-map 
#| fig-cap: Area of wetlands associated with each species in 25 major catchments across the basin, either by *Name* or where that species has been *Recorded* in the ALA. This is simply the area of wetlands, and does not include any inundation information, but instead forms the baseline maximum amount of area that could be achieved within either wetland-type grouping.  

totalhab_maps <- purrr::imap(totalhab_basin_map, \(x, i)
                             x + ggtitle(stringr::str_replace(i, '_', ' ') |> 
                                           stringr::str_to_sentence())) |>
  wrap_plots() + 
  plot_layout(guides = 'collect')  

totalhab_maps 
```

# Appendix: Other species

The main text presents red gum as an example species, here we show the same figures for the other species, noting important deviations from red gum.

When summed over the basin and averaged over time, (@fig-bar-bb, @fig-bar-c, @fig-bar-l).

```{r}
#| label: fig-bar-bb
#| fig-cap: Favourable area for black box as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 12
#| fig-height: 9
all_stacked_bars$black_box
```

```{r}
#| label: fig-bar-c
#| fig-cap: Favourable area for coolabah as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 12
#| fig-height: 9
#| 
all_stacked_bars$coolabah
```

```{r}
#| label: fig-bar-l
#| fig-cap: Favourable area for lignum as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 12
#| fig-height: 9
#| 
all_stacked_bars$lignum
```

Timeseries of the favourable area at the basin-scale, (@fig-ts-bb, @fig-ts-c, @fig-ts-l).

```{r}
#| label: fig-ts-bb
#| fig-cap: Favourable area for black box as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 16
#| fig-height: 22

all_stacked_ts$black_box
```

```{r}
#| label: fig-ts-c
#| fig-cap: Favourable area for coolabah as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 16
#| fig-height: 22
#| 
all_stacked_ts$coolabah
```

```{r}
#| label: fig-ts-l
#| fig-cap: Favourable area for lignum as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 16
#| fig-height: 22
#| 
all_stacked_ts$lignum
```

Spatial variation across catchments, (@fig-map-bb, @fig-map-c, @fig-map-l).

```{r}
#| label: fig-map-bb
#| fig-cap: Favourable area for black box as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 16
#| fig-height: 9
all_interactmap$black_box
```

```{r}
#| label: fig-map-c
#| fig-cap: Favourable area for coolabah as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 16
#| fig-height: 9
#| 
all_interactmap$coolabah
```

```{r}
#| label: fig-map-l
#| fig-cap: Favourable area for lignum as assessed by wetland type, process-based, and interactive models, as is done for red gum in the main text.
#| fig-width: 16
#| fig-height: 9
#| 
all_interactmap$lignum
```

# Appendix: Life cycles/identifying limitations

Most would work in a Life cycle-pinch point paper

This creates the individual plots and develops the story. Then some get glued together for the main results.

## Basin-scale over time

### Habitat alone

Over the whole basin, mean yearly inundation levels of all wetlands are approximately 10^10^ m^2^. Unsurprisingly, there is more inundation in the sets of Recorded wetland types than the Named wetland types, though the relative amounts varies between species @fig-habitat-bar .

```{r}
#| label: fig-habitat-bar
#| fig-cap: Area of inundation in wetlands associated with each species in the basin, either by *Name* or where that species has been *Recorded* in the ALA, averaged over time. Error bars are standard deviation over time, giving a description of the variability, rather than CI.

# Should we sort out the facetting by duplicating'All wetlands' across all species? Probably, but this works.

hab_bar_panel <- purrr::imap(hab_basin_bar, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

hab_bar_panel
```

### Process alone

Each species shows the largest area of success in the adult life stage, followed by germination and seedlings @fig-process-bar. To understand the importance of each life stage alone as well as the life cycle itself, we examine each stage alone and sequentialy. When considered indepedently (Adult, Germination, Seedling), every species has high adult favourability and low areas of seedling favourability. Note that the decline in favourability for these three stages is not due to the life cycle, because they are considered independently. The consequences of the life cycle are seen in the Regeneration and Recruitment stages, which require favourable conditions in preceding stages. By comparing these stages to their respective independent stage, we can see that requiring adult favourability decreases the area of germination favourability only slightly, while requiring germination success reduces the already-low seedling favourability by multiple orders of magnitude to the overall Recruitment favourability value @fig-process-bar. *For a pinch points paper, we could work this one up, and do two dimensions- through the life cycle, but also across the independent-sequential to get the specific impact of the life cycle itself*.

```{r}
#| label: fig-process-bar
#| fig-cap: Area of favourability after each stage in the life cycle. We present these for the stages *independently* and *sequentially*, with the difference between the two (e.g. between Germinaton and Regeneration) being the consequence of requiring success in preceding stages. Error bars are standard deviation over time, giving a description of the variability, rather than CI.

proc_bar_panel <- purrr::imap(proc_basin_bar, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

proc_bar_panel
```

### Interactive

The simplest way to consider the interactive models is to think of them sequentially; i.e. if we have a series of life cycle stages, then we can ask about a habitat requirement as the next step in the life cycle @fig-interact-seq-bar . This paralells the treatment in (Holt et al. in review) and represents a process-centric approach that limits the processes to a habitat covariate at the final step. Note here that the two wetland restrictions are not nested, and so each follows from the Recruitment life stage. *For a paper on how life cycles and habitats determine pinch points, this one would be really good, and we could easily work it up into a relativized version too*.

```{r}
#| label: fig-interact-seq-bar
#| fig-cap: Area of favourability after each stage in the life cycle, followed by wetland type restrictions. Error bars are standard deviation over time, giving a description of the variability, rather than CI.

interact_seq_panel <- purrr::imap(interact_seq_basin_bar, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_seq_panel
```

To examine the impact of wetland type requirements on each life stage, rather than only as a final step, we compare the favourable area for each life stage (as in @fig-process-bar) alone and restricted by wetland requirements. This identifies the life stages that are most sensitive to wetland requirements (and so are the stages with the most favourable area outside designated wetland types) @fig-interact-proc-bar. A subset of this plot with only the sequential life stages, and recolored to accentuate the wetland types, is used in the main bar plot in the text.

```{r}
#| label: fig-interact-proc-bar
#| fig-cap: Area of favourability of each stage in the life cycle, both independent and sequential, and the reduction in each stage from wetland requirements. Error bars are standard deviation over time, giving a description of the variability, rather than CI.

interact_proc_panel <- purrr::imap(interact_proc_basin_bar, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_proc_panel
```

A similar approach for the wetland type restrictions identifies how requiring processes to occur within them reduces the area of favourability. A subset of this plot, recolored to accentuate the model type, is used in the main bar plot in the text.

```{r}
#| label: fig-interact-hab-bar
#| fig-cap: Area of favourability of each wetland type group and the reduction in favourable area when successful recruitment is required within that group. Error bars are standard deviation over time, giving a description of the variability, rather than CI.

interact_hab_panel <- purrr::imap(interact_hab_basin_bar, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_hab_panel
```

## Basin-scale timeseries

### Habitat alone

A habitat-only model suggests that area is favourable if it is inundated in either Recorded wetland types or Named wetland types. Both are a subset of the total wetland inundation in the MDB, with Recorded types being a larger set and so having a larger amount of inundation @fig-habitat-ts .

```{r}
#| label: fig-habitat-ts
#| fig-cap: Area of inundation in wetlands associated with each species in the basin, either by *Name* or where that species has been *Recorded* in the ALA.

# Should we sort out the facetting by duplicating'All wetlands' across all species? Probably, but this works.

hab_alone_panel <- purrr::imap(hab_basin_ts, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

hab_alone_panel
```

### Process alone

In a process-based model, the amount of favourable area for each life stage depends on the specific environmental requirements for that stage. Moreover, these stages are sequential, and so even if all requirements for seedling survival are met in a year, there may not be successful recruitment if there was not germination approximately six months prior to the favourable seedling conditions. In @fig-all-process-basin, we plot both the independent life stages (Adults, plus Germination and Seedling) as well as the sequential stages (Adult-Regeneration-Recruitment). From these plots, we can clearly see that seedling survival is the most limiting life stage for all species. Further, life-history dependence provides limitation beyond the individual stages. The Regeneration line (Adult + Germination) is almost always lower than the independent Germination line, indicating that there are locations favourable to germination but lacking favourable adult conditions to provide seed. Similarly, even though seeling survival is quite low in general, Recruitment is even lower; there are many times when seedlings *could* survive, but there were not preceding conditions favourable for Regeneration.

The species are quite different in these relationships. Lignum and Red gum are much less limited by seedling survival than Black box or Coolabah, as a consequence of shorter requirements for soil moisture maintenance @fig-all-process-basin . Unlike the other species, Coolabah does not show additional limitation of Regeneration beyond Germination, and so all favourable germination conditions occur in areas that are favourable for adults.

```{r}
#| label: fig-all-process-basin
#| fig-cap: Area favourable for each life stage in a process model, both independently (dashed) and sequentially (solid). Note that Coolabah and Lignum have long lookbacks for adult condition, and so cannot assess adult favourability for a large proprotion of the timeseries.

all_proc_panel <- purrr::imap(all_proc_basin_ts, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

all_proc_panel
```

*If we want to go for the life-history pinch-points analyses*: Here, we could do a relativization in two dimensions- How does each stage in the sequential reduce things relative to the preceding stage, and how does the joint compare to the individual (e.g. Regeneration vs Germination). The first would give proprotional loss at each step, and the second would say how much the sequencing itself is introducing limitation. The wetland-type filters off the end of this are possible, as shown in the next two figures @fig-interact-named-basin and @fig-interact-recorded-basin. Those proportional drops could also be included.

### Interactive habitat and process

To look at the interaction between wetland type models and process-based models, we can examine how the joint area differs from the area of their independent outcomes. This is dealt with in detail in the main text.

```{r}
#| label: fig-interact-named-basin
#| fig-cap: Area favourable for the wetland-type-based model using Named habitat alone, the process model alone (at the final recruitment stage) and jointly. Venn diagrams below each figure show the relationship of overlapping habitat area between the two models, with the area in the overlap being the area in the interactive model.

interact_named_panel <- purrr::imap(interact_named_basin_ts, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  purrr::map2(.y = vennplots_named,
                   \(x,y) wrap_plots(x,y, nrow = 2))  |> 
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_named_panel

```

```{r}
#| label: fig-interact-recorded-basin
#| fig-cap: Area favourable for the wetland-type-based model using Recorded habitat alone, the process model alone (at the final recruitment stage) and jointly. Venn diagrams below each figure show the relationship of overlapping habitat area between the two models, with the area in the overlap being the area in the interactive model.

interact_recorded_panel <- purrr::imap(interact_recorded_basin_ts, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  purrr::map2(.y = vennplots_named,
                   \(x,y) wrap_plots(x,y, nrow = 2))  |> 
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_recorded_panel
```

## Spatial variation across catchments

In addition to temporal variation, there is striking spatial variation in favourability for these species across the basin, and the different life stages and wetland type requirements are differently limiting across the basin. To examine this spatial variation, we calculate the favourable area within each of 25 large subcatchments in the basin.

### Habitat alone

Within the available wetlands of the respective types (total areas shown in @fig-habitattype-map , we ask how much area is inundated @fig-habitat-map.

```{r}
#| label: fig-habitat-map
#| fig-cap: Area of inundation in wetlands associated with each species in 25 major catchments across the basin, either by *Name* or where that species has been *Recorded* in the ALA.

hab_alone_maps <- purrr::imap(hab_basin_map, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

hab_alone_maps
```

### Process alone

Both independent (top) and sequential. Going to need to panel this one up differently across species.

```{r}
#| label: fig-process-map
#| fig-cap: Area of favourability after each stage in the life cycle in 25 major catchments across the basin. We present these for the stages *independently* (top) and *sequentially*, as we did in @fig-process-bar. Thus, the top panels are the 'Adult' 'Germination', and 'Seedling' stages as used elsewhere. The difference between the top and bottom (e.g. between Germinaton and Regeneration) being the consequence of requiring success in preceding stages.

# Should we sort out the facetting by duplicating'All wetlands' across all species? Probably, but this works.

proc_alone_maps <- purrr::imap(proc_indepseq_basin_map, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

proc_alone_maps
```

### Interactive

To examine how a habitat filter further limits the favourable area after all biological processes have occurred, we show those filters as a final step in the sequence @fig-interact-seq-map. *This is an ideal point for a sequence of relativised figures too*.

```{r}
#| label: fig-interact-seq-map
#| fig-cap: Area of favourability after each stage in the life cycle in 25 major catchments across the basin, followed by a final step of filtering by wetland type. The final two panels are the different specifications of wetland type, and so both are limits beyond the 'Recruitment' stage. *clearly need to play with fig dims here*.

interact_procseq_maps <- purrr::imap(interact_procseq_map, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_procseq_maps
```

Similarly, we can examine how the area of favourability changes within each wetland type as we move from the total area of those wetland types (top) to requiring inundation (middle) to requiring successful recruitment to occur within them @fig-interact-hab-map. The middle panels here are the 'Recorded wetland types' and 'Named wetland types' in the text, where we always assume inundation is required. The combination of @fig-interact-seq-map and @fig-interact-hab-map, without the preceding life stages or the total wetland areas, forms the map figure in the text.

```{r}
#| label: fig-interact-hab-map
#| fig-cap: Area of favourability in each of 25 major catchments due to inundation of wetland types (top) and when recruitment conditions are also favourable within those types (bottom). *clearly need to play with fig dims here*.

interact_habseq_maps <- purrr::imap(interact_habseq_map, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

interact_habseq_maps
```

## Still to do for in-depth and pinch points

### Relativised change (especially if we go for pinch points)

### spatio-temporal (catchment-paneled timeseries)

### Selected catchment-scale bars
