---
title: "SRA_analysis"
format: html
editor: visual
---

## Libraries/Paths/Functions

```{r}
#| include: false

library(CC2)
library(werptoolkitr)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)
library(foreach)

# get directories
source('directorySet.R')

#devtools::build("E:/Georgia/CC2")

catch_cat_sf <- function(which_strict, catchments = cleancatch, outerdir = 'hello') {
  foreach(i = catchments,
          .combine = dplyr::bind_rows,
          .multicombine = TRUE) %do% {
            thiscatch <- readRDS(file.path(datOut, outerdir, which_strict, 
                                           paste0(i, '_', which_strict, '.rds')))
          }
}  

calc_shan <- function(x) {
    px <- x/sum(x)
    shan <- -sum(px*log(px))
    return(shan)
}

# Need a clean name to bring in data
catchments <- ltimNoNorth |> 
   mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

cleancatch <- catchments$name_clean

# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')

preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')

comparison_years <- data.frame(timeperiod = c("pre-BP", "current"),
                               timestart = c(preBPtimestart, currenttimestart),
                               timeend = c(preBPtimeend, currenttimeend),
                               lubridate::year(currenttimeend))

save_plots <- TRUE

```

```{r}
#| include: false
qaelpath <- myhome
#qaelpath <- path.expand(qaelpath)
datDir <- file.path(qaelpath, "Deakin University/QAEL - MER/Model/dataBase")
datOut <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out")
project_dir <- file.path(datOut, 'werpstyle')
hydro_dir <- file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR_numeric_gauges')
ewr_results <- file.path(project_dir, 'MANUAL')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output_numeric_gauges')

comp_results <- file.path(project_dir, 'comparer_output') 

data_path <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out/SRA_analysis/Final_datasets")
plot_path <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out/SRA_analysis/Final_plots")
```

## Climate categories

```{r}
#Climate categorgy data:
Climate_Categories <- read.csv(file.path(qaelpath, "Deakin University", "QAEL - SRA - SRA", "Climate_Categories_Coloured_2023.csv"), check.names = FALSE)

Climate_Categories <- Climate_Categories |>
  pivot_longer(cols = `Barwon-Darling`:`Total MDB`, names_to = "Climate_category.data", values_to = "Climate_Category")

Climate_Categories <- Climate_Categories |>
  mutate(Climate_Category = factor(Climate_Category, levels = c("Very Dry", "Dry", "Moderate", "Wet", "Very Wet")))|>
  rename(year = `Start of water Year`)

#FOR MER-STYLE
# read in the mapping of sdls/valleys to the climate category areas:
Climate_Category_to_polygons_MER <- read.csv(file.path(qaelpath, "Deakin University", "QAEL - SRA - SRA", "Climate_Category_to_polygons.csv"))

Climate_Category_to_polygons_MER <- Climate_Category_to_polygons_MER |>
  dplyr::select(Climate_category.data, ValleyName)|>
  filter(Climate_category.data != "")|>
  filter(ValleyName != "")|>
  distinct(Climate_category.data, ValleyName)

#NEED to REMEMBER TO REMOVE THIS::::
Climate_Category_to_polygons_MER <- filter(Climate_Category_to_polygons_MER, !row_number() %in% c(2))

Climate_Category_to_polygons_MER <- Climate_Category_to_polygons_MER |> 
   mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

#Palette
pal_climate <-  stats::setNames(c("#ED2024", "#FAA41A", "#F6EB14", "#87CDE9", "#282A73"), levels(Climate_Categories$Climate_Category))
class(pal_climate) <- 'colors'

#dont think this worked:
pal_score <- stats::setNames(adjustcolor(pal_climate, alpha.f = 0.5),
                             c("very low", "Low", "medium", "high", "very high"))
class(pal_score) <- 'colors'

#"#ED202480" "#FAA41A80" "#F6EB1480" "#87CDE980" "#282A7380"


```

## Data - Connectivity
```{r}
#LATERALconnectivity - Valley
Timeseries_Valley_LATERALconnectivity <- readRDS(file.path(data_path, "Timeseries_Valley_LATERALconnectivity.rds"))

Timeseries_Valley_LATERALconnectivity <- left_join(Timeseries_Valley_LATERALconnectivity, Climate_Category_to_polygons_MER, by = join_by(ValleyName)) 
  
Timeseries_Valley_LATERALconnectivity <- Timeseries_Valley_LATERALconnectivity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#LATERALconnectivity - Basin
Timeseries_Basin_LATERALconnectivity <- readRDS(file.path(data_path, "Timeseries_Basin_LATERALconnectivity.rds"))

Timeseries_Basin_LATERALconnectivity$Climate_category.data <- "Total MDB"

Timeseries_Basin_LATERALconnectivity <- Timeseries_Basin_LATERALconnectivity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#LONGITUDINALconnectivity - Valley
Timeseries_Valley_LONGITUDINALconnectivity <- readRDS(file.path(data_path, "Timeseries_Valley_LONGITUDINALconnectivity.rds"))

Timeseries_Valley_LONGITUDINALconnectivity <- left_join(Timeseries_Valley_LONGITUDINALconnectivity, Climate_Category_to_polygons_MER, by = join_by(ValleyName)) 
  
Timeseries_Valley_LONGITUDINALconnectivity <- Timeseries_Valley_LONGITUDINALconnectivity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#LONGITUDINALconnectivity - Basin
Timeseries_Basin_LONGITUDINALconnectivity <- readRDS(file.path(data_path, "Timeseries_Basin_LONGITUDINALconnectivity.rds"))

Timeseries_Basin_LONGITUDINALconnectivity$Climate_category.data <- "Total MDB"
  
Timeseries_Basin_LONGITUDINALconnectivity <- Timeseries_Basin_LONGITUDINALconnectivity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

```



## Data - ANAE diversity and inundation
```{r}
#ANAEdiversity
#ANAEdiversity - Valley
Timeseries_Valley_ANAEdiversity <- catch_cat_sf('diversity_shannon_area', outerdir = 'diversity')
Timeseries_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
  mutate(year = lubridate::year(lubridate::ymd(time)))|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(ValleyName, name_clean)) 
Timeseries_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

diversity_anae_summary <- catch_cat_sf('diversity_anae_summary', outerdir = 'diversity')

#ANAEdiversity - Basin
Timeseries_Basin_ANAEdiversity <- diversity_anae_summary |>
    st_drop_geometry() |>
    summarise(total_area = sum(area_inundated), .by = c(ANAE_DESC, time)) |> # the 'abundance', e.g. number of wetlands of each type
    filter(total_area > 0) |> # otherwise the log dies, and they don't count anyway.
    summarise(diversity_shannon_area = calc_shan(total_area), .by = c(time)) |>
    arrange(time)|> 
  bind_cols(basin) |> 
  st_as_sf()

Timeseries_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
  mutate(year = lubridate::year(lubridate::ymd(time)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

##ANAEinudation

total_inun_area <- diversity_anae_summary |>
  sf::st_drop_geometry() |>
  summarise(area_inundated = sum(area_inundated),
            total_area = sum(total_area),
            n_inundated = sum(n_inundated),
            n_anaes = sum(n_anaes),
            .by = c(time, name_clean, ValleyName)) |>
  mutate(prop_wetland_inundated = area_inundated/total_area) |>
  left_join(werptoolkitr::cewo_valleys, by = 'ValleyName') |>
  st_as_sf()

#ggplot(total_inun_area, aes(x = time, y = prop_wetland_inundated)) + geom_point() + geom_line() + facet_wrap('ValleyName')
#area_inundated is raw, prop_wetland_inundated is the proportion of wetland in each catchment that is inundated

```


## Data - ANAE veg

```{r}
#Data with climate categories attached or attach here
#LATERALconnectivity
#LONGITUDINALconnectivity
#ANAEdiversity
#BLACKBOXgermination
#BLACKBOXseedlings
#BLACKBOXgerminationseedlings
#BLACKBOXadult
#REDGUMgermination
#REDGUMseedlings
#REDGUMgerminationseedlings
#REDGUMadult
#LIGNUMgermination
#LIGNUMseedlings
#LIGNUMgerminationseedlings
#LIGNUMadult
#COOLABAHgermination
#COOLABAHseedlings
#COOLABAHgerminationseedlings
#COOLABAHadult

#BLACKBOXgermination
Timeseries_Valley_BLACKBOXgermination <- catch_cat_sf('germ_catch', outerdir = 'black_box') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'regeneration')

Timeseries_Basin_BLACKBOXgermination <- Timeseries_Valley_BLACKBOXgermination |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#BLACKBOXseedlings
Timeseries_Valley_BLACKBOXseedlings <- catch_cat_sf('seed_catch', outerdir = 'black_box_old') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'seed')

Timeseries_Basin_BLACKBOXseedlings <- Timeseries_Valley_BLACKBOXseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#BLACKBOXgerminationseedlings
Timeseries_Valley_BLACKBOXgerminationseedlings <- catch_cat_sf('germ_and_seed_catch', outerdir = 'black_box') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ_and_seed')

Timeseries_Basin_BLACKBOXgerminationseedlings <- Timeseries_Valley_BLACKBOXgerminationseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#BLACKBOXadult
Timeseries_Valley_BLACKBOXadult <- catch_cat_sf('adult_catch', outerdir = 'black_box') |> 
  filter(date > lubridate::ymd(19950101)) |>   # There's no adult data prior to 1995 because of the lookback period
  mutate(stage = 'adult')

Timeseries_Basin_BLACKBOXadult <- Timeseries_Valley_BLACKBOXadult |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#BLACKBOX - Valley
Timeseries_Valley_BLACKBOX <- bind_rows(Timeseries_Valley_BLACKBOXgermination, Timeseries_Valley_BLACKBOXseedlings)
Timeseries_Valley_BLACKBOX <- bind_rows(Timeseries_Valley_BLACKBOX, Timeseries_Valley_BLACKBOXgerminationseedlings)
Timeseries_Valley_BLACKBOX <- bind_rows(Timeseries_Valley_BLACKBOX, Timeseries_Valley_BLACKBOXadult)

Timeseries_Valley_BLACKBOX <- Timeseries_Valley_BLACKBOX |>
  mutate(year = lubridate::year(lubridate::ymd(date)))|>
  rename(name_clean = ValleyName)|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(name_clean)) 

Timeseries_Valley_BLACKBOX <- Timeseries_Valley_BLACKBOX |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#BLACKBOX - Basin
Timeseries_Basin_BLACKBOX <- bind_rows(Timeseries_Basin_BLACKBOXgermination, Timeseries_Basin_BLACKBOXseedlings)
Timeseries_Basin_BLACKBOX <- bind_rows(Timeseries_Basin_BLACKBOX, Timeseries_Basin_BLACKBOXgerminationseedlings)
Timeseries_Basin_BLACKBOX <- bind_rows(Timeseries_Basin_BLACKBOX, Timeseries_Basin_BLACKBOXadult)

Timeseries_Basin_BLACKBOX <- Timeseries_Basin_BLACKBOX |>
  mutate(year = lubridate::year(lubridate::ymd(date)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_BLACKBOX <- Timeseries_Basin_BLACKBOX |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))


#REDGUMgermination
Timeseries_Valley_REDGUMgermination <- catch_cat_sf('germ_catch', outerdir = 'black_box') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ')

Timeseries_Basin_REDGUMgermination <- Timeseries_Valley_REDGUMgermination |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#REDGUMseedlings
Timeseries_Valley_REDGUMseedlings <- catch_cat_sf('seed_catch', outerdir = 'red_gum') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'seed')

Timeseries_Basin_REDGUMseedlings <- Timeseries_Valley_REDGUMseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#REDGUMgerminationseedlings
Timeseries_Valley_REDGUMgerminationseedlings <- catch_cat_sf('germ_and_seed_catch', outerdir = 'red_gum') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ_and_seed')

Timeseries_Basin_REDGUMgerminationseedlings <- Timeseries_Valley_REDGUMgerminationseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#REDGUMadult
Timeseries_Valley_REDGUMadult <- catch_cat_sf('adult_catch', outerdir = 'red_gum') |> 
  filter(date > lubridate::ymd(19950101)) |>   # There's no adult data prior to 1995 because of the lookback period
  mutate(stage = 'adult')

Timeseries_Basin_REDGUMadult <- Timeseries_Valley_REDGUMadult |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#REDGUM - Valley
Timeseries_Valley_REDGUM <- bind_rows(Timeseries_Valley_REDGUMgermination, Timeseries_Valley_REDGUMseedlings)
Timeseries_Valley_REDGUM <- bind_rows(Timeseries_Valley_REDGUM, Timeseries_Valley_REDGUMgerminationseedlings)
Timeseries_Valley_REDGUM <- bind_rows(Timeseries_Valley_REDGUM, Timeseries_Valley_REDGUMadult)

Timeseries_Valley_REDGUM <- Timeseries_Valley_REDGUM |>
  mutate(year = lubridate::year(lubridate::ymd(date)))|>
  rename(name_clean = ValleyName)|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(name_clean)) 

Timeseries_Valley_REDGUM <- Timeseries_Valley_REDGUM |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#REDGUM - Basin
Timeseries_Basin_REDGUM <- bind_rows(Timeseries_Basin_REDGUMgermination, Timeseries_Basin_REDGUMseedlings)
Timeseries_Basin_REDGUM <- bind_rows(Timeseries_Basin_REDGUM, Timeseries_Basin_REDGUMgerminationseedlings)
Timeseries_Basin_REDGUM <- bind_rows(Timeseries_Basin_REDGUM, Timeseries_Basin_REDGUMadult)

Timeseries_Basin_REDGUM <- Timeseries_Basin_REDGUM |>
  mutate(year = lubridate::year(lubridate::ymd(date)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_REDGUM <- Timeseries_Basin_REDGUM |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))


#LIGNUMgermination
Timeseries_Valley_LIGNUMgermination <- catch_cat_sf('germ_catch', outerdir = 'lignum') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ')

Timeseries_Basin_LIGNUMgermination <- Timeseries_Valley_LIGNUMgermination |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#LIGNUMseedlings
Timeseries_Valley_LIGNUMseedlings <- catch_cat_sf('seed_catch', outerdir = 'lignum') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'seed')

Timeseries_Basin_LIGNUMseedlings <- Timeseries_Valley_LIGNUMseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#LIGNUMgerminationseedlings
Timeseries_Valley_LIGNUMgerminationseedlings <- catch_cat_sf('germ_and_seed_catch', outerdir = 'lignum') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ_and_seed')

Timeseries_Basin_LIGNUMgerminationseedlings <- Timeseries_Valley_LIGNUMgerminationseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#LIGNUMadult
Timeseries_Valley_LIGNUMadult <- catch_cat_sf('adult_catch', outerdir = 'lignum') |> 
  filter(date > lubridate::ymd(19950101)) |>   # There's no adult data prior to 1995 because of the lookback period
  mutate(stage = 'adult')

Timeseries_Basin_LIGNUMadult <- Timeseries_Valley_LIGNUMadult |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#LIGNUM - Valley
Timeseries_Valley_LIGNUM <- bind_rows(Timeseries_Valley_LIGNUMgermination, Timeseries_Valley_LIGNUMseedlings)
Timeseries_Valley_LIGNUM <- bind_rows(Timeseries_Valley_LIGNUM, Timeseries_Valley_LIGNUMgerminationseedlings)
Timeseries_Valley_LIGNUM <- bind_rows(Timeseries_Valley_LIGNUM, Timeseries_Valley_LIGNUMadult)

Timeseries_Valley_LIGNUM <- Timeseries_Valley_LIGNUM |>
  mutate(year = lubridate::year(lubridate::ymd(date)))|>
  rename(name_clean = ValleyName)|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(name_clean)) 

Timeseries_Valley_LIGNUM <- Timeseries_Valley_LIGNUM |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#LIGNUM - Basin
Timeseries_Basin_LIGNUM <- bind_rows(Timeseries_Basin_LIGNUMgermination, Timeseries_Basin_LIGNUMseedlings)
Timeseries_Basin_LIGNUM <- bind_rows(Timeseries_Basin_LIGNUM, Timeseries_Basin_LIGNUMgerminationseedlings)
Timeseries_Basin_LIGNUM <- bind_rows(Timeseries_Basin_LIGNUM, Timeseries_Basin_LIGNUMadult)

Timeseries_Basin_LIGNUM <- Timeseries_Basin_LIGNUM |>
  mutate(year = lubridate::year(lubridate::ymd(date)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_LIGNUM <- Timeseries_Basin_LIGNUM |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))


#COOLABAHgermination
Timeseries_Valley_COOLABAHgermination <- catch_cat_sf('germ_catch', outerdir = 'coolabah') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ')

Timeseries_Basin_COOLABAHgermination <- Timeseries_Valley_COOLABAHgermination |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#COOLABAHseedlings
Timeseries_Valley_COOLABAHseedlings <- catch_cat_sf('seed_catch', outerdir = 'coolabah') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'seed')

Timeseries_Basin_COOLABAHseedlings <- Timeseries_Valley_COOLABAHseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#COOLABAHgerminationseedlings
Timeseries_Valley_COOLABAHgerminationseedlings <- catch_cat_sf('germ_and_seed_catch', outerdir = 'coolabah') |> 
  filter(date > lubridate::ymd(19880101)) |>   # There's no data prior ot 1988
  mutate(stage = 'germ_and_seed')

Timeseries_Basin_COOLABAHgerminationseedlings <- Timeseries_Valley_COOLABAHgerminationseedlings |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#COOLABAHadult
Timeseries_Valley_COOLABAHadult <- catch_cat_sf('adult_catch', outerdir = 'coolabah') |> 
  filter(date > lubridate::ymd(19950101)) |>   # There's no adult data prior to 1995 because of the lookback period
  mutate(stage = 'adult')

Timeseries_Basin_COOLABAHadult <- Timeseries_Valley_COOLABAHadult |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area, na.rm = TRUE),
            .by = c(date, stage)) |>
  bind_cols(basin) |> 
  st_as_sf()

#COOLABAH - Valley
Timeseries_Valley_COOLABAH <- bind_rows(Timeseries_Valley_COOLABAHgermination, Timeseries_Valley_COOLABAHseedlings)
Timeseries_Valley_COOLABAH <- bind_rows(Timeseries_Valley_COOLABAH, Timeseries_Valley_COOLABAHgerminationseedlings)
Timeseries_Valley_COOLABAH <- bind_rows(Timeseries_Valley_COOLABAH, Timeseries_Valley_COOLABAHadult)

Timeseries_Valley_COOLABAH <- Timeseries_Valley_COOLABAH |>
  mutate(year = lubridate::year(lubridate::ymd(date)))|>
  rename(name_clean = ValleyName)|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(name_clean)) 

Timeseries_Valley_COOLABAH <- Timeseries_Valley_COOLABAH |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#COOLABAH - Basin
Timeseries_Basin_COOLABAH <- bind_rows(Timeseries_Basin_COOLABAHgermination, Timeseries_Basin_COOLABAHseedlings)
Timeseries_Basin_COOLABAH <- bind_rows(Timeseries_Basin_COOLABAH, Timeseries_Basin_COOLABAHgerminationseedlings)
Timeseries_Basin_COOLABAH <- bind_rows(Timeseries_Basin_COOLABAH, Timeseries_Basin_COOLABAHadult)

Timeseries_Basin_COOLABAH <- Timeseries_Basin_COOLABAH |>
  mutate(year = lubridate::year(lubridate::ymd(date)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_COOLABAH <- Timeseries_Basin_COOLABAH |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

```

## IS Scaling

```{r}
#LATERALconnectivity
Timeseries_Valley_LATERALconnectivity <- Timeseries_Valley_LATERALconnectivity |>
  ungroup()|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = ewr_achieved)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #Valley
  group_by(ValleyName)|>  
  mutate(Outcome_ValScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_ValScaled    = ifelse(is.nan(Outcome_ValScaled), 0, Outcome_ValScaled)) |>
  #YrType
  group_by(ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Valley_LATERALconnectivity <- Timeseries_Valley_LATERALconnectivity |>
    filter(year>=2009)|>
    group_by(ValleyName)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Valley_LATERALconnectivity <- Timeseries_Valley_LATERALconnectivity |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(ValleyName)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_ValScaled_mean = mean(Outcome_ValScaled),
              Outcome_ValScaled_SE = plotrix::std.error(Outcome_ValScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Valley_LATERALconnectivity <- left_join(Condition_Valley_LATERALconnectivity, Trend_Valley_LATERALconnectivity, by = join_by(ValleyName))
Condition_Trend_Valley_LATERALconnectivity$Indicator <- "Lateral connectivity" 
Condition_Trend_Valley_LATERALconnectivity$Label <- "Lateral connectivity (EWR achieved)" 
Condition_Trend_Valley_LATERALconnectivity$Scale <- "Valley" 

Timeseries_Basin_LATERALconnectivity <- Timeseries_Basin_LATERALconnectivity |>
  ungroup()|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = ewr_achieved)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #YrType
  group_by(Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Basin_LATERALconnectivity <- Timeseries_Basin_LATERALconnectivity |>
  ungroup()|>  
  filter(year>=2009)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Basin_LATERALconnectivity <- Timeseries_Basin_LATERALconnectivity |>
  ungroup()|>  
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Basin_LATERALconnectivity <- bind_cols(Condition_Basin_LATERALconnectivity, Trend_Basin_LATERALconnectivity)
Condition_Trend_Basin_LATERALconnectivity$Indicator <- "Lateral connectivity" 
Condition_Trend_Basin_LATERALconnectivity$Label <- "Lateral connectivity (EWR achieved)" 
Condition_Trend_Basin_LATERALconnectivity$Scale <- "Basin" 

#LONGITUDINALconnectivity
Timeseries_Valley_LONGITUDINALconnectivity <- Timeseries_Valley_LONGITUDINALconnectivity |>
  ungroup()|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = ewr_achieved)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #Valley
  group_by(ValleyName)|>  
  mutate(Outcome_ValScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_ValScaled    = ifelse(is.nan(Outcome_ValScaled), 0, Outcome_ValScaled)) |>
  #YrType
  group_by(ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Valley_LONGITUDINALconnectivity <- Timeseries_Valley_LONGITUDINALconnectivity |>
    filter(year>=2009)|>
    group_by(ValleyName)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Valley_LONGITUDINALconnectivity <- Timeseries_Valley_LONGITUDINALconnectivity |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(ValleyName)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_ValScaled_mean = mean(Outcome_ValScaled),
              Outcome_ValScaled_SE = plotrix::std.error(Outcome_ValScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Valley_LONGITUDINALconnectivity <- left_join(Condition_Valley_LONGITUDINALconnectivity, Trend_Valley_LONGITUDINALconnectivity, by = join_by(ValleyName))
Condition_Trend_Valley_LONGITUDINALconnectivity$Indicator <- "Longitudinal connectivity" 
Condition_Trend_Valley_LONGITUDINALconnectivity$Label <- "Longitudinal connectivity (EWR achieved)" 
Condition_Trend_Valley_LONGITUDINALconnectivity$Scale <- "Valley" 

Timeseries_Basin_LONGITUDINALconnectivity <- Timeseries_Basin_LONGITUDINALconnectivity |>
  ungroup()|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = ewr_achieved)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #YrType
  group_by(Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Basin_LONGITUDINALconnectivity <- Timeseries_Basin_LONGITUDINALconnectivity |>
  ungroup()|>  
  filter(year>=2009)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Basin_LONGITUDINALconnectivity <- Timeseries_Basin_LONGITUDINALconnectivity |>
  ungroup()|>  
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Basin_LONGITUDINALconnectivity <- bind_cols(Condition_Basin_LONGITUDINALconnectivity, Trend_Basin_LONGITUDINALconnectivity)
Condition_Trend_Basin_LONGITUDINALconnectivity$Indicator <- "Longitudinal connectivity" 
Condition_Trend_Basin_LONGITUDINALconnectivity$Label <- "Longitudinal connectivity (EWR achieved)" 
Condition_Trend_Basin_LONGITUDINALconnectivity$Scale <- "Basin" 


# done up to here.


#REDGUM
Timeseries_Valley_REDGUM <- Timeseries_Valley_REDGUM |>
  ungroup()|>
  #Total 
  group_by(stage)|>
  mutate(Outcome_TotalScaled  = (area-min(area))/(max(area)-min(area))) |>  
  mutate(Outcome_TotalScaled  = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Obs
  group_by(stage, ValleyName)|>
  mutate(Outcome_ObsScaled    = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_ObsScaled    = ifelse(is.nan(Outcome_ObsScaled), 0, Outcome_ObsScaled)) |>
  #YrType
  group_by(stage, ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) |>  
  #IS
  mutate(Outcome_IS = (Outcome_TotalScaled*0.3)+ (Outcome_ObsScaled*0.4)+ (Outcome_YrTypeScaled*0.3))

#   #CS
# Timeseries_Valley_REDGUMcs <- Timeseries_Valley_REDGUM|>
#   select(stage, ValleyName, geometry, year, Climate_Category, Outcome_IS)|>
#   pivot_wider(names_from = stage, values_from = Outcome_IS) |>
#   mutate(Outcome_CS = (germ_and_seed*0.5)+(adult*0.5))

Timeseries_Basin_REDGUM <- Timeseries_Basin_REDGUM |>
  ungroup()|>
  #Obs 
  group_by(stage)|>
  mutate(Outcome_ObsScaled    = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_ObsScaled    = ifelse(is.nan(Outcome_ObsScaled), 0, Outcome_ObsScaled)) |>  
  #YrType
  group_by(stage, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) |>  
  #IS
  mutate(Outcome_IS = (Outcome_ObsScaled*0.5)+ (Outcome_YrTypeScaled*0.5))

#   #CS
# Timeseries_Basin_REDGUMcs <- Timeseries_Basin_REDGUM|>
#   select(stage, geometry, year, Climate_Category, Outcome_IS)|>
#   pivot_wider(names_from = stage, values_from = Outcome_IS) |>
#   mutate(Outcome_CS = (germ_and_seed*0.5)+(adult*0.5))


#LIGNUM
Timeseries_Valley_LIGNUM <- Timeseries_Valley_LIGNUM |>
  ungroup()|>
  #Total 
  group_by(stage)|>
  mutate(Outcome_TotalScaled  = (area-min(area))/(max(area)-min(area))) |>  
  mutate(Outcome_TotalScaled  = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Obs
  group_by(stage, ValleyName)|>
  mutate(Outcome_ObsScaled    = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_ObsScaled    = ifelse(is.nan(Outcome_ObsScaled), 0, Outcome_ObsScaled)) |>
  #YrType
  group_by(stage, ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) |>  
  #IS
  mutate(Outcome_IS = (Outcome_TotalScaled*0.3)+ (Outcome_ObsScaled*0.4)+ (Outcome_YrTypeScaled*0.3))

#   #CS
# Timeseries_Valley_LIGNUMcs <- Timeseries_Valley_LIGNUM|>
#   select(stage, ValleyName, geometry, year, Climate_Category, Outcome_IS)|>
#   pivot_wider(names_from = stage, values_from = Outcome_IS) |>
#   mutate(Outcome_CS = (germ_and_seed*0.5)+(adult*0.5))

Timeseries_Basin_LIGNUM <- Timeseries_Basin_LIGNUM |>
  ungroup()|>
  #Obs 
  group_by(stage)|>
  mutate(Outcome_ObsScaled    = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_ObsScaled    = ifelse(is.nan(Outcome_ObsScaled), 0, Outcome_ObsScaled)) |>  
  #YrType
  group_by(stage, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) |>  
  #IS
  mutate(Outcome_IS = (Outcome_ObsScaled*0.5)+ (Outcome_YrTypeScaled*0.5))

#   #CS
# Timeseries_Basin_LIGNUMcs <- Timeseries_Basin_LIGNUM|>
#   select(stage, geometry, year, Climate_Category, Outcome_IS)|>
#   pivot_wider(names_from = stage, values_from = Outcome_IS) |>
#   mutate(Outcome_CS = (germ_and_seed*0.5)+(adult*0.5))

#COOLABAH
Timeseries_Valley_COOLABAH <- Timeseries_Valley_COOLABAH |>
  ungroup()|>
  #Total 
  group_by(stage)|>
  mutate(Outcome_TotalScaled  = (area-min(area))/(max(area)-min(area))) |>  
  mutate(Outcome_TotalScaled  = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Obs
  group_by(stage, ValleyName)|>
  mutate(Outcome_ObsScaled    = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_ObsScaled    = ifelse(is.nan(Outcome_ObsScaled), 0, Outcome_ObsScaled)) |>
  #YrType
  group_by(stage, ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) |>  
  #IS
  mutate(Outcome_IS = (Outcome_TotalScaled*0.3)+ (Outcome_ObsScaled*0.4)+ (Outcome_YrTypeScaled*0.3))

#   #CS
# Timeseries_Valley_COOLABAHcs <- Timeseries_Valley_COOLABAH|>
#   select(stage, ValleyName, geometry, year, Climate_Category, Outcome_IS)|>
#   pivot_wider(names_from = stage, values_from = Outcome_IS) |>
#   mutate(Outcome_CS = (germ_and_seed*0.5)+(adult*0.5))

Timeseries_Basin_COOLABAH <- Timeseries_Basin_COOLABAH |>
  ungroup()|>
  #Obs 
  group_by(stage)|>
  mutate(Outcome_ObsScaled    = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_ObsScaled    = ifelse(is.nan(Outcome_ObsScaled), 0, Outcome_ObsScaled)) |>  
  #YrType
  group_by(stage, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (area-min(area))/(max(area)-min(area))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) |>  
  #IS
  mutate(Outcome_IS = (Outcome_ObsScaled*0.5)+ (Outcome_YrTypeScaled*0.5))

#   #CS
# Timeseries_Basin_COOLABAHcs <- Timeseries_Basin_COOLABAH|>
#   select(stage, geometry, year, Climate_Category, Outcome_IS)|>
#   pivot_wider(names_from = stage, values_from = Outcome_IS) |>
#   mutate(Outcome_CS = (germ_and_seed*0.5)+(adult*0.5))


```

## Add geometry 

```{r}
#LATERALconnectivity
Timeseries_Valley_LATERALconnectivity <- left_join(Timeseries_Valley_LATERALconnectivity, cewo_valleys, by = join_by(ValleyName))

Timeseries_Basin_LATERALconnectivity$geometry <- basin$geometry

#LONGITUDINALconnectivity
Timeseries_Valley_LONGITUDINALconnectivity <- left_join(Timeseries_Valley_LONGITUDINALconnectivity, cewo_valleys, by = join_by(ValleyName))

Timeseries_Basin_LONGITUDINALconnectivity$geometry <- basin$geometry

```


```{r}
#Data with climate categories attached or attach here
Timeseries_Valley_LATERALconnectivity$Indicator <- "LATERALconnectivity"
Timeseries_Valley_LONGITUDINALconnectivity$Indicator <-  "LONGITUDINALconnectivity"
Timeseries_Valley_ANAEdiversity$Indicator <- "ANAEdiversity"
Timeseries_Valley_BLACKBOX$Indicator <- paste("BLACKBOX", Timeseries_Valley_BLACKBOX$stage, sep = "")
Timeseries_Valley_REDGUM$Indicator <- paste("REDGUM", Timeseries_Valley_REDGUM$stage, sep = "")
Timeseries_Valley_LIGNUM$Indicator <- paste("LIGNUM", Timeseries_Valley_LIGNUM$stage, sep = "")
Timeseries_Valley_COOLABAH$Indicator <- paste("COOLABAH", Timeseries_Valley_COOLABAH$stage, sep = "")

All_indicators <- bind_rows(Timeseries_Valley_LATERALconnectivity, Timeseries_Valley_LONGITUDINALconnectivity)
#All_indicators <-  bind_rows(All_indicators, Timeseries_Valley_ANAEdiversity)
All_indicators <-  bind_rows(Timeseries_Valley_ANAEdiversity, Timeseries_Valley_BLACKBOX)
All_indicators <-  bind_rows(All_indicators, Timeseries_Valley_REDGUM)
All_indicators <-  bind_rows(All_indicators, Timeseries_Valley_LIGNUM)
All_indicators <-  bind_rows(All_indicators, Timeseries_Valley_COOLABAH)
#All_indicators <-  bind_rows(All_indicators, Timeseries_Valley_LATERALconnectivity)
# All_indicators <-  bind_rows(All_indicators, Timeseries_Valley_LONGITUDINALconnectivity)


```

```{r}
max(All_indicators$year, rm.na = TRUE)

All_indicators_summary <- All_indicators |>
  group_by(ValleyName, Indicator)|>
  filter(year %in% c(2022:2018))|>
  reframe(Outcome_TotalScaled = weighted.mean(Outcome_TotalScaled, year),
          Outcome_BasScaled = weighted.mean(Outcome_BasScaled, year),
          Outcome_ObsScaled  = weighted.mean(Outcome_ObsScaled, year),
          Outcome_YrTypeScaled  = weighted.mean(Outcome_YrTypeScaled, year))

All_indicators_summary <- All_indicators_summary|>
  group_by(Indicator)|>
  pivot_longer(cols = Outcome_TotalScaled:Outcome_YrTypeScaled)

```

```{r}

Tile_plot1 <- ggplot(data = filter(All_indicators_summary, ValleyName == "Avoca"), 
       aes(x = name, y = Indicator, fill = value))+
  geom_tile()+
  #scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Indicator")+
  theme(axis.text.x = element_text(angle = 90))

Tile_plot1

ggsave(plot = Tile_plot1, filename = file.path(plot_path, paste0("Tile_plot_AVOCA", Sys.Date(), ".tiff")), device = "tiff",
       width = 4, height = 8)



Tile_plot2 <- ggplot(data = filter(All_indicators_summary, Indicator == "ANAEdiversity"), 
       aes(x = name, y = ValleyName, fill = value))+
  geom_tile()+
  #scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Indicator")+
  theme(axis.text.x = element_text(angle = 90))

Tile_plot2

ggsave(plot = Tile_plot2, filename = file.path(plot_path, paste0("Tile_plot_ANAEdiversity", Sys.Date(), ".tiff")), device = "tiff",
       width = 4, height = 8)

```


## Stepping through scaling

with one example

```{r}
Plot_Timeseries_Basin_LATERAL_IS1 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = ewr_achieved))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(EWR achieved)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS2 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_TotalScaled))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(TotalRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS3 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_ObsScaled))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(ObsRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS4 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_YrTypeScaled))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(YrTypeRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS5 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

IS_example_plot <- Plot_Timeseries_Basin_LATERAL_IS1 +
  Plot_Timeseries_Basin_LATERAL_IS2 +
  Plot_Timeseries_Basin_LATERAL_IS3 +
  Plot_Timeseries_Basin_LATERAL_IS4 +
  Plot_Timeseries_Basin_LATERAL_IS5 + plot_layout(ncol = 2, guides = "collect")

ggsave(plot = IS_example_plot, filename = file.path(plot_path, paste0("IS_example_plot_LATERALconnectivity_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)
```

## SUGGESTED

add current condition and trend to left hand corner ? lines for year type mean? (some kind of range 95%ile?)
Condition = yr type scaled. = good fair poor

Fit spline with 1) all data and 2) all data excluding post BP - amiar?


```{r}
#BASIN
temp <- Timeseries_Basin_LATERALconnectivity |>
  group_by(Climate_Category)|>
  reframe(Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
          Outcome_ObsScaled_mean = mean(Outcome_ObsScaled), 
          Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
          
          Outcome_TotalScaled_25 = quantile(Outcome_TotalScaled, probs = c(0.25)),
          Outcome_ObsScaled_25 = quantile(Outcome_ObsScaled, probs = c(0.25)), 
          Outcome_YrTypeScaled_25 = quantile(Outcome_YrTypeScaled, probs = c(0.25)),
          
          Outcome_TotalScaled_75 = quantile(Outcome_TotalScaled, probs = c(0.75)),
          Outcome_ObsScaled_75 = quantile(Outcome_ObsScaled, probs = c(0.75)), 
          Outcome_YrTypeScaled_75 = quantile(Outcome_YrTypeScaled, probs = c(0.75))
          
          )|>
  filter(!is.na(Climate_Category))

#Map Pre and Post basin plan
temp2 <- Timeseries_Basin_LATERALconnectivity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) 

temp3 <- temp2|> 
  group_by(timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS),
          Outcome_YrTypeScaled = mean(Outcome_YrTypeScaled),
          year = max(year))  

Current_trend <- temp3$Outcome_YrTypeScaled[2] - temp3$Outcome_YrTypeScaled[1]

temp4 <- temp2 |>
  group_by(timeperiod)|>
  filter(timeperiod != "other")|>
  mutate(year = max(year))


Model <- lm(Outcome_YrTypeScaled ~ year, data = temp2, conf.int = TRUE)
Model$coefficients[2]
summary(Model)
confint(Model)


filter(temp2, timeperiod == 'Pre-BP')
filter(temp2, timeperiod == 'Current')

# temp2 |>
#   group_by(timeperiod)|>
#   reframe

CurrentYear <- Timeseries_Basin_LATERALconnectivity |>
  filter(year == 2022)

Current5Years <- Timeseries_Basin_LATERALconnectivity |>
  ungroup()|>
  filter(year %in% c(2019, 2020, 2021, 2022, 2023))

Confidence <- t.test(Current5Years$Outcome_YrTypeScaled)
Confidence$conf.int


t.test(Current5Years$Outcome_YrTypeScaled ~ 1)
t.test(Current5Years$Outcome_YrTypeScaled, rep(0.92, time = 5))

predict()

Condition <- data.frame(
  Label_type = c("Current_condition", "YrType_condition", "Optimum_condition", "Trend_5yr", "Trend_uncertainty"),
  Label_text = c(paste("Current condition = ", round(CurrentYear$Outcome_TotalScaled, 2)*100, "% ", "(74-100)", sep = ""),
                 paste("Very good for a wet year (medium confidence)", sep = ""), 
                 #paste("Very good within the basin (medium confidence)", sep = ""), 
                 paste("Very good compared to optimum (medium confidence)", sep = ""), 
                 paste("Trend = ", "0.028 (-0.010 - 0.067)", sep = ""),
                 paste("Improving (high confidence)", sep = "")),
  vjustvar = c(1,2,3,4,5), #<- adjust
  Label_colour = c("very high","high","high","very high", "very high"))
  Condition$xpos = -Inf
  Condition$ypos = Inf
  Condition$hjustvar = 0 

  
  #c("very low", "Low", "medium", "high", "very high"))
#class(Condition$Label_colour) <- 'colors'


Plot_Timeseries_Basin_LATERAL_IS6 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_ObsScaled))+
  
  geom_rect(xmin = lubridate::year(currenttimestart), xmax = lubridate::year(currenttimeend), ymin = 0, ymax = 1, fill= "beige") +
  geom_rect(xmin = lubridate::year(preBPtimestart), xmax = lubridate::year(preBPtimeend), ymin = 0, ymax = 1, fill= "beige") +
    
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_25, colour = Climate_Category), linetype = "solid", alpha = 0.5)+
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_75, colour = Climate_Category), linetype = "longdash", alpha = 0.5)+
  geom_line(colour = "grey80")+
  geom_label(data = Condition, aes(x = xpos, y = ypos, label=Label_text, hjust=hjustvar, vjust=vjustvar, fill = Label_colour), label.r = unit(0, "pt"))+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  geom_point(data = CurrentYear, aes(x = year, y = Outcome_ObsScaled, colour = Climate_Category), size = 5)+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  #geom_smooth(data = filter(Timeseries_Basin_LATERALconnectivity, !is.na(Climate_Category)), aes(colour = Climate_Category), linewidth = 0.5, se = FALSE)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(ObsRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)+
  geom_vline(xintercept = 2008, linetype = "solid")+
geom_line(data = temp3, aes(x = year, y = Outcome_YrTypeScaled))+
scale_fill_manual(values = pal_score, aesthetics = "fill", guide = "none") 


Plot_Timeseries_Basin_LATERAL_IS6

ggsave(plot = Plot_Timeseries_Basin_LATERAL_IS6, filename = file.path(plot_path, paste0("SUGGESTED_plot_Basin_LATERALconnectivity_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 6)

```
```{r}
BD_data <- Timeseries_Valley_LATERALconnectivity|>
  filter(ValleyName == "Barwon Darling")

temp <- BD_data |>
  group_by(Climate_Category)|>
  reframe(Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
          Outcome_BasScaled_mean = mean(Outcome_BasScaled), 
          Outcome_ObsScaled_mean = mean(Outcome_ObsScaled), 
          Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
          
          Outcome_TotalScaled_25 = quantile(Outcome_TotalScaled, probs = c(0.25)),
          Outcome_ObsScaled_25 = quantile(Outcome_ObsScaled, probs = c(0.25)), 
          Outcome_YrTypeScaled_25 = quantile(Outcome_YrTypeScaled, probs = c(0.25)),
          
          Outcome_TotalScaled_75 = quantile(Outcome_TotalScaled, probs = c(0.75)),
          Outcome_ObsScaled_75 = quantile(Outcome_ObsScaled, probs = c(0.75)), 
          Outcome_YrTypeScaled_75 = quantile(Outcome_YrTypeScaled, probs = c(0.75))
          
          )|>
  filter(!is.na(Climate_Category))

#Map Pre and Post basin plan
temp2 <- BD_data |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) 

temp3 <- temp2|> 
  group_by(timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS),
          Outcome_YrTypeScaled = mean(Outcome_YrTypeScaled),
          year = max(year))  

Current_trend <- temp3$Outcome_YrTypeScaled[2] - temp3$Outcome_YrTypeScaled[1]

temp4 <- temp2 |>
  group_by(timeperiod)|>
  filter(timeperiod != "other")|>
  mutate(year = max(year))


Model <- lm(Outcome_YrTypeScaled ~ year, data = temp2, conf.int = TRUE)
Model$coefficients[2]
summary(Model)
confint(Model)


filter(temp2, timeperiod == 'Pre-BP')
filter(temp2, timeperiod == 'Current')

# temp2 |>
#   group_by(timeperiod)|>
#   reframe

CurrentYear <- BD_data |>
  filter(year == 2022)


Timeseries_Valley_LATERALconnectivity |>
  filter(ValleyName == "Barwon Darling")|>
  filter(year == 2022)

Current5Years <- BD_data |>
  ungroup()|>
  filter(year %in% c(2019, 2020, 2021, 2022, 2023))

Confidence <- t.test(Current5Years$Outcome_YrTypeScaled)
Confidence$conf.int


t.test(Current5Years$Outcome_YrTypeScaled ~ 1)
t.test(Current5Years$Outcome_YrTypeScaled, rep(0.92, time = 5))

#predict()

Condition <- data.frame(
  Label_type = c("Current_condition", "YrType_condition", "Basin_condition",  "Optimum_condition", "Trend_5yr", "Trend_uncertainty"),
  Label_text = c(paste("Current condition = ", round(CurrentYear$Outcome_TotalScaled, 2)*100, "% ", "(67-94)", sep = ""),
                 paste("good for a wet year (medium confidence)", sep = ""), 
                 paste("good within the basin (medium confidence)", sep = ""), 
                 paste("good compared to optimum (medium confidence)", sep = ""), 
                 paste("Trend = ", "-0.017 (-0.027 - -0.008)", sep = ""),
                 paste("Declining (very high confidence)", sep = "")),
  vjustvar = c(1,2,3,4,5,6), #<- adjust
  Label_colour = c("high","high","high","high","very low", "very low"))
  Condition$xpos = -Inf
  Condition$ypos = Inf
  Condition$hjustvar = 0 

  
  #c("very low", "Low", "medium", "high", "very high"))
#class(Condition$Label_colour) <- 'colors'


Plot_Timeseries_BD_LATERAL_IS6<- ggplot(data = BD_data, 
       aes(x = year, y = Outcome_ObsScaled))+
  
  geom_rect(xmin = lubridate::year(currenttimestart), xmax = lubridate::year(currenttimeend), ymin = 0, ymax = 1, fill= "beige") +
  geom_rect(xmin = lubridate::year(preBPtimestart), xmax = lubridate::year(preBPtimeend), ymin = 0, ymax = 1, fill= "beige") +
    
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_25, colour = Climate_Category), linetype = "solid", alpha = 0.5)+
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_75, colour = Climate_Category), linetype = "longdash", alpha = 0.5)+
  geom_line(colour = "grey80")+
  geom_label(data = Condition, aes(x = xpos, y = ypos, label=Label_text, hjust=hjustvar, vjust=vjustvar, fill = Label_colour), label.r = unit(0, "pt"))+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  geom_point(data = CurrentYear, aes(x = year, y = Outcome_ObsScaled, colour = Climate_Category), size = 5)+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  #geom_smooth(data = filter(Timeseries_Basin_LATERALconnectivity, !is.na(Climate_Category)), aes(colour = Climate_Category), linewidth = 0.5, se = FALSE)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(ObsRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)+
  facet_wrap(~ValleyName)+
  geom_vline(xintercept = 2008, linetype = "solid")+
geom_line(data = temp3, aes(x = year, y = Outcome_YrTypeScaled))+
scale_fill_manual(values = pal_score, aesthetics = "fill", guide = "none") 


Plot_Timeseries_BD_LATERAL_IS6

ggsave(plot = Plot_Timeseries_BD_LATERAL_IS6, filename = file.path(plot_path, paste0("SUGGESTED_plot_BD_LATERALconnectivity_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 6)
```


## Stepping through combining ISs

```{r}
Plot_Timeseries_Basin_BLACKBOX1 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = germ))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box germination IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX2 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = seed))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box seedling IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX3 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = germ_and_seed))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box gemination and seedling IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX4 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = adult))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box adult IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX5 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

CS_example_plot <- Plot_Timeseries_Basin_BLACKBOX1 +
  Plot_Timeseries_Basin_BLACKBOX2 +
  Plot_Timeseries_Basin_BLACKBOX3 +
  Plot_Timeseries_Basin_BLACKBOX4 +
  Plot_Timeseries_Basin_BLACKBOX5 + plot_layout(ncol = 2, guides = "collect")

CS_example_plot

ggsave(plot = CS_example_plot, filename = file.path(plot_path, paste0("CS_example_plot_BLACKBOX_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)
```

## LATERALconnectivity - Valley

i dont seem to have gauges in the: "Avoca"        "Kiewa"        "Mitta Mitta"  "Upper Murray" "Wimmera" 

```{r}
#Timeseries
Plot_Timeseries_Valley_LATERALconnectivity <- ggplot(data = Timeseries_Valley_LATERALconnectivity, aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Valley_LATERALconnectivity

ggsave(plot = Plot_Timeseries_Valley_LATERALconnectivity, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_LATERALconnectivity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_LATERALconnectivity <- ggplot(data = Timeseries_Valley_LATERALconnectivity, 
       aes(x = Climate_Category, y = Outcome_IS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_LATERALconnectivity

ggsave(plot = Boxplot_Timeseries_Valley_LATERALconnectivity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories 
#NEED TO JOIN GEOMETRY
Tagg_ClimCats_Valley_LATERALconnectivity <- Timeseries_Valley_LATERALconnectivity|>
  group_by(ValleyName, geometry, Climate_Category)|>
  reframe(Outcome_IS = weighted.mean(Outcome_IS, year))


Map_Tagg_ClimCats_Valley_LATERALconnectivity <- ggplot(data = Tagg_ClimCats_Valley_LATERALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Lateral connectivity IS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_LATERALconnectivity

ggsave(plot = Map_Tagg_ClimCats_Valley_LATERALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_LATERALconnectivity <- Timeseries_Valley_LATERALconnectivity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS))

Map_Tagg_PrePostBP_Valley_LATERALconnectivity <- ggplot(data = Tagg_PrePostBP_Valley_LATERALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1), na.value="white") +
  labs(fill = "Lateral connectivity IS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_LATERALconnectivity

ggsave(plot = Map_Tagg_PrePostBP_Valley_LATERALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## LATERALconnectivity - Basin

```{r}
#Timeseries
Plot_Timeseries_Basin_LATERALconnectivity <- ggplot(data = Timeseries_Basin_LATERALconnectivity, aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERALconnectivity

ggsave(plot = Plot_Timeseries_Basin_LATERALconnectivity, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_LATERALconnectivity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_LATERALconnectivity <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = Climate_Category, y = Outcome_IS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Basin_LATERALconnectivity

ggsave(plot = Boxplot_Timeseries_Basin_LATERALconnectivity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_LATERALconnectivity <- Timeseries_Basin_LATERALconnectivity|>
  group_by(Climate_Category, geometry)|>
  reframe(Outcome_IS = weighted.mean(Outcome_IS, year))

Map_Tagg_ClimCats_Basin_LATERALconnectivity <- ggplot(data = Tagg_ClimCats_Basin_LATERALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Lateral connectivity IS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_LATERALconnectivity

ggsave(plot = Map_Tagg_ClimCats_Basin_LATERALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_LATERALconnectivity <- Timeseries_Basin_LATERALconnectivity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod, geometry) |>
  reframe(Outcome_IS = mean(Outcome_IS))

Map_Tagg_PrePostBP_Basin_LATERALconnectivity <- ggplot(data = Tagg_PrePostBP_Basin_LATERALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Lateral connectivity IS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_LATERALconnectivity

ggsave(plot = Map_Tagg_PrePostBP_Basin_LATERALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## LONGITUDINALconnectivity - Valley

```{r}
#Timeseries
Plot_Timeseries_Valley_LONGITUDINALconnectivity <- ggplot(data = Timeseries_Valley_LONGITUDINALconnectivity, aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Longitudinal connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Valley_LONGITUDINALconnectivity

ggsave(plot = Plot_Timeseries_Valley_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_LONGITUDINALconnectivity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_LONGITUDINALconnectivity <- ggplot(data = Timeseries_Valley_LONGITUDINALconnectivity, 
       aes(x = Climate_Category, y = Outcome_IS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Longitudinal connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_LONGITUDINALconnectivity

ggsave(plot = Boxplot_Timeseries_Valley_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_LONGITUDINALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Valley_LONGITUDINALconnectivity <- Timeseries_Valley_LONGITUDINALconnectivity|>
  group_by(ValleyName, Climate_Category, geometry)|>
  reframe(Outcome_IS = weighted.mean(Outcome_IS, year))

Map_Tagg_ClimCats_Valley_LONGITUDINALconnectivity <- ggplot(data = Tagg_ClimCats_Valley_LONGITUDINALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Longitudinal connectivity IS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_LONGITUDINALconnectivity

ggsave(plot = Map_Tagg_ClimCats_Valley_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_LONGITUDINALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_LONGITUDINALconnectivity <- Timeseries_Valley_LONGITUDINALconnectivity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS))

Map_Tagg_PrePostBP_Valley_LONGITUDINALconnectivity <- ggplot(data = Tagg_PrePostBP_Valley_LONGITUDINALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Longitudinal connectivity IS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_LONGITUDINALconnectivity

ggsave(plot = Map_Tagg_PrePostBP_Valley_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_LONGITUDINALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## LONGITUDINALconnectivity - Basin

```{r}
#Timeseries
Plot_Timeseries_Basin_LONGITUDINALconnectivity <- ggplot(data = Timeseries_Basin_LONGITUDINALconnectivity, aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Longitudinal connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LONGITUDINALconnectivity

ggsave(plot = Plot_Timeseries_Basin_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_LONGITUDINALconnectivity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_LONGITUDINALconnectivity <- ggplot(data = Timeseries_Basin_LONGITUDINALconnectivity, 
       aes(x = Climate_Category, y = Outcome_IS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Longitudinal connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Basin_LONGITUDINALconnectivity

ggsave(plot = Boxplot_Timeseries_Basin_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_LONGITUDINALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_LONGITUDINALconnectivity <- Timeseries_Basin_LONGITUDINALconnectivity|>
  group_by(Climate_Category)|>
  reframe(Outcome_IS = weighted.mean(Outcome_IS, year))
Tagg_ClimCats_Basin_LONGITUDINALconnectivity$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_LONGITUDINALconnectivity <- ggplot(data = Tagg_ClimCats_Basin_LONGITUDINALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Longitudinal connectivity IS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_LONGITUDINALconnectivity

ggsave(plot = Map_Tagg_ClimCats_Basin_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_LONGITUDINALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_LONGITUDINALconnectivity <- Timeseries_Basin_LONGITUDINALconnectivity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS))
Tagg_PrePostBP_Basin_LONGITUDINALconnectivity$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_LONGITUDINALconnectivity <- ggplot(data = Tagg_PrePostBP_Basin_LONGITUDINALconnectivity,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Longitudinal connectivity IS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_LONGITUDINALconnectivity

ggsave(plot = Map_Tagg_PrePostBP_Basin_LONGITUDINALconnectivity, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_LONGITUDINALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## ANAEdiversity - Valley

```{r}
#Timeseries
Plot_Timeseries_Valley_ANAEdiversity <- ggplot(data = Timeseries_Valley_ANAEdiversity, aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "ANAE diversity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)#+ 
  #xlim(1900,NA)

Plot_Timeseries_Valley_ANAEdiversity

ggsave(plot = Plot_Timeseries_Valley_ANAEdiversity, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_ANAEdiversity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_ANAEdiversity <- ggplot(data = Timeseries_Valley_ANAEdiversity, 
       aes(x = Climate_Category, y = Outcome_IS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "ANAE diversity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_ANAEdiversity

ggsave(plot = Boxplot_Timeseries_Valley_ANAEdiversity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_ANAEdiversity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity|>
  group_by(ValleyName, Climate_Category, geometry)|>
  reframe(Outcome_IS = weighted.mean(Outcome_IS, year))

Map_Tagg_ClimCats_Valley_ANAEdiversity <- ggplot(data = Tagg_ClimCats_Valley_ANAEdiversity,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "ANAE diversity IS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_ANAEdiversity

ggsave(plot = Map_Tagg_ClimCats_Valley_ANAEdiversity, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_ANAEdiversity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS))

Map_Tagg_PrePostBP_Valley_ANAEdiversity <- ggplot(data = Tagg_PrePostBP_Valley_ANAEdiversity,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "ANAE diversity IS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_ANAEdiversity

ggsave(plot = Map_Tagg_PrePostBP_Valley_ANAEdiversity, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_ANAEdiversity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## ANAEdiversity - Basin

```{r}
#Timeseries
Plot_Timeseries_Basin_ANAEdiversity <- ggplot(data = Timeseries_Basin_ANAEdiversity, aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "ANAE diversity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)#+ 
  #xlim(1900,NA)

Plot_Timeseries_Basin_ANAEdiversity

ggsave(plot = Plot_Timeseries_Basin_ANAEdiversity, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_ANAEdiversity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_ANAEdiversity <- ggplot(data = Timeseries_Basin_ANAEdiversity, 
       aes(x = Climate_Category, y = Outcome_IS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "ANAE diversity IS")+
  theme(axis.text.x = element_text(angle = 90))#+
  #ylim(0,1)

Boxplot_Timeseries_Basin_ANAEdiversity

ggsave(plot = Boxplot_Timeseries_Basin_ANAEdiversity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_ANAEdiversity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity|>
  group_by(Climate_Category)|>
  reframe(Outcome_IS = weighted.mean(Outcome_IS, year))
Tagg_ClimCats_Basin_ANAEdiversity$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_ANAEdiversity <- ggplot(data = Tagg_ClimCats_Basin_ANAEdiversity,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "ANAE diversity IS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_ANAEdiversity

ggsave(plot = Map_Tagg_ClimCats_Basin_ANAEdiversity, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_ANAEdiversity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS))
Tagg_PrePostBP_Basin_ANAEdiversity$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_ANAEdiversity <- ggplot(data = Tagg_PrePostBP_Basin_ANAEdiversity,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_IS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "ANAE diversity IS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_ANAEdiversity

ggsave(plot = Map_Tagg_PrePostBP_Basin_ANAEdiversity, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_ANAEdiversity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## BLACKBOX CS - Valley

```{r}
#Timeseries
Plot_Timeseries_Valley_BLACKBOX <- ggplot(data = Timeseries_Valley_BLACKBOXcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Valley_BLACKBOX

ggsave(plot = Plot_Timeseries_Valley_BLACKBOX, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_BLACKBOX", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_BLACKBOX <- ggplot(data = Timeseries_Valley_BLACKBOXcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_BLACKBOX

ggsave(plot = Boxplot_Timeseries_Valley_BLACKBOX, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_BLACKBOX","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Valley_BLACKBOXcs <- Timeseries_Valley_BLACKBOXcs|>
  group_by(ValleyName, Climate_Category, geometry)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))

Map_Tagg_ClimCats_Valley_BLACKBOX <- ggplot(data = Tagg_ClimCats_Valley_BLACKBOXcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_BLACKBOX

ggsave(plot = Map_Tagg_ClimCats_Valley_BLACKBOX, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_BLACKBOX","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_BLACKBOXcs <- Timeseries_Valley_BLACKBOXcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))

Map_Tagg_PrePostBP_Valley_BLACKBOX <- ggplot(data = Tagg_PrePostBP_Valley_BLACKBOXcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_BLACKBOX

ggsave(plot = Map_Tagg_PrePostBP_Valley_BLACKBOX, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_BLACKBOX","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## BLACKBOX CS - Basin

```{r}
#Timeseries
Plot_Timeseries_Basin_BLACKBOX <- ggplot(data = Timeseries_Basin_BLACKBOXcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Basin_BLACKBOX

ggsave(plot = Plot_Timeseries_Basin_BLACKBOX, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_BLACKBOX", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_BLACKBOX <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Basin_BLACKBOX

ggsave(plot = Boxplot_Timeseries_Basin_BLACKBOX, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_BLACKBOX","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_BLACKBOXcs <- Timeseries_Basin_BLACKBOXcs|>
  group_by(Climate_Category)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))
Tagg_ClimCats_Basin_BLACKBOXcs$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_BLACKBOX <- ggplot(data = Tagg_ClimCats_Basin_BLACKBOXcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_BLACKBOX

ggsave(plot = Map_Tagg_ClimCats_Basin_BLACKBOX, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_BLACKBOX","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_BLACKBOXcs <- Timeseries_Basin_BLACKBOXcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))
Tagg_PrePostBP_Basin_BLACKBOXcs$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_BLACKBOX <- ggplot(data = Tagg_PrePostBP_Basin_BLACKBOXcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_BLACKBOX

ggsave(plot = Map_Tagg_PrePostBP_Basin_BLACKBOX, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_BLACKBOX","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## REDGUM CS - Valley
 
```{r}
#Timeseries
Plot_Timeseries_Valley_REDGUM <- ggplot(data = Timeseries_Valley_REDGUMcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Valley_REDGUM

ggsave(plot = Plot_Timeseries_Valley_REDGUM, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_REDGUM", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_REDGUM <- ggplot(data = Timeseries_Valley_REDGUMcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_REDGUM

ggsave(plot = Boxplot_Timeseries_Valley_REDGUM, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_REDGUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Valley_REDGUMcs <- Timeseries_Valley_REDGUMcs|>
  group_by(ValleyName, Climate_Category, geometry)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))

Map_Tagg_ClimCats_Valley_REDGUM <- ggplot(data = Tagg_ClimCats_Valley_REDGUMcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_REDGUM

ggsave(plot = Map_Tagg_ClimCats_Valley_REDGUM, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_REDGUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_REDGUMcs <- Timeseries_Valley_REDGUMcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))

Map_Tagg_PrePostBP_Valley_REDGUM <- ggplot(data = Tagg_PrePostBP_Valley_REDGUMcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_REDGUM

ggsave(plot = Map_Tagg_PrePostBP_Valley_REDGUM, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_REDGUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## REDGUM CS - Basin
 
```{r}
#Timeseries
Plot_Timeseries_Basin_REDGUM <- ggplot(data = Timeseries_Basin_REDGUMcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Basin_REDGUM

ggsave(plot = Plot_Timeseries_Basin_REDGUM, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_REDGUM", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_REDGUM <- ggplot(data = Timeseries_Basin_REDGUMcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Basin_REDGUM

ggsave(plot = Boxplot_Timeseries_Basin_REDGUM, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_REDGUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_REDGUMcs <- Timeseries_Basin_REDGUMcs|>
  group_by(Climate_Category)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))
Tagg_ClimCats_Basin_REDGUMcs$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_REDGUM <- ggplot(data = Tagg_ClimCats_Basin_REDGUMcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_REDGUM

ggsave(plot = Map_Tagg_ClimCats_Basin_REDGUM, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_REDGUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_REDGUMcs <- Timeseries_Basin_REDGUMcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))
Tagg_PrePostBP_Basin_REDGUMcs$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_REDGUM <- ggplot(data = Tagg_PrePostBP_Basin_REDGUMcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_REDGUM

ggsave(plot = Map_Tagg_PrePostBP_Basin_REDGUM, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_REDGUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## LIGNUM CS - Valley
 
```{r}
#Timeseries
Plot_Timeseries_Valley_LIGNUM <- ggplot(data = Timeseries_Valley_LIGNUMcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Valley_LIGNUM

ggsave(plot = Plot_Timeseries_Valley_LIGNUM, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_LIGNUM", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_LIGNUM <- ggplot(data = Timeseries_Valley_LIGNUMcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_LIGNUM

ggsave(plot = Boxplot_Timeseries_Valley_LIGNUM, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_LIGNUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Valley_LIGNUMcs <- Timeseries_Valley_LIGNUMcs|>
  group_by(ValleyName, Climate_Category, geometry)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))

Map_Tagg_ClimCats_Valley_LIGNUM <- ggplot(data = Tagg_ClimCats_Valley_LIGNUMcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_LIGNUM

ggsave(plot = Map_Tagg_ClimCats_Valley_LIGNUM, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_LIGNUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_LIGNUMcs <- Timeseries_Valley_LIGNUMcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))

Map_Tagg_PrePostBP_Valley_LIGNUM <- ggplot(data = Tagg_PrePostBP_Valley_LIGNUMcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_LIGNUM

ggsave(plot = Map_Tagg_PrePostBP_Valley_LIGNUM, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_LIGNUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## LIGNUM CS - Basin
 
```{r}
#Timeseries
Plot_Timeseries_Basin_LIGNUM <- ggplot(data = Timeseries_Basin_LIGNUMcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Basin_LIGNUM

ggsave(plot = Plot_Timeseries_Basin_LIGNUM, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_LIGNUM", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_LIGNUM <- ggplot(data = Timeseries_Basin_LIGNUMcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Basin_LIGNUM

ggsave(plot = Boxplot_Timeseries_Basin_LIGNUM, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_LIGNUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_LIGNUMcs <- Timeseries_Basin_LIGNUMcs|>
  group_by(Climate_Category)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))
Tagg_ClimCats_Basin_LIGNUMcs$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_LIGNUM <- ggplot(data = Tagg_ClimCats_Basin_LIGNUMcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_LIGNUM

ggsave(plot = Map_Tagg_ClimCats_Basin_LIGNUM, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_LIGNUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_LIGNUMcs <- Timeseries_Basin_LIGNUMcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))
Tagg_PrePostBP_Basin_LIGNUMcs$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_LIGNUM <- ggplot(data = Tagg_PrePostBP_Basin_LIGNUMcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_LIGNUM

ggsave(plot = Map_Tagg_PrePostBP_Basin_LIGNUM, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_LIGNUM","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## COOLABAH CS - Valley
 
```{r}
#Timeseries
Plot_Timeseries_Valley_COOLABAH <- ggplot(data = Timeseries_Valley_COOLABAHcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Valley_COOLABAH

ggsave(plot = Plot_Timeseries_Valley_COOLABAH, filename = file.path(plot_path, paste0("Plot_Timeseries_Valley_COOLABAH", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 8)

#Boxplot
Boxplot_Timeseries_Valley_COOLABAH <- ggplot(data = Timeseries_Valley_COOLABAHcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Valley_COOLABAH

ggsave(plot = Boxplot_Timeseries_Valley_COOLABAH, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Valley_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Valley_COOLABAHcs <- Timeseries_Valley_COOLABAHcs|>
  group_by(ValleyName, Climate_Category, geometry)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))

Map_Tagg_ClimCats_Valley_COOLABAH <- ggplot(data = Tagg_ClimCats_Valley_COOLABAHcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Valley_COOLABAH

ggsave(plot = Map_Tagg_ClimCats_Valley_COOLABAH, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Valley_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Valley_COOLABAHcs <- Timeseries_Valley_COOLABAHcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(ValleyName, geometry, timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))

Map_Tagg_PrePostBP_Valley_COOLABAH <- ggplot(data = Tagg_PrePostBP_Valley_COOLABAHcs,  
       aes(geometry = geometry)) +
  geom_sf(data = cewo_valleys, aes(geometry = geometry), fill = NA)+
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Valley_COOLABAH

ggsave(plot = Map_Tagg_PrePostBP_Valley_COOLABAH, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Valley_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```

## COOLABAH CS - Basin
 
```{r}
#Timeseries
Plot_Timeseries_Basin_COOLABAH <- ggplot(data = Timeseries_Basin_COOLABAHcs, aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #facet_wrap(~ValleyName, scales = "free_y", ncol = 3)+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Timeseries_Basin_COOLABAH

ggsave(plot = Plot_Timeseries_Basin_COOLABAH, filename = file.path(plot_path, paste0("Plot_Timeseries_Basin_COOLABAH", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 6, height = 4)

#Boxplot
Boxplot_Timeseries_Basin_COOLABAH <- ggplot(data = Timeseries_Basin_COOLABAHcs, 
       aes(x = Climate_Category, y = Outcome_CS))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category.data, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Boxplot_Timeseries_Basin_COOLABAH

ggsave(plot = Boxplot_Timeseries_Basin_COOLABAH, filename = file.path(plot_path, paste0("Boxplot_Timeseries_Basin_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Climate Categories
Tagg_ClimCats_Basin_COOLABAHcs <- Timeseries_Basin_COOLABAHcs|>
  group_by(Climate_Category)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))
Tagg_ClimCats_Basin_COOLABAHcs$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_COOLABAH <- ggplot(data = Tagg_ClimCats_Basin_COOLABAHcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_COOLABAH

ggsave(plot = Map_Tagg_ClimCats_Basin_COOLABAH, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_COOLABAHcs <- Timeseries_Basin_COOLABAHcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))
Tagg_PrePostBP_Basin_COOLABAHcs$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_COOLABAH <- ggplot(data = Tagg_PrePostBP_Basin_COOLABAHcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_COOLABAH

ggsave(plot = Map_Tagg_PrePostBP_Basin_COOLABAH, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Trend
# TREND PLOT HERE
```




























