---
title: "SRA_analysis"
format: html
editor: visual
---

## Libraries/Paths/Functions

```{r}
#| include: false

library(CC2)
library(werptoolkitr)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)
library(foreach)

# get directories
source('directorySet.R')

#devtools::build("E:/Georgia/CC2")

catch_cat_sf <- function(which_strict, catchments = cleancatch, outerdir = 'hello') {
  foreach(i = catchments,
          .combine = dplyr::bind_rows,
          .multicombine = TRUE) %do% {
            thiscatch <- readRDS(file.path(datOut, outerdir, which_strict, 
                                           paste0(i, '_', which_strict, '.rds')))
          }
}  

calc_shan <- function(x) {
    px <- x/sum(x)
    shan <- -sum(px*log(px))
    return(shan)
}

# Need a clean name to bring in data
catchments <- ltimNoNorth |> 
   mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

cleancatch <- catchments$name_clean

# Making these up for now, we'll want to be consistent
currenttimestart <- lubridate::ymd('20190101')
currenttimeend <- lubridate::ymd('20240301')

preBPtimestart <- lubridate::ymd('20070101')
preBPtimeend <- lubridate::ymd('20120101')

comparison_years <- data.frame(timeperiod = c("pre-BP", "current"),
                               timestart = c(preBPtimestart, currenttimestart),
                               timeend = c(preBPtimeend, currenttimeend),
                               lubridate::year(currenttimeend))

save_plots <- TRUE


#| include: false
qaelpath <- myhome
#qaelpath <- path.expand(qaelpath)
datDir <- file.path(qaelpath, "Deakin University/QAEL - MER/Model/dataBase")
datOut <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out")
project_dir <- file.path(datOut, 'werpstyle')
hydro_dir <- file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR_numeric_gauges')
ewr_results <- file.path(project_dir, 'MANUAL')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output_numeric_gauges')

comp_results <- file.path(project_dir, 'comparer_output') 

data_path <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out/SRA_analysis/Final_datasets")
plot_path <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out/SRA_analysis/DraftReport_plots")
```

## Climate categories

```{r}
#Climate categorgy data:
Climate_Categories <- read.csv(file.path(qaelpath, "Deakin University", "QAEL - SRA - SRA", "Climate_Categories_Coloured_2023.csv"), check.names = FALSE)

Climate_Categories <- Climate_Categories |>
  pivot_longer(cols = `Barwon-Darling`:`Total MDB`, names_to = "Climate_category.data", values_to = "Climate_Category")

Climate_Categories <- Climate_Categories |>
  mutate(Climate_Category = factor(Climate_Category, levels = c("Very Dry", "Dry", "Moderate", "Wet", "Very Wet")))|>
  rename(year = `Start of water Year`)

#FOR MER-STYLE
# read in the mapping of sdls/valleys to the climate category areas:
Climate_Category_to_polygons_MER <- read.csv(file.path(qaelpath, "Deakin University", "QAEL - SRA - SRA", "Climate_Category_to_polygons.csv"))

Climate_Category_to_polygons_MER <- Climate_Category_to_polygons_MER |>
  dplyr::select(Climate_category.data, ValleyName)|>
  filter(Climate_category.data != "")|>
  filter(ValleyName != "")|>
  distinct(Climate_category.data, ValleyName)

Climate_Category_to_polygons_MER <- Climate_Category_to_polygons_MER |> 
   mutate(name_clean = stringr::str_remove_all(ValleyName, ' '))

#Palette
pal_climate <-  stats::setNames(c("#ED2024", "#FAA41A", "#F6EB14", "#87CDE9", "#282A73"), levels(Climate_Categories$Climate_Category))
class(pal_climate) <- 'colors'

#dont think this worked:
pal_score <- stats::setNames(adjustcolor(pal_climate, alpha.f = 0.5),
                             c("very low", "Low", "medium", "high", "very high"))
class(pal_score) <- 'colors'

#"#ED202480" "#FAA41A80" "#F6EB1480" "#87CDE980" "#282A7380"

pal_indicator <-  stats::setNames(c("#ED2024", "#282A73"), c("Lateral connectivity", "ANAE inundation"))
class(pal_climate) <- 'colors'


```

## Data - Connectivity
```{r}
#LATERALconnectivity - Valley
Timeseries_Valley_LATERALconnectivity <- readRDS(file.path(data_path, "Timeseries_Valley_LATERALconnectivity.rds"))
Timeseries_Valley_LATERALconnectivity$Indicator <- "Lateral connectivity"
Timeseries_Valley_LATERALconnectivity$Label <- "Lateral connectivity (EWR achieved)"
Timeseries_Valley_LATERALconnectivity$Scale <- "Valley"

#LATERALconnectivity - Basin
Timeseries_Basin_LATERALconnectivity <- readRDS(file.path(data_path, "Timeseries_Basin_LATERALconnectivity.rds"))
Timeseries_Basin_LATERALconnectivity$Indicator <- "Lateral connectivity"
Timeseries_Basin_LATERALconnectivity$Label <- "Lateral connectivity (EWR achieved)"
Timeseries_Basin_LATERALconnectivity$Scale <- "Basin"

#LONGITUDINALconnectivity - Valley
Timeseries_Valley_LONGITUDINALconnectivity <- readRDS(file.path(data_path, "Timeseries_Valley_LONGITUDINALconnectivity.rds"))
Timeseries_Valley_LONGITUDINALconnectivity$Indicator <- "Longitudinal connectivity"
Timeseries_Valley_LONGITUDINALconnectivity$Label <- "Longitudinal connectivity (EWR achieved)"
Timeseries_Valley_LONGITUDINALconnectivity$Scale <- "Valley"

#LONGITUDINALconnectivity - Basin
Timeseries_Basin_LONGITUDINALconnectivity <- readRDS(file.path(data_path, "Timeseries_Basin_LONGITUDINALconnectivity.rds"))
Timeseries_Basin_LONGITUDINALconnectivity$Indicator <- "Longitudinal connectivity"
Timeseries_Basin_LONGITUDINALconnectivity$Label <- "Longitudinal connectivity (EWR achieved)"
Timeseries_Basin_LONGITUDINALconnectivity$Scale <- "Basin"

#Valley
Timeseries_Valley_EWRconnectivity <- bind_rows(Timeseries_Valley_LATERALconnectivity,
                                              Timeseries_Valley_LONGITUDINALconnectivity)

Timeseries_Valley_EWRconnectivity <- left_join(Timeseries_Valley_EWRconnectivity, Climate_Category_to_polygons_MER, by = join_by(ValleyName)) 
  
Timeseries_Valley_EWRconnectivity <- Timeseries_Valley_EWRconnectivity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

# unique(Climate_Categories$Climate_category.data) #"Border Rivers"
# unique(Timeseries_Valley_EWRconnectivity$Climate_category.data) #"Border Rivers"
# unique(Climate_Category_to_polygons_MER$Climate_category.data)
# unique(Climate_Category_to_polygons_MER$ValleyName)

#Basin
Timeseries_Basin_EWRconnectivity <- bind_rows(Timeseries_Basin_LATERALconnectivity,
                                              Timeseries_Basin_LONGITUDINALconnectivity)

Timeseries_Basin_EWRconnectivity$Climate_category.data <- "Total MDB"
  
Timeseries_Basin_EWRconnectivity <- Timeseries_Basin_EWRconnectivity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

# NEED TO CUT DATA IN BIG SHEET to 1988 and cut off 2023 -->
Timeseries_Valley_EWRconnectivity <- filter(Timeseries_Valley_EWRconnectivity, year > 1987 & year < 2023)
Timeseries_Basin_EWRconnectivity <- filter(Timeseries_Basin_EWRconnectivity, year > 1987 & year < 2023)

```

## Data - ANAE diversity
```{r}
#ANAEdiversity
#ANAEdiversity - Valley
Timeseries_Valley_ANAEdiversity <- catch_cat_sf('diversity_shannon_area', outerdir = 'diversity')

Timeseries_Valley_ANAEdiversity$Indicator <- "ANAE diversity"
Timeseries_Valley_ANAEdiversity$Label <- "ANAE diversity (shannon diversity)"
Timeseries_Valley_ANAEdiversity$Scale <- "Valley"

Timeseries_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
  mutate(year = lubridate::year(lubridate::ymd(time)))|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(ValleyName, name_clean))

Timeseries_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#ANAEdiversity - Basin
diversity_anae_summary <- catch_cat_sf('diversity_anae_summary', outerdir = 'diversity')

Timeseries_Basin_ANAEdiversity <- diversity_anae_summary |>
    st_drop_geometry() |>
    summarise(total_area = sum(area_inundated), .by = c(ANAE_DESC, time)) |> # the 'abundance', e.g. number of wetlands of each type
    filter(total_area > 0) |> # otherwise the log dies, and they don't count anyway.
    summarise(diversity_shannon_area = calc_shan(total_area), .by = c(time)) |>
    arrange(time)|> 
  bind_cols(basin) |> 
  st_as_sf()

Timeseries_Basin_ANAEdiversity$Indicator <- "ANAE diversity"
Timeseries_Basin_ANAEdiversity$Label <- "ANAE diversity (shannon diversity)"
Timeseries_Basin_ANAEdiversity$Scale <- "Basin"

Timeseries_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
  mutate(year = lubridate::year(lubridate::ymd(time)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))


```

## Data - ANAE inundation
```{r}
##ANAEinundation
#Valley
Timeseries_Valley_ANAEinundation <- diversity_anae_summary |>
  sf::st_drop_geometry() |>
  summarise(area_inundated = sum(area_inundated),
            total_area = sum(total_area),
            n_inundated = sum(n_inundated),
            n_anaes = sum(n_anaes),
            .by = c(time, name_clean, ValleyName)) |>
  mutate(prop_wetland_inundated = area_inundated/total_area) |>
  left_join(werptoolkitr::cewo_valleys, by = 'ValleyName') |>
  st_as_sf()

Timeseries_Valley_ANAEinundation$Indicator <- "ANAE inundation"
Timeseries_Valley_ANAEinundation$Label <- "ANAE inundation (area)" 
Timeseries_Valley_ANAEinundation$Scale <- "Valley"

Timeseries_Valley_ANAEinundation <- Timeseries_Valley_ANAEinundation |>
  mutate(year = lubridate::year(lubridate::ymd(time)))|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(ValleyName, name_clean))

Timeseries_Valley_ANAEinundation <- Timeseries_Valley_ANAEinundation |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

#Basin
Timeseries_Basin_ANAEinundation <- Timeseries_Valley_ANAEinundation |>
    st_drop_geometry() |>
    summarise(area_inundated = sum(area_inundated), 
              total_area = sum(total_area),
              .by = c(time)) |> # the 'abundance', e.g. number of wetlands of each type
  bind_cols(basin) |> 
  st_as_sf()

Timeseries_Basin_ANAEinundation$Indicator <- "ANAE inundation"
Timeseries_Basin_ANAEinundation$Label <- "ANAE inundation (area)"
Timeseries_Basin_ANAEinundation$Scale <- "Basin"

Timeseries_Basin_ANAEinundation <- Timeseries_Basin_ANAEinundation |>
  mutate(year = lubridate::year(lubridate::ymd(time)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_ANAEinundation <- Timeseries_Basin_ANAEinundation |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

```


## Data - ANAE veg
```{r}
# Read in data
# Setting these up to read in all the species at once with purrr
species <- c('black_box', 'red_gum', 'coolabah', 'lignum')
# species <- c('black_box', 'coolabah', 'lignum')

# Germination
# The first step in the life cycle is germination. It requires
germ <- purrr::map(species, \(x) catch_cat_sf('germ_area', outerdir = x) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration',
         species = x)) |> 
  bind_rows()

# Seedling survival
# 
# The second step in the life cycle is survival of seedlings post-germination. When considered on its own (i.e. were conditions right for seedling survival), we get the following.
seed <- purrr::map(species, \(x) catch_cat_sf('seedling_area', outerdir = x) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling',
         species = x)) |> 
  bind_rows()

# Germination and seedlings
# The life cycle is sequential, and so what we are interested in ultimately is regeneration success; that is, germination and subsequent survival. Here, we as whether conditions supported seedling survival after successful germination conditions. Thus, this is not simply the minimum of the upper two, it actually takes sequencing into account, and we lose some areas of successful seedling conditions because they were not preceded by germination.
germ_and_seed <- purrr::map(species, \(x) catch_cat_sf('germ_and_seed', outerdir = x) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment',
         species = x)) |> 
  bind_rows()

# Adult condition
# Here, we assess area of favourable adult condition, primarily as a consequence of inundation duration and periods between events. This is not connected to the regeneration due to the length of available data and tree life spans.

adult <- purrr::map(species, \(x) catch_cat_sf('adult_area', outerdir = x) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19950101)) |> 
  mutate(stage = 'adult',
         species = x)) |> 
  bind_rows()

# All together
all_strictures <- bind_rows(germ, seed, germ_and_seed, adult)

all_strictures <- all_strictures |>
  mutate(Indicator = paste(sub("_", " ", species), stage, sep = " "),
         Label = paste(Indicator, "(area)", sep = " "),
         Scale = "Valley")

Timeseries_Valley_ANAEvegetation <- all_strictures |>
  mutate(year = lubridate::year(lubridate::ymd(date)))|>
  rename(name_clean = ValleyName)|>
  left_join(Climate_Category_to_polygons_MER, by = join_by(name_clean))

Timeseries_Valley_ANAEvegetation <- Timeseries_Valley_ANAEvegetation |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))

# Basin
Timeseries_Basin_ANAEvegetation <- all_strictures |> 
  sf::st_drop_geometry() |> 
  summarise(area = sum(area),
            .by = c(date, stage, species, Indicator, Label)) |>
  bind_cols(basin) |> 
  st_as_sf()

Timeseries_Basin_ANAEvegetation$Scale <- "Basin"

Timeseries_Basin_ANAEvegetation <- Timeseries_Basin_ANAEvegetation |>
  mutate(year = lubridate::year(lubridate::ymd(date)),
         Climate_category.data = "Total MDB")

Timeseries_Basin_ANAEvegetation <- Timeseries_Basin_ANAEvegetation |>
  left_join(Climate_Categories, by = join_by(year, Climate_category.data))


```

## IS Scaling - EWRconnectivity
```{r}
#EWRconnectivity
#ANAEinundation
#ANAEvegetation

#EWRconnectivity
#Valley
Timeseries_Valley_EWRconnectivity <- Timeseries_Valley_EWRconnectivity |>
  ungroup()|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = ewr_achieved)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #Valley
  group_by(ValleyName)|>  
  mutate(Outcome_ValScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_ValScaled    = ifelse(is.nan(Outcome_ValScaled), 0, Outcome_ValScaled)) |>
  #YrType
  group_by(ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Valley_EWRconnectivity <- Timeseries_Valley_EWRconnectivity |>
    filter(year>=2009)|>
    group_by(Indicator, ValleyName)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Valley_EWRconnectivity <- Timeseries_Valley_EWRconnectivity |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, ValleyName, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_ValScaled_mean = mean(Outcome_ValScaled),
              Outcome_ValScaled_SE = plotrix::std.error(Outcome_ValScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Valley_EWRconnectivity <- left_join(Condition_Valley_EWRconnectivity, Trend_Valley_EWRconnectivity, by = join_by(Indicator, ValleyName))

#Basin
Timeseries_Basin_EWRconnectivity <- Timeseries_Basin_EWRconnectivity |>
  ungroup()|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = ewr_achieved)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #YrType
  group_by(Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Basin_EWRconnectivity <- Timeseries_Basin_EWRconnectivity |>
    filter(year>=2009)|>
    group_by(Indicator)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Basin_EWRconnectivity <- Timeseries_Basin_EWRconnectivity |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Basin_EWRconnectivity <- left_join(Condition_Basin_EWRconnectivity, Trend_Basin_EWRconnectivity, by = join_by(Indicator))
```

## IS Scaling - diversity 
```{r}
#EWRconnectivity
#ANAEinundation
#ANAEvegetation

#ANAEinundation
#Valley
Timeseries_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
  ungroup()|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = diversity_shannon_area)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #Valley
  group_by(ValleyName)|>  
  mutate(Outcome_ValScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_ValScaled    = ifelse(is.nan(Outcome_ValScaled), 0, Outcome_ValScaled)) |>
  #YrType
  group_by(ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
    filter(year>=2009)|>
    group_by(Indicator, ValleyName)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Valley_ANAEdiversity <- Timeseries_Valley_ANAEdiversity |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, ValleyName, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_ValScaled_mean = mean(Outcome_ValScaled),
              Outcome_ValScaled_SE = plotrix::std.error(Outcome_ValScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Valley_ANAEdiversity <- left_join(Condition_Valley_ANAEdiversity, Trend_Valley_ANAEdiversity, by = join_by(Indicator, ValleyName))

#Basin
Timeseries_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
  ungroup()|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = diversity_shannon_area)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #YrType
  group_by(Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
    filter(year>=2009)|>
    group_by(Indicator)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Basin_ANAEdiversity <- Timeseries_Basin_ANAEdiversity |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Basin_ANAEdiversity <- left_join(Condition_Basin_ANAEdiversity, Trend_Basin_ANAEdiversity, by = join_by(Indicator))
```


## IS Scaling - ANAEinundation 
```{r}
#EWRconnectivity
#ANAEinundation
#ANAEvegetation

#ANAEinundation
#Valley
Timeseries_Valley_ANAEinundation <- Timeseries_Valley_ANAEinundation |>
  ungroup()|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = area_inundated)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #Valley
  group_by(ValleyName)|>  
  mutate(Outcome_ValScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_ValScaled    = ifelse(is.nan(Outcome_ValScaled), 0, Outcome_ValScaled)) |>
  #YrType
  group_by(ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Valley_ANAEinundation <- Timeseries_Valley_ANAEinundation |>
    filter(year>=2009)|>
    group_by(Indicator, ValleyName)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Valley_ANAEinundation <- Timeseries_Valley_ANAEinundation |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, ValleyName, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_ValScaled_mean = mean(Outcome_ValScaled),
              Outcome_ValScaled_SE = plotrix::std.error(Outcome_ValScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Valley_ANAEinundation <- left_join(Condition_Valley_ANAEinundation, Trend_Valley_ANAEinundation, by = join_by(Indicator, ValleyName))

#Basin
Timeseries_Basin_ANAEinundation <- Timeseries_Basin_ANAEinundation |>
  ungroup()|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = area_inundated)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #YrType
  group_by(Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Basin_ANAEinundation <- Timeseries_Basin_ANAEinundation |>
    filter(year>=2009)|>
    group_by(Indicator)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Basin_ANAEinundation <- Timeseries_Basin_ANAEinundation |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Basin_ANAEinundation <- left_join(Condition_Basin_ANAEinundation, Trend_Basin_ANAEinundation, by = join_by(Indicator))
```

## IS Scaling - ANAEvegetation
```{r}
#ANAEvegetation
#Valley
Timeseries_Valley_ANAEvegetation <- Timeseries_Valley_ANAEvegetation |>
  ungroup()|>
  filter(!is.na(area))|>
  group_by(Indicator)|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = area)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #Valley
  group_by(ValleyName)|>  
  mutate(Outcome_ValScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_ValScaled    = ifelse(is.nan(Outcome_ValScaled), 0, Outcome_ValScaled)) |>
  #YrType
  group_by(ValleyName, Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Valley_ANAEvegetation <- Timeseries_Valley_ANAEvegetation |>
    filter(year>=2009)|>
    group_by(Indicator, ValleyName)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Valley_ANAEvegetation <- Timeseries_Valley_ANAEvegetation |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, ValleyName, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_ValScaled_mean = mean(Outcome_ValScaled),
              Outcome_ValScaled_SE = plotrix::std.error(Outcome_ValScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Valley_ANAEvegetation <- left_join(Condition_Valley_ANAEvegetation, Trend_Valley_ANAEvegetation, by = join_by(Indicator, ValleyName))

#Basin
Timeseries_Basin_ANAEvegetation <- Timeseries_Basin_ANAEvegetation |>
  ungroup()|>
  group_by(Indicator)|>
  filter(!is.na(area))|>
  filter(year>=1988)|>
  #Outcome
  mutate(Outcome = area)|>
  #Total 
  mutate(Outcome_TotalScaled  = (Outcome-0)/(1-0)) |>
  mutate(Outcome_TotalScaled    = ifelse(is.nan(Outcome_TotalScaled), 0, Outcome_TotalScaled)) |>
  #Basin 
  mutate(Outcome_BasScaled    = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_BasScaled    = ifelse(is.nan(Outcome_BasScaled), 0, Outcome_BasScaled)) |>
  #YrType
  group_by(Climate_Category)|>
  mutate(Outcome_YrTypeScaled = (Outcome-min(Outcome))/(max(Outcome)-min(Outcome))) |>
  mutate(Outcome_YrTypeScaled    = ifelse(is.nan(Outcome_YrTypeScaled), 0, Outcome_YrTypeScaled)) 

Trend_Basin_ANAEvegetation <- Timeseries_Basin_ANAEvegetation |>
    filter(year>=2009 & year != 2023)|>
    group_by(Indicator)|>
    do({model = lm(Outcome_YrTypeScaled ~ year, data = .)    # create your model
      data.frame(broom::tidy(model))})|>          # get model info
    filter(term == "year")

Condition_Basin_ANAEvegetation <- Timeseries_Basin_ANAEvegetation |>
  filter(year %in% c(2022, 2021, 2020, 2019, 2018))|>
    group_by(Indicator, Label, Scale)|>
    summarise(Outcome_mean = mean(Outcome),
              Outcome_SE = plotrix::std.error(Outcome),
              Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
              Outcome_TotalScaled_SE = plotrix::std.error(Outcome_TotalScaled),
              Outcome_BasScaled_mean = mean(Outcome_BasScaled),
              Outcome_BasScaled_SE = plotrix::std.error(Outcome_BasScaled),
              Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
              Outcome_YrTypeScaled_SE = plotrix::std.error(Outcome_YrTypeScaled))

Condition_Trend_Basin_ANAEvegetation <- left_join(Condition_Basin_ANAEvegetation, Trend_Basin_ANAEvegetation, by = join_by(Indicator))
```
## Joins
```{r}
Indicators_keep <- c('black box adult', 'black box recruitment', 'coolabah adult', 'coolabah recruitment',  'lignum adult', 'lignum recruitment',  'red gum adult', 'red gum recruitment')

Condition_Trend_Valley <- bind_rows(    st_drop_geometry(Condition_Trend_Valley_EWRconnectivity),
st_drop_geometry(Condition_Trend_Valley_ANAEdiversity),
st_drop_geometry(Condition_Trend_Valley_ANAEinundation),
st_drop_geometry(filter(Condition_Trend_Valley_ANAEvegetation, Indicator %in% Indicators_keep)))

Condition_Trend_Basin <- bind_rows(    st_drop_geometry(Condition_Trend_Basin_EWRconnectivity),
st_drop_geometry(Condition_Trend_Basin_ANAEdiversity),
st_drop_geometry(Condition_Trend_Basin_ANAEinundation),
st_drop_geometry(filter(Condition_Trend_Basin_ANAEvegetation, Indicator %in% Indicators_keep)))

Timeseries_Valley <- bind_rows(st_drop_geometry(Timeseries_Valley_EWRconnectivity),
st_drop_geometry(Timeseries_Valley_ANAEdiversity),
st_drop_geometry(Timeseries_Valley_ANAEinundation),
st_drop_geometry(filter(Timeseries_Valley_ANAEvegetation, stage == "recruitment" | stage == "adult")))

Timeseries_Basin <- bind_rows(st_drop_geometry(Timeseries_Basin_EWRconnectivity),
st_drop_geometry(Timeseries_Basin_ANAEdiversity),
st_drop_geometry(Timeseries_Basin_ANAEinundation),
st_drop_geometry(filter(Timeseries_Basin_ANAEvegetation, stage == "recruitment" | stage == "adult")))

Timeseries_Basin$ValleyName <- "Basin wide"

Timeseries <- bind_rows(Timeseries_Valley, Timeseries_Basin)

```

## Stepping through scaling

with one example

```{r}
Plot_Timeseries_Basin_LATERAL_IS1 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = ewr_achieved))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(EWR achieved)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS2 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_TotalScaled))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(TotalRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS3 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_ObsScaled))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(ObsRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS4 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_YrTypeScaled))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(YrTypeRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS5 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1900,NA)

IS_example_plot <- Plot_Timeseries_Basin_LATERAL_IS1 +
  Plot_Timeseries_Basin_LATERAL_IS2 +
  Plot_Timeseries_Basin_LATERAL_IS3 +
  Plot_Timeseries_Basin_LATERAL_IS4 +
  Plot_Timeseries_Basin_LATERAL_IS5 + plot_layout(ncol = 2, guides = "collect")

ggsave(plot = IS_example_plot, filename = file.path(plot_path, paste0("IS_example_plot_LATERALconnectivity_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)
```

## SUGGESTED

add current condition and trend to left hand corner ? lines for year type mean? (some kind of range 95%ile?)
Condition = yr type scaled. = good fair poor

Fit spline with 1) all data and 2) all data excluding post BP - amiar?


```{r}
#BASIN
temp <- Timeseries_Basin_LATERALconnectivity |>
  group_by(Climate_Category)|>
  reframe(Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
          Outcome_ObsScaled_mean = mean(Outcome_ObsScaled), 
          Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
          
          Outcome_TotalScaled_25 = quantile(Outcome_TotalScaled, probs = c(0.25)),
          Outcome_ObsScaled_25 = quantile(Outcome_ObsScaled, probs = c(0.25)), 
          Outcome_YrTypeScaled_25 = quantile(Outcome_YrTypeScaled, probs = c(0.25)),
          
          Outcome_TotalScaled_75 = quantile(Outcome_TotalScaled, probs = c(0.75)),
          Outcome_ObsScaled_75 = quantile(Outcome_ObsScaled, probs = c(0.75)), 
          Outcome_YrTypeScaled_75 = quantile(Outcome_YrTypeScaled, probs = c(0.75))
          
          )|>
  filter(!is.na(Climate_Category))

#Map Pre and Post basin plan
temp2 <- Timeseries_Basin_LATERALconnectivity |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) 

temp3 <- temp2|> 
  group_by(timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS),
          Outcome_YrTypeScaled = mean(Outcome_YrTypeScaled),
          year = max(year))  

Current_trend <- temp3$Outcome_YrTypeScaled[2] - temp3$Outcome_YrTypeScaled[1]

temp4 <- temp2 |>
  group_by(timeperiod)|>
  filter(timeperiod != "other")|>
  mutate(year = max(year))


Model <- lm(Outcome_YrTypeScaled ~ year, data = temp2, conf.int = TRUE)
Model$coefficients[2]
summary(Model)
confint(Model)


filter(temp2, timeperiod == 'Pre-BP')
filter(temp2, timeperiod == 'Current')

# temp2 |>
#   group_by(timeperiod)|>
#   reframe

CurrentYear <- Timeseries_Basin_LATERALconnectivity |>
  filter(year == 2022)

Current5Years <- Timeseries_Basin_LATERALconnectivity |>
  ungroup()|>
  filter(year %in% c(2019, 2020, 2021, 2022, 2023))

Confidence <- t.test(Current5Years$Outcome_YrTypeScaled)
Confidence$conf.int


t.test(Current5Years$Outcome_YrTypeScaled ~ 1)
t.test(Current5Years$Outcome_YrTypeScaled, rep(0.92, time = 5))

predict()

Condition <- data.frame(
  Label_type = c("Current_condition", "YrType_condition", "Optimum_condition", "Trend_5yr", "Trend_uncertainty"),
  Label_text = c(paste("Current condition = ", round(CurrentYear$Outcome_TotalScaled, 2)*100, "% ", "(74-100)", sep = ""),
                 paste("Very good for a wet year (medium confidence)", sep = ""), 
                 #paste("Very good within the basin (medium confidence)", sep = ""), 
                 paste("Very good compared to optimum (medium confidence)", sep = ""), 
                 paste("Trend = ", "0.028 (-0.010 - 0.067)", sep = ""),
                 paste("Improving (high confidence)", sep = "")),
  vjustvar = c(1,2,3,4,5), #<- adjust
  Label_colour = c("very high","high","high","very high", "very high"))
  Condition$xpos = -Inf
  Condition$ypos = Inf
  Condition$hjustvar = 0 

  
  #c("very low", "Low", "medium", "high", "very high"))
#class(Condition$Label_colour) <- 'colors'


Plot_Timeseries_Basin_LATERAL_IS6 <- ggplot(data = Timeseries_Basin_LATERALconnectivity, 
       aes(x = year, y = Outcome_ObsScaled))+
  
  geom_rect(xmin = lubridate::year(currenttimestart), xmax = lubridate::year(currenttimeend), ymin = 0, ymax = 1, fill= "beige") +
  geom_rect(xmin = lubridate::year(preBPtimestart), xmax = lubridate::year(preBPtimeend), ymin = 0, ymax = 1, fill= "beige") +
    
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_25, colour = Climate_Category), linetype = "solid", alpha = 0.5)+
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_75, colour = Climate_Category), linetype = "longdash", alpha = 0.5)+
  geom_line(colour = "grey80")+
  geom_label(data = Condition, aes(x = xpos, y = ypos, label=Label_text, hjust=hjustvar, vjust=vjustvar, fill = Label_colour), label.r = unit(0, "pt"))+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  geom_point(data = CurrentYear, aes(x = year, y = Outcome_ObsScaled, colour = Climate_Category), size = 5)+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  #geom_smooth(data = filter(Timeseries_Basin_LATERALconnectivity, !is.na(Climate_Category)), aes(colour = Climate_Category), linewidth = 0.5, se = FALSE)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(ObsRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)+
  geom_vline(xintercept = 2008, linetype = "solid")+
geom_line(data = temp3, aes(x = year, y = Outcome_YrTypeScaled))+
scale_fill_manual(values = pal_score, aesthetics = "fill", guide = "none") 


Plot_Timeseries_Basin_LATERAL_IS6

ggsave(plot = Plot_Timeseries_Basin_LATERAL_IS6, filename = file.path(plot_path, paste0("SUGGESTED_plot_Basin_LATERALconnectivity_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 6)

```
```{r}
BD_data <- Timeseries_Valley_LATERALconnectivity|>
  filter(ValleyName == "Barwon Darling")

temp <- BD_data |>
  group_by(Climate_Category)|>
  reframe(Outcome_TotalScaled_mean = mean(Outcome_TotalScaled),
          Outcome_BasScaled_mean = mean(Outcome_BasScaled), 
          Outcome_ObsScaled_mean = mean(Outcome_ObsScaled), 
          Outcome_YrTypeScaled_mean = mean(Outcome_YrTypeScaled),
          
          Outcome_TotalScaled_25 = quantile(Outcome_TotalScaled, probs = c(0.25)),
          Outcome_ObsScaled_25 = quantile(Outcome_ObsScaled, probs = c(0.25)), 
          Outcome_YrTypeScaled_25 = quantile(Outcome_YrTypeScaled, probs = c(0.25)),
          
          Outcome_TotalScaled_75 = quantile(Outcome_TotalScaled, probs = c(0.75)),
          Outcome_ObsScaled_75 = quantile(Outcome_ObsScaled, probs = c(0.75)), 
          Outcome_YrTypeScaled_75 = quantile(Outcome_YrTypeScaled, probs = c(0.75))
          
          )|>
  filter(!is.na(Climate_Category))

#Map Pre and Post basin plan
temp2 <- BD_data |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) 

temp3 <- temp2|> 
  group_by(timeperiod) |>
  reframe(Outcome_IS = mean(Outcome_IS),
          Outcome_YrTypeScaled = mean(Outcome_YrTypeScaled),
          year = max(year))  

Current_trend <- temp3$Outcome_YrTypeScaled[2] - temp3$Outcome_YrTypeScaled[1]

temp4 <- temp2 |>
  group_by(timeperiod)|>
  filter(timeperiod != "other")|>
  mutate(year = max(year))


Model <- lm(Outcome_YrTypeScaled ~ year, data = temp2, conf.int = TRUE)
Model$coefficients[2]
summary(Model)
confint(Model)


filter(temp2, timeperiod == 'Pre-BP')
filter(temp2, timeperiod == 'Current')

# temp2 |>
#   group_by(timeperiod)|>
#   reframe

CurrentYear <- BD_data |>
  filter(year == 2022)


Timeseries_Valley_LATERALconnectivity |>
  filter(ValleyName == "Barwon Darling")|>
  filter(year == 2022)

Current5Years <- BD_data |>
  ungroup()|>
  filter(year %in% c(2019, 2020, 2021, 2022, 2023))

Confidence <- t.test(Current5Years$Outcome_YrTypeScaled)
Confidence$conf.int


t.test(Current5Years$Outcome_YrTypeScaled ~ 1)
t.test(Current5Years$Outcome_YrTypeScaled, rep(0.92, time = 5))

#predict()

Condition <- data.frame(
  Label_type = c("Current_condition", "YrType_condition", "Basin_condition",  "Optimum_condition", "Trend_5yr", "Trend_uncertainty"),
  Label_text = c(paste("Current condition = ", round(CurrentYear$Outcome_TotalScaled, 2)*100, "% ", "(67-94)", sep = ""),
                 paste("good for a wet year (medium confidence)", sep = ""), 
                 paste("good within the basin (medium confidence)", sep = ""), 
                 paste("good compared to optimum (medium confidence)", sep = ""), 
                 paste("Trend = ", "-0.017 (-0.027 - -0.008)", sep = ""),
                 paste("Declining (very high confidence)", sep = "")),
  vjustvar = c(1,2,3,4,5,6), #<- adjust
  Label_colour = c("high","high","high","high","very low", "very low"))
  Condition$xpos = -Inf
  Condition$ypos = Inf
  Condition$hjustvar = 0 

  
  #c("very low", "Low", "medium", "high", "very high"))
#class(Condition$Label_colour) <- 'colors'


Plot_Timeseries_BD_LATERAL_IS6<- ggplot(data = BD_data, 
       aes(x = year, y = Outcome_ObsScaled))+
  
  geom_rect(xmin = lubridate::year(currenttimestart), xmax = lubridate::year(currenttimeend), ymin = 0, ymax = 1, fill= "beige") +
  geom_rect(xmin = lubridate::year(preBPtimestart), xmax = lubridate::year(preBPtimeend), ymin = 0, ymax = 1, fill= "beige") +
    
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_25, colour = Climate_Category), linetype = "solid", alpha = 0.5)+
  geom_hline(data = temp, aes(yintercept = Outcome_TotalScaled_75, colour = Climate_Category), linetype = "longdash", alpha = 0.5)+
  geom_line(colour = "grey80")+
  geom_label(data = Condition, aes(x = xpos, y = ypos, label=Label_text, hjust=hjustvar, vjust=vjustvar, fill = Label_colour), label.r = unit(0, "pt"))+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  geom_point(data = CurrentYear, aes(x = year, y = Outcome_ObsScaled, colour = Climate_Category), size = 5)+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  #geom_smooth(data = filter(Timeseries_Basin_LATERALconnectivity, !is.na(Climate_Category)), aes(colour = Climate_Category), linewidth = 0.5, se = FALSE)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity\n(ObsRange IS)")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)+
  facet_wrap(~ValleyName)+
  geom_vline(xintercept = 2008, linetype = "solid")+
geom_line(data = temp3, aes(x = year, y = Outcome_YrTypeScaled))+
scale_fill_manual(values = pal_score, aesthetics = "fill", guide = "none") 


Plot_Timeseries_BD_LATERAL_IS6

ggsave(plot = Plot_Timeseries_BD_LATERAL_IS6, filename = file.path(plot_path, paste0("SUGGESTED_plot_BD_LATERALconnectivity_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 6)
```


## Stepping through combining ISs

```{r}
Plot_Timeseries_Basin_BLACKBOX1 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = germ))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box germination IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX2 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = seed))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box seedling IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX3 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = germ_and_seed))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box gemination and seedling IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX4 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = adult))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box adult IS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_Basin_BLACKBOX5 <- ggplot(data = Timeseries_Basin_BLACKBOXcs, 
       aes(x = year, y = Outcome_CS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Black box CS")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

CS_example_plot <- Plot_Timeseries_Basin_BLACKBOX1 +
  Plot_Timeseries_Basin_BLACKBOX2 +
  Plot_Timeseries_Basin_BLACKBOX3 +
  Plot_Timeseries_Basin_BLACKBOX4 +
  Plot_Timeseries_Basin_BLACKBOX5 + plot_layout(ncol = 2, guides = "collect")

CS_example_plot

ggsave(plot = CS_example_plot, filename = file.path(plot_path, paste0("CS_example_plot_BLACKBOX_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)
```

## LATERALconnectivity - EXAMPLE - Barwon Darling

```{r}
#Timeseries
Plot_Timeseries_BarwonDarling_LATERALconnectivity <- ggplot(data = filter(Timeseries_Valley_EWRconnectivity, Indicator == "Lateral connectivity" & ValleyName == "Barwon Darling") , aes(x = year, y = Outcome))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  theme_bw()+
  theme(strip.background =element_rect(fill=NA),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  facet_wrap(~ValleyName)+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity (EWR achieved)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ 
  xlim(1988,NA)

Plot_Timeseries_BarwonDarling_LATERALconnectivity

ggsave(plot = Plot_Timeseries_BarwonDarling_LATERALconnectivity, filename = file.path(plot_path, paste0("Plot_Timeseries_BarwonDarling_LATERALconnectivity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 5, height = 3)

Timeseries_Valley_EWRconnectivity$Climate_Category

#Boxplot
Boxplot_Timeseries_BarwonDarling_LATERALconnectivity <- ggplot(data = filter(Timeseries_Valley_EWRconnectivity, Indicator == "Lateral connectivity" & ValleyName == "Barwon Darling" & year > 1988
                                                                             & !is.na(Climate_Category)), 
       aes(x = Climate_Category, y = Outcome, colour = Climate_Category))+
  geom_boxplot(aes())+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName)+
  theme_bw()+
  theme(strip.background =element_rect(fill=NA),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  labs(x = "SWC", colour = "SWC", y = "Lateral connectivity (EWR achieved)")+
  theme(axis.text.x = element_text(angle = 90))

Boxplot_Timeseries_BarwonDarling_LATERALconnectivity

ggsave(plot = Boxplot_Timeseries_BarwonDarling_LATERALconnectivity, filename = file.path(plot_path, paste0("Boxplot_Timeseries_BarwonDarling_LATERALconnectivity","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 5, height = 3)

#Timeseries - Climate category scaled for trend
Plot_Trend_Timeseries_BarwonDarling_LATERALconnectivity <- ggplot(data = filter(Timeseries_Valley_EWRconnectivity, Indicator == "Lateral connectivity" & ValleyName == "Barwon Darling" & year>=2009), 
                                                            aes(x = year, y = Outcome_YrTypeScaled))+
  geom_line(colour = "grey80")+
  geom_point(colour = "black")+ # i think keep these points black so it doesn't look weird that all the very wet points fall at the bottom??
  geom_smooth(formula = "y ~ x", method = "lm", colour = "black") +
  theme_bw()+
  theme(strip.background =element_rect(fill=NA),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  facet_wrap(~ValleyName)+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity (EWR achieved)")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

Plot_Trend_Timeseries_BarwonDarling_LATERALconnectivity

ggsave(plot = Plot_Trend_Timeseries_BarwonDarling_LATERALconnectivity, filename = file.path(plot_path, paste0("Plot_Trend_Timeseries_BarwonDarling_LATERALconnectivity", "_", Sys.Date(), ".tiff")), device = "tiff",
       width = 5, height = 3)
```
## LIST OF VALLEYS BY INDICATOR:
```{r}
#MAKE LIST OF VALLEYS BY INDICATORS:
Valley_indicator_list <- tibble(
  IndicatorX = (sort(rep(unique(Timeseries$Indicator), 
                           times = length(unique(Timeseries$ValleyName))))),
  ValleyNameY = (rep(unique(Timeseries$ValleyName), 
                     times = length(unique(Timeseries$Indicator)))),
)

# EXCLUSIONS:
#Some valleys dont have EWRs - cannot assess lateral or longitudinal connectivity
Valleys_no_EWRs <- c("Avoca", "Kiewa", "Mitta Mitta", "Upper Murray", "Wimmera")
Indicators_no_EWRs <- c("Longitudinal connectivity", "Lateral connectivity")

#Castlereagh does not have CF or BF EWRs (only SF LF and OB) - cannot assess longitudinal connectivity
Valley_indicator_list<- Valley_indicator_list |>
  filter(!(ValleyNameY == "Castlereagh" & IndicatorX == "Longitudinal connectivity"))|>
  filter(!(ValleyNameY %in% Valleys_no_EWRs & IndicatorX %in% Indicators_no_EWRs))

#Tibble should have this many rows:
312 - 1 - 10



```

## Timeseries plots
<!-- # BRoken works for lateral but not longitudinal???? same for Central Murray. -->
 #BASIN PLOTS

```{r}
#Timeseries

Plot_Timeseries <- function(IndicatorX, ValleyNameY, data) {
 data1 <- data |>
    filter(Indicator == IndicatorX & ValleyName == ValleyNameY)
  
 plot1 <- ggplot(data = data1, aes(x = year, y = Outcome))+
    geom_line(colour = "grey80")+
    geom_point(aes(colour = Climate_Category))+#, colour = "black")+
    scale_colour_manual(values = pal_climate, aesthetics = "colour") +
    theme_bw()+
    theme(strip.background =element_rect(fill=NA),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    facet_wrap(~ValleyName)+
    labs(x = "Year", colour = "SWC", y = unique(data1$Label))+
    theme(axis.text.x = element_text(angle = 90))
  
 ggsave(plot = plot1, 
         filename = file.path(plot_path, "Timeseries", paste0("Plot_Timeseries_", 
                                                              stringr::str_remove_all(unique(data1$ValleyName), ' '), "_",
                                                              stringr::str_remove_all(unique(data1$Indicator), ' '), "_", Sys.Date(), ".tiff")), 
         device = "tiff", width = 5, height = 3)
}

# RUN and SAVE PLOT
purrr::pmap(Valley_indicator_list, ~Plot_Timeseries(IndicatorX = .x, ValleyNameY = .y, data = Timeseries))

#Valley_indicator_list<- Valley_indicator_list[271,]

```

## Boxplots

```{r}
#boxplots

Plot_Boxplots <- function(IndicatorX, ValleyNameY, data) {
 data1 <- data |>
    filter(Indicator == IndicatorX & ValleyName == ValleyNameY)|>
    filter(year > 1988)|>
    filter(!is.na(Climate_Category))
    
 plot1 <- ggplot(data = data1, 
       aes(x = Climate_Category, y = Outcome, colour = Climate_Category))+
  geom_boxplot(aes())+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~ValleyName)+
  theme_bw()+
  theme(strip.background =element_rect(fill=NA),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  labs(x = "SWC", colour = "SWC", y = unique(data1$Label))+
  theme(axis.text.x = element_text(angle = 90))

 ggsave(plot = plot1, 
         filename = file.path(plot_path, "Boxplots", paste0("Boxplot_Timeseries_", unique(data1$name_clean), "_", stringr::str_remove_all(unique(data1$Indicator), ' '), "_", Sys.Date(), ".tiff")), 
         device = "tiff", width = 5, height = 3)
 
}

# RUN and SAVE PLOT
purrr::pmap(Valley_indicator_list, ~Plot_Boxplots(IndicatorX = .x, ValleyNameY = .y, data = Timeseries))

#Valley_indicator_list<- Valley_indicator_list[101,]

```

# Trend timeseries

```{r}
#Trend timeseries

Plot_Trend_Timeseries <- function(IndicatorX, ValleyNameY, data) {
 data1 <- data |>
    filter(Indicator == IndicatorX & ValleyName == ValleyNameY)|>
    filter(year >= 2009)|>
    filter(!is.na(Climate_Category))
    
 plot1 <- ggplot(data = data1, 
       aes(x = year, y = Outcome_YrTypeScaled))+
  geom_line(colour = "grey80")+
  geom_point(colour = "black")+ # i think keep these points black so it doesn't look weird that all the very wet points fall at the bottom??
  geom_smooth(formula = "y ~ x", method = "lm", colour = "black") +
  theme_bw()+
  theme(strip.background =element_rect(fill=NA),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  facet_wrap(~ValleyName)+
  labs(x = "Year", y = unique(data1$Label))+
  theme(axis.text.x = element_text(angle = 90))

 ggsave(plot = plot1, 
         filename = file.path(plot_path, "Trend", paste0("Trend_Timeseries_", unique(data1$name_clean), "_", stringr::str_remove_all(unique(data1$Indicator), ' '), "_", Sys.Date(), ".tiff")), 
         device = "tiff", width = 5, height = 3)
 
}

# RUN and SAVE PLOT
purrr::pmap(Valley_indicator_list, ~Plot_Trend_Timeseries(IndicatorX = .x, ValleyNameY = .y, data = Timeseries))

#Valley_indicator_list<- Valley_indicator_list[34,]

# Timeseries|>
#     filter(Indicator == Valley_indicator_list[34,]$IndicatorX & ValleyName == Valley_indicator_list[34,]$ValleyNameY)

```
## Connecting Inundation to EWR lateral connectivity 
```{r}
Timeseries_Connecting_Basin <- Timeseries |>
  ungroup()|>
  filter(ValleyName == "Basin wide")|>
  select(ValleyName, Indicator, year, Outcome_BasScaled, Climate_Category)|>
  filter(Indicator == "ANAE inundation" | Indicator == "Lateral connectivity")|>
  pivot_wider(names_from = Indicator, values_from = Outcome_BasScaled)

plot1 <- ggplot(data = Timeseries_Connecting_Basin, aes(x = `Lateral connectivity`, y = `ANAE inundation`))+
    smplot2::sm_statCorr(corr_method = 'spearman', colour = "black")+
    geom_point(aes(colour = Climate_Category))+
    scale_colour_manual(values = pal_climate, aesthetics = "colour") +
    theme_bw()+
    theme(strip.background =element_rect(fill=NA),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    facet_wrap(~ValleyName)+
    labs(colour = "SWC")+
    theme(axis.text.x = element_text(angle = 90))

 ggsave(plot = plot1, 
         filename = file.path(plot_path, "Inundation_correlation", paste0("CorrelationPlot_", 
                                                              stringr::str_remove_all(unique(Timeseries_Connecting_Basin$ValleyName), ' '), "_", Sys.Date(), ".tiff")), 
         device = "tiff", width = 5, height = 3)

```
## Connecting Inundation to EWR lateral connectivity 

```{r}
## Connecting Inundation to EWR lateral connectivity 
Plot_Timeseries_ANAEInundation_EWRLateralconnectivity <- function(IndicatorX, ValleyNameY, data) {
 data1 <- data |>
  ungroup()|>
  filter(ValleyName == ValleyNameY)|>
  select(ValleyName, Indicator, year, Outcome_ValScaled, Climate_Category)|>
  filter(Indicator == "ANAE inundation" | Indicator == "Lateral connectivity")|>
  pivot_wider(names_from = Indicator, values_from = Outcome_ValScaled)
  
 plot1 <- ggplot(data = data1, aes(x = `Lateral connectivity`, y = `ANAE inundation`))+
    smplot2::sm_statCorr(corr_method = 'spearman', colour = "black")+
    geom_point(aes(colour = Climate_Category))+
    scale_colour_manual(values = pal_climate, aesthetics = "colour") +
    theme_bw()+
    theme(strip.background =element_rect(fill=NA),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    facet_wrap(~ValleyName)+
    labs(colour = "SWC")+
    theme(axis.text.x = element_text(angle = 90))
  
 ggsave(plot = plot1, 
         filename = file.path(plot_path, "Inundation_correlation", paste0("CorrelationPlot_", 
                                                              stringr::str_remove_all(unique(data1$ValleyName), ' '), "_",
                                                              stringr::str_remove_all(unique(data1$Indicator), ' '), "_", Sys.Date(), ".tiff")), 
         device = "tiff", width = 5, height = 3)
}

#SUBSET LIST
Valley_indicator_list_subset <- Valley_indicator_list |>
  filter(IndicatorX == "Lateral connectivity")

# RUN and SAVE PLOT
purrr::pmap(Valley_indicator_list_subset, ~Plot_Timeseries_ANAEInundation_EWRLateralconnectivity(IndicatorX = .x, ValleyNameY = .y, data = Timeseries))

#Valley_indicator_list<- Valley_indicator_list[271,]


Timeseries |>
  filter(ValleyName == "Basin wide")|>
  filter(Indicator == "ANAE inundation" | Indicator == "Lateral connectivity")

```
 
 
 
## Condition and Trend Values
 
```{r}
write.csv(
  Condition_Trend_Basin,
  file.path(plot_path, "Condition_and_Trend_values", paste0("Condition_and_Trend_Basin", "_", Sys.Date(), ".csv")))

write.csv(
  Condition_Trend_Valley,
  file.path(plot_path, "Condition_and_Trend_values", paste0("Condition_and_Trend_Valley", "_", Sys.Date(), ".csv")))
```

## TILE plots

```{r}

Condition_Trend_Basin_data <- Condition_Trend_Basin |>
  ungroup()|>
  group_by()|>
  mutate(estimate_scaled = estimate + 0.5)|>
  select(-term)|>
  mutate(estimate_scaled = estimate + 0.5)|>
  pivot_longer(cols = c(Outcome_TotalScaled_mean, Outcome_BasScaled_mean, Outcome_YrTypeScaled_mean, estimate_scaled), names_to = "Variable", values_to = "Value")|>
  mutate(Error = case_when(Variable == "Outcome_TotalScaled_mean" ~ Outcome_TotalScaled_SE,
                           Variable == "Outcome_BasScaled_mean" ~ Outcome_BasScaled_SE,
                           Variable == "Outcome_YrTypeScaled_mean" ~ Outcome_YrTypeScaled_SE,
                           Variable == "estimate_scaled" ~ std.error))|>
  mutate(Condition = ifelse(Value > 0.75, "Very good",
                       ifelse(Value > 0.50, "Good",
                        ifelse(Value == 0.50, "No slope",
                              ifelse(Value > 0.25, "Poor",
                                     ifelse(Value >= 0.00, "Very poor", "NOT SURE"))))))

ggplot(data = Condition_Trend_Basin_data, 
       aes(x = Variable, y = Indicator, fill = Condition))+
  geom_tile()+
  #scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Indicator")+
  theme(axis.text.x = element_text(angle = 90))

Tile_plot1

ggsave(plot = Tile_plot1, filename = file.path(plot_path, paste0("Tile_plot_AVOCA", Sys.Date(), ".tiff")), device = "tiff",
       width = 4, height = 8)



Tile_plot2 <- ggplot(data = filter(All_indicators_summary, Indicator == "ANAEdiversity"), 
       aes(x = name, y = ValleyName, fill = value))+
  geom_tile()+
  #scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  #labs(x = "Year", colour = "SWC", y = "Indicator")+
  theme(axis.text.x = element_text(angle = 90))

Tile_plot2

ggsave(plot = Tile_plot2, filename = file.path(plot_path, paste0("Tile_plot_ANAEdiversity", Sys.Date(), ".tiff")), device = "tiff",
       width = 4, height = 8)
-1*-1

```





## Add geometry 

```{r}


#EWRconnectivity
Timeseries_Valley_EWRconnectivity <- left_join(Timeseries_Valley_EWRconnectivity, cewo_valleys, by = join_by(ValleyName))

Timeseries_Basin_EWRconnectivity$geometry <- basin$geometry

```

## MAPs - not done yet

```{r}
#Map Climate Categories
Tagg_ClimCats_Basin_COOLABAHcs <- Timeseries_Basin_COOLABAHcs|>
  group_by(Climate_Category)|>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = weighted.mean(Outcome_CS, year))
Tagg_ClimCats_Basin_COOLABAHcs$geometry <- basin$geometry


Map_Tagg_ClimCats_Basin_COOLABAH <- ggplot(data = Tagg_ClimCats_Basin_COOLABAHcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

Map_Tagg_ClimCats_Basin_COOLABAH

ggsave(plot = Map_Tagg_ClimCats_Basin_COOLABAH, filename = file.path(plot_path, paste0("Map_Tagg_ClimCats_Basin_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

#Map Pre and Post basin plan
Tagg_PrePostBP_Basin_COOLABAHcs <- Timeseries_Basin_COOLABAHcs |> 
  ungroup()|>
  mutate(timeperiod = case_when((year > lubridate::year(currenttimestart) & 
                                   year < lubridate::year(currenttimeend)) ~ 'Current',
                                (year > lubridate::year(preBPtimestart) & 
                                    year < lubridate::year(preBPtimeend)) ~ 'Pre-BP',
                                .default = 'other')) |> 
  filter(timeperiod != 'other') |> 
  mutate(timeperiod = factor(timeperiod, levels = c('Pre-BP', 'Current'))) |> 
  group_by(timeperiod) |>
  filter(!is.nan(Outcome_CS) & !is.na(Outcome_CS))|>
  reframe(Outcome_CS = mean(Outcome_CS))
Tagg_PrePostBP_Basin_COOLABAHcs$geometry <- basin$geometry

Map_Tagg_PrePostBP_Basin_COOLABAH <- ggplot(data = Tagg_PrePostBP_Basin_COOLABAHcs,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = Outcome_CS))+
  #geom_sf_text(aes(label = ValleyName), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis',
                      limits = c(0,1)) +
  labs(fill = "Black box CS", y = "", x = "", colour = "")+
  facet_wrap(~timeperiod)

Map_Tagg_PrePostBP_Basin_COOLABAH

ggsave(plot = Map_Tagg_PrePostBP_Basin_COOLABAH, filename = file.path(plot_path, paste0("Map_Tagg_PrePostBP_Basin_COOLABAH","_", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 8)

```

```{r}
nrow(Valley_indicator_list)*3 + nrow(Valley_indicator_list_subset)

```

