---
title: "Data cleaning and setup"
editor: visual
echo: false
# setting fig-width: 7 and fig-height: 5 are the defaults, changing here to be more standard ms sizes
format:
  html:
    embed-resources: true
    toc: true
    fig-width: 9
    fig-height: 6
    comments:
      hypothesis: true
  docx:
    toc: true
    toc-depth: 2
    prefer-html: true
    fig-width: 9
    fig-height: 6
    reference-doc: ../default_word_template.docx
bibliography: references.bib
---

This is essentially a data cleaning script, but I like being able to put in notes and intermediate figs and whatnot. The idea is then it will get knitr::purled, I think. I could use a quarto include, but I don't want all the text etc.

```{r}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
#| include: false
library(eFlowEval)
library(sf)
source('directorySet.R')
source('R/catch_cat_sf.R')
library(dplyr)
library(ggplot2)
library(foreach) # needed internally for some funs
library(patchwork)
library(kableExtra)
```

```{r}

paperdatadir <- '' # was 'habprocesspaper/' when we used different data.

# I might end up linking these with the catchment-clipped version, but that would take a restructure. In the meantime, let's just do them separately.

figpath <- file.path(datOut, 'habprocesspaper', 'Figures', 'uncatchment')
tspath <- file.path(figpath, 'timeseries')
barpath <- file.path(figpath, 'bar')
mappath <- file.path(figpath, 'map')

if (!dir.exists(figpath)) {
  dir.create(figpath, recursive = TRUE)
}

if (!dir.exists(tspath)) {
  dir.create(tspath, recursive = TRUE)
}

if (!dir.exists(barpath)) {
  dir.create(barpath, recursive = TRUE)
}

if (!dir.exists(mappath)) {
  dir.create(mappath, recursive = TRUE)
}
```

## Data read-in

I'm leading with this because we're tweaking the data, but it could all be offloaded to a script to focus on the ms. Or just collapse the section.

I'm splitting this up into a few sections since the process and anae-clipped (2 ways) gets confusing to do in one go.

### Background

First, a few useful background pieces- which species, what are the anae types and a bit of a summary, etc

```{r}
#| label: which-data
species <- c('black_box', 'red_gum', 'coolabah', 'lignum')
species_names <- species |> 
  stringr::str_replace('_', ' ') |> 
  stringr::str_to_sentence()
```

```{r}
valleys <- ltimNoNorth |> 
  select(-ValleyID, -ValleyCode) |> 
  mutate(name_orig = ValleyName,
         ValleyName = stringr::str_remove_all(ValleyName, ' '))
```

What are the anae types?

```{r}
# this dataset generated in the diversity analysis is really useful to get overall info about what got inundated and the wetland areas, but it's massive. I need it here though to get assorted areas and the full set of anae types
diversity_anae_summary <- catch_cat_sf('diversity_anae_summary', 'diversity')
```

```{r}
# all_anaes <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))
# bbala <- readRDS(file.path(datOut, 'vegmapping', 'black_box_anae_type.rds'))

alatypes <- foreach(i = species,
                    .combine = bind_rows, .multicombine = TRUE) %do% {
  readRDS(file.path(datOut, 'vegmapping', paste0(i, '_anae_type.rds'))) |> 
                        mutate(species = i)
                    }

# That's useful to have in a dataframe, but in a few places I want a list too
type_list <- vector(mode = 'list', length = length(species)) |> setNames(species)
for (s in species) {
  
  # stolen from woody_general
    veg_grep <- dplyr::case_when(s == 'black_box' ~ 'black box',
                               s == 'red_gum' ~ 'red gum',
                               s == 'coolabah' ~ 'cool',
                               s == 'lignum' ~ 'lignum')
    
    
  spalatypes <- alatypes |> 
    filter(species == s) |> 
    pull(ANAE_DESC)
  
  # Use the full set of ANAEs, not just those that show up in the alas.
  spnametypes <- diversity_anae_summary |> 
    filter(grepl(veg_grep, ANAE_DESC, ignore.case = TRUE)) |> 
    pull(ANAE_DESC) |> 
    unique()
  
  type_list[[s]] <- list(alatype = spalatypes, nametype = spnametypes)
}

# Double check we pick up all the 'name's in the alas
# for (i in species) {
#   stype <- alatypes |> 
#     filter(species == i) |> 
#     select(ANAE_DESC) |> 
#     pull() |> 
#     unique()
#   
#   print(all(tl$nametype[[i]] %in% stype))
# }
# We do, so comment that out.


# We get the area in the different types below.
```

Where are the ala records?

```{r}
# use the anae overlap records, not the mdb, since the anae match the rest.
alarecords <- foreach(i = species,
                    .combine = bind_rows, .multicombine = TRUE) %do% {
  readRDS(file.path(datOut, 'vegmapping', paste0(i, '_anae_records.rds'))) |> 
                        mutate(species = i)
                    }

allrecords <- foreach(i = species,
                    .combine = bind_rows, .multicombine = TRUE) %do% {
  readRDS(file.path(datOut, 'vegmapping', paste0(i, '_mdb_records.rds'))) |> 
                        mutate(species = i)
                    }

allrecords <- allrecords |> 
  mutate(in_ala = recordID %in% alarecords$recordID)
```

### Process-only

These are the strictures for just biological processes.

```{r}
adult <- purrr::map(species, \(x) 
                    catch_cat_sf('adult_area', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult',
         species = x)) |> 
  bind_rows()

germ <- purrr::map(species, \(x) 
                   catch_cat_sf('germ_area', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination',
         species = x)) |> 
  bind_rows()

seed <- purrr::map(species, \(x) 
                   catch_cat_sf('seedling_area',
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling',
         species = x)) |> 
  bind_rows()

# Two step
adult_germ <- purrr::map(species, \(x) 
                            catch_cat_sf('adult_germ_area',
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_regen',
         species = x)) |> 
  bind_rows()

adult_germ_seed <- purrr::map(species, \(x) 
                            catch_cat_sf('adult_germ_seed_area',
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment',
         species = x)) |> 
  bind_rows()


```

### Habitat only

```{r}
# Keep using 'stage' as the name of the data, since it makes joining for comparison easier.

inun_anae_all <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun',
                                outerdir = paste0(paperdatadir, x)) |> 
                                 # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'all_wetlands',
         species = x)) |> 
  bind_rows()

inun_anae_name <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun_anae_name',
                                outerdir = paste0(paperdatadir, x)) |> 
                                 # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'anae_name',
         species = x)) |> 
  bind_rows()
  
# For most things, we'll use the records, but with the catchment clip requiring 10 or more to count. We will probably want the non-clipped in an appendix section.
inun_anae_ala <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun_anae_ala_catchment', 
                                outerdir = paste0(paperdatadir, x)) |> 
                                # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'anae_ala',
         species = x)) |> 
  bind_rows()

```

There are also two other sorts of baselines we might want for the habitat- the total amount of inundation in *any* wetland type, and the total amount of area in each set of habitats, ignoring inundation. I had been doing this in the appendix, but think I'll move the data extraction here, anyway.

```{r}
# One use- total area of wetland habitat regardless of inundation for each species in various ways
# First, get rid of the yearly since total area doesn't change and simplify

typearea <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  summarise(total_area = unique(total_area), .by = c(ANAE_DESC, name_clean))

# Now I want to get the total area attributable to each species' types. This seems like it should be a grouped operation, but they aren't mutually exclusive, so it's actually better to work with type_list and filter

# using the same stage names lets us use the same colors
total_wetland_area <- foreach(s = species, .combine = bind_rows, .multicombine = TRUE) %do% {
  alaarea <- typearea |> 
    # set area of non-matching types to 0, then sum over the catchment
    mutate(total_area = ifelse(ANAE_DESC %in% type_list[[s]]$alatype, total_area, 0)) |> 
    summarise(total_area = sum(total_area), .by = name_clean) |> 
    mutate(species = s, stage = 'anae_ala')
  
  namearea <- typearea |> 
    mutate(total_area = ifelse(ANAE_DESC %in% type_list[[s]]$nametype, total_area, 0)) |> 
    summarise(total_area = sum(total_area), .by = name_clean) |> 
    mutate(species = s, stage = 'anae_name')
  
  bind_rows(alaarea, namearea) |> 
    rename(ValleyName = name_clean)
}

total_wetland_area <- total_wetland_area |> 
  rename(area = total_area)


total_wetland_area_basin <- total_wetland_area |> 
  summarise(area = sum(area), .by = c(species, stage))

total_wetland_area <- total_wetland_area |> 
  left_join(valleys, by = 'ValleyName') |> 
  st_as_sf()
```

```{r}
#| eval: false
# a check of that, probably delete if passes- does that actually have all the anae wetlands?
all_anae <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))

all_anae <- all_anae |> 
  mutate(area = st_area(geometry))

all(unique(all_anae$ANAE_DESC) %in% typearea$ANAE_DESC)

# Yes, so no need for both.
```

```{r}

# First, simplify
# There's no species differences here
inun_area <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  rename(date = time) |> 
  mutate(ValleyName = name_clean) |> 
  summarise(area = sum(area_inundated, na.rm = TRUE),
            stage = 'wetland_inundation',
            .by = c(date, ValleyName)) |>
    left_join(valleys) |> 
    st_as_sf() |> 
  select(-name_orig)

```

### Interactive

Include independent and full for the stages. Skip the adult_germ, it's not very interesting

```{r}
# ALA records

# For most things, we will put the catchment conditions on these records, though in an appendix we may want to compare them.

adult_ala <- purrr::map(species, \(x) catch_cat_sf('adult_area_anae_ala_catchment', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_ala',
         species = x)) |> 
  bind_rows()

germ_ala <- purrr::map(species, \(x) catch_cat_sf('germ_area_anae_ala_catchment', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination_ala',
         species = x)) |> 
  bind_rows()

seed_ala <- purrr::map(species, \(x) catch_cat_sf('seedling_area_anae_ala_catchment', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling_ala',
         species = x)) |> 
  bind_rows()

adult_germ_ala <- purrr::map(species, \(x) catch_cat_sf('adult_germ_area_anae_ala_catchment', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration_ala',
         species = x)) |> 
  bind_rows()

adult_germ_seed_ala <- purrr::map(species, \(x) catch_cat_sf('adult_germ_seed_area_anae_ala_catchment', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment_ala',
         species = x)) |> 
  bind_rows()

# Name
# *don't* clip these by catchment, since it's about where the named wetlands are
adult_name <- purrr::map(species, \(x) catch_cat_sf('adult_area_anae_name', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_name',
         species = x)) |> 
  bind_rows()

germ_name <- purrr::map(species, \(x) catch_cat_sf('germ_area_anae_name', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination_name',
         species = x)) |> 
  bind_rows()

seed_name <- purrr::map(species, \(x) catch_cat_sf('seedling_area_anae_name', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling_name',
         species = x)) |> 
  bind_rows()

adult_germ_name <- purrr::map(species, \(x) catch_cat_sf('adult_germ_area_anae_name', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration_name',
         species = x)) |> 
  bind_rows()

adult_germ_seed_name <- purrr::map(species, \(x) catch_cat_sf('adult_germ_seed_area_anae_name', 
                                outerdir = paste0(paperdatadir, x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment_name',
         species = x)) |> 
  bind_rows()
```

### Concatenate

```{r}
all_data <- bind_rows(adult, germ, seed, 
                         adult_germ, adult_germ_seed, 
                         adult_ala, germ_ala, seed_ala,
                      adult_germ_ala, adult_germ_seed_ala,
                         adult_name, germ_name, seed_name,
                      adult_germ_name,
                      adult_germ_seed_name,
                         inun_anae_name, inun_anae_ala,
                      inun_area)

# To make data line up, we need a numeric year sometimes
all_data <- all_data |> 
  mutate(year = lubridate::year(date))

# Sum to the basin
all_data_basin <- all_data |>
  sf::st_drop_geometry() |>
  summarise(area = sumna(area),
            .by = c(date, year, stage, species)) |>
  bind_cols(basin) |>
  st_as_sf()

# average over time
all_data_time <- all_data |>
  group_by(ValleyName, stage, species) |> 
  summarise(area = meanna(area)) |>
  ungroup()

# sum to basin and average over time
all_data_basin_time <- all_data_basin |>
  group_by(stage, species) |> 
 summarise(area = meanna(area)) |> 
  ungroup()

rm(adult, germ, seed,
   adult_germ, adult_germ_seed,
   adult_ala, germ_ala, seed_ala,
   adult_germ_ala,
   adult_germ_seed_ala,
   adult_name, germ_name, seed_name,
   adult_germ_name,
   adult_germ_seed_name,
   inun_anae_name, inun_anae_ala, inun_area)

```

Set up a standard color palette for the types. Could do the same for species if we every plot those, and should choose a standard ramp for things like maps. Could do it for catchments too, but there's a million. This is ugly, but changing it is easy.

Clean up the names

```{r}
# Set up various groupings
# the different types
anae_stages <- c('Named wetland types', 'Recorded wetland types', 'All wetlands')
process_stages <- c('Adult', 'Germination', 'Seedling',
                    'Regeneration', 'Recruitment')
combo_stages <- c('Adult and Named', 'Germination and Named',
                  'Seedling and Named', 'Regeneration and Named', 'Recruitment and Named',
                  'Adult and Recorded', 'Germination and Recorded',
                  'Seedling and Recorded', 'Regeneration and Recorded',
                  'Recruitment and Recorded')

sequential_stages <- c('Adult', 'Regeneration', 'Recruitment',
                       'Recruitment and Named', 'Recruitment and Recorded')

sequential_hab <- c('Named wetland types', 'Recorded wetland types', 'All wetlands',
                       'Recruitment and Named', 'Recruitment and Recorded')

# The different comparisons across type
hab_all <- c('All wetlands', process_stages)
hab_named <- c('Named wetland types', combo_stages[grepl('Named', combo_stages)])
hab_record <- c('Recorded wetland types', combo_stages[grepl('Recorded', combo_stages)])

proc_adult <- c('Adult', combo_stages[grepl('Adult', combo_stages)])
proc_germ <- c('Germination', combo_stages[grepl('Germination', combo_stages)])
proc_seed <- c('Seedling', combo_stages[grepl('Seed', combo_stages)])
proc_regen <- c('Regeneration', combo_stages[grepl('Regeneration', combo_stages)])
proc_recruit <- c('Recruitment', combo_stages[grepl('Recruitment', combo_stages)])

```

```{r}
clean_stages <- function(x) {
  x <- x |> 
    mutate(stage_name = case_when(
      stage == 'adult' ~ 'Adult',
      stage == 'germination' ~ 'Germination',
      stage == 'seedling' ~ 'Seedling',
      stage == 'adult_regen' ~ 'Regeneration',
      stage == 'recruitment' ~ 'Recruitment',
      stage == 'adult_ala' ~ 'Adult and Recorded',
      stage == 'germination_ala' ~ 'Germination and Recorded',
      stage == 'seedling_ala' ~ 'Seedling and Recorded',
      stage == 'regeneration_ala' ~ 'Regeneration and Recorded',
      stage == 'recruitment_ala' ~ 'Recruitment and Recorded',
      stage == 'adult_name' ~ 'Adult and Named',
      stage == 'germination_name' ~ 'Germination and Named',
      stage == 'seedling_name' ~ 'Seedling and Named',
      stage == 'regeneration_name' ~ 'Regeneration and Named',
      stage == 'recruitment_name' ~ 'Recruitment and Named',
      stage == 'anae_name' ~ 'Named wetland types',
      stage == 'anae_ala' ~ 'Recorded wetland types',
      stage == 'wetland_inundation' ~ 'All wetlands',
      .default = 'FAIL'
    ),
    stage_name = factor(stage_name,
                        levels = c('All wetlands',
                                   'Recorded wetland types',
                                   'Named wetland types',
                                   'Adult', 'Germination', 'Seedling',
                                   'Regeneration', 'Recruitment',
                                   'Adult and Recorded',
                                   'Germination and Recorded',
                                   'Seedling and Recorded',
                                   'Regeneration and Recorded',
                                   'Recruitment and Recorded',
                                   'Adult and Named',
                                   'Germination and Named',
                                   'Seedling and Named',
                                   'Regeneration and Named',
                                   'Recruitment and Named')),
    # create an independent stage flag. don't includ adults, since they're both
    is_independent_proc = case_when(
      stage %in% c('germination', 'seedling',
                                                 'germination_ala', 'seedling_ala',
                                                 'germination_name', 'seedling_name') ~
                                      'independent',
                                    stage %in% c('adult', 'adult_regen', 'recruitment',
                                                 'adult_ala', 'adult_regen_ala',
                                                 'recruitment_ala',
                                                 'adult_name', 'adult_regen_name',
                                                 'recruitment_name') ~ 'sequential',
                                    .default = NA
      ),
    is_independent_proc = factor(is_independent_proc, levels = c('sequential', 'independent'))) |> 
    mutate(hab_type = case_when(
      stage_name %in% hab_all ~ "All wetlands",
                                stage_name %in% hab_named ~ "Named wetland types",
                                stage_name %in% hab_record ~ "Recorded wetland types",
                                .default = NA
      ),
           hab_type = factor(hab_type, levels = c('All wetlands',
                                                  'Recorded wetland types',
                                                  'Named wetland types')),
           proc_type = case_when(
             stage_name %in% proc_adult ~ "Adult",
                                 stage_name %in% proc_germ ~ "Germination",
                                 stage_name %in% proc_seed ~ "Seedling",
                                 stage_name %in% proc_regen ~ "Regeneration",
                                 stage_name %in% proc_recruit ~ "Recruitment",
                                 .default = NA
             ),
           model_type = case_when(
             stage_name %in% anae_stages ~ 'Wetland type',
                                  stage_name %in% process_stages ~ "Process",
                                  stage_name %in% combo_stages ~ "Process within\nwetland type", 
                                  .default = NA),
           model_type = factor(model_type, levels = c('Wetland type', 'Process', 'Process within\nwetland type')),
           proc_type = factor(proc_type, levels = c('Adult', 'Germination', 'Seedling', 'Regeneration', 'Recruitment')))
  
}
```

Use that to clean data

```{r}
all_data <- clean_stages(all_data)
all_data_basin <- clean_stages(all_data_basin)
all_data_time <- clean_stages(all_data_time)
all_data_basin_time <- clean_stages(all_data_basin_time)

# the wetland type area regardless of inundation
total_wetland_area <- clean_stages(total_wetland_area)
```

```{r}
# just to make it easy to access
stages <- unique(all_data$stage)
stagenames <- unique(all_data$stage_name)



#  "palettetown::surskit"
# "RColorBrewer::Set3"
# This worked pretty well with 12, but is a mess with 15.
# stage_pal <- HydroBOT::make_pal(stages, "rcartocolor::Safe")

# This is going to take some tweaking to get right.
# having hte names in separate vectors can make some filtering easier
# "beyonce::X41" "ggprism::plasma" "rcartocolor::ag_Sunset" "RColorBrewer::RdPu", direction = -1 "PNWColors::Sunset2"
anae_cols <- HydroBOT::make_pal(anae_stages, "rcartocolor::ag_Sunset")

process_stages <- c('Adult', 'Germination', 'Seedling',
                    'Regeneration', 'Recruitment')

process_cols <- HydroBOT::make_pal(process_stages,
                                       "calecopal::superbloom1")
# that last one is just barely too purple
process_cols[names(process_cols) == 'Recruitment'] <- '#527E87FF' # '#477173FF'

combo_cols <- HydroBOT::make_pal(combo_stages, "rcartocolor::Safe")

stage_pal <- c(anae_cols, process_cols, combo_cols)
class(stage_pal) <- 'colors'

# probably need to change this
type_pal <- HydroBOT::make_pal(c('Wetland type', 'Process', 'Process within\nwetland type'), "trekcolors::starfleet")


# make a consistent set of shapes that allows patchworking
shape_type <- scales::shape_pal()(3) |> 
  setNames(names(type_pal))

# make an alpha scale for that too
alpha_type <- c('Wetland type' = 1, 'Process' = 1, 'Process within\nwetland type' = 0.75)

# make an alpha scale for that too
line_type <- c('Wetland type' = 'solid', 'Process' = 'solid', 'Process within\nwetland type' = 'dashed')
```
