---
title: "Red gum analyses"
editor: visual
echo: false
# setting fig-width: 7 and fig-height: 5 are the defaults, changing here to be more standard ms sizes
format:
  html:
    embed-resources: true
    toc: true
    fig-width: 9
    fig-height: 6
    comments:
      hypothesis: true
  docx:
    toc: true
    toc-depth: 2
    prefer-html: true
    fig-width: 9
    fig-height: 6
    reference-doc: ../default_word_template.docx
bibliography: references.bib
---

This is essentially a script, but I like being able to put in notes and intermediate figs and whatnot. The idea is then it will get knitr::purled, I think. I could use a quarto include, but I don't want all the text etc.

It relies on 2_data_cleaning.qmd. Knit it, run it, and trash it.

This is ugly. Would be better to have functions and only return what we need, but we need a lot.

```{r}
#| label: read-data-clean
knitr::purl(file.path('HabProcessPaper', '2_data_cleaning.qmd'),
            file.path('HabProcessPaper', '2_data_cleaning.R'))

source(file.path('HabProcessPaper', '2_data_cleaning.R'))

unlink(file.path('HabProcessPaper', '2_data_cleaning.R'))
```

# PLOT BUILDING

The order these are easiest to build in is not necessarily the best presentation order.

## Basin-scale bar graphs over time

### Habitat alone

```{r}
#| label: habitat-bar-function
make_habitat_bar <- function(species) {
  
  hab_basin_bar <- all_data_basin |>
  filter((species == {{species}} | 
            is.na(species)) & 
           stage_name %in% anae_stages) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
  ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
  scale_fill_manual(values = stage_pal) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)', fill = 'Model')

  
  return(hab_basin_bar)
}

# Individual per-species plots
hab_basin_bar <- purrr::map(species, make_habitat_bar) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-bar-function
make_process_bar <- function(species) {
  
  proc_basin_bar <- all_data_basin |>
    filter((species == {{species}} |
              is.na(species)) & 
             stage_name %in% process_stages) |>
    sf::st_drop_geometry() |>
    summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
              sd_area = sd(log10(area + 1), na.rm = TRUE),
              is_independent_proc = unique(is_independent_proc),
              .by = stage_name) |>
    mutate(base_stage = case_when(
      stage_name == 'Adult' ~ 'Adult',
      stage_name %in% c('Germination', 'Regeneration') ~ 'Regeneration',
      stage_name %in% c('Seedling', 'Recruitment') ~ 'Recruitment'
      ),
      base_stage = factor(base_stage, levels = levels(stage_name))) |>
    ggplot(aes(x = base_stage, y = mean_area, fill = stage_name, color = is_independent_proc)) +
    geom_col(position = position_dodge()) +
    geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                   position = position_dodge(width = 0.9)) +
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = c(sequential = 'black', independent = 'grey70')) +
    HydroBOT::theme_werp_toolkit() +
    labs(y = 'Mean log(area + 1)', x = 'Step',
         fill = 'Life stage', color = 'Stage type')
  
  
  return(proc_basin_bar)
}

# Individual per-species plots
proc_basin_bar <- purrr::map(species, make_process_bar) |> 
  setNames(species)
```

### Interactive

Sequence through life cycle and then a habitat filter

```{r}
#| label: interact-sequential-function
make_interact_seq_bar <- function(species) {
  
 seq_proc_basin_bar <- all_data_basin |>
  filter((species == {{species}} |
            is.na(species)) & 
           stage_name %in% sequential_stages) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
  ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
  scale_fill_manual(values = stage_pal) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)',
       fill = 'Life stage')

  
  return(seq_proc_basin_bar)
}

# Individual per-species plots
interact_seq_basin_bar <- purrr::map(species, make_interact_seq_bar) |> 
  setNames(species)
```

What is the effect of process occurring within each habitat type?

```{r}
#| label: interact-sequential-hab-function
make_interact_hab_bar <- function(species) {
  
new_basin_bar_hab <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, hab_type, model_type)) |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
  ggplot(aes(x = hab_type, y = mean_area, fill = stage_name, color = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)',
       fill = 'Model', color = 'Model type')

  
  return(new_basin_bar_hab)
}

# Individual per-species plots
interact_hab_basin_bar <- purrr::map(species, make_interact_hab_bar) |> 
  setNames(species)
```

How much does habitat restrict each stage?

```{r}
#| label: interact-sequential-proc-function
make_interact_proc_bar <- function(species) {
  
new_basin_bar_proc <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           !is.na(proc_type)) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, model_type)) |>
  ggplot(aes(x = proc_type, y = mean_area, fill = stage_name, color = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = 'Mean log(area + 1)',
       fill = 'Model', color = 'Model type')

  
  return(new_basin_bar_proc)
}

# Individual per-species plots
interact_proc_basin_bar <- purrr::map(species, make_interact_proc_bar) |> 
  setNames(species)
```

### Stacked fig for paper

Make the simplified versions that accentuate what we want for the ms.

```{r}
#| label: interact-for-stacking
make_interact_hab2proc_bar <- function(species) {
  
basin_bar_hab2proc <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |>
  mutate(hab_comp = ifelse(grepl('Recruit', stage_name),
                           'Recruitment', as.character(hab_type)),
         hab_comp = factor(hab_comp, levels = levels(stage_name))) |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, hab_type, model_type, hab_comp)) |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
  ggplot(aes(x = hab_type, y = mean_area, fill = hab_comp,
             color = model_type,
             alpha = model_type,
             linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model",
       color = "Model type", linetype = "Model type",
       alpha = 'Model type')

  
  return(basin_bar_hab2proc)
}

make_interact_proc2hab_bar <- function(species) {
  
basin_bar_proc2hab <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           !is.na(proc_type) &
           !grepl('Germ|Seed', stage_name)) |>
  mutate(hab_comp = ifelse(as.character(hab_type) == 'All wetlands',
                           as.character(proc_type), as.character(hab_type)),
         hab_comp = factor(hab_comp, levels = c(levels(proc_type), "Recorded wetland types","Named wetland types"))) |>
  sf::st_drop_geometry() |>
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, hab_comp, model_type)) |>
  ggplot(aes(x = proc_type, y = mean_area,
             fill = hab_comp,
             color = model_type,
             alpha = model_type,
             linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model",
       color = "Model type", linetype = "Model type",
       alpha = 'Model type')

  
  return(basin_bar_proc2hab)
}

# Individual per-species plots
interact_basin_bar_hab2proc <- purrr::map(species, make_interact_hab2proc_bar) |> 
  setNames(species)
interact_basin_bar_proc2hab <- purrr::map(species, make_interact_proc2hab_bar) |> 
  setNames(species)
```

Make a legend for the barplot

```{r}
#| label: make-bar-legend
bar_legend_plot <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           stage_name %in% c(sequential_stages, anae_stages) &
           !grepl('Germ|Seed', stage_name)) |>
  sf::st_drop_geometry() |> 
  mutate(stage_fake = ifelse(grepl(' and ', as.character(stage_name)), 
                             as.character(hab_type),
                             as.character(stage_name)),
         stage_fake = factor(stage_fake, levels = levels(stage_name))) |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_fake, proc_type, model_type)) |>
ggplot(aes(x = proc_type, y = mean_area, 
           fill = stage_fake, 
           color = model_type, 
           alpha = model_type,
           linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model", 
       color = "Model type", linetype = "Model type", 
       alpha = 'Model type')

barbottom <- bar_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(fill = guide_legend(nrow = 3), color = guide_legend(nrow = 3))


bar_legend <- ggpubr::get_legend(bar_legend_plot)
bar_bottom_legend <- ggpubr::get_legend(barbottom)
```

```{r}
#| label: stacked-bar

# Save these out by default
make_stacked_bars <- function(species, print = TRUE) {
  
  bar_layout_stack <- "
AAA#C
BBB#C
"
  compare_bar <- (interact_basin_bar_hab2proc[[species]] +
                  scale_x_discrete(labels = \(x)
                                   stringr::str_wrap(x, width = 100)) +
                  theme(legend.position = 'none')) +
  (interact_basin_bar_proc2hab[[species]] + scale_x_discrete(labels = \(x)
                                        stringr::str_wrap(x, width = 100)) +
     theme(legend.position = 'none'))  +
  wrap_plots(ggpubr::as_ggplot(bar_legend), plot_spacer()) +
  plot_layout(design = bar_layout_stack)


  if (print) {
    thispath <- file.path(barpath, paste0(species, '_bar'))
    galenR::ggsave_multi(filename = thispath, plot = compare_bar, 
                         device = c('png', 'svg'),
                         width = 12, height = 9, units = "cm")
  }

  return(compare_bar)

}

all_stacked_bars <- purrr::map(species, make_stacked_bars) |> 
  setNames(species)
```

## Basin-scale timeseries

### Habitat alone

```{r}
#| label: habitat-ts-function
make_habitat_timeseries <- function(species) {
  
  hab_basin_ts <- all_data_basin |> 
  filter((species %in% {{species}} | is.na(species)) & 
           stage_name %in% anae_stages) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  # Seems like a good idea, but the 'All wetlands' isn't duplicated over species.
  # if (length(species) > 1) {
  #   hab_basin_ts <- hab_basin_ts +
  #     facet_wrap('species')
  # } 
  
  return(hab_basin_ts)
}

# Individual per-species plots
hab_basin_ts <- purrr::map(species, make_habitat_timeseries) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-ts-fun-allstages

make_all_process_ts <- function(species) {
  proc_basin_ts <- all_data_basin |> 
    filter(species == {{species}} & stage_name %in% process_stages) |> 
    ggplot(aes(x = year, y = log10(area + 1), color = stage_name,
           linetype = is_independent_proc, shape = model_type)) +
    geom_line(show.legend = TRUE) +
    geom_point(show.legend = TRUE) +
    scale_shape_manual(values = shape_type) +
    scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
    HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
    labs(y = "log(area + 1)", color = "Model",
       linetype = "Stage type", shape = "Model type")
  
  return(proc_basin_ts)
}

all_proc_basin_ts <- purrr::map(species, make_all_process_ts) |> 
  setNames(species)
```

Sequential

```{r}
#| label: proc-seq-ts-function
make_seq_process_ts <- function(species) {
  proc_basin_seq_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           # both process and sequential
           stage_name %in% process_stages &
           stage_name %in% sequential_stages) |> 
    ggplot(aes(x = year, y = log10(area + 1), 
               color = stage_name, 
               shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(proc_basin_seq_ts)
}


seq_proc_basin_ts <- purrr::map(species, make_seq_process_ts) |> 
  setNames(species)
```

### Interactive

Here, we decided the easiest is to do the relevant wetland types in separate panels

```{r}
#| label: proc-named-interact-ts-function
make_named_process_interact_ts <- function(species) {
  
  inter_basin_named_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           stage_name %in% c('Named wetland types', 'Recruitment and Named', 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(inter_basin_named_ts)
  
}



make_recorded_process_interact_ts <- function(species) {
  
  inter_basin_recorded_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           stage_name %in% c('Recorded wetland types', 
                             'Recruitment and Recorded', 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1),
           color = stage_name, shape = model_type)) +
  geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
      scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  scale_y_continuous() +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(inter_basin_recorded_ts)
}

interact_named_basin_ts <- purrr::map(species, 
                                      make_named_process_interact_ts) |> 
  setNames(species)
interact_recorded_basin_ts <- purrr::map(species,
                                         make_recorded_process_interact_ts) |> 
  setNames(species)
```

Construct Venn diagrams. I guess go ahead and do it for both recorded and named

```{r}
#| label: make-venn-data

# I think I will split this into data prep and plot construction

recorded_venn_data <- function(species) {
  # First, extract and organise the data into the right format (a col with the two main things with the interaction as 'overlap')
  venncheck <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(species == {{species}} & 
             stage_name %in% c('Recorded wetland types',
                               'Recruitment and Recorded',
                               'Recruitment')) |> 
    mutate(area = log10(area + 1)) |>
    mutate(area = area/max(area, na.rm = TRUE)) |> 
    # need to do a funny flip-flop here to get overlap in its own column
    tidyr::pivot_wider(id_cols = date,
                       names_from = stage_name,
                       values_from = area) |> 
    tidyr::pivot_longer(cols = c(Recruitment, `Recorded wetland types`),
                        names_to = 'stage_name',
                        values_to = 'area') |> 
    rename(overlap = `Recruitment and Recorded`)
  
  # Now calculate the radii and centers we need to plot with geom_circle
  venncheck <- venncheck |> 
    mutate(radius = sqrt(area/pi)) |> 
    mutate(d = galenR::find_d(unique(overlap),
                              radii = radius),
           .by = date) |> 
    mutate(centers = d*c(-0.5, 0.5)) |> 
    mutate(year = lubridate::year(date))
  
  return(venncheck)
}

named_venn_data <- function(species) {
  # First, extract and organise the data into the right format (a col with the two main things with the interaction as 'overlap')
  venncheck <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(species == {{species}} & 
             stage_name %in% c('Named wetland types',
                               'Recruitment and Named',
                               'Recruitment')) |> 
    mutate(area = log10(area + 1)) |>
    mutate(area = area/max(area, na.rm = TRUE)) |> 
    # need to do a funny flip-flop here to get overlap in its own column
    tidyr::pivot_wider(id_cols = date,
                       names_from = stage_name,
                       values_from = area) |> 
    tidyr::pivot_longer(cols = c(Recruitment, `Named wetland types`),
                        names_to = 'stage_name',
                        values_to = 'area') |> 
    rename(overlap = `Recruitment and Named`)
  
  # Now calculate the radii and centers we need to plot with geom_circle
  venncheck <- venncheck |> 
    mutate(radius = sqrt(area/pi)) |> 
    mutate(d = galenR::find_d(unique(overlap),
                              radii = radius),
           .by = date) |> 
    mutate(centers = d*c(-0.5, 0.5)) |> 
    mutate(year = lubridate::year(date))
  
  return(venncheck)
}

venndata_recorded <- purrr::map(species, recorded_venn_data) |> 
  setNames(species)
venndata_named <- purrr::map(species, named_venn_data) |> 
  setNames(species)
```

Create a legend that has all the levels. We could do something with limits and breaks, but it's terrible

```{r}
#| label: make-ts-legend
ts_legend_plot <- all_data_basin |>
  filter(is.na(is_independent_proc) | is_independent_proc == 'sequential') |>
  filter(!stage_name %in% c('Adult and Recorded', 'Regeneration and Recorded',
                            'Adult and Named', 'Regeneration and Named')) |>
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point() +
  HydroBOT::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")

# Some other legend orientations for testing
ts_legend_plot_bottom <- ts_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = guide_legend(nrow = 3), color = guide_legend(nrow = 3))

ts_legend_plot_bottom_notype <- ts_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = 'none', color = guide_legend(nrow = 3))

ts_legend <- ggpubr::get_legend(ts_legend_plot)
ts_legend_bottom <- ggpubr::get_legend(ts_legend_plot_bottom)
ts_legend_bottom_notype <- ggpubr::get_legend(ts_legend_plot_bottom_notype)

```

```{r}
#| label: venn-plot-funs

# this takes data, not species, as an argument
make_venn_plots <- function(venn_data) {
  vennplot <- ggplot(venn_data) + 
  ggforce::geom_circle(mapping = aes(x0 = year, y0 = centers, 
                            r = radius, 
                            fill = factor(stage_name)),
              alpha = 0.7) + 
   scale_fill_manual(values = stage_pal) +
  coord_fixed() + 
  lims(x = c(1988, NA)) +
  HydroBOT::theme_werp_toolkit(axis.ticks.y = element_blank(),
                                   axis.text.y = element_blank(),
                                   legend.position = 'none')
  return(vennplot)
}

vennplots_recorded <- purrr::map(venndata_recorded, make_venn_plots)
vennplots_named <- purrr::map(venndata_named, make_venn_plots)
```

### Stacked fig for paper

```{r}
#| label: stacked-fig

# Save these out by default
make_stacked_fig <- function(species, print = TRUE) {
  
  topplot <- (hab_basin_ts[[species]] + theme(legend.position = 'none')) + 
    (seq_proc_basin_ts[[species]] + theme(legend.position = 'none'))

ts_plot <-  topplot /
  (interact_named_basin_ts[[species]] + 
     theme(legend.position = 'none',
           axis.text.x = element_blank())) /
     (interact_recorded_basin_ts[[species]]  + 
        theme(legend.position = 'none',
              axis.text.x = element_blank(),
              plot.margin = unit(c(5,5,0,5), 'points'))) /
  wrap_plots(vennplots_recorded[[species]] + 
               theme(plot.margin = unit(c(0,5,5,5), 'points'))) /
  wrap_plots(ggpubr::as_ggplot(ts_legend_bottom)) + #ts_legend_bottom_notype
  plot_layout(heights = c(5,5,5,1,3)) +
  plot_annotation(tag_levels = list(c('a', 'b', 'c', 'd', 'e', '')))

  if (print) {
    thispath <- file.path(tspath, paste0(species, '_timeseries'))
    galenR::ggsave_multi(filename = thispath, plot = ts_plot, 
                         device = c('png', 'svg'),
                         width = 16, height = 22, units = "cm")
  }

  return(ts_plot)

}

all_stacked_ts <- purrr::map(species, make_stacked_fig) |> 
  setNames(species)
```

## Maps

### Background- ala records

The raw records

```{r}
#| label: ala-function
make_ala_record_map <- function(species) {
  
  # just species-facet, so no need to filter
  ala_maps <- alarecords |>
    mutate(species_name = stringr::str_replace(species, '_', ' ') |>
                                 stringr::str_to_sentence()) |> 
  # filter(species == {{species}}) |>
  ggplot() +
    geom_sf(data = valleys, fill = 'azure', color = 'grey80') +
    geom_sf(alpha = 0.3) +
  facet_wrap("species_name") +
  HydroBOT::theme_werp_toolkit(legend.position = 'none')

  
  return(ala_maps)
}

# Individual per-species plots
ala_records_map <- make_ala_record_map(NULL)
```

```{r}
#| label: allrecords-function
make_all_record_map <- function(species) {
  
  # just species-facet, so no need to filter
  ala_maps <- allrecords |>
    mutate(species_name = stringr::str_replace(species, '_', ' ') |>
                                 stringr::str_to_sentence()) |> 
  # filter(species == {{species}}) |>
  ggplot() +
    geom_sf(data = valleys, fill = 'azure', color = 'grey80') +
    geom_sf(alpha = 0.3, mapping = aes(color = in_ala)) +
  facet_wrap("species_name") +
    scale_color_manual(values = c('burlywood', 'seagreen') ) +
  HydroBOT::theme_werp_toolkit(legend.position = 'none')

  
  return(ala_maps)
}

# Individual per-species plots
all_records_map <- make_all_record_map(NULL)
```

summed by catchment (the sum by type is done in making the tables)

```{r}
#| label: ala-catch-function
make_ala_catch_map <- function() {
  
  catch_ala <- st_join(valleys, select(alarecords, species)) |>
  summarise(n_records = n(),
            .by = c(geometry, species, ValleyName)) |> 
  filter(!is.na(species))

# That drops the non-matches, which is super annoying
allpairs <- tidyr::expand_grid(species, ValleyName = unique(valleys$ValleyName))
joinpairs <- catch_ala |>
  st_drop_geometry() |>
  select(species, ValleyName)
missingpairs <- setdiff(allpairs, joinpairs) |>
  mutate(n_records = 0)

missingpairs <- left_join(missingpairs, valleys, by = 'ValleyName')

catch_ala <- bind_rows(catch_ala, missingpairs)

ala_catch_maps <- catch_ala |>
  mutate(species_name = stringr::str_replace(species, '_', ' ') |>
           stringr::str_to_sentence()) |>
  # filter(species == {{species}}) |>
  ggplot() +
  # geom_sf(data = basin, fill = 'azure') +
  geom_sf(aes(fill = log10(n_records))) +
  facet_wrap("species_name") +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  return(ala_catch_maps)
}

# Individual per-species plots
ala_catch_map <- make_ala_catch_map()
```

### Habitat alone

```{r}
#| label: habitat-map-function
make_habitat_map <- function(species) {
  
  hab_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in% anae_stages) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(hab_maps)
}

# Individual per-species plots
hab_basin_map <- purrr::map(species, make_habitat_map) |> 
  setNames(species)
```

The baseline- how much area is there in each habitat type?

We could make this for the other plots too; it is the ultimate baseline for the habitat analyses.

```{r}
#| label: totalhabitat-area-function
make_totalhabitat_map <- function(species) {
  
  hab_maps <- total_wetland_area |>
  filter(species == {{species}} & stage_name %in% anae_stages) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(hab_maps)
}

# Individual per-species plots
totalhab_basin_map <- purrr::map(species, make_totalhabitat_map) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-map-function
make_process_indep_map <- function(species) {
  
  pi_maps <- all_data_time |>
  filter(species == {{species}} &
           stage_name %in% c('Adult', 'Germination', 'Seedling')) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(pi_maps)
}

make_process_seq_map <- function(species) {
  
  ps_maps <- all_data_time |>
  filter(species == {{species}} & 
           stage_name %in% c('Adult', 'Regeneration', 'Recruitment')) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(ps_maps)
}

# Individual per-species plots
proc_indep_basin_map <- purrr::map(species, make_process_indep_map) |> 
  setNames(species)
proc_seq_basin_map <- purrr::map(species, make_process_seq_map) |> 
  setNames(species)
```

A joined version of the above. I had been using patchwork, but I think it's probably cleaner to just duplicate adults and facet

```{r}
#| label: process-indepseq-map-function
make_process_indepseq_map <- function(species) {
  
  # there's a lot of data cleaning, so just do it first
  adult_indep <- all_data_time |>
    filter(stage_name == "Adult") |>
    mutate(is_independent_proc = 'independent') |>
    bind_rows(all_data_time) |>
    mutate(base_stage = case_when(
      stage_name == 'Adult' ~ 'Adult',
      stage_name %in% c('Germination', 'Regeneration') ~ 'Regeneration',
      stage_name %in% c('Seedling', 'Recruitment') ~ 'Recruitment'
    ),
    base_stage = factor(base_stage, levels = levels(stage_name))) |>
    filter(species == {{species}} &
             base_stage %in% c('Adult', 'Regeneration', 'Recruitment'))
  
  # I was trying to label panels with their specific name, but it didn't work well
  # label_data <- adult_indep |>
  #   filter(species == 'red_gum' &
  #            base_stage %in% c('Adult', 'Regeneration', 'Recruitment')) |>
  #   filter(ValleyName == 'Warrego') |>
  #   reframe(stage_name = unique(stage_name), .by = geometry) |>
  #   st_as_sf()
  
  bio_both_maps <-
    ggplot() +
    geom_sf(data = adult_indep, aes(fill = log10(area + 1))) +
    # geom_sf_text(data = label_data,
    #              aes(label = stage_name), nudge_x = 1, nudge_y = 1) +
    scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
    facet_grid(is_independent_proc~base_stage) +
    HydroBOT::theme_werp_toolkit() +
    labs(fill = "log(area + 1)")
  
  
  
  return(bio_both_maps)
}

# Individual per-species plots
proc_indepseq_basin_map <- purrr::map(species, make_process_indepseq_map) |> 
  setNames(species)
```

### Interactive

Just interactive- I don't think we'll actually use this anywhere.

```{r}
#| label: interactive-alone-map-function
#| eval: false
make_interact_alone_map <- function(species) {
  
inter_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in%
           c('Recruitment and Named', 'Recruitment and Recorded')) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(inter_maps)
}

# Individual per-species plots
interact_alone_map <- purrr::map(species, make_interact_alone_map) |> 
  setNames(species)
```

Sequenced off process

```{r}
#| label: interactive-procseq-map-function
make_interact_procseq_map <- function(species) {
  
inter_seq_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in%
           sequential_stages) |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")

  
  return(inter_seq_maps)
}

# Individual per-species plots
interact_procseq_map <- purrr::map(species, make_interact_procseq_map) |> 
  setNames(species)
```

Sequenced off habitat

```{r}
#| label: interactive-habseq-map-function
make_interact_habseq_map <- function(species) {
  
  # Change the names here from the standard set to make the comparison clearer
habseqdata <- total_wetland_area |>
  mutate(stage_name = ifelse(grepl('Recorded', stage_name),
                             'Total Recorded', 'Total Named'),
         stage_name = factor(stage_name,
                             levels = c('Total Recorded', 'Total Named',
                                        levels(all_data_time$stage_name)))) |>
  bind_rows(all_data_time) |>
  mutate(stage_name = case_when(stage_name == 'Recorded wetland types' ~ 'Recorded and inundated',
                                stage_name == 'Named wetland types' ~ 'Named and inundated',
                                .default = stage_name),
         stage_name = factor(stage_name,
                             levels = c('Total Recorded', 'Total Named',
                                        'Recorded and inundated','Named and inundated',
                                        levels(all_data_time$stage_name)))) |>
  filter(species == {{species}} &
           stage_name %in% c(sequential_hab, 'Total Recorded', 'Total Named',
                             'Recorded and inundated','Named and inundated'))

inter_habseq_maps <- habseqdata |>
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_wrap('stage_name', nrow = 3) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = "log(area + 1)")
  
  return(inter_habseq_maps)
}

# Individual per-species plots
interact_habseq_map <- purrr::map(species, make_interact_habseq_map) |> 
  setNames(species)
```

The plot for the paper

```{r}
#| label: map-for-paper

# Save these out by default
make_interact2d_fig <- function(species, print = TRUE) {
  
  inter_matrix_maps <- all_data_time |>
  filter((species == {{species}} | 
            is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment')) |>
  mutate(stage_name = forcats::fct_drop(stage_name)) |>
  # filter(!is.na(species)) |> #
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_wrap('stage_name', nrow = 2, drop = FALSE) +
  # facet_wrap('stage_name', ncol = 3) +
  HydroBOT::theme_werp_toolkit() +
  labs(fill = 'log(area + 1)')



  if (print) {
    thispath <- file.path(mappath, paste0(species, '_map'))
    galenR::ggsave_multi(filename = thispath, 
                         plot = inter_matrix_maps, 
                         device = c('png', 'svg'),
                         width = 16, height = 9, units = "cm")
  }

  return(inter_matrix_maps)

}

all_interactmap <- purrr::map(species, make_interact2d_fig) |> 
  setNames(species)
```
