---
title: "Figures and analyses for method matters"
editor: visual
echo: false
format:
  html:
    embed-resources: true
    toc: true
    fig-width: 9
    fig-height: 6
    comments:
      hypothesis: true
  docx:
    toc: true
    toc-depth: 2
    prefer-html: true
    fig-width: 9
    fig-height: 6
    reference-doc: default_word_template.docx
bibliography: references.bib
---

This is essentially a script, but I like being able to put in notes and intermediate figs and whatnot. The idea is then it will get knitr::purled. In practice, for the paper, these get inserted into Word. For other purposes, we could use a quarto include, but I don't want all the text etc.

It relies on 2_data_cleaning.qmd. Knit it, run it, and trash it.

This is ugly. Would be better to have functions and only return what we need, but we need a lot.

```{r}
#| label: read-data-clean
knitr::purl(file.path('HabProcessPaper', '2_data_cleaning.qmd'),
            file.path('HabProcessPaper', '2_data_cleaning.R'))

source(file.path('HabProcessPaper', '2_data_cleaning.R'))

unlink(file.path('HabProcessPaper', '2_data_cleaning.R'))
```

# PLOT BUILDING

The order these are easiest to build in is not necessarily the best presentation order.

## Basin-scale boxplots over time

### Habitat alone

```{r}
#| label: habitat-box-function
make_habitat_box <- function(species) {
  
    hab_basin_box <- all_data_basin |>
  filter((species == {{species}} | 
            is.na(species)) & 
           stage_name %in% anae_stages) |>
  sf::st_drop_geometry() |>
  ggplot(aes(x = stage_name, y = (hectares + 1/10000), fill = stage_name)) +
  geom_boxplot() +
    # delete this later, useful to see how the data is distributed
  # geom_point(position = position_jitter(width = 0.1), alpha = 0.5) +
  scale_fill_manual(values = stage_pal) +
    scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = 'hectares', fill = 'Model')

  
  return(hab_basin_box)
}

# Individual per-species plots
hab_basin_box <- purrr::map(species, make_habitat_box) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-box-function
make_process_box <- function(species) {
  
  
  proc_basin_box <- all_data_basin |>
    filter((species == {{species}} |
              is.na(species)) &
             stage_name %in% process_stages) |>
    sf::st_drop_geometry() |>
      mutate(base_stage = case_when(
      stage_name == 'Adult' ~ 'Adult',
      stage_name %in% c('Germination', 'Regeneration') ~ 'Regeneration',
      stage_name %in% c('Seedling', 'Recruitment') ~ 'Recruitment'
      ),
      base_stage = factor(base_stage, levels = levels(stage_name))) |>
    ggplot(aes(x = base_stage, y = hectares + 1/10000,
               fill = stage_name,
               color = is_independent_proc)) +
    geom_boxplot(position = position_dodge()) +
    # geom_point(alpha = 0.5,
    #                position = position_jitterdodge(jitter.width = 0.4)) +
    scale_fill_manual(values = stage_pal) +
    scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
    scale_color_manual(values = c(sequential = 'black', independent = 'grey70')) +
    galenR::theme_clean() +
    labs(y = 'hectares', x = 'Step',
         fill = 'Life stage', color = 'Stage type')
  
  
  return(proc_basin_box)
}

# Individual per-species plots
proc_basin_box <- purrr::map(species, make_process_box) |> 
  setNames(species)
```

### Interactive

Sequence through life cycle and then a habitat filter

```{r}
#| label: interact-sequential-function
make_interact_seq_box <- function(species) {
  
   seq_proc_basin_box <- all_data_basin |>
  filter((species == {{species}} |
            is.na(species)) & 
           stage_name %in% sequential_stages) |>
  sf::st_drop_geometry() |>
    ggplot(aes(x = stage_name, y = hectares + 1/10000, fill = stage_name)) +
  geom_boxplot() +
  # geom_point(alpha = 0.5, position = position_dodge(width = 0.1)) +
  scale_fill_manual(values = stage_pal) +
     scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = 'hectares',
       fill = 'Life stage')

  
  return(seq_proc_basin_box)
}

# Individual per-species plots
interact_seq_basin_box <- purrr::map(species, make_interact_seq_box) |> 
  setNames(species)
```

What is the effect of process occurring within each habitat type?

```{r}
#| label: interact-sequential-hab-function
make_interact_hab_box <- function(species) {
  
new_basin_box_hab <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
  ggplot(aes(x = hab_type, y = hectares + 1/10000, fill = stage_name, color = model_type)) +
  geom_boxplot(position = position_dodge()) +
    # geom_point(alpha = 0.5,
    #                position = position_jitterdodge(jitter.width = 0.4)) +
       scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = type_pal) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = 'hectares',
       fill = 'Model', color = 'Model type')

  
  return(new_basin_box_hab)
}

# Individual per-species plots
interact_hab_basin_box <- purrr::map(species, make_interact_hab_box) |> 
  setNames(species)
```

How much does habitat restrict each stage?

```{r}
#| label: interact-sequential-proc-function
make_interact_proc_box <- function(species) {

  
  new_basin_box_proc <- all_data_basin |>
    filter((species == {{species}} | is.na(species)) &
             !is.na(proc_type)) |>
    sf::st_drop_geometry() |>
    ggplot(aes(x = proc_type, y = hectares + 1/10000, fill = stage_name, color = model_type)) +
    geom_boxplot(position = position_dodge()) +
    # geom_point(alpha = 0.5,
    #            position = position_jitterdodge(jitter.width = 0.4)) +
    scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
    galenR::theme_clean(axis.title.x = element_blank()) +
    labs(y = 'hectares',
         fill = 'Model', color = 'Model type')

  
  return(new_basin_box_proc)
}

# Individual per-species plots
interact_proc_basin_box <- purrr::map(species, make_interact_proc_box) |> 
  setNames(species)
```

### Stacked fig for paper

Make the simplified versions that accentuate what we want for the ms.

```{r}
#| label: interact-for-stacking
make_interact_hab2proc_box <- function(species) {

basin_box_hab2proc <- all_data_basin |>
  filter((species == {{species}} | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |>
  mutate(hab_v_proc = ifelse(grepl('Recruit', stage_name),
                           'Recruitment', 'None (habitat only)'),
         hab_v_proc = factor(hab_v_proc, 
                             levels = c('None (habitat only)', 
                                        'Adult', 'Regeneration', 'Recruitment'))) |>
  mutate(fill_hab = ifelse(is.na(proc_type), 'dummy', as.character(hab_type)),
         fill_hab = factor(fill_hab, levels = c('dummy', levels(hab_type)))) |> 
    # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
  ggplot(aes(x = hab_type, y = hectares + 1/10000, fill = fill_hab,
             color = hab_v_proc)) +
    geom_boxplot(position = position_dodge(), show.legend = TRUE,
                 size = 0.4, outlier.size = 0.4) +
    # geom_point(alpha = 0.5,
    #            position = position_jitterdodge(jitter.width = 0.4)) +
    scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  scale_fill_manual(values = wetland_type_pal_fill, guide = FALSE) +
  scale_color_manual(values = c(process_cols_seq,
                                'None (habitat only)' = 'black')) +
  galenR::theme_clean(axis.title.x = element_blank(),
                               axis.text = element_text(color = "black")) +
  labs(y = "Favorable area (ha)",
       color = "Process-based model")


  return(basin_box_hab2proc)
}

make_interact_proc2hab_box <- function(species) {

basin_box_proc2hab <- all_data_basin |>
    sf::st_drop_geometry() |>
  filter((species == {{species}} | is.na(species)) &
           !is.na(proc_type) &
           !grepl('Germ|Seed', stage_name)) |>
  mutate(hab_v_proc = ifelse(is.na(proc_type), 'None (habitat only)', as.character(proc_type)),
         hab_v_proc = factor(hab_v_proc, levels = c('None (habitat only)', levels(proc_type)))) |>
  mutate(fill_hab = ifelse(proc_type != 'Recruitment', 'dummy', as.character(hab_type)),
         fill_hab = factor(fill_hab, levels = c('dummy', levels(hab_type)))) |>
    ggplot(aes(x = proc_type, y = hectares + 1/10000,
               fill = fill_hab,
             color = hab_type)) +
    geom_boxplot(position = position_dodge(), show.legend = TRUE,
                 size = 0.4, outlier.size = 0.4) +
    # geom_point(alpha = 0.5,
    #            position = position_jitterdodge(jitter.width = 0.4)) +
    scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  scale_fill_manual(values = wetland_type_pal_fill) +
  scale_color_manual(values = wetland_type_pal) +
  galenR::theme_clean(axis.title.x = element_blank(),
                               axis.text = element_text(color = "black")) +
  labs(y = "Favorable area (ha)", fill = "Habitat-based model",
       color = "Habitat-based model")


  return(basin_box_proc2hab)
}

# Individual per-species plots
interact_basin_box_hab2proc <- purrr::map(species, make_interact_hab2proc_box) |> 
  setNames(species)
interact_basin_box_proc2hab <- purrr::map(species, make_interact_proc2hab_box) |> 
  setNames(species)
```

```{r}
#| label: stacked-box

# Save these out by default
make_stacked_boxs <- function(species, print = TRUE) {
  
  
#   box_layout_stack <- "
# AAA#C
# BBB#C
# "
  compare_box <- (interact_basin_box_hab2proc[[species]] +
                  scale_x_discrete(labels = scales::label_wrap(14))) /
  (interact_basin_box_proc2hab[[species]] + 
     scale_x_discrete(labels = scales::label_wrap(14))) +
    plot_annotation(tag_levels = 'a') 


  if (print) {
    thispath <- file.path(boxpath, paste0(species, '_box'))
    galenR::ggsave_multi(filename = thispath, plot = compare_box, 
                         device = c('png', 'pdf'),
                         width = 16, height = 12, units = "cm")
  }

  return(compare_box)

}

all_stacked_boxs <- purrr::map(species, make_stacked_boxs) |> 
  setNames(species)



```

Make a table of the means

```{r}

basin_table <- all_data_basin |>
  st_drop_geometry() |> 
  mutate(hab_v_proc = ifelse(is.na(proc_type), 'Habitat inundation', as.character(proc_type)),
         hab_v_proc = factor(hab_v_proc, levels = c('Habitat inundation', levels(proc_type)))) |>
  filter(!grepl('Germ|Seed', stage_name)) |>
   
  summarise(hectares = mean(hectares, na.rm = TRUE),
            .by = c(stage_name, species, hab_v_proc, hab_type))
```

Make some tables of the means.

```{r}
# It is possible to have adult favourability *higher* than wetland_inundation, and adult_ala and adult_name higher than anae_ala and anae_name (which are both inundation areas), becuase the favourability does not rely on inundation, and certainly not in that year.  

# it *should* always be less than the total area of wetlands or the named types, but that's not what this is looking at.

areatab <- function(species1) {
  artab <- basin_table |> 
  filter(species == species1 | is.na(species)) |> # THe NA species is no process or habitat filters (i.e. Process = None, habitat = all wetland types) 
  select(-stage_name, -species) |>
  mutate(hectares = formatC(hectares, 
                                                        format = 'f', 
                                                        digits = 2,
                                                        big.mark = ',')) |> # Technically, this could be anything, since we're splitting polygons. And orig data is in meters.
  tidyr::pivot_wider(names_from = hab_v_proc, values_from = hectares) |> 
  select(' ' = hab_type, `Habitat inundation`, everything()) |> 
    flextable::flextable()
  # knitr::kable() |>
  # column_spec(1, bold = TRUE, border_right = TRUE) |> 
  # kable_styling()
  
  return(artab)
}

tablist <- purrr::map(species, areatab) |> 
  setNames(species)

purrr::imap(tablist, \(x,y) flextable::save_as_docx(x, path = file.path(boxpath, paste0(y, '_summary_table.docx'))))

tablist
```

## Basin-scale timeseries

### Habitat alone

```{r}
#| label: habitat-ts-function
make_habitat_timeseries <- function(species) {
  
  hab_basin_ts <- all_data_basin |> 
  filter((species %in% {{species}} | is.na(species)) & 
           stage_name %in% anae_stages) |> 
ggplot(aes(x = year, y = hectares + 1/10000, 
           color = wetland_colour, shape = proc_shape)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE, size =3)  +
    scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
    scale_color_manual(values = wetland_type_pal) +
  scale_shape_manual(values = shape_type_process, guide = FALSE) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "Favorable area (ha)", color = "Habitat model",
       shape = "Process model")
  
  # Seems like a good idea, but the 'All wetlands' isn't duplicated over species.
  # if (length(species) > 1) {
  #   hab_basin_ts <- hab_basin_ts +
  #     facet_wrap('species')
  # } 
  
  return(hab_basin_ts)
}

# Individual per-species plots
hab_basin_ts <- purrr::map(species, make_habitat_timeseries) |> 
  setNames(species)

```

Calculate some fractions

```{r}
areatab <- total_wetland_area_basin |> 
  filter(species == 'red_gum' | is.na(species)) |> 
  select(-species, -area) |> 
  tidyr::pivot_wider(names_from = stage, values_from = hectares) |> 
  mutate(fracname = anae_name/anae_all, fracala = anae_ala/anae_all)
areatab
```

```{r}

  hab_basin_area_scaled_ts <- all_data_basin |> 
    st_drop_geometry() |> 
  filter((species %in% 'red_gum' | is.na(species)) & 
           stage_name %in% anae_stages) |> 
    select(year, hectares, stage_name) |> 
    tidyr::pivot_wider(names_from = stage_name, values_from = hectares) |> 
    mutate(area_all = areatab$anae_all,
           area_name = areatab$anae_name,
           area_ala = areatab$anae_ala) |> 
    mutate(`All wetland types` = `All wetland types`/area_all,
           `Named wetland types` = `Named wetland types`/area_name,
           `Recorded wetland types` = `Recorded wetland types`/area_ala)
  # 
  # mutate(fracname_inun = `Named wetland types`/`All wetland types`,
  #        fracala_inun = `Recorded wetland types`/`All wetland types`)
hab_basin_area_scaled_ts |> 
  select(year, contains('wetland')) |> 
  tidyr::pivot_longer(cols = contains('wetland'), 
                      names_to = 'Wetland type model', values_to = 'Fraction area\ninundated') |> 
  ggplot(aes(x = year, y = `Fraction area\ninundated`, color = `Wetland type model`)) +
  geom_point() + geom_line() +
   scale_color_manual(values = wetland_type_pal) +
  galenR::theme_clean(axis.title.x = element_blank())
```

### Process alone

```{r}
#| label: process-ts-fun-allstages

make_all_process_ts <- function(species) {
  proc_basin_ts <- all_data_basin |> 
    filter(species == {{species}} & stage_name %in% process_stages) |> 
    ggplot(aes(x = year, y = hectares + 1/10000, color = stage_name,
           linetype = is_independent_proc, shape = model_type)) +
    geom_line(show.legend = TRUE) +
    geom_point(show.legend = TRUE, size =3) +
        scale_y_continuous(trans = 'log10', labels = scales::label_log()) +

    scale_shape_manual(values = shape_type) +
    scale_color_manual(values = stage_pal) +
    galenR::theme_clean(axis.title.x = element_blank()) +
    labs(y = "Favorable area (ha)", color = "Model",
       linetype = "Stage type", shape = "Model type")
  
  return(proc_basin_ts)
}

all_proc_basin_ts <- purrr::map(species, make_all_process_ts) |> 
  setNames(species)
```

Sequential

```{r}
#| label: proc-seq-ts-function
make_seq_process_ts <- function(species) {
  proc_basin_seq_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           # both process and sequential
           stage_name %in% process_stages &
           stage_name %in% sequential_stages) |> 
    ggplot(aes(x = year, y = hectares + 1/10000, 
               color = hab_type, shape = stage_name), alpha = 1) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE, size =3)  +
            scale_y_continuous(trans = 'log10', labels = scales::label_log()) +

  scale_color_manual(values = wetland_type_pal, guide = FALSE) +
  scale_shape_manual(values = shape_type_process) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "Favorable area (ha)", color = "Habitat model", shape = "Process model")
  
  return(proc_basin_seq_ts)
}


seq_proc_basin_ts <- purrr::map(species, make_seq_process_ts) |> 
  setNames(species)
```

### Interactive

Here, we decided the easiest is to do the relevant wetland types in separate panels

```{r}
#| label: proc-named-interact-ts-function
make_named_process_interact_ts <- function(species) {
  
  inter_basin_named_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           stage_name %in% c('Named wetland types', 'Recruitment and Named', 'Recruitment')) |> 
ggplot(aes(x = year, y = hectares + 1/10000, 
           color = wetland_colour , shape = proc_shape )) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE, size =3)  +
            scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  scale_color_manual(values = wetland_type_pal) +
  scale_shape_manual(values = shape_type_process) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "Favorable area (ha)", color = "Habitat model", shape = "Process model")
  
  return(inter_basin_named_ts)
  
}



make_recorded_process_interact_ts <- function(species) {
  
  inter_basin_recorded_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           stage_name %in% c('Recorded wetland types', 
                             'Recruitment and Recorded', 'Recruitment')) |> 
ggplot(aes(x = year, y = hectares + 1/10000,
           color = wetland_colour , shape = proc_shape )) +
  geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE, size =3)  +
  scale_color_manual(values = wetland_type_pal) +
  scale_shape_manual(values = shape_type_process) +
            scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "Favorable area (ha)", color = "Habitat model", shape = "Process model")
  
  return(inter_basin_recorded_ts)
}

interact_named_basin_ts <- purrr::map(species, 
                                      make_named_process_interact_ts) |> 
  setNames(species)
interact_recorded_basin_ts <- purrr::map(species,
                                         make_recorded_process_interact_ts) |> 
  setNames(species)
```

Construct Venn diagrams. I guess go ahead and do it for both recorded and named

```{r}
#| label: make-venn-data

# I think I will split this into data prep and plot construction

recorded_venn_data <- function(species) {
  # First, extract and organise the data into the right format (a col with the two main things with the interaction as 'overlap')
  venncheck <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(species == {{species}} & 
             stage_name %in% c('Recorded wetland types',
                               'Recruitment and Recorded',
                               'Recruitment')) |> 
    # need to think harder about these, but we're changin them anyway.
    # can't use hectares, or we get some <1 and that gives - logs and that gives NaN for sqrt in the radius
    mutate(logarea = log10(area + 1)) |>
    mutate(proplogarea = logarea/max(logarea, na.rm = TRUE),
        # mutate(proparea = (hectares+1)/max((hectares+1), na.rm = TRUE),
  
      proc_shape = case_when(
      stage == 'adult' ~ 'Adult',
      stage == 'germination' ~ 'Germination',
      stage == 'seedling' ~ 'Seedling',
      stage == 'adult_regen' ~ 'Regeneration',
      stage == 'recruitment' ~ 'Recruitment',
      stage == 'adult_ala' ~ 'Adult',
      stage == 'germination_ala' ~ 'Germination',
      stage == 'seedling_ala' ~ 'Seedling',
      stage == 'regeneration_ala' ~ 'Regeneration',
      stage == 'recruitment_ala' ~ 'Recruitment',
      stage == 'adult_name' ~ 'Adult',
      stage == 'germination_name' ~ 'Germination',
      stage == 'seedling_name' ~ 'Seedling ',
      stage == 'regeneration_name' ~ 'Regeneration',
      stage == 'recruitment_name' ~ 'Recruitment',
      stage == 'anae_name' ~ 'None (habitat only)',
      stage == 'anae_ala' ~ 'None (habitat only)',
      stage == 'wetland_inundation' ~ 'None (habitat only)',
      .default = stage_name
    ),
    
      wetland_colour = case_when(
      stage == 'adult' ~ 'All wetland types',
      stage == 'germination' ~ 'All wetland types',
      stage == 'seedling' ~ 'All wetland types',
      stage == 'adult_regen' ~ 'All wetland types',
      stage == 'recruitment' ~ 'All wetland types',
      stage == 'adult_ala' ~ 'All wetland types',
      stage == 'germination_ala' ~ 'Recorded wetland types',
      stage == 'seedling_ala' ~ 'Recorded wetland types',
      stage == 'regeneration_ala' ~ 'Recorded wetland types',
      stage == 'recruitment_ala' ~ 'Recorded wetland types',
      stage == 'adult_name' ~ 'Named wetland types',
      stage == 'germination_name' ~ 'Named wetland types',
      stage == 'seedling_name' ~ 'Named wetland types',
      stage == 'regeneration_name' ~ 'Named wetland types',
      stage == 'recruitment_name' ~ 'Named wetland types',
      stage == 'anae_name' ~ 'Named wetland types',
      stage == 'anae_ala' ~ 'Recorded wetland types',
      stage == 'wetland_inundation' ~ 'All wetland types',
      .default = stage_name
    ),
    proc_shape = factor(proc_shape,
                        levels = c('Adult', 'Germination', 'Seedling',
                                   'Regeneration', 'Recruitment',
                                   'None (habitat only)'))) |> 
    # need to do a funny flip-flop here to get overlap in its own column
    tidyr::pivot_wider(id_cols = date,
                       names_from = stage_name,
                       values_from = proplogarea) |> 
    tidyr::pivot_longer(cols = c(Recruitment, `Recorded wetland types`),
                        names_to = 'stage_name',
                        values_to = 'proplogarea') |> 
    rename(overlap = `Recruitment and Recorded`)
  
  # Now calculate the radii and centers we need to plot with geom_circle
  venncheck <- venncheck |> 
    mutate(radius = sqrt(proplogarea/pi)) |> 
    mutate(d = galenR::find_d(unique(overlap),
                              radii = radius),
           .by = date) |> 
    mutate(centers = d*c(-0.5, 0.5)) |> 
    mutate(year = lubridate::year(date))
  
  return(venncheck)
}

named_venn_data <- function(species) {
  # First, extract and organise the data into the right format (a col with the two main things with the interaction as 'overlap')
  venncheck <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(species == {{species}} & 
             stage_name %in% c('Named wetland types',
                               'Recruitment and Named',
                               'Recruitment')) |> 
    # need to think harder about these, but we're changin them anyway
    mutate(logarea = log10(area + 1)) |>
    mutate(proplogarea = logarea/max(logarea, na.rm = TRUE),
        # mutate(proparea = (hectares+1)/max((hectares+1), na.rm = TRUE),
      proc_shape = case_when(
      stage == 'adult' ~ 'Adult',
      stage == 'germination' ~ 'Germination',
      stage == 'seedling' ~ 'Seedling',
      stage == 'adult_regen' ~ 'Regeneration',
      stage == 'recruitment' ~ 'Recruitment',
      stage == 'adult_ala' ~ 'Adult',
      stage == 'germination_ala' ~ 'Germination',
      stage == 'seedling_ala' ~ 'Seedling',
      stage == 'regeneration_ala' ~ 'Regeneration',
      stage == 'recruitment_ala' ~ 'Recruitment',
      stage == 'adult_name' ~ 'Adult',
      stage == 'germination_name' ~ 'Germination',
      stage == 'seedling_name' ~ 'Seedling ',
      stage == 'regeneration_name' ~ 'Regeneration',
      stage == 'recruitment_name' ~ 'Recruitment',
      stage == 'anae_name' ~ 'None (habitat only)',
      stage == 'anae_ala' ~ 'None (habitat only)',
      stage == 'wetland_inundation' ~ 'None (habitat only)',
      .default = stage_name
    ),
      wetland_colour = case_when(
      stage == 'adult' ~ 'All wetland types',
      stage == 'germination' ~ 'All wetland types',
      stage == 'seedling' ~ 'All wetland types',
      stage == 'adult_regen' ~ 'All wetland types',
      stage == 'recruitment' ~ 'All wetland types',
      stage == 'adult_ala' ~ 'All wetland types',
      stage == 'germination_ala' ~ 'Recorded wetland types',
      stage == 'seedling_ala' ~ 'Recorded wetland types',
      stage == 'regeneration_ala' ~ 'Recorded wetland types',
      stage == 'recruitment_ala' ~ 'Recorded wetland types',
      stage == 'adult_name' ~ 'Named wetland types',
      stage == 'germination_name' ~ 'Named wetland types',
      stage == 'seedling_name' ~ 'Named wetland types',
      stage == 'regeneration_name' ~ 'Named wetland types',
      stage == 'recruitment_name' ~ 'Named wetland types',
      stage == 'anae_name' ~ 'Named wetland types',
      stage == 'anae_ala' ~ 'Recorded wetland types',
      stage == 'wetland_inundation' ~ 'All wetland types',
      .default = stage_name
    ),
    proc_shape = factor(proc_shape,
                        levels = c('Adult', 'Germination', 'Seedling',
                                   'Regeneration', 'Recruitment',
                                   'None (habitat only)'))) |> 
    # need to do a funny flip-flop here to get overlap in its own column
    tidyr::pivot_wider(id_cols = date,
                       names_from = stage_name,
                       values_from = proplogarea) |> 
    tidyr::pivot_longer(cols = c(Recruitment, `Named wetland types`),
                        names_to = 'stage_name',
                        values_to = 'proplogarea') |> 
    rename(overlap = `Recruitment and Named`)
  
  # Now calculate the radii and centers we need to plot with geom_circle
  venncheck <- venncheck |> 
    mutate(radius = sqrt(proplogarea/pi)) |> 
    mutate(d = galenR::find_d(unique(overlap),
                              radii = radius),
           .by = date) |> 
    mutate(centers = d*c(-0.5, 0.5)) |> 
    mutate(year = lubridate::year(date))
  
  return(venncheck)
}

venndata_recorded <- purrr::map(species, recorded_venn_data) |> 
  setNames(species)


venndata_named <- purrr::map(species, named_venn_data) |> 
  setNames(species)
```

Create a legend that has all the levels. We could do something with limits and breaks, but it's terrible

```{r}
#| label: make-ts-legend
ts_legend_plot <- all_data_basin |>
  filter(is.na(is_independent_proc) | is_independent_proc == 'sequential') |>
  filter(!stage_name %in% c('Adult and Recorded', 'Regeneration and Recorded',
                            'Adult and Named', 'Regeneration and Named')) |>
ggplot(aes(x = year, y = hectares + 1/10000, 
           color = wetland_colour, shape = proc_shape)) +
  geom_line() +
              scale_y_continuous(trans = 'log10', labels = scales::label_log()) +

  scale_color_manual(values = wetland_type_pal) +
  scale_shape_manual(values = shape_type_process) +
geom_point() +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "hectares", color = "Wetland type models", shape = "Process-based models")

# Some other legend orientations for testing
ts_legend_plot_bottom <- ts_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = guide_legend(nrow = 4), color = guide_legend(nrow = 3))

ts_legend_plot_bottom_notype <- ts_legend_plot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = 'none', color = guide_legend(nrow = 3))

ts_legend <- ggpubr::get_legend(ts_legend_plot)
ts_legend_bottom <- ggpubr::get_legend(ts_legend_plot_bottom)
ts_legend_bottom_notype <- ggpubr::get_legend(ts_legend_plot_bottom_notype)

```

```{r}
#| label: venn-plot-funs

# this takes data, not species, as an argument
make_venn_plots <- function(venn_data) {
  vennplot <- ggplot(venn_data) + 
  ggforce::geom_circle(mapping = aes(x0 = year, y0 = centers, 
                            r = radius, 
                            fill = factor(stage_name)),
              alpha = 0.5) + 
    
  ggforce::geom_circle(mapping = aes(x0 = year, y0 = centers, 
                            r = radius, 
                            color = factor(stage_name)),
              alpha = 1) + 
   scale_fill_manual(values = c(wetland_type_pal,
                                'Recruitment' = 
                                  as.character(wetland_type_pal['All wetland types']))) +
   scale_colour_manual(values = c(wetland_type_pal,
                                'Recruitment' = 
                                  as.character(wetland_type_pal['All wetland types']))) +
  coord_fixed() + 
  lims(x = c(1988, NA)) +
  galenR::theme_clean(axis.ticks.y = element_blank(),
                                   axis.text.y = element_blank(),
                                   legend.position = 'none')
  return(vennplot)
}

vennplots_recorded <- purrr::map(venndata_recorded, make_venn_plots)
vennplots_named <- purrr::map(venndata_named, make_venn_plots)


unique(venndata_recorded$red_gum$stage_name)
```

### Stacked fig for paper

```{r}
#| label: stacked-fig

# Save these out by default
make_stacked_fig <- function(species, print = TRUE) {
  
  topplot <- (hab_basin_ts[[species]] + 
                theme(legend.position = 'bottom', 
                      legend.title.position = 'top', 
                      legend.direction = 'vertical',
             legend.title = element_blank()) +
               ggtitle('Habitat-based')) + 
    (seq_proc_basin_ts[[species]] + 
       theme(legend.position = 'bottom', 
                      legend.title.position = 'top', 
                      legend.direction = 'vertical',
             legend.title = element_blank()) +
               ggtitle('Process-based'))

ts_plot <-  topplot /
  (interact_named_basin_ts[[species]] + 
     theme(legend.position = 'none',
           axis.text.x = element_blank()) +
               ggtitle('Combined models: recruitment and named')) /
     (interact_recorded_basin_ts[[species]]  + 
        theme(legend.position = 'none',
              # axis.text.x = element_blank(),
              # plot.margin = unit(c(5,5,0,5), 'points')
              ) +
               ggtitle('Combined models: recruitment and recorded')
      ) + # /
  # wrap_plots(vennplots_recorded[[species]] + 
  #              theme(plot.margin = unit(c(0,5,5,5), 'points'))) /
  # wrap_plots(ggpubr::as_ggplot(ts_legend_bottom)) + #ts_legend_bottom_notype
  # plot_layout(heights = c(5,5,5,1,3)) +
    plot_layout(heights = c(4,4,4)) +
  plot_annotation(tag_levels = list(c('a', 'b', 'c', 'd')))

  if (print) {
    thispath <- file.path(tspath, paste0(species, '_timeseries'))
    galenR::ggsave_multi(filename = thispath, plot = ts_plot, 
                         device = c('png', 'pdf'),
                         width = 16, height = 22, units = "cm")
  }

  return(ts_plot)

}

all_stacked_ts <- purrr::map(species, make_stacked_fig) |> 
  setNames(species)
```

### Overlap fig

we want overlap vs % time conditions met. For each spp and life stage.

Overlap is fine (it's the Recruitment and Named), but then we need the separate parts.

```{r}
separated_habproc <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(stage_name %in% c('Named wetland types',
                             'Recorded wetland types',
                             'Recruitment and Named',
                             'Recruitment and Recorded',
                             'Recruitment')) |> 
  select(year, stage_name, species, hectares) |> 
  tidyr::pivot_wider(names_from = stage_name, values_from = hectares) |> 
  mutate(`Recruitment outside Named` = (Recruitment - `Recruitment and Named`),
         `Named only` = (`Named wetland types`-Recruitment),
         `Recruitment outside Recorded` = (Recruitment - 
                                             `Recruitment and Recorded`),
         `Recorded only` = (`Recorded wetland types`- Recruitment))

```

These are basically it, though they aren't particularly informative vs. what's in the paper.

```{r}

overlapcolors <- c(wetland_type_pal['Named wetland types'],
                   wetland_type_pal['Recorded wetland types'],
             'Named only' = "#8DA0CBFF",
             'Recorded only' = "#FC8D62FF",
             'Recruitment and Named' = "#8DA0CBFF",
             'Recruitment and Recorded' = '#FC8D62FF',
             'Recruitment' = '#66C2A5FF',
             'Recruitment outside Named' = '#66C2A5FF',
             'Recruitment outside Recorded' = '#66C2A5FF'
             )



make_named_overlap_ts <- function(species) {
  
  interact_named_basin_ts <- purrr::map(species, 
                                      make_named_process_interact_ts) |> 
  setNames(species)
named_separated_ts <- separated_habproc |> 
  tidyr::pivot_longer(cols = -c(year, species), 
                      names_to = 'stage_name', 
                      values_to = 'hectares') |>
  filter(stage_name %in% c('Recruitment and Named',
                           'Recruitment outside Named',
                           'Named only',
                           'Named wetland types',
                           'Recruitment') &
         species == {{species}}) |> 
mutate(Type = case_when(stage_name %in% 
                          c('Recruitment', 'Named wetland types') ~ 'Total',
                          stage_name %in% 
                          c('Recruitment outside Named', 'Named only',
                            'Recruitment and Named') ~ 'Separate')) |> 
  mutate(stage_name = factor(stage_name, 
                             levels = c('Named wetland types', 'Recruitment',
                                        'Named only', 'Recruitment outside Named',
                                        'Recruitment and Named'))) |> 
ggplot(aes(y = hectares, x = year, color = stage_name, 
           shape = Type, linetype = Type)) + 
  geom_point() + geom_line() +
  scale_color_manual(values = overlapcolors) +
  # scale_shape_manual(values = shape_type_process) +
            scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "Favorable area (ha)", color = "Grouping",
       linetype = 'Combination', shape = "Combination")

return(named_separated_ts)
}

make_recorded_overlap_ts <- function(species) {
  recorded_separated_ts <- separated_habproc |> 
  tidyr::pivot_longer(cols = -c(year, species), 
                      names_to = 'stage_name', 
                      values_to = 'hectares') |>
  filter(stage_name %in% c('Recruitment and Recorded',
                           'Recruitment outside Recorded',
                           'Recorded only',
                           'Recorded wetland types',
                           'Recruitment') &
         species == {{species}}) |> 
mutate(Type = case_when(stage_name %in% 
                          c('Recruitment', 'Recorded wetland types') ~ 'Total',
                          stage_name %in% 
                          c('Recruitment outside Recorded', 'Recorded only',
                            'Recruitment and Recorded') ~ 'Separate')) |> 
  mutate(stage_name = factor(stage_name, 
                             levels = c('Recorded wetland types', 'Recruitment',
                                        'Recorded only',
                                        'Recruitment outside Recorded',
                                        'Recruitment and Recorded'))) |> 
ggplot(aes(y = hectares, x = year, color = stage_name, 
           shape = Type, linetype = Type)) + 
  geom_point() + geom_line() +
  scale_color_manual(values = overlapcolors) +
  # scale_shape_manual(values = shape_type_process) +
            scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  galenR::theme_clean(axis.title.x = element_blank()) +
  labs(y = "Favorable area (ha)", color = "Grouping", shape = "Combination",
       linetype = "Combination")
  
  return(recorded_separated_ts)
}

overlap_named_basin_ts <- purrr::map(species, 
                                      make_named_overlap_ts) |> 
  setNames(species)

overlap_recorded_basin_ts <- purrr::map(species, 
                                      make_recorded_overlap_ts) |> 
  setNames(species)
```

```{r}
overlap_named_basin_ts['red_gum']
```

```{r}
overlap_recorded_basin_ts['red_gum']
```

Print it out

```{r}


make_stack_overlap <- function(species) {
  ts_plot <- overlap_named_basin_ts[[species]] / 
    overlap_recorded_basin_ts[[species]] + 
    plot_layout(guides = 'collect')
  
    thispath <- file.path(tspath, paste0(species, '_timeseries_overlap'))
    galenR::ggsave_multi(filename = thispath, plot = ts_plot, 
                         device = c('png', 'pdf'),
                         width = 16, height = 16, units = "cm")
}

stack_overlap_ts <- purrr::map(species, make_stack_overlap)

```

Tabular is actually better in a lot of ways.

```{r}
recorded_sep_ts <- separated_habproc |> 
  select(species, year, `Recruitment outside Recorded`, `Recruitment and Recorded`,
         `Recorded only`, Recruitment, `Recorded wetland types`)

named_sep_ts <- separated_habproc |> 
  select(species, year, `Recruitment outside Named`, `Recruitment and Named`, `Named only`,
         `Named only`, Recruitment, `Named wetland types`)

recorded_sep <- recorded_sep_ts |> 
  summarise(across(matches('Recruit|Record'), \(x) mean(x, na.rm = TRUE)),
            .by = "species") 



named_sep <- named_sep_ts |> 
  summarise(across(matches('Recruit|Named'), \(x) mean(x, na.rm = TRUE)),
            .by = "species")

# print those out
recorded_sep |> 
  mutate(across(matches('Recruit|Record'), \(x) formatC(x, 
                                                        format = 'f', 
                                                        digits = 2,
                                                        big.mark = ','))) |> 
  flextable::flextable() |> 
  flextable::save_as_docx(path = file.path(tspath, 'overall_separated_record.docx'))

named_sep |> 
    mutate(across(matches('Recruit|Record'), \(x) formatC(x, 
                                                        format = 'f', 
                                                        digits = 2,
                                                        big.mark = ','))) |> 
  flextable::flextable() |> 
  flextable::save_as_docx(path = file.path(tspath, 'overall_separated_named.docx'))
```

Save those out

```{r}
make_ts_separated_tab <- function(species1) {
  recorded_sep_ts |> 
      mutate(across(matches('Recruit|Record'), \(x) formatC(x, 
                                                        format = 'f', 
                                                        digits = 2,
                                                        big.mark = ','))) |> 
    filter(species == {{species1}}) |> 
    flextable::flextable() |> 
  flextable::save_as_docx(path = file.path(tspath, paste0(species1, '_separated_record.docx')))
  
    named_sep_ts |> 
        mutate(across(matches('Recruit|Record'), \(x) formatC(x, 
                                                        format = 'f', 
                                                        digits = 2,
                                                        big.mark = ','))) |> 
    filter(species == {{species1}}) |> 
    flextable::flextable() |> 
  flextable::save_as_docx(path = file.path(tspath, paste0(species1, '_separated_named.docx')))
}

purrr::map(species, make_ts_separated_tab)
```

### Tolerance

Get the tolerance and proportion of tolerance for the new figure

```{r}

# For some reason this is easier to break apart
tolerance_width_recruit <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(stage_name %in% c('Recruitment',
                             'Recruitment and Named',
                             'Recruitment and Recorded')) |> 
  select(year, stage_name, species, hectares) |> 
  tidyr::pivot_wider(names_from = stage_name, values_from = hectares) |> 
  summarise(tolerance_width = sum(Recruitment, na.rm = TRUE),
            overlap_named = sum(`Recruitment and Named`, na.rm = TRUE),
            overlap_recorded = sum(`Recruitment and Recorded`, na.rm = TRUE),
            .by = species) |> 
  mutate(stage_name = 'Recruitment')

tolerance_width_regen <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(stage_name %in% c('Regeneration',
                             'Regeneration and Named',
                             'Regeneration and Recorded')) |> 
  select(year, stage_name, species, hectares) |> 
  tidyr::pivot_wider(names_from = stage_name, values_from = hectares) |> 
  summarise(tolerance_width = sum(Regeneration, na.rm = TRUE),
            overlap_named = sum(`Regeneration and Named`, na.rm = TRUE),
            overlap_recorded = sum(`Regeneration and Recorded`, na.rm = TRUE),
            .by = species) |> 
  mutate(stage_name = 'Regeneration')
  
tolerance_width_adult <- all_data_basin |> 
    sf::st_drop_geometry() |> 
    filter(stage_name %in% c('Adult',
                             'Adult and Named',
                             'Adult and Recorded')) |> 
  select(year, stage_name, species, hectares) |> 
  tidyr::pivot_wider(names_from = stage_name, values_from = hectares) |> 
  summarise(tolerance_width = sum(Adult, na.rm = TRUE),
            overlap_named = sum(`Adult and Named`, na.rm = TRUE),
            overlap_recorded = sum(`Adult and Recorded`, na.rm = TRUE),
            .by = species) |> 
  mutate(stage_name = 'Adult')

tolerance_width <- bind_rows(tolerance_width_recruit, tolerance_width_regen, tolerance_width_adult) |> 
  mutate(stage_name = factor(stage_name, levels = levels(all_data_basin$stage_name))) |> 
  mutate(proportion_overlap_recorded = overlap_recorded/tolerance_width,
         proportion_overlap_named = overlap_named/tolerance_width)
  
```

Most of the naive plots here kind of dance around the issue. Like this one, which doesn't look at the proportion.

```{r}
ggplot(tolerance_width, 
       aes(x = tolerance_width, y = overlap_recorded, color = stage_name, shape = species, group = stage_name)) + geom_line() +
  geom_point() +
 scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean()
```

```{r}
ggplot(tolerance_width, 
       aes(x = tolerance_width, y = overlap_named, color = stage_name, shape = species, group = stage_name)) + geom_line() +
  geom_point() +
 scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean()
```

What we really want is whether the overlap is a consistent fraction of the 'tolerance'. That's only one axis and it captures the main issue that we'd expect both to go up together.

```{r}
prop_record <- tolerance_width  |> 
ggplot(aes(y = proportion_overlap_recorded, 
           x = forcats::fct_reorder(species, proportion_overlap_recorded),
           color = stage_name)) + 
  geom_point()  +
  geom_line(aes(group = stage_name)) +
  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean() +
  labs(y = 'Overlap proportion', x = NULL, color = 'Life stage')

prop_named <-  tolerance_width  |> 
ggplot(aes(y = proportion_overlap_named, 
           x = forcats::fct_reorder(species, proportion_overlap_recorded), # keep order the same
           color = stage_name)) + 
  geom_point()   +
  geom_line(aes(group = stage_name)) +
  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean() +
  labs(y = 'Overlap proportion', x = NULL, color = 'Life stage')

prop_record + prop_named + 
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides = 'collect')
```

Does it make more sense to flip?

```{r}
prop_record_s <- tolerance_width  |> 
ggplot(aes(y = proportion_overlap_recorded, 
           x = stage_name,
           color = species)) + 
  geom_point()  +
  geom_line(aes(group = species)) +
  # scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean() +
  labs(y = 'Overlap proportion', x = NULL, color = 'Species')

prop_named_s <-  tolerance_width  |> 
ggplot(aes(y = proportion_overlap_named, 
           x = stage_name, 
           color = species)) + 
  geom_point()   +
  geom_line(aes(group = species)) +
#  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean() +
  labs(y = 'Overlap proportion', x = NULL, color = 'Species')

prop_record_s + prop_named_s + 
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides = 'collect')
```

This is better - does more environmental tolerance (tolerance) mean that a greater proportion of the tolerated area is in both models (overlap)? IE does tolerance reduce the impact of model choice?

Across stages, yes. Across species, not clear.

```{r}
prop_v_tolerance_record <- tolerance_width  |> 
ggplot(aes(y = proportion_overlap_recorded, 
           x = tolerance_width, color = stage_name, shape = species, group = stage_name)) + 
  geom_point()  +
  geom_line(aes(group = stage_name)) +
  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean() +
  scale_x_continuous(trans = 'log10')
  # labs(y = 'Overlap proportion', x = NULL, color = 'Life stage')

prop_v_tolerance_named <- tolerance_width  |> 
ggplot(aes(y = proportion_overlap_named, 
           x = tolerance_width, color = stage_name, shape = species, group = stage_name)) + 
  geom_point()   +
  geom_line(aes(group = stage_name)) +
  scale_color_manual(values = process_cols_seq) +
  galenR::theme_clean() +
  scale_x_continuous(trans = 'log10')
  # labs(y = 'Overlap proportion', x = NULL, color = 'Life stage')

prop_v_tolerance_record + prop_v_tolerance_named + 
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides = 'collect')
```

How about a version where we look at recruitment across species for both recorded and named, and then another panel where we draw the lines across stages?

```{r}
# The above is good, but just isn't working very well with the legends. Can i do a better job witht hem?
prop_v_tolerance_record_v_name <- tolerance_width  |> 
  select(tolerance_width, stage_name, species, proportion_overlap_recorded, proportion_overlap_named) |> 
  tidyr::pivot_longer(cols = starts_with('proportion'),
                      names_to = 'hab_mod', values_to = 'overlap_proportion') |>
  mutate(hab_mod = stringr::str_replace_all(hab_mod, 'proportion_overlap_', '')) |> 
  mutate(hab_mod = stringr::str_to_sentence(hab_mod))  |> 
  mutate(species = stringr::str_replace_all(species, '_', ' '),
         species = stringr::str_to_sentence(species))|>
  filter(stage_name == 'Recruitment') |> 
ggplot(aes(y = overlap_proportion, 
           x = tolerance_width, 
           linetype = hab_mod,
           shape = stage_name,
           group = hab_mod)) + 
  geom_point(aes(color = species)) +
  geom_line(aes(group = hab_mod)) +
  scale_shape_manual(values = c(16,17,15) |> 
                       setNames(c('Adult', 'Regeneration', 'Recruitment')),
                     guide = FALSE) +
  scale_color_manual(values = spp_pal, guide = FALSE) +
    scale_x_continuous(trans = 'log10', labels = scales::label_log()) +
  galenR::theme_clean()  +
  labs(y = 'Overlap proportion', x = 'Tolerance (process area in ha)',
       color = 'Species', shape = 'Process', linetype = 'Habitat')
  # labs(y = 'Overlap proportion', x = NULL, color = 'Life stage')

prop_v_tolerance_stages <- tolerance_width  |> 
    select(tolerance_width, stage_name, species, proportion_overlap_recorded, proportion_overlap_named) |> 
    tidyr::pivot_longer(cols = starts_with('proportion'),
                        names_to = 'hab_mod', values_to = 'overlap_proportion') |>
    mutate(hab_mod = stringr::str_replace_all(hab_mod, 'proportion_overlap_', '')) |> 
    mutate(hab_mod = stringr::str_to_sentence(hab_mod)) |> 
  mutate(species = stringr::str_replace_all(species, '_', ' '),
         species = stringr::str_to_sentence(species)) |> 
    ggplot(aes(y = overlap_proportion, 
               x = tolerance_width, 
               shape = stage_name,
               color = species,
               linetype = hab_mod,
               group = interaction(species, hab_mod))) + 
    geom_point()   +
    geom_line() +
    galenR::theme_clean() +
  scale_color_manual(values = spp_pal) +
    scale_x_continuous(trans = 'log10', labels = scales::label_log()) +
  labs(y = 'Overlap proportion', x = 'Tolerance (process area in ha)',
       color = 'Species', shape = 'Process', linetype = 'Habitat')

tolerance_panel <- prop_v_tolerance_record_v_name / 
                  prop_v_tolerance_stages + 
  plot_annotation(tag_levels = 'a') + plot_layout(guides = 'collect')

tolerance_panel

# this is overall, so I guess save it with the boxplots
    galenR::ggsave_multi(filename = file.path(boxpath, 'tolerance'),
                         plot = tolerance_panel,
                         device = c('png', 'pdf'),
                         width = 16, height = 12, units = "cm")

```

## Maps

### Background- ala records

The raw records

```{r}
#| label: ala-function
make_ala_record_map <- function(species) {
  
  # just species-facet, so no need to filter
  ala_maps <- alarecords |>
    mutate(species_name = stringr::str_replace(species, '_', ' ') |>
                                 stringr::str_to_sentence()) |> 
  # filter(species == {{species}}) |>
  ggplot() +
    geom_sf(data = valleys, fill = 'azure', color = 'grey80') +
    geom_sf(alpha = 0.3) +
  facet_wrap("species_name") +
  galenR::theme_clean(legend.position = 'none')

  
  return(ala_maps)
}

# Individual per-species plots
ala_records_map <- make_ala_record_map(NULL)
```

```{r}
#| label: allrecords-function
make_all_record_map <- function(species) {
  
  # just species-facet, so no need to filter
  ala_maps <- allrecords |>
    mutate(species_name = stringr::str_replace(species, '_', ' ') |>
                                 stringr::str_to_sentence()) |> 
  # filter(species == {{species}}) |>
  ggplot() +
    geom_sf(data = valleys, fill = 'azure', color = 'grey80') +
    geom_sf(alpha = 0.3, mapping = aes(color = in_ala)) +
  facet_wrap("species_name") +
    scale_color_manual(values = c('burlywood', 'seagreen') ) +
        scale_x_continuous(breaks = c(140, 150)) +
    scale_y_continuous(breaks = c(-28, -32, -36)) +
  galenR::theme_clean(legend.position = 'none')

  
  return(ala_maps)
}

# Individual per-species plots
all_records_map <- make_all_record_map(NULL)

galenR::ggsave_multi(file.path(mappath, 'ala_records'), plot = all_records_map,
             device = c('pdf', 'png'),
                     width = 12, height = 12, units = 'cm')
```

summed by catchment (the sum by type is done in making the tables)

```{r}
#| label: ala-catch-function
make_ala_catch_map <- function() {
  
  catch_ala <- st_join(valleys, select(alarecords, species)) |>
  summarise(n_records = n(),
            .by = c(geometry, species, ValleyName)) |> 
  filter(!is.na(species))

# That drops the non-matches, which is super annoying
allpairs <- tidyr::expand_grid(species, ValleyName = unique(valleys$ValleyName))
joinpairs <- catch_ala |>
  st_drop_geometry() |>
  select(species, ValleyName)
missingpairs <- setdiff(allpairs, joinpairs) |>
  mutate(n_records = 0)

missingpairs <- left_join(missingpairs, valleys, by = 'ValleyName')

catch_ala <- bind_rows(catch_ala, missingpairs)

ala_catch_maps <- catch_ala |>
  mutate(species_name = stringr::str_replace(species, '_', ' ') |>
           stringr::str_to_sentence()) |>
  # filter(species == {{species}}) |>
  ggplot() +
  # geom_sf(data = basin, fill = 'azure') +
  geom_sf(aes(fill = n_records)) +
  facet_wrap("species_name") +
  scale_fill_viridis_c(option = 'mako', trans = 'log10',
                       labels = scales::label_log()) + # , limits = (c(0, 22))
      scale_x_continuous(breaks = c(140, 150)) +
    scale_y_continuous(breaks = c(-28, -32, -36)) +
  galenR::theme_clean() +
  labs(fill = "ALA records")

  return(ala_catch_maps)
}

# Individual per-species plots
ala_catch_map <- make_ala_catch_map()

galenR::ggsave_multi(file.path(mappath, 'ala_catchment'), plot = ala_catch_map,
             device = c('pdf', 'png'),
                     width = 12, height = 12, units = 'cm')

```

### Habitat alone

```{r}
#| label: habitat-map-function
make_habitat_map <- function(species) {
  
  hab_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in% anae_stages) |>
  ggplot(aes(fill = hectares + 1/10000)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', labels = scales::label_log()) + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  galenR::theme_clean() +
  labs(fill = "hectares")

  
  return(hab_maps)
}

# Individual per-species plots
hab_basin_map <- purrr::map(species, make_habitat_map) |> 
  setNames(species)
```

The baseline- how much area is there in each habitat type?

We could make this for the other plots too; it is the ultimate baseline for the habitat analyses.

```{r}
#| label: totalhabitat-area-function
make_totalhabitat_map <- function(species) {
  
  hab_maps <- total_wetland_area |>
  filter(species == {{species}} & stage_name %in% anae_stages) |>
  ggplot(aes(fill = hectares)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log()) + # , limits = (c(0, 22))
  facet_grid(.~stage_name, labeller = label_wrap_gen(18)) +
    scale_x_continuous(breaks = c(140, 150)) +
    scale_y_continuous(breaks = c(-28, -32, -36)) +
  galenR::theme_clean() +
  labs(fill = "Area (ha)")

  
  return(hab_maps)
}

# Individual per-species plots
totalhab_basin_map <- purrr::map(species, make_totalhabitat_map) |> 
  setNames(species)
```

Make that plot; previously in the 'Appendces' qmd

```{r}
totalhab_maps <- purrr::imap(totalhab_basin_map, \(x, i)
                             x + ggtitle(stringr::str_replace(i, '_', ' ') |> 
                                           stringr::str_to_sentence())) |>
  wrap_plots() + 
  plot_layout(guides = 'collect') & 
  # make common limits
  scale_fill_viridis_c(option = 'mako', 
                       trans = 'log10', , 
                       labels = scales::label_log(),
                       limits = c(1, 10^7)) &
  theme(legend.position = 'bottom')

galenR::ggsave_multi(file.path(mappath, 'wetland_area'), plot = totalhab_maps,
             device = c('pdf', 'png'),
                     width = 16, height = 12, units = 'cm')
```

### Process alone

```{r}
#| label: process-map-function
make_process_indep_map <- function(species) {
  
  pi_maps <- all_data_time |>
  filter(species == {{species}} &
           stage_name %in% c('Adult', 'Germination', 'Seedling')) |>
  ggplot(aes(fill = hectares + 1/10000)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', labels = scales::label_log()) + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  galenR::theme_clean() +
  labs(fill = "hectares")

  
  return(pi_maps)
}

make_process_seq_map <- function(species) {
  
  ps_maps <- all_data_time |>
  filter(species == {{species}} & 
           stage_name %in% c('Adult', 'Regeneration', 'Recruitment')) |>
  ggplot(aes(fill = hectares + 1/10000)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', labels = scales::label_log()) + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  galenR::theme_clean() +
  labs(fill = "hectares")

  
  return(ps_maps)
}

# Individual per-species plots
proc_indep_basin_map <- purrr::map(species, make_process_indep_map) |> 
  setNames(species)
proc_seq_basin_map <- purrr::map(species, make_process_seq_map) |> 
  setNames(species)
```

A joined version of the above. I had been using patchwork, but I think it's probably cleaner to just duplicate adults and facet

```{r}
#| label: process-indepseq-map-function
make_process_indepseq_map <- function(species) {
  
  # there's a lot of data cleaning, so just do it first
  adult_indep <- all_data_time |>
    filter(stage_name == "Adult") |>
    mutate(is_independent_proc = 'independent') |>
    bind_rows(all_data_time) |>
    mutate(base_stage = case_when(
      stage_name == 'Adult' ~ 'Adult',
      stage_name %in% c('Germination', 'Regeneration') ~ 'Regeneration',
      stage_name %in% c('Seedling', 'Recruitment') ~ 'Recruitment'
    ),
    base_stage = factor(base_stage, levels = levels(stage_name))) |>
    filter(species == {{species}} &
             base_stage %in% c('Adult', 'Regeneration', 'Recruitment'))
  
  bio_both_maps <-
    ggplot() +
    geom_sf(data = adult_indep, aes(fill = hectares + 1/10000)) +
    # geom_sf_text(data = label_data,
    #              aes(label = stage_name), nudge_x = 1, nudge_y = 1) +
    scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log()) + # , limits = (c(0, 22))
    facet_grid(is_independent_proc~base_stage) +
    galenR::theme_clean() +
    labs(fill = "hectares")
  
  
  
  return(bio_both_maps)
}

# Individual per-species plots
proc_indepseq_basin_map <- purrr::map(species, make_process_indepseq_map) |> 
  setNames(species)
```

### Interactive

Just interactive- I don't think we'll actually use this anywhere.

```{r}
#| label: interactive-alone-map-function
#| eval: false
make_interact_alone_map <- function(species) {
  
inter_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in%
           c('Recruitment and Named', 'Recruitment and Recorded')) |>
  ggplot(aes(fill = hectares + 1/10000)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log()) + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  galenR::theme_clean() +
  labs(fill = "hectares")

  
  return(inter_maps)
}

# Individual per-species plots
interact_alone_map <- purrr::map(species, make_interact_alone_map) |> 
  setNames(species)
```

Sequenced off process

```{r}
#| label: interactive-procseq-map-function
make_interact_procseq_map <- function(species) {
  
inter_seq_maps <- all_data_time |>
  filter(species == {{species}} & stage_name %in%
           sequential_stages) |>
  ggplot(aes(fill = hectares + 1/10000)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log()) + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  galenR::theme_clean() +
  labs(fill = "hectares")

  
  return(inter_seq_maps)
}

# Individual per-species plots
interact_procseq_map <- purrr::map(species, make_interact_procseq_map) |> 
  setNames(species)
```

Sequenced off habitat

```{r}
#| label: interactive-habseq-map-function
make_interact_habseq_map <- function(species) {
  
  # Change the names here from the standard set to make the comparison clearer
  habseqdata <- total_wetland_area |>
    mutate(stage_name = ifelse(grepl('Recorded', stage_name),
                               'Total Recorded', 'Total Named'),
           stage_name = factor(stage_name,
                               levels = c('Total Recorded', 'Total Named',
                                          levels(all_data_time$stage_name)))) |>
    bind_rows(all_data_time) |>
    mutate(stage_name = case_when(stage_name == 'Recorded wetland types' ~
                                    'Recorded and inundated',
                                  stage_name == 'Named wetland types' ~ 
                                    'Named and inundated',
                                  .default = stage_name),
           stage_name = factor(stage_name,
                               levels = c('Total Recorded', 'Total Named',
                                          'Recorded and inundated',
                                          'Named and inundated',
                                          levels(all_data_time$stage_name)))) |>
    filter(species == {{species}} &
             stage_name %in% c(sequential_hab, 'Total Recorded', 'Total Named',
                               'Recorded and inundated','Named and inundated'))
  
  inter_habseq_maps <- habseqdata |>
    ggplot(aes(fill = hectares + 1/10000)) +
    geom_sf() +
    scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log()) + # , limits = (c(0, 22))
    facet_wrap('stage_name', nrow = 3) +
    galenR::theme_clean() +
    labs(fill = "hectares")
  
  return(inter_habseq_maps)
}

# Individual per-species plots
interact_habseq_map <- purrr::map(species, make_interact_habseq_map) |> 
  setNames(species)
```

The plot for the paper

```{r}
#| label: map-for-paper

# Save these out by default
make_interact2d_fig <- function(species, print = TRUE) {
  
  inter_matrix_maps <- all_data_time |>
  filter((species == {{species}} | 
            is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment')) |>
  mutate(stage_name = forcats::fct_drop(stage_name)) |>
    mutate(model_type = as.character(model_type),
           model_type = stringr::str_remove_all(model_type, ' within\nwetland type')) |> 
  # filter(!is.na(species)) |> #
  ggplot(aes(fill = hectares + 1/10000)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log()) + # , limits = (c(0, 22))
    facet_grid(model_type ~ hab_type) +
  # facet_wrap('stage_name', nrow = 2, drop = FALSE) +
  # facet_wrap('stage_name', ncol = 3) +
    # Deal with overlapping x-labels
    # panel.spacing = unit(1, "lines")
    scale_x_continuous(breaks = c(140, 150)) +
    scale_y_continuous(breaks = c(-28, -32, -36)) +
  galenR::theme_clean() + 
  labs(fill = 'Favorable\narea (ha)')



  if (print) {
    thispath <- file.path(mappath, paste0(species, '_map'))
    galenR::ggsave_multi(filename = thispath, 
                         plot = inter_matrix_maps, 
                         device = c('png', 'pdf'),
                         width = 16, height = 10, units = "cm")
  }

  return(inter_matrix_maps)

}

all_interactmap <- purrr::map(species, make_interact2d_fig) |> 
  setNames(species)
```

This gives the numbers we need for some comparisons in the paper text

```{r}

# a basin-wide comparison
percbasin <- all_data_time |> 
  st_drop_geometry() |> 
  filter(species == 'red_gum' | is.na(species)) |> 
  summarise(hectares = sum(hectares, na.rm = TRUE), .by = stage_name)

# Get the reduction % of area from all wetlands to named
(percbasin$hectares[percbasin$stage_name == 'All wetland types'] - 
    percbasin$hectares[percbasin$stage_name == 'Named wetland types']) /
  percbasin$hectares[percbasin$stage_name == 'All wetland types']

# This is useful but I really just want a table.
catchtable <- all_data_time |> 
    st_drop_geometry() |> 
  mutate(hab_v_proc = ifelse(is.na(proc_type), 'Habitat inundation', as.character(proc_type)),
         hab_v_proc = factor(hab_v_proc, levels = c('Habitat inundation', levels(proc_type)))) |>
  filter((species == 'red_gum' | is.na(species)) &
           stage_name %in% c(sequential_hab, 'Recruitment')) |> 
  select(ValleyName, stage_name, hectares)
  
catchtable <- catchtable |> 
  tidyr::pivot_wider(id_cols = ValleyName, names_from = stage_name, values_from = hectares)
  
# calculate the % loss in each catchment from all to named for a line in the paper
catchtable |> mutate(`Recorded loss` = (`All wetland types`- `Recorded wetland types`) / 
                       `All wetland types`,
  `Named loss` = (`All wetland types`- `Named wetland types`) / 
    `All wetland types`) |> 
  select(ValleyName, `Recorded loss`, `Named loss`) |> 
  arrange(`Named loss`) |> 
  mutate(`Recorded loss` = round(`Recorded loss`, 2),
         `Named loss` = round(`Named loss`, 2)) |> 
  flextable::flextable() |> 
  flextable::save_as_docx(path = file.path(mappath, 'habitat_loss_table.docx'))

# calculate the % comparison of area from recruitment vs habitat inundation in all wetland types (or maybe all the different types?)

catchtable |> mutate(`Recruitment in All` = `Recruitment` / 
                       `All wetland types`,
                     `Recruitment in Recorded` = `Recruitment and Recorded` / 
                       `Recorded wetland types`,
                     `Recruitment in Named` = `Recruitment and Named` / 
                       `Named wetland types`) |> 
  select(ValleyName, `Recruitment in All`, `Recruitment in Recorded`, `Recruitment in Named`) |> 
  arrange(`Recruitment in All`) |> 
  mutate(across(where(is.numeric), \(x) round(x, 6))) |> 
  flextable::flextable()# |> 
  flextable::save_as_docx(path = file.path(mappath, 'recruitment_prop_table.docx'))

# dramatically restricted the favourable area to a small number of catchments in the southern Basin
catchtable |> 
  select(ValleyName, `Recruitment and Named`) |> 
  mutate(`Recruitment and Named` = round(`Recruitment and Named`, 4))
```

```{r}
# coolabah had nearly no area favourable for recruitment and these did not overlap with recorded or named wetland types

all_data_time |> 
  filter(species == 'coolabah' & stage_name == 'Recruitment')
```

```{r}
# another quick calc
 getperc <- all_data_time |>
  st_drop_geometry() |> 
    filter((species == 'red_gum' | 
                is.na(species)) &
               stage_name %in% c(sequential_hab, 'Recruitment')) |>
  filter(grepl('Conda|Barwon', ValleyName))# |> 
  #View()
```

Make a table for red gum

```{r}
catchtable |>
  select(ValleyName,
         `All wetland types`, `Recorded wetland types`, `Named wetland types`,
         `Recruitment`, `Recruitment and Recorded`, `Recruitment and Named`) |> 
    mutate(across(where(is.numeric), \(x) round(x, 2))) |> 
  flextable::flextable() |> 
  flextable::save_as_docx(path = file.path(mappath, 'red_gum_catchments.docx'))
```

## ANAEs

```{r}
#| eval: false
# takes a long time, don't run if not necessary
ANAEs <- readRDS(file.path(datOut,"anae_simplify", "all_anae_simplify.rds"))

# 
# plot_ananes <- ggplot(ANAEs[1:250,])+
#     geom_sf()
# plot_ananes
# ggsave(plot = plot_ananes, file.path(mappath, "anaes.pdf"), device = "pdf")
```

Complete ANAES

```{r}
#| eval: false
# takes a long time, don't run if not necessary
anaes <- readRDS(file.path(datOut, 'anae_simplify', 'all_anae_simplify.rds'))
anaes <- anaes |> mutate(loghectares = log10(as.numeric(area)+1)/10000)
```

```{r}
#| eval: false
# takes a long time, don't run if not necessary
with_legend <- ggplot() +
  geom_sf(data = basin, fill = 'black') + 
  geom_sf(data = anaes, mapping = aes(fill = loghectares, color = loghectares)) +
  scale_color_viridis_c(option = 'mako') +
  scale_fill_viridis_c(option = 'mako') +
  theme_werp_toolkit()
```

```{r}
#| eval: false
# takes a long time, don't run if not necessary
with_color <- ggplot() +
  geom_sf(data = basin, fill = 'black') + 
  geom_sf(data = anaes, mapping = aes(fill = loghectares, color = loghectares)) +
  scale_color_viridis_c(option = 'mako') +
  scale_fill_viridis_c(option = 'mako') +
  theme_void() +
  theme(legend.position = 'none')
```

```{r}
#| eval: false
# takes a long time, don't run if not necessary
without_color <- ggplot() +
  geom_sf(data = basin, fill = 'black') + 
  geom_sf(data = anaes, mapping = aes(fill = loghectares), color = NA) +
  # scale_color_viridis_c(option = 'mako') +
  scale_fill_viridis_c(option = 'mako') +
  theme_void() +
  theme(legend.position = 'none')
```

```{r}
#| eval: false
# takes a long time, don't run if not necessary
    thispath <- file.path(mappath, paste0('all_anaes'))
    galenR::ggsave_multi(filename = thispath, plot = without_color, 
                         device = c('png', 'pdf'),
                         width = 16, height = 22, units = "cm")
```

## Valleys

```{r}

vcols <- galenR::make_pal(c('dummy1', 'dummy2', 'dummy3', 
                              HydroBOT::cewo_valleys$ValleyName),
                            # 'grDevices::GnBu')
                            'grDevices::Purple-Yellow')


cvlabel <- ggplot(data = HydroBOT::cewo_valleys) + 
  geom_sf(mapping = aes(fill = ValleyName)) +
  # geom_sf_text(mapping = aes(label = ValleyName)) +
  ggrepel::geom_text_repel(mapping = aes(label = ValleyName, geometry = geometry),
                           stat = 'sf_coordinates', force = 0.2) +
  # geom_sf_text(mapping = aes(label = ValleyName)) + 
  galenR::theme_clean(legend.position = 'none') +
  scale_fill_manual(values = vcols)

cvlabel
```

```{r}
thispath <- file.path(mappath, paste0('labeled_catchments'))
    galenR::ggsave_multi(filename = thispath, plot = cvlabel, 
                         device = c('png', 'pdf'),
                         width = 16, height = 22, units = "cm")
```

## An illustrative data figure

Try Chowilla. Which is not itself a ramsar, but contains the

```         
Riverland Wetland Complex
```

```{r}
ramchow <- filter(eFlowEval::ramsarBoundsMDB, 
                        grepl('Riverland', Wetland))
       
ggplot() + 
  geom_sf(data = HydroBOT::cewo_valleys) + 
  geom_sf(data = ramchow, 
          aes(fill = Wetland))
```

We need to go back to the raw outputs for the lower murray and crop

Start with inundation, get it to work. Then which others do I want?

```{r}
#| eval: false
inun_chow <- readRDS(file.path(datOut, 'red_gum', 'anae_inun', 'LowerMurray_anae_inun.rds'))
```

Code to re-run to get the data that was previously only saved post-aggregation. This is fine, but easiest to just set a breakpoint in the middle and finish re-doing everything.

```{r}
#| eval: false
red_gum(out_dir = datOut, 
        catchment = 'LowerMurray', 
        save_anaes = TRUE)
```

Read that in

```{r}
type_filters <- readRDS(file.path(datOut, 'red_gum',
                                  'all_anaes',
                                  'LowerMurray',
                                  'type_filters.rds'))
anae_results <- readRDS(file.path(datOut, 'red_gum',
                                  'all_anaes',
                                  'LowerMurray',
                                  'compare_for_paper.rds'))
```

Get the right anaes

```{r}
# Do this like the other filters
inter_chow <- st_intersection(type_filters, ramchow)
type_filters <- type_filters |> 
  mutate(in_chowilla = UID %in% inter_chow$UID)

# but we also actually want to just cut the stars
polyindices <- which(type_filters$UID %in% inter_chow$UID)

chowanae <- purrr::map(anae_results, \(x) x[,polyindices,])

```

Make each of those an sf

```{r}
chowsf <- chowanae |> purrr::map(\(x) x |> 
                                   st_as_sf() |> 
                                   tidyr::pivot_longer(cols = -geometry, 
                                                       names_to = 'date', 
                                                       values_to = 'area') |> 
                                   mutate(date = lubridate::ymd(date), 
                                          hectares = area/10000))
```

```{r}
ggplot(filter(chowsf$inundation, date %in% c(chowsf$inundation$date[32:37])), 
       aes(fill = hectares)) + 
  geom_sf(color = NA) + 
  facet_wrap('date') +
  paletteer::scale_fill_paletteer_c(palette = 'ggthemes::Blue-Green Sequential',
                                    trans = 'log10', 
                                    labels = scales::label_log())
```

But we don't actually find any recruitment in chowilla, so will need use regeneration. This is just illustrative, so no need really to use a particular life stage, and recruitment is always so low it's hard to find any good examples.

```{r}
ggplot(filter(chowsf$regeneration, date %in% c(chowsf$inundation$date[32:37])), 
       aes(fill = hectares)) + 
  geom_sf(color = NA) + 
  facet_wrap('date') +
  paletteer::scale_fill_paletteer_c(palette = 'ggthemes::Blue-Green Sequential',
                                    trans = 'log10', 
                                    labels = scales::label_log())
```

Habitat

```{r}
ggplot(filter(chowsf$named, date %in% c(chowsf$inundation$date[32:37])), 
       aes(fill = hectares)) + 
  geom_sf(color = NA) + 
  facet_wrap('date') +
  paletteer::scale_fill_paletteer_c(palette = 'ggthemes::Blue-Green Sequential',
                                    trans = 'log10', 
                                    labels = scales::label_log())
```

combined

```{r}
ggplot(filter(chowsf$regen_and_named, date %in% c(chowsf$inundation$date[32:37])), 
       aes(fill = hectares)) + 
  geom_sf(color = NA) + 
  facet_wrap('date') +
  paletteer::scale_fill_paletteer_c(palette = 'ggthemes::Blue-Green Sequential',
                                    trans = 'log10', 
                                    labels = scales::label_log())

```

Make the plot

First, join the datasets we want so we can facet. That will make the legend easier. Presuming we don't actually want different color palettes.

```{r}
chowsf <- purrr::imap(chowsf, \(x,y) x |> mutate(model = y))
```

```{r}
chowstack <- bind_rows(chowsf$inundation, 
                       chowsf$regeneration, 
                       chowsf$named, 
                       chowsf$regen_and_named)
```

```{r}
chowillus <- chowstack |> 
  filter(date %in% c(chowsf$inundation$date[35])) |> 
  mutate(model = case_when(model == 'inundation' ~ 'Inundation',
                           model == 'named' ~ 'Habitat model',
                           model == 'regeneration' ~'Process model',
                           model == 'regen_and_named' ~'Combined model'),
         model = factor(model, levels = c('Inundation', 'Habitat model', 'Process model', 'Combined model'))) |> 
  ggplot(aes(fill = hectares)) + 
  geom_sf(color = NA) + 
  facet_grid(.~ model)  +
  scale_fill_viridis_c(option = 'mako',
                       trans = 'log10', 
                       labels = scales::label_log())+
  # paletteer::scale_fill_paletteer_c(palette = 'ggthemes::Blue-Green Sequential',
  #                                   trans = 'log10', 
  #                                   labels = scales::label_log()) +
  scale_x_continuous(breaks = c(140.8, 141)) +
  scale_y_continuous(breaks = c(-34.2, -34.1, -34, -33.9)) +
  galenR::theme_clean(legend.position = 'bottom') + 
  labs(fill = 'Favorable\narea (ha)')

chowillus
```

```{r}
    galenR::ggsave_multi(filename = file.path(mappath, 'riverland_illustration'), 
                         plot = chowillus, 
                         device = c('png', 'pdf'),
                         width = 18, height = 8, units = "cm")
```

Situate that

```{r}
riverland_loc <- ggplot(data = HydroBOT::basin) + # |> filter(ValleyName == 'Lower Murray')
  geom_sf(fill = 'azure') +
  # geom_sf(data = st_intersection(HydroBOT::basin_rivers, HydroBOT::cewo_valleys |> 
  #                                  filter(ValleyName == 'Lower Murray')), 
  #         color = 'skyblue') +
  geom_sf(data = ramchow, fill = 'firebrick', color = 'firebrick') +
  ggrepel::geom_text_repel(data = ramchow, 
                           mapping = aes(label = stringr::str_wrap(Wetland, 12), geometry = geometry),
                           stat = 'sf_coordinates',
                           nudge_x = 3, nudge_y = 1) +
      scale_x_continuous(breaks = c(140, 145, 150)) +
  galenR::theme_clean(axis.title = element_blank())

riverland_loc

    galenR::ggsave_multi(filename = file.path(mappath, 'riverland_location'), 
                         plot = riverland_loc, 
                         device = c('png', 'pdf'),
                     width = 8, height = 8, units = 'cm')
```
