---
title: "Red gum analyses"
format: html
editor: visual
echo: false
bibliography: references.bib
---

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
#| include: false
library(eFlowEval)
library(sf)
source('directorySet.R')
source('R/catch_cat_sf.R')
library(dplyr)
library(ggplot2)
library(foreach) # needed internally for some funs
library(patchwork)
library(kableExtra)
```

```{r}

figpath <- file.path(datOut, 'habprocesspaper', 'Figures')

if (!dir.exists(figpath)) {
  dir.create(figpath, recursive = TRUE)
}
```

## Data read-in

I'm leading with this because we're tweaking the data, but it could all be offloaded to a script to focus on the ms. Or just collapse the section.

I'm splitting this up into a few sections since the process and anae-clipped (2 ways) gets confusing to do in one go.

### Background

First, a few useful background pieces- which species, what are the anae types and a bit of a summary, etc

```{r}
#| label: which-data
species <- c('black_box', 'red_gum', 'coolabah', 'lignum')
species_names <- species |> 
  stringr::str_replace('_', ' ') |> 
  stringr::str_to_sentence()
```

```{r}
valleys <- ltimNoNorth |> 
  select(-ValleyID, -ValleyCode) |> 
  mutate(name_orig = ValleyName,
         ValleyName = stringr::str_remove_all(ValleyName, ' '))
```

What are the anae types?

```{r}
# this dataset generated in the diversity analysis is really useful to get overall info about what got inundated and the wetland areas, but it's massive. I need it here though to get assorted areas and the full set of anae types
diversity_anae_summary <- catch_cat_sf('diversity_anae_summary', 'diversity')
```

```{r}
# all_anaes <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))
# bbala <- readRDS(file.path(datOut, 'vegmapping', 'black_box_anae_type.rds'))

alatypes <- foreach(i = species,
                    .combine = bind_rows, .multicombine = TRUE) %do% {
  readRDS(file.path(datOut, 'vegmapping', paste0(i, '_anae_type.rds'))) |> 
                        mutate(species = i)
                    }

# That's useful to have in a dataframe, but in a few places I want a list too
type_list <- vector(mode = 'list', length = length(species)) |> setNames(species)
for (s in species) {
  
  # stolen from woody_general
    veg_grep <- dplyr::case_when(s == 'black_box' ~ 'black box',
                               s == 'red_gum' ~ 'red gum',
                               s == 'coolabah' ~ 'cool',
                               s == 'lignum' ~ 'lignum')
    
    
  spalatypes <- alatypes |> 
    filter(species == s) |> 
    pull(ANAE_DESC)
  
  # Use the full set of ANAEs, not just those that show up in the alas.
  spnametypes <- diversity_anae_summary |> 
    filter(grepl(veg_grep, ANAE_DESC, ignore.case = TRUE)) |> 
    pull(ANAE_DESC) |> 
    unique()
  
  type_list[[s]] <- list(alatype = spalatypes, nametype = spnametypes)
}

# Double check we pick up all the 'name's in the alas
# for (i in species) {
#   stype <- alatypes |> 
#     filter(species == i) |> 
#     select(ANAE_DESC) |> 
#     pull() |> 
#     unique()
#   
#   print(all(tl$nametype[[i]] %in% stype))
# }
# We do, so comment that out.
```

### Process-only

These are the strictures for just biological processes.

```{r}
adult <- purrr::map(species, \(x) 
                    catch_cat_sf('adult_area', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult',
         species = x)) |> 
  bind_rows()

germ <- purrr::map(species, \(x) 
                   catch_cat_sf('germ_area', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination',
         species = x)) |> 
  bind_rows()

seed <- purrr::map(species, \(x) 
                   catch_cat_sf('seedling_area',
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling',
         species = x)) |> 
  bind_rows()

# Two step
adult_germ <- purrr::map(species, \(x) 
                            catch_cat_sf('adult_germ_area',
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_regen',
         species = x)) |> 
  bind_rows()

adult_germ_seed <- purrr::map(species, \(x) 
                            catch_cat_sf('adult_germ_seed_area',
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment',
         species = x)) |> 
  bind_rows()


```

### Habitat only

```{r}
# Keep using 'stage' as the name of the data, since it makes joining for comparison easier.

inun_anae_all <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun',
                                outerdir = paste0('habprocesspaper/', x)) |> 
                                 # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'all_wetlands',
         species = x)) |> 
  bind_rows()

inun_anae_name <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun_anae_name',
                                outerdir = paste0('habprocesspaper/', x)) |> 
                                 # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'anae_name',
         species = x)) |> 
  bind_rows()
  
inun_anae_ala <- purrr::map(species,
                             \(x) catch_cat_sf('anae_inun_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
                                # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
    mutate(stage = 'anae_ala',
         species = x)) |> 
  bind_rows()

```

There are also two other sorts of baselines we might want for the habitat- the total amount of inundation in *any* wetland type, and the total amount of area in each set of habitats, ignoring inundation. I had been doing this in the appendix, but think I'll move the data extraction here, anyway.

```{r}
# One use- total area of wetland habitat regardless of inundation for each species in various ways
# First, get rid of the yearly since total area doesn't change and simplify

typearea <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  summarise(total_area = unique(total_area), .by = c(ANAE_DESC, name_clean))

# Now I want to get the total area attributable to each species' types. This seems like it should be a grouped operation, but they aren't mutually exclusive, so it's actually better to work with type_list and filter

# using the same stage names lets us use the same colors
total_wetland_area <- foreach(s = species, .combine = bind_rows, .multicombine = TRUE) %do% {
  alaarea <- typearea |> 
    filter(ANAE_DESC %in% type_list[[s]]$alatype) |> 
    summarise(total_area = sum(total_area), .by = name_clean) |> 
    mutate(species = s, stage = 'anae_ala')
  
  namearea <- typearea |> 
    filter(ANAE_DESC %in% type_list[[s]]$nametype) |> 
    summarise(total_area = sum(total_area), .by = name_clean) |> 
    mutate(species = s, stage = 'anae_name')
  
  bind_rows(alaarea, namearea) |> 
    rename(ValleyName = name_clean)
}

total_wetland_area_basin <- total_wetland_area |> 
  summarise(total_area = sum(total_area), .by = c(species, stage))
```

```{r}
#| eval: false
# a check of that, probably delete if passes- does that actually have all the anae wetlands?
all_anae <- readRDS(file.path(datOut, 'ANAEcatchment', 'ANAEcatchment.rds'))

all_anae <- all_anae |> 
  mutate(area = st_area(geometry))

all(unique(all_anae$ANAE_DESC) %in% typearea$ANAE_DESC)

# Yes, so no need for both.
```

```{r}

# First, simplify
# There's no species differences here
inun_area <- diversity_anae_summary |> 
  st_drop_geometry() |> 
  rename(date = time) |> 
  mutate(ValleyName = name_clean) |> 
  summarise(area = sum(area_inundated, na.rm = TRUE),
            stage = 'wetland_inundation',
            .by = c(date, ValleyName)) |>
    left_join(valleys) |> 
    st_as_sf() |> 
  select(-name_orig)

```

### Interactive

Include independent and full for the stages. Skip the adult_germ, it's not very interesting

```{r}
# ALA records

adult_ala <- purrr::map(species, \(x) catch_cat_sf('adult_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_ala',
         species = x)) |> 
  bind_rows()

germ_ala <- purrr::map(species, \(x) catch_cat_sf('germ_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination_ala',
         species = x)) |> 
  bind_rows()

seed_ala <- purrr::map(species, \(x) catch_cat_sf('seedling_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling_ala',
         species = x)) |> 
  bind_rows()

adult_germ_ala <- purrr::map(species, \(x) catch_cat_sf('adult_germ_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration_ala',
         species = x)) |> 
  bind_rows()

adult_germ_seed_ala <- purrr::map(species, \(x) catch_cat_sf('adult_germ_seed_area_anae_ala', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment_ala',
         species = x)) |> 
  bind_rows()

# Name

adult_name <- purrr::map(species, \(x) catch_cat_sf('adult_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no adult data prior to 1995 because of the lookback period
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'adult_name',
         species = x)) |> 
  bind_rows()

germ_name <- purrr::map(species, \(x) catch_cat_sf('germ_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'germination_name',
         species = x)) |> 
  bind_rows()

seed_name <- purrr::map(species, \(x) catch_cat_sf('seedling_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'seedling_name',
         species = x)) |> 
  bind_rows()

adult_germ_name <- purrr::map(species, \(x) catch_cat_sf('adult_germ_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'regeneration_name',
         species = x)) |> 
  bind_rows()

adult_germ_seed_name <- purrr::map(species, \(x) catch_cat_sf('adult_germ_seed_area_anae_name', 
                                outerdir = paste0('habprocesspaper/', x)) |> 
  # There's no data prior ot 1988
  filter(date > lubridate::ymd(19880101)) |> 
  mutate(stage = 'recruitment_name',
         species = x)) |> 
  bind_rows()
```

### Concatenate

```{r}
all_data <- bind_rows(adult, germ, seed, 
                         adult_germ, adult_germ_seed, 
                         adult_ala, germ_ala, seed_ala,
                      adult_germ_ala, adult_germ_seed_ala,
                         adult_name, germ_name, seed_name,
                      adult_germ_name,
                      adult_germ_seed_name,
                         inun_anae_name, inun_anae_ala,
                      inun_area)

# To make data line up, we need a numeric year sometimes
all_data <- all_data |> 
  mutate(year = lubridate::year(date))

# Sum to the basin
all_data_basin <- all_data |>
  sf::st_drop_geometry() |>
  summarise(area = sumna(area),
            .by = c(date, year, stage, species)) |>
  bind_cols(basin) |>
  st_as_sf()

# average over time
all_data_time <- all_data |>
  group_by(ValleyName, stage, species) |> 
  summarise(area = meanna(area)) |>
  ungroup()

# sum to basin and average over time
all_data_basin_time <- all_data_basin |>
  group_by(stage, species) |> 
 summarise(area = meanna(area)) |> 
  ungroup()

# rm(adult, germ, seed, 
#    adult_germ, adult_germ_seed, 
#    adult_ala, germ_ala, seed_ala, 
#    adult_germ_seed_ala,
#    adult_name, germ_name, seed_name, 
#    adult_germ_seed_name,
#    inun_anae_name, inun_anae_ala, inun_area)



```

Set up a standard color palette for the types. Could do the same for species if we every plot those, and should choose a standard ramp for things like maps. Could do it for catchments too, but there's a million. This is ugly, but changing it is easy.

Clean up the names

```{r}
# Set up various groupings
# the different types
anae_stages <- c('Named wetland types', 'Recorded wetland types', 'All wetlands')
process_stages <- c('Adult', 'Germination', 'Seedling',
                    'Regeneration', 'Recruitment')
combo_stages <- c('Adult and Named', 'Germination and Named',
                  'Seedling and Named', 'Regeneration and Named', 'Recruitment and Named',
                  'Adult and Recorded', 'Germination and Recorded',
                  'Seedling and Recorded', 'Regeneration and Recorded',
                  'Recruitment and Recorded')

sequential_stages <- c('Adult', 'Regeneration', 'Recruitment',
                       'Recruitment and Named', 'Recruitment and Recorded')

sequential_hab <- c('Named wetland types', 'Recorded wetland types', 'All wetlands',
                       'Recruitment and Named', 'Recruitment and Recorded')

# The different comparisons across type
hab_all <- c('All wetlands', process_stages)
hab_named <- c('Named wetland types', combo_stages[grepl('Named', combo_stages)])
hab_record <- c('Recorded wetland types', combo_stages[grepl('Recorded', combo_stages)])

proc_adult <- c('Adult', combo_stages[grepl('Adult', combo_stages)])
proc_germ <- c('Germination', combo_stages[grepl('Germination', combo_stages)])
proc_seed <- c('Seedling', combo_stages[grepl('Seed', combo_stages)])
proc_regen <- c('Regeneration', combo_stages[grepl('Regeneration', combo_stages)])
proc_recruit <- c('Recruitment', combo_stages[grepl('Recruitment', combo_stages)])

```

```{r}
clean_stages <- function(x) {
  x <- x |> 
    mutate(stage_name = case_when(stage == 'adult' ~ 'Adult',
                                  stage == 'germination' ~ 'Germination',
                                  stage == 'seedling' ~ 'Seedling',
                                  stage == 'adult_regen' ~ 'Regeneration',
                                  stage == 'recruitment' ~ 'Recruitment',
                                  stage == 'adult_ala' ~ 'Adult and Recorded',
                                  stage == 'germination_ala' ~ 'Germination and Recorded',
                                  stage == 'seedling_ala' ~ 'Seedling and Recorded',
                                  stage == 'regeneration_ala' ~ 'Regeneration and Recorded',
                                  stage == 'recruitment_ala' ~ 'Recruitment and Recorded',
                                  stage == 'adult_name' ~ 'Adult and Named',
                                  stage == 'germination_name' ~ 'Germination and Named',
                                  stage == 'seedling_name' ~ 'Seedling and Named',
                                  stage == 'regeneration_name' ~ 'Regeneration and Named',
                                  stage == 'recruitment_name' ~ 'Recruitment and Named',
                                  stage == 'anae_name' ~ 'Named wetland types',
                                  stage == 'anae_ala' ~ 'Recorded wetland types',
                                  stage == 'wetland_inundation' ~ 'All wetlands',
                                  .default = 'FAIL'),
           stage_name = factor(stage_name,
                               levels = c('All wetlands',
                                          'Recorded wetland types',
                                          'Named wetland types',
                                          'Adult', 'Germination', 'Seedling',
                                          'Regeneration', 'Recruitment',
                                          'Adult and Recorded',
                                          'Germination and Recorded',
                                          'Seedling and Recorded',
                                          'Regeneration and Recorded',
                                          'Recruitment and Recorded',
                                          'Adult and Named',
                                          'Germination and Named',
                                          'Seedling and Named',
                                          'Regeneration and Named',
                                          'Recruitment and Named')),
           # create an independent stage flag. don't includ adults, since they're both
           is_independent_proc = case_when(stage %in% c('germination', 'seedling',
                                                        'germination_ala', 'seedling_ala',
                                                        'germination_name', 'seedling_name') ~
                                             'independent',
                                           stage %in% c('adult', 'adult_regen', 'recruitment',
                                                        'adult_ala', 'adult_regen_ala',
                                                        'recruitment_ala',
                                                        'adult_name', 'adult_regen_name',
                                                        'recruitment_name') ~ 'sequential',
                                           .default = NA),
           is_independent_proc = factor(is_independent_proc, levels = c('sequential', 'independent'))) |> 
    mutate(hab_type = case_when(stage_name %in% hab_all ~ "All wetlands",
                                stage_name %in% hab_named ~ "Named wetland types",
                                stage_name %in% hab_record ~ "Recorded wetland types",
                                .default = NA),
           hab_type = factor(hab_type, levels = c('All wetlands',
                                                  'Recorded wetland types',
                                                  'Named wetland types')),
           proc_type = case_when(stage_name %in% proc_adult ~ "Adult",
                                 stage_name %in% proc_germ ~ "Germination",
                                 stage_name %in% proc_seed ~ "Seedling",
                                 stage_name %in% proc_regen ~ "Regeneration",
                                 stage_name %in% proc_recruit ~ "Recruitment",
                                 .default = NA),
           model_type = case_when(stage_name %in% anae_stages ~ 'Wetland type',
                                  stage_name %in% process_stages ~ "Process",
                                  stage_name %in% combo_stages ~ "Process within\nwetland type", 
                                  .default = NA),
           proc_type = factor(proc_type, levels = c('Adult', 'Germination', 'Seedling', 'Regeneration', 'Recruitment')))
  
}
```

Use that to clean data

```{r}
all_data <- clean_stages(all_data)
all_data_basin <- clean_stages(all_data_basin)
all_data_time <- clean_stages(all_data_time)
all_data_basin_time <- clean_stages(all_data_basin_time)
```

```{r}
# just to make it easy to access
stages <- unique(all_data$stage)
stagenames <- unique(all_data$stage_name)



#  "palettetown::surskit"
# "RColorBrewer::Set3"
# This worked pretty well with 12, but is a mess with 15.
# stage_pal <- werptoolkitr::make_pal(stages, "rcartocolor::Safe")

# This is going to take some tweaking to get right.
# having hte names in separate vectors can make some filtering easier
# "beyonce::X41" "ggprism::plasma" "rcartocolor::ag_Sunset" "RColorBrewer::RdPu", direction = -1 "PNWColors::Sunset2"
anae_cols <- werptoolkitr::make_pal(anae_stages, "rcartocolor::ag_Sunset")

process_stages <- c('Adult', 'Germination', 'Seedling',
                    'Regeneration', 'Recruitment')

process_cols <- werptoolkitr::make_pal(process_stages,
                                       "calecopal::superbloom1")
# that last one is just barely too purple
process_cols[names(process_cols) == 'Recruitment'] <- '#527E87FF' # '#477173FF'

combo_cols <- werptoolkitr::make_pal(combo_stages, "rcartocolor::Safe")

stage_pal <- c(anae_cols, process_cols, combo_cols)
class(stage_pal) <- 'colors'

# probably need to change this
type_pal <- werptoolkitr::make_pal(c('Habitat', 'Process', 'Process within\nhabitat'), "trekcolors::starfleet")


# make a consistent set of shapes that allows patchworking
shape_type <- scales::shape_pal()(3) |> 
  setNames(names(type_pal))

# make an alpha scale for that too
alpha_type <- c('Habitat' = 1, 'Process' = 1, 'Process within\nhabitat' = 0.75)

# make an alpha scale for that too
line_type <- c('Habitat' = 'solid', 'Process' = 'solid', 'Process within\nhabitat' = 'dashed')
```

# PLOT BUILDING

The order these are easiest to build in is not necessarily the best presentation order.

## Basin-scale timeseries

### Habitat alone

```{r}
#| label: habitat-ts-function
make_habitat_timeseries <- function(species) {
  
  hab_basin_ts <- all_data_basin |> 
  filter((species %in% {{species}} | is.na(species)) & 
           stage_name %in% anae_stages) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  # Seems like a good idea, but the 'All wetlands' isn't duplicated over species.
  # if (length(species) > 1) {
  #   hab_basin_ts <- hab_basin_ts +
  #     facet_wrap('species')
  # } 
  
  return(hab_basin_ts)
}

# Individual per-species plots
hab_basin_ts <- purrr::map(species, make_habitat_timeseries) |> 
  setNames(species)
```

### Process alone

```{r}
#| label: process-ts-fun-allstages

make_all_process_ts <- function(species) {
  proc_basin_ts <- all_data_basin |> 
    filter(species == {{species}} & stage_name %in% process_stages) |> 
    ggplot(aes(x = year, y = log10(area + 1), color = stage_name,
           linetype = is_independent_proc, shape = model_type)) +
    geom_line(show.legend = TRUE) +
    geom_point(show.legend = TRUE) +
    scale_shape_manual(values = shape_type) +
    scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
    werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
    labs(y = "log(area + 1)", color = "Model",
       linetype = "Stage type", shape = "Model type")
  
  return(proc_basin_ts)
}

all_proc_basin_ts <- purrr::map(species, make_all_process_ts) |> 
  setNames(species)
```

Sequential

```{r}

make_seq_process_ts <- function(species) {
  proc_basin_seq_ts <- all_data_basin |> 
  filter(species %in% {{species}} & 
           # both process and sequential
           stage_name %in% process_stages &
           stage_name %in% sequential_stages) |> 
    ggplot(aes(x = year, y = log10(area + 1), 
               color = stage_name, 
               shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
  
  return(proc_basin_seq_ts)
}


seq_proc_basin_ts <- purrr::map(species, make_seq_process_ts) |> 
  setNames(species)
```

# Appendix

This creates the individual plots and develops the story. Then some get glued together for the main results.

## Basin-scale timeseries

### Habitat alone

A habitat-only model suggests that area is favourable if it is inundated in either Recorded wetland types or Named wetland types. Both are a subset of the total wetland inundation in the MDB, with Recorded types being a larger set and so having a larger amount of inundation @fig-process-habitat .

```{r}
#| label: fig-process-habitat
#| fig-cap: Area of inundation in wetlands associated with each species in the basin, either by *Name* or where that species has been *Recorded* in the ALA.

# Should we sort out the facetting by duplicating'All wetlands' across all species? Probably, but this works.

hab_alone_panel <- purrr::imap(hab_basin_ts, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

hab_alone_panel
```

### Process alone

In a process-based model, the amount of favourable area for each life stage depends on the specific environmental requirements for that stage. Moreover, these stages are sequential, and so even if all requirements for seedling survival are met in a year, there may not be successful recruitment if there was not germination approximately six months prior to the favourable seedling conditions. In @fig-all-process-basin, we plot both the independent life stages (Adults, plus Germination and Seedling) as well as the sequential stages (Adult-Regeneration-Recruitment). From these plots, we can clearly see that seedling survival is the most limiting life stage for all species. Further, life-history dependence provides limitation beyond the individual stages. The Regeneration line (Adult + Germination) is almost always lower than the independent Germination line, indicating that there are locations favourable to germination but lacking favourable adult conditions to provide seed. Similarly, even though seeling survival is quite low in general, Recruitment is even lower; there are many times when seedlings *could* survive, but there were not preceding conditions favourable for Regeneration.

The species are quite different in these relationships. Lignum and Red gum are much less limited by seedling survival than Black box or Coolabah, as a consequence of shorter requirements for soil moisture maintenance @fig-all-process-basin . Unlike the other species, Coolabah does not show additional limitation of Regeneration beyond Germination, and so all favourable germination conditions occur in areas that are favourable for adults.

```{r}
#| label: fig-all-process-basin
#| fig-cap: Area favourable for each life stage in a process model, both independently (dashed) and sequentially (solid). Note that Coolabah and Lignum have long lookbacks for adult condition, and so cannot assess adult favourability for a large proprotion of the timeseries.

all_proc_panel <- purrr::imap(all_proc_basin_ts, \(x, i) 
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>  
  wrap_plots() +
  plot_layout(guides = 'collect')

all_proc_panel
```

*If we want to go for the life-history pinch-points analyses*: Here, we could do a relativization in two dimensions- How does each stage in the sequential reduce things relative to the preceding stage, and how does the joint compare to the individual (e.g. Regeneration vs Germination). The first would give proprotional loss at each step, and the second would say how much the sequencing itself is introducing limitation.

I want to facet that, but there's no easy way because recruitment should be in both. So just panel it

```{r}
inter_basin_key_ts <- all_data_basin |> 
  filter(species == 'red_gum' & 
           stage_name %in% c('Named wetland types', 'Recruitment and Named', 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")



inter_basin_recorded_ts <- all_data_basin |> 
  filter(species == 'red_gum' & 
           stage_name %in% c('Recorded wetland types', 'Recruitment and Recorded', 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1),
           color = stage_name, shape = model_type)) +
  geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
      scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  scale_y_continuous() +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")

inter_basin_key_ts
inter_basin_recorded_ts
```

Can I get the venns to work?

```{r}
venncheck <- all_data_basin |> 
  sf::st_drop_geometry() |> 
  filter(species == 'red_gum' & 
           stage_name %in% c('Recorded wetland types',
                             'Recruitment and Recorded',
                             'Recruitment')) |> 
  mutate(area = log10(area + 1)) |>
  mutate(area = area/max(area, na.rm = TRUE)) |> 
  # need to do a funny flip-flop here to get overlap in its own column
  tidyr::pivot_wider(id_cols = date,
                     names_from = stage_name,
                     values_from = area) |> 
  tidyr::pivot_longer(cols = c(Recruitment, `Recorded wetland types`),
                      names_to = 'stage_name',
                      values_to = 'area') |> 
  rename(overlap = `Recruitment and Recorded`)

```

```{r}
venncheck <- venncheck |> 
  # filter(!is.na(overlap)) |> 
  mutate(radius = sqrt(area/pi)) |> 
  mutate(d = galenR::find_d(unique(overlap),
                            radii = radius),
         .by = date) |> 
  mutate(centers = d*c(-0.5, 0.5)) |> 
  mutate(year = lubridate::year(date))
```

```{r}
ggplot(venncheck) + 
  ggforce::geom_circle(mapping = aes(x0 = lubridate::year(date), y0 = centers, 
                            r = radius, 
                            fill = factor(stage_name)),
              alpha = 0.7) + 
   scale_fill_manual(values = stage_pal) +
  coord_fixed() + 
  theme(legend.position = 'bottom')
```

Now, can I get those overlain on the above? Along the bottom? As another panel? select a few and put them by the relevant points?

```{r}
vennplot <- ggplot(venncheck) + 
  ggforce::geom_circle(mapping = aes(x0 = year, y0 = centers, 
                            r = radius, 
                            fill = factor(stage_name)),
              alpha = 0.7) + 
   scale_fill_manual(values = stage_pal) +
  coord_fixed() + 
  theme(legend.position = 'none')
```

Lining up x is a pain

```{r}
inter_basin_recorded_yr <- all_data_basin |> 
  filter(species == 'red_gum' & 
           stage_name %in% c('Recorded wetland types',
                             'Recruitment and Recorded',
                             'Recruitment')) |> 
  mutate(year = lubridate::year(date)) |> 
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
  geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
      scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  scale_y_continuous() +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")
```

-   lims(x = c(1990, 2022))

```{r}
(inter_basin_recorded_yr) /
  (vennplot + lims(x = c(1988, NA)) +
     werptoolkitr::theme_werp_toolkit(axis.ticks.y = element_blank(),
                                      axis.text.y = element_blank(),
                                      legend.position = 'none'))
```

We could plot that straight onto the values, but the axes are uneven. Could we sort out a geom_ellipse that modified a and b according to the different scales? Probably, but that's further into the guts of ggplot than I really want to get.

So, can we pick three, modify their y so it's about right relativelyh, and then use inset_element? The inset keeps re-adjusting so it doesn't fit. recalculate. Scale by multiplying area

```{r}
vensub <- venncheck |> 
                   filter(year %in% c(1988, 1995, 2001, 2006, 2022)) |> 
  mutate(radius = sqrt(4*area/pi)) |> 
  mutate(d = galenR::find_d(unique(4*overlap),
                            radii = radius),
         .by = date) |> 
  mutate(centers = d*c(-0.5, 0.5)) |> 
  mutate(year = lubridate::year(date)) |> 
  mutate(offset = rep(c(0, 3, 6, 7, 0), each = 2),
         offcenters = centers + offset) |> 
  # 0-radius so we keep the full size of the plot
  mutate(radius = ifelse(year %in% c(1990, 2022), 0, radius),
         centers = ifelse(year == 1990, 0, 
                          ifelse(year == 2022, 10, centers)))

venn3 <- ggplot(vensub) + 
  ggforce::geom_circle(mapping = aes(x0 = year, y0 = offcenters, 
                            r = radius, 
                            fill = factor(stage_name)),
              alpha = 0.7) + 
   scale_fill_manual(values = stage_pal) + 
  lims(x = c(1988, 2023)) +
  coord_fixed() + 
  theme_void() +
    theme(legend.position = 'none')

venn3
```

```{r}
inter_basin_recorded_yr +
  inset_element(venn3, left = 0, bottom = 0, right = 1, top = 1)
```

Combine those

```{r}
# I thought including limits = c(all stages here) would work to include them all with guides = collect, but it's not. I think I might have to make a dummy plot
# 
# (inter_basin_key_ts +
#     scale_color_manual(values = stage_pal, 
#                        limits = c('Named wetland types',
#                                   'Recruitment and Named',
#                                   'Recruitment',
#                                   'Recorded wetland types',
#                                   'Recruitment and Recorded'),
#                        breaks = c('Named wetland types',
#                                   'Recruitment and Named',
#                                   'Recruitment',
#                                   'Recorded wetland types',
#                                   'Recruitment and Recorded'))) + 
#   (inter_basin_recorded_ts +
#      
#     scale_color_manual(values = stage_pal, 
#                        limits = c('Named wetland types',
#                                   'Recruitment and Named',
#                                   'Recruitment',
#                                   'Recorded wetland types',
#                                   'Recruitment and Recorded'),
#                        breaks = c('Named wetland types',
#                                   'Recruitment and Named',
#                                   'Recruitment',
#                                   'Recorded wetland types',
#                                   'Recruitment and Recorded'))) + 
#   plot_layout(guides = 'collect')
```

We could do the scale\_ with limits and breaks, but it's terrible. Going to be easier to make a dummy plot and steal its legend

```{r}
dummyplot <- all_data_basin |>
  filter(is.na(is_independent_proc) | is_independent_proc == 'sequential') |>
  filter(!stage_name %in% c('Adult and Recorded', 'Regeneration and Recorded',
                            'Adult and Named', 'Regeneration and Named')) |>
ggplot(aes(x = year, y = log10(area + 1), 
           color = stage_name, shape = model_type)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point() +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model", shape = "Model type")


dummylegend <- ggpubr::get_legend(dummyplot)

dummybottom <- dummyplot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = guide_legend(nrow = 3), color = guide_legend(nrow = 3))

dummybottom_notype <- dummyplot + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(shape = 'none', color = guide_legend(nrow = 3))




bottomlegend <- ggpubr::get_legend(dummybottom)
bottomnotype <- ggpubr::get_legend(dummybottom_notype)


```

\

```{r}
layout_square <- "
AAABBB#E
CCCDDD#E
"


(hab_basin_ts + theme(legend.position = 'none')) + 
    (proc_basin_seq_ts + theme(legend.position = 'none')) + 
  (inter_basin_key_ts + theme(legend.position = 'none')) +
     (inter_basin_recorded_ts  + theme(legend.position = 'none'))  +
  ggpubr::as_ggplot(dummylegend) +
  plot_layout(design = layout_square)
```

```{r}
# (hab_basin_ts + proc_basin_seq_ts) / inter_basin_key_ts / inter_basin_recorded_ts +
#   plot_layout(guides = 'collect')

```

```{r}
layout_stack <- "
AABB#E
CCCC#E
DDDD#E
"


(hab_basin_ts + theme(legend.position = 'none')) + 
    (proc_basin_seq_ts + theme(legend.position = 'none')) + 
  (inter_basin_key_ts + theme(legend.position = 'none')) +
     (inter_basin_recorded_ts  + theme(legend.position = 'none')) +
  ggpubr::as_ggplot(dummylegend) +
  plot_layout(design = layout_stack)
```

I really want to scooch the venn up to lay right on the x-axis of the timeseries, but can't get patchwork to do it.

```{r}
venlims <- vennplot + lims(x = c(1988, NA)) +
     werptoolkitr::theme_werp_toolkit(axis.ticks.y = element_blank(),
                                      axis.text.y = element_blank(),
                                      legend.position = 'none')
```

```{r}
# # This is an absolutely bonkers way of squashing down the height of the venn panel
# layout_stack_venn <- "
# AABB
# AABB
# AABB
# AABB
# AABB
# CCCC
# CCCC
# CCCC
# CCCC
# CCCC
# DDDD
# DDDD
# DDDD
# DDDD
# DDDD
# EEEE
# FFFF
# FFFF
# FFFF
# "
# 
# # Call this good for now, but I think if I 
# 

# 
# 
# ts_plot <- (hab_basin_ts + theme(legend.position = 'none')) + 
#     (proc_basin_seq_ts + theme(legend.position = 'none')) + 
#   (inter_basin_key_ts + theme(legend.position = 'none',
#                               axis.text.x = element_blank())) +
#      (inter_basin_recorded_ts  + theme(legend.position = 'none',
#                                        axis.text.x = element_blank())) +
#   wrap_plots(venlims) +
#   wrap_plots(ggpubr::as_ggplot(bottomlegend)) + #bottomnotype
#   plot_layout(design = layout_stack_venn) +
#   plot_annotation(tag_levels = list(c('a', 'b', 'c', 'd', 'e', '')))
# 
# ts_plot
# 
# ggsave(file.path(figpath, 'red_gum_timeseries.png'),
#        ts_plot, width = 16, height = 22, units = "cm")
# ggsave(file.path(figpath, 'red_gum_timeseries.svg'),
#        ts_plot, width = 16, height = 22, units = "cm")
```

```{r}

topplot <- (hab_basin_ts + theme(legend.position = 'none')) + 
    (proc_basin_seq_ts + theme(legend.position = 'none'))
ts_plot <-  topplot /
  (inter_basin_key_ts + theme(legend.position = 'none',
                              axis.text.x = element_blank())) /
     (inter_basin_recorded_ts  + theme(legend.position = 'none',
                                       axis.text.x = element_blank(),
                                       plot.margin = unit(c(5,5,0,5), 'points'))) /
  wrap_plots(venlims + theme(plot.margin = unit(c(0,5,5,5), 'points'))) /
  wrap_plots(ggpubr::as_ggplot(bottomlegend)) + #bottomnotype
  plot_layout(heights = c(5,5,5,1,3)) +
  plot_annotation(tag_levels = list(c('a', 'b', 'c', 'd', 'e', '')))

ts_plot

ggsave(file.path(figpath, 'red_gum_timeseries.png'),
       ts_plot, width = 16, height = 22, units = "cm")
ggsave(file.path(figpath, 'red_gum_timeseries.svg'),
       ts_plot, width = 16, height = 22, units = "cm")
```

ggpubr has different but also annoying issues

```{r}
# ggpubstack <- ggpubr::ggarrange(
#   ggpubr::ggarrange((hab_basin_ts + theme(legend.position = 'none')), 
#     (proc_basin_seq_ts + theme(legend.position = 'none')), nrow = 1), 
#   (inter_basin_key_ts + theme(legend.position = 'none',
#                               axis.text.x = element_blank())),
#      (inter_basin_recorded_ts  + theme(legend.position = 'none',
#                                        axis.text.x = element_blank())),
#   venlims,
#   nrow = 4, heights = c(4,4,4,1), legend.grob = bottomlegend
# )
# 
# ggpubstack
```

This should work best, but it stuffs up the alignment

```{r}
# lstack <- "
# AABB
# CCCC
# DDDD
# EEEE
# "
# 
# venlims <- vennplot + lims(x = c(1988, NA)) +
#      werptoolkitr::theme_werp_toolkit(axis.ticks.y = element_blank(),
#                                       axis.text.y = element_blank(),
#                                       legend.position = 'none')
# 
# 
# ts_ploti <- (hab_basin_ts + theme(legend.position = 'none')) + 
#     (proc_basin_seq_ts + theme(legend.position = 'none')) + 
#   (inter_basin_key_ts + theme(legend.position = 'none',
#                               axis.text.x = element_blank())) +
#      (inter_basin_recorded_ts  + theme(legend.position = 'none',
#                                        axis.text.x = element_blank()) +
#         inset_element(venlims,
#                       left = 0, bottom = -0.7, right = 1, top = 0.3,
#       align_to = 'panel')) +
#   wrap_plots(ggpubr::as_ggplot(bottomnotype)) +
#   plot_layout(design = lstack)
# 
# ts_ploti
# 
# ggsave(file.path(figpath, 'timeseries.png'),
#        ts_ploti, width = 16, height = 24, units = "cm")
# ggsave(file.path(figpath, 'timeseries.svg'),
#        ts_ploti, width = 16, height = 24, units = "cm")
```

We can summarise those over time, making bar graphs

```{r}

# Don't use basin_time or we can't get the time-variance
hab_basin_bar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & stage_name %in% anae_stages) |> 
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
    scale_fill_manual(values = stage_pal) +
  werptoolkitr::theme_werp_toolkit()

hab_basin_bar

```

Process, both sequential and independent

```{r}
proc_basin_bar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & stage_name %in% process_stages) |> 
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            is_independent_proc = unique(is_independent_proc),
            .by = stage_name) |>
ggplot(aes(x = stage_name, y = mean_area, fill = stage_name, color = is_independent_proc)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
    scale_fill_manual(values = stage_pal) +
  scale_color_manual(values = c(sequential = 'black', independent = 'grey70')) +
  werptoolkitr::theme_werp_toolkit()

proc_basin_bar
```

We have always treated the habitat restriction as another step in the sequence, and I'm having a hard time reframing that in my head, so I'm going to keep making those figs

```{r}
seq_proc_basin_bar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & stage_name %in% sequential_stages) |> 
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
    scale_fill_manual(values = stage_pal) +
  werptoolkitr::theme_werp_toolkit()

seq_proc_basin_bar
```

```{r}
seq_hab_basin_bar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & stage_name %in% sequential_hab) |> 
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
    scale_fill_manual(values = stage_pal) +
  werptoolkitr::theme_werp_toolkit()

seq_hab_basin_bar
```

and matching the all-together timeseries

```{r}
inter_basin_bar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & stage_name %in% c(sequential_hab, 'Recruitment')) |>
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage_name) |>
ggplot(aes(x = stage_name, y = mean_area, fill = stage_name)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
    scale_fill_manual(values = stage_pal) +
  werptoolkitr::theme_werp_toolkit()

inter_basin_bar

```

Those stepthrough plots give me (an) idea(s). Let's see if I can pull it off

I think it's the same data as above, just reorganised

```{r}
new_basin_bar_hab <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, hab_type, model_type)) |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
ggplot(aes(x = hab_type, y = mean_area, fill = stage_name, color = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank())

new_basin_bar_hab
```

THis one goes to the appendix

```{r}
new_basin_bar_proc2 <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           !is.na(proc_type)) |>
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, model_type)) |>
ggplot(aes(x = proc_type, y = mean_area, fill = stage_name, color = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank())

new_basin_bar_proc2
```

Same, but only the sequential

```{r}
new_seq_hab_bar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           !is.na(proc_type) &
           !grepl('Germ|Seed', stage_name)) |>
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, model_type)) |>
ggplot(aes(x = proc_type, y = mean_area, fill = stage_name,
           color = model_type, linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  scale_linetype_manual(values = line_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model", 
       color = "Model type", linetype = "Model type")

new_seq_hab_bar
```

Those are filled with the particular stage, and colored by process v hab. But what if I do that differently? Is it clearer, or less clear? The colors won't match the timeseries, but is that OK if it's clearer?

```{r}
new_seq_hab_bar_c <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           !is.na(proc_type) &
           !grepl('Germ|Seed', stage_name)) |>
  mutate(hab_comp = ifelse(as.character(hab_type) == 'All wetlands',
                           as.character(proc_type), as.character(hab_type)),
         hab_comp = factor(hab_comp, levels = c(levels(proc_type), "Recorded wetland types","Named wetland types"))) |> 
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, proc_type, hab_comp, model_type)) |>
ggplot(aes(x = proc_type, y = mean_area, 
           fill = hab_comp, 
           color = model_type, 
           alpha = model_type,
           linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model", 
       color = "Model type", linetype = "Model type", 
       alpha = 'Model type')

new_seq_hab_bar_c
```

And similar for the habitat-referenced

```{r}
new_basin_bar_hab_c <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           stage_name %in% c(sequential_hab, 'Recruitment') &
           !is.na(hab_type)) |>
  sf::st_drop_geometry() |> 
  mutate(hab_comp = ifelse(grepl('Recruit', stage_name),
                           'Recruitment', as.character(hab_type)),
         hab_comp = factor(hab_comp, levels = levels(stage_name))) |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_name, hab_type, model_type, hab_comp)) |>
  # In this situation, recruitment alone *is* both- it's within all habitats- I think just note that though
ggplot(aes(x = hab_type, y = mean_area, fill = hab_comp, 
           color = model_type, 
           alpha = model_type,
           linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
  scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +  
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model", 
       color = "Model type", linetype = "Model type", 
       alpha = 'Model type')

new_basin_bar_hab_c
```

Dummy the bar legend

```{r}
dummybar <- all_data_basin |> 
  filter((species == 'red_gum' | is.na(species)) & 
           stage_name %in% c(sequential_stages, anae_stages) &
           !grepl('Germ|Seed', stage_name)) |>
  sf::st_drop_geometry() |> 
  mutate(stage_fake = ifelse(grepl(' and ', as.character(stage_name)), 
                             as.character(hab_type),
                             as.character(stage_name)),
         stage_fake = factor(stage_fake, levels = levels(stage_name))) |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = c(stage_fake, proc_type, model_type)) |>
ggplot(aes(x = proc_type, y = mean_area, 
           fill = stage_fake, 
           color = model_type, 
           alpha = model_type,
           linetype = model_type)) +
  geom_col(position = 'dodge') +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area),
                 position = position_dodge2(width = 0.9)) + # Why 0.9?
    scale_fill_manual(values = stage_pal) +
    scale_color_manual(values = type_pal) +
  scale_alpha_manual(values = alpha_type) +
  scale_linetype_manual(values = line_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "Mean\nlog(area + 1)", fill = "Model", 
       color = "Model type", linetype = "Model type", 
       alpha = 'Model type')

dummybar


barbottom <- dummybar + 
  theme(legend.position = 'bottom', legend.title.position = 'top') +
  guides(fill = guide_legend(nrow = 3), color = guide_legend(nrow = 3))


bar_legend <- ggpubr::get_legend(dummybar)
bar_bottom_legend <- ggpubr::get_legend(barbottom)
```

This one is better, once i sort otu the labels/colors and the adult + regen data

```{r}


((new_basin_bar_hab + theme(legend.position = 'none')) + 
    (new_seq_hab_bar + theme(legend.position = 'none'))) +
  ggpubr::as_ggplot(bar_legend) +
plot_layout(guides = 'collect')

```

```{r}

bar_layout_stack <- "
AAA#C
BBB#C
"

bar_layout_side <- "
AABB#C
"

compare_bar <- (new_basin_bar_hab_c + 
                  scale_x_discrete(labels = \(x) 
                                   stringr::str_wrap(x, width = 100)) +
                  theme(legend.position = 'none')) + 
  (new_seq_hab_bar_c + scale_x_discrete(labels = \(x) 
                                        stringr::str_wrap(x, width = 100)) +
     theme(legend.position = 'none'))  +
    wrap_plots(ggpubr::as_ggplot(bar_legend), plot_spacer()) +
plot_layout(design = bar_layout_stack)

compare_bar

ggsave(file.path(figpath, 'red_gum_bars.png'),
       compare_bar, width = 16, height = 9, units = "cm")
ggsave(file.path(figpath, 'red_gum_maps.svg'),
       compare_bar, width = 16, height = 9, units = "cm")
```

```{r}
bar_layout_side <- "
AABB
CCCC
"

compare_bar_S <- (new_basin_bar_hab_c + 
                  scale_x_discrete(labels = \(x) 
                                   stringr::str_wrap(x, width = 12)) +
                  theme(legend.position = 'none')) + 
  (new_seq_hab_bar_c + scale_x_discrete(labels = \(x) 
                                        stringr::str_wrap(x, width = 12)) +
     theme(legend.position = 'none'))  +
    wrap_plots(ggpubr::as_ggplot(bar_bottom_legend)) +
plot_layout(design = bar_layout_side)

compare_bar_S

ggsave(file.path(figpath, 'red_gum_bars_side.png'),
       compare_bar_S, width = 16, height = 9, units = "cm")
ggsave(file.path(figpath, 'red_gum_bars_side.svg'),
       compare_bar_S, width = 16, height = 9, units = "cm")
```

```{r}
bar_layout_side2 <- "
AABB#C
"

compare_bar_S2 <- (new_basin_bar_hab_c + 
                  scale_x_discrete(labels = \(x) 
                                   stringr::str_wrap(x, width = 12)) +
                  theme(legend.position = 'none')) + 
  (new_seq_hab_bar_c + scale_x_discrete(labels = \(x) 
                                        stringr::str_wrap(x, width = 12)) +
     theme(legend.position = 'none'))  +
    wrap_plots(ggpubr::as_ggplot(bar_legend), plot_spacer()) +
plot_layout(design = bar_layout_side2)

compare_bar_S2

ggsave(file.path(figpath, 'red_gum_bars_side2.png'),
       compare_bar_S2, width = 16, height = 9, units = "cm")
ggsave(file.path(figpath, 'red_gum_bars_side2.svg'),
       compare_bar_S2, width = 16, height = 9, units = "cm")
```

Now, can we do something similar with maps? Do we need the difference/relative? Or is it enough to just plot the raw dta? Also a q for the bars- we could do a relativized version to look at the proportional sensitivity, but would that just confuse the issue?

And for maps, should we relativise to area in each catchmentz/

Really, the sort of sequential figs we have for process (and all over MER) are great. the catch is the bifurcation introduced by the two habitat types. It makes the vis hard.

## Maps

Just the hab

```{r}
all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% anae_stages) |> 
  ggplot(aes(fill = area)) +
  geom_sf() +
  scale_fill_viridis_c(option = 'mako', trans = 'log10') +
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()
```

Habitat

```{r}

# Should I facet? Or should I make each panel separately and stitch together with patchwork?
hab_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% anae_stages) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()

hab_maps
```

## Process

```{r}
bio_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% process_stages) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()

bio_maps
```

As above, does that one actually make more sense as the independents and then the sequentials?

```{r}
bio_indep_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% c('Adult', 'Germination', 'Seedling')) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()

bio_indep_maps
```

```{r}
bio_seq_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% c('Adult', 'Regeneration', 'Recruitment')) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()

bio_seq_maps
```

Those two might work well paneled up

```{r}
bio_indep_maps / 
  bio_seq_maps +
  plot_layout(guides = 'collect')
```

## Interactive

JUST the interactive

```{r}
inter_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% 
           c('Recruitment and Named', 'Recruitment and Recorded')) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()

inter_maps
```

We can also put them on the end of the sequential, as we did in the bar graphs. It's a little bit weird, because they aren't sequential with each other.

```{r}
inter_seq_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% 
           sequential_stages) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_grid(.~stage_name) +
  werptoolkitr::theme_werp_toolkit()

inter_seq_maps
```

Similarly, we can 'sequence' them off the habitat

```{r}
inter_habseq_maps <- all_data_time |> 
  filter(species == 'red_gum' & stage_name %in% sequential_hab) |> 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_wrap('stage_name', nrow = 2) +
  werptoolkitr::theme_werp_toolkit()

inter_habseq_maps
```

What I want is a comparison matrix. Can I get that to work without too much monkeying?

We could drop that top panel, but it's actually informative. Moving top to bottom is the effect of requireing process, moving from left to either of the middle and right column is the effect of limiting to habitat types.

```{r}
# Don't like this
# levels(all_data_time$stage_name) <- c('', levels(all_data_time$stage_name))

inter_matrix_maps <- all_data_time |> 
  filter((species == 'red_gum' | is.na(species)) & 
           stage_name %in% c(sequential_hab, 'Recruitment')) |> 
  mutate(stage_name = forcats::fct_drop(stage_name)) |> 
  # filter(!is.na(species)) |> # 
  ggplot(aes(fill = log10(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') + # , limits = (c(0, 22))
  facet_wrap('stage_name', nrow = 2, drop = FALSE) +
  # facet_wrap('stage_name', ncol = 3) +
  werptoolkitr::theme_werp_toolkit() +
  labs(fill = 'log(area + 1)')

inter_matrix_maps


ggsave_multi(file.path(figpath, 'red_gum_interaction_map'),
        plot = inter_matrix_maps,
        devices = c('png', 'svg', 'pdf'),
        width = 16, height = 9, units = "cm")

ggsave(file.path(figpath, 'red_gum_interaction_map'), device = 'png',
       inter_matrix_maps, width = 16, height = 9, units = "cm")
ggsave(file.path(figpath, 'red_gum_interaction_map'), device = c('svg', 'pdf'),
       inter_matrix_maps, width = 16, height = 9, units = "cm")
```

We could obviously fill those two middle panels with the difference or the relative change, but is it needed? or is the bar plot covering it?

Make the relative anyway for the appendix, I think,

### Scratch

```{r}
#| label: fig-process-basin
#| fig-cap: Area favourable for sequential life stages in the basin

# # We need the bits of this elsewhere, but I don't think we acutally need to display it anywhere.
# 
seq_proc_panel <- purrr::imap(seq_proc_basin_ts, \(x, i)
                   x + ggtitle(stringr::str_replace(i, '_', ' ') |>
                                 stringr::str_to_sentence())) |>
  wrap_plots() +
  plot_layout(guides = 'collect')

seq_proc_panel
```

We can do those separately (below), but I think that covers it pretty well.

```{r}
#| label: fig-process-sequential-basin
#| fig-cap: Area favourable for red gum life stages in the basin
seq_proc_basin_ts <- all_data_basin |> 
  filter(species == 'red_gum' & stage_name %in% sequential_stages) |> 
ggplot(aes(x = year, y = (area + 1), color = stage_name)) +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point() +
  werptoolkitr::theme_werp_toolkit()

seq_proc_basin_ts

```

```{r}
#| label: fig-hab-sequential-basin
#| fig-cap: Area favourable for red gum life stages in the basin
seq_hab_basin_ts <- all_data_basin |> 
  filter(species == 'red_gum' & stage_name %in% sequential_hab) |> 
ggplot(aes(x = year, y = area, color = stage_name)) +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point() +
  werptoolkitr::theme_werp_toolkit()

seq_hab_basin_ts
```

Both. We could throw the whole smash together to see how habitat affects each stage, @fig-processxhab-basin, but it's more reasonable to either look at each stage separately (likely in an appendix) or as the sequential set of processes (and maybe habs)?

```{r}
#| label: fig-processxhab-basin
#| fig-cap: Area favourable for red gum life stages in the basin
all_data_basin |> 
  filter(species == 'red_gum' & stage_name %in% combo_stages) |> 
ggplot(aes(x = year, y = area, color = stage_name)) +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point()
```

```{r}
#| label: fig-inter-basin
#| fig-cap: Area favourable for red gum life stages in the basin
inter_basin_ts <- all_data_basin |> 
  filter(species == 'red_gum' & stage_name %in% c(sequential_hab, 'Recruitment')) |> 
ggplot(aes(x = year, y = log10(area + 1), color = stage_name, shape = model_type)) +
    geom_line(show.legend = TRUE) +
  geom_point(show.legend = TRUE)  +
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  scale_shape_manual(values = shape_type) +
  werptoolkitr::theme_werp_toolkit(axis.title.x = element_blank()) +
  labs(y = "log(area + 1)", color = "Model",
       shape = "Model type")

inter_basin_ts
```

# OLD- more complete data explore

# Intro

Skipping the big-picture stuff, what set of comparisons do we want to make and why? (some/most of this goes to methods)

-   Strictures capture biological process- how much favourable area do we get for those processes?

-   Habitat definitions exist that capture current wetlands with characteristic veg (cite Shane)

    -   Some are named (e.g. River red gum forest riparian zone or floodplain)

    -   The species obviously live elsewhere as well, so we can also define 'acceptable' habitat types

-   We want to know how physical conditions (inundation and soil moisture - maybe temp but it's not in now) affect the spatio-temporal patterns of favourability across the basin.

-   We can judge this based on both biological process and habitat type and together

    -   And compare them- they tell us different things

-   The two approaches have different benefits and drawbacks

    -   Missing covariates in both cases

    -   Inability to forecast with habitat- 'red gum' habitat will change as climate shifts

    -   a gajillion others

-   Linking them together solves some problems (covariates, largely), but may exacerbate others (climate shifts)

*The organisation here is very much a first pass.* It may be that, for example, we should set up the main arguments and comparisons with just a paneled set of the basin-scale figures from each section, since they're easier to read, and then dive into the catchments; i.e invert the nested structure that I have here.

# Methods

I'll work on writing them up for SRA anyway, and stuff them in here for the processing. Most of the strictures come from [@roberts2011; @casanova2015; @jensen2008; @rogers2011]. We'll need to cite the MER paper in review, probably, along with the github (for both this project and MER).

Adults are not connected to the rest of the life stages because the persistence time is too long- germination during the period considered is not likely to be the dominant driver of adult numbers.

*Notes* Ana Backstrom made the points that a) some species (e.g. lignum) don't really regenerate from germination, but from vegetative sprouting, and b) the non-woody veg is likely highly correlated with the germination stricture. For a, we've changed the name to germination. We haven't explicitly addressed b, but it is a good point- this is just asking if there's inundation followed by a short wet period, so likely is a good estimate of a flush of annuals. If we can find cites for that, that would be good. *and* if we can find cites for the length of time those annuals need to survive to seed set (I think that might actually be the only thing that's really reffed in the original MER veg- will look), then we can use the machinery for 'seedling survival' here to have a 'survival until seed set' for herbacious veg. Which would also be great- that'd be a whole life cycle. But that wasn't in SRA, so hasn't been done (except to the extent we already did it in MER).

I have called 'germ and then seed' 'recruitment'.

Area units are m\^2 to avoid errors when we adjust some and not others during processing. Hectares should /10000.

The adults typically have long lookback windows, so have a lot of NA in the first part of the timeseries.

Need to bring over a short summary of the ALA pull method for defining habitat type

Need the actual stricture definitions- I'm going to need to write that for SRA anyway.

I'm doing everything below for one species, because I'm focusing on the comparisons of different life stage and different model types, rather than comparison of species. Also, most species' strictures are very similar (as a result of limited info). Thinking we lay out all the arguments for one, then make appendices with parallel plots for the others, and draw out any interesting differences we see when we do that.

Layout/structure of comparisons

-   Process-based strictures one at a time and sequentially (biological). No habitat

-   Inundation of habitat types (by name and ala records). No biology

-   Compare the strict biological to the strict habitat

-   Joint- process-based with a habitat filter (i.e. interactive)

# Process-only analyses

Will need to clean figures up, obviously. All species are in the dataframes, I'm just plotting one here for simplicity. veg4_data_check has a quick and dirty way to make parallel figs for all species, but it's too crude for a ms, so I'm just using one species here as an example to build on.

## Adult condition

Here, we assess area of favourable adult condition, primarily as a consequence of inundation duration and periods between events.

```{r}
all_process |> 
  filter(stage == 'adult'& species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
all_process |> 
  filter(stage == 'adult'& species == 'red_gum') |> 
ggplot(aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

Basin-scale

```{r}
all_process_basin |> 
  filter(stage == 'adult'& species == 'red_gum') |> 
  ggplot(aes(x = year, y = area)) +
  geom_line() +
  geom_point() +
  theme(legend.position = 'none')
```

## Germination

Just based on requirements for preceding inundation and subsequent soil moisture, we get the area of wetlands with favourable germination/germination conditions (@fig-regen-catch, @fig-regen-map).

```{r}
#| label: fig-regen-catch
#| fig-cap: Area favourable for red gum germination in each catchment
all_process |> 
  filter(stage == 'germination'& species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
#| label: fig-regen-map
#| fig-cap: Area favourable for red gum germination in each catchment as a map
all_process |> 
  filter(stage == 'germination'& species == 'red_gum') |> 
ggplot(aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

At the basin scale, @fig-regen-basin, we see temporal variation. We should probably drop this and just use the one in the Lifecycle comparison section.

```{r}
#| label: fig-regen-basin
#| fig-cap: Area favourable for red gum germination summed across the basin
all_process_basin |> 
  filter(stage == 'germination'& species == 'red_gum') |> 
  ggplot(aes(x = year, y = area)) +
  geom_line() +
  geom_point() +
  theme(legend.position = 'none')
```

## Seedling survival

The third step in the life cycle is survival of seedlings post-germination. When considered on its own (i.e. were conditions right for seedling survival), there is very little favourable area anywhere @fig-seed-catch, @fig-seed-map.

```{r}
#| label: fig-seed-catch
#| fig-cap: Area favourable for red gum seedling survival in each catchment
all_process |> 
  filter(stage == 'seedling'& species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
#| label: fig-seed-map
#| fig-cap: Area favourable for red gum seedling survival in each catchment
all_process |> 
  filter(stage == 'seedling'& species == 'red_gum') |> 
ggplot(aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

At the basin scale, that is @fig-seed-basin.

```{r}
#| label: fig-seed-basin
#| fig-cap: Area favourable for red gum seedling survival summed to basin
all_process_basin |> 
  filter(stage == 'seedling'& species == 'red_gum') |> 
  ggplot(aes(x = year, y = area)) +
  geom_line() +
  geom_point() +
  theme(legend.position = 'none')
```

And these are actually much more permissive seedling strictures than typical. 6 mo instead of 2 years. Are they wrong? I think probably not; there are cites that say there have only been a couple successful events in 100 years in the basin (I think was for red gum? I'll dig it up- but still, for long-lived trees, seedling survival may in fact be very infrequent and still be fine).

## Sequential life-cycle

The life cycle is sequential, and so what we are interested in ultimately is recruitment success; that is, germination and subsequent survival until maturity or at least some sort of 'establishment'. Here, we ask whether conditions supported germination *from adults* and whether there was seedling survival *after successful germination conditions*. Thus, this is not simply the minimum of the upper figures, it takes sequencing into account, and we lose some areas of successful seedling conditions because they were not preceded by germination.

*I'm going to stop cross-reffing and captioning figs unless there's somewhere where it's really needed, just need to get the story sorted first*

### Adult then germ

```{r}
all_process |> 
  filter(stage == 'adult_regen'& species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
all_process |> 
  filter(stage == 'adult_regen'& species == 'red_gum') |> 
ggplot(aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

At the basin scale, that is

```{r}
all_process_basin |> 
  filter(stage == 'adult_regen'& species == 'red_gum') |> 
  ggplot(aes(x = year, y = area)) +
  geom_line() +
  geom_point() +
  theme(legend.position = 'none')
```

### Recruitment (full cycle)

```{r}
all_process |> 
  filter(stage == 'recruitment'& species == 'red_gum') |> 
ggplot(aes(x = year, y = log(area), color = ValleyName)) +
  geom_line() + 
  facet_wrap('ValleyName') +
  theme(legend.position = 'none')
```

```{r}
all_process |> 
  filter(stage == 'recruitment'& species == 'red_gum') |> 
ggplot(aes(fill = log(area))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

At the basin scale, that is

```{r}
all_process_basin |> 
  filter(stage == 'recruitment'& species == 'red_gum') |> 
  ggplot(aes(x = year, y = area)) +
  geom_line() +
  geom_point() +
  theme(legend.position = 'none')
```

## Lifecyle comparison

We can compare these areas of favourability for each life stage

The adults swamp the others. Though not everywhere- it's spatio-temporally variable.

```{r}
all_process |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() + 
  scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Ignoring adults is still not very informative- germination just comes in as obviously swamping recruitment. Maybe it's just a bad idea to try to plot them together, no matter how obvious that is as a thing to do a priori. Really, what we probably need is the sort of conditional plot I did for MER.

```{r}
all_process |> 
  filter(species == 'red_gum' & stage != 'adult') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() + 
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

At the basin scale, we see the same pattern but cleaner @fig-process-basin . I use a log transform to better see the non-adult stages, though it makes the massive difference to the adult stage less obvious.

```{r}
#| label: fig-process-basin
#| fig-cap: Area favourable for red gum life stages in the basin
all_process_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point()
```

If we summarise over time, we can make a cool bar graph (or, should we use time as error?)

```{r}

  # Need to manually log if we do the error bars- log of mean != mean of log.
all_process_basin |> 
  filter(species == 'red_gum') |>
  sf::st_drop_geometry() |> 
  summarise(mean_area = mean(log10(area + 1), na.rm = TRUE),
            sd_area = sd(log10(area + 1), na.rm = TRUE),
            .by = stage) |>
ggplot(aes(x = stage, y = mean_area, fill = stage)) +
  geom_col() +
  geom_linerange(mapping = aes(ymin = mean_area-sd_area, ymax = mean_area + sd_area)) +
  # scale_y_continuous(trans = 'log10') +
    scale_fill_manual(values = stage_pal)


```

## Summary

So, ignoring habitat information, we can see that seedling survival is the limiting factor. We haven't connected adults with the earlier stages, so we sort of have two measures of condition- recruitment and persistence. Note also that the germ and seedling survival is smaller than just seedling survival, because there has to have been germination first.

# Habitat only

The above asks about whether conditions favour the biology of the plants. At the simplest, the habitat ignores the biology, and asks if there was inundation in the "correct" habitat type. We also have just straight up inundation area, but that seems like it would go in an appendix, if anywhere.

We can also include habitat information, and do so in two ways: First, some of the ANAE types are explicitly 'red gum', `r type_list$red_gum$nametype[1]`. There are also ALA records of of each species that we have intersected with the ANAE to get a list of ANAE types with records [@tbl-ala-records]. In the analysis, only those types with \> 0.5% of the total records were used (this is methods). *I've made the cut off ones lighter here, but might work better to have a different background. Or leave them off, but I think it's worth showing, probably.*

As with the figures elsewhere, we should/could make this table for all species, but I'm just checking with red gum. I thought about having a column for each species, but the anae types differ and the sorting changes, so since the idea is to focus on species requirements it just gets confusing.

```{r}
#| label: tbl-ala-records
#| tbl-cap: Habitat types with red gum records in Atlas of Living Australia, with number of records. Those in light grey are < 0.5% of the total, and were not included in the set of ALA habitat types used. 
#| 
rgtab <- alatypes |> 
  filter(species == 'red_gum') |> 
  select(ANAE_DESC, Records = n_records) |> 
  arrange(desc(Records))

cutoff <- which(rgtab$Records < sum(rgtab$Records)*0.005)
named <- which(grepl('red gum', rgtab$ANAE_DESC, ignore.case = TRUE))

rgtab |> 
  knitr::kable() |> 
  kable_styling() |> 
  row_spec(named, bold = TRUE, background = 'lightgreen') |> 
  row_spec(cutoff, color = 'grey')
```

See veg1_anae_mapping.qmd for a map of the ALA records if we want to include that, maybe as an appendix. and veg9_methods for a better treatment of the tables.

This just asks how much inundated area there is in each 'suitable' habitat type, as defined by name or ALA records @fig-habitat-catch . As above, it could be called 'favourable area' if favourability is just determined by wetland type.

We might want to split the two habitat sets out- this shows they're very different, which we need to do, but they're so different we might want to look at them separately. Still, there's a simple but *very* important point here that species don't only live in 'their' habitat type, and there's likely much more opportunity across the basin for them to get inundated if we consider all the habitat types in which they're found. That's not surprising, but this quantifies it (and others don't seem to consider it).

I haven't logged area here to illustrate how striking the difference is, but have logged it below. Not sure which is better.

```{r}
#| label: fig-habitat-catch
#| fig-cap: Area of inundation in ANAE types that match the name ('anae_name') or where there are ALA records ('anae_ala') for red gum.
inun_anae_types |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() + 
    scale_color_manual(values = stage_pal) +
facet_wrap('ValleyName')
```

A map example, separate here because of scaling and readability. It's too much, but cool spatio-temporal patterns.

```{r}
inun_anae_types |> 
  filter(species == 'red_gum' & stage == 'anae_name') |> 
ggplot(aes(fill = log10(area + 1))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

```{r}
inun_anae_types |> 
  filter(species == 'red_gum' & stage == 'anae_ala') |> 
ggplot(aes(fill = log10(area + 1))) +
  geom_sf(color = NA) +
  facet_wrap('date') +
  scale_fill_viridis_c()
```

At the basin scale

```{r}
inun_anae_types_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

# Comparing process and habitat

We've now seen what we get for 'favourable area' for process-based models and for habitat types. Now, we compare how they differ in terms of what they tell us when considered separately @fig-hab-strict-catch, @fig-hab-strict-basin.

There are a couple very interesting comparisons to do here- what area do we get from the germ, adult, and these habitat requirements @fig-hab-strict-catch ? Could put adult_germ_seed in there, but we know it's basically 0 **and that's really important but makes a dumb plot**- if seeds are the dominant pinch point, that won't get picked up at all when you look at inundation of ANAES in the 'red gum' type- just like germ and adult condition, the inundation of red gum will look basically OK most of the time, but actual population condition depends on seedling survival which has a very different pattern. Is there a way to show that? Or is it just something to bring out in the discussion?

Need to work on scales and presentation of the different types, but putting on log helps. Basically, adult is highest, ala is MUCH larger than name, and germ tends to be on the same order as name, though there's quite a lot of (particularly spatial) variation around that statement- some catchments have a lot more germ than 'red gum' ANAE types, and others have a lot less.

What to say about it?

-   We get more favourable area from adults than from habitat, so some anae types look good for adults but don't have records of that species. Could be places to move into.

-   germination is typically smaller and more variable than habitat (though this is spatio-temporally variable), so not all the inundated area is suitable for germination. Due to e.g. timing.

-   Full recruitment is MUCH smaller and infrequent, and likely the limiting factor for the population. Its pattern does not get picked up at all by habitat inundation

```{r}
#| label: fig-hab-strict-catch
#| fig-cap: Area favourable for each red gum life stage and the two definitions of habitat *without interactions*, i.e. 'germination' here is in all ANAE wetlands, not only those that are 'habitat'.
process_and_hab |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
  scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin

```{r}
#| label: fig-hab-strict-basin
#| fig-cap: Area favourable for each red gum life stage and the two definitions of habitat *without interactions*, i.e. 'germination' here is in all ANAE wetlands, not only those that are 'habitat'.
process_and_hab_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

# Interactive strictures and habitat

Then, we ask what happens if we have both- ie there are biological strictures, but also requirements for habitat?

This lets us ask questions from two directions with the same set of data by comparing each model alone with the interactive model where we need both successful processes and habitats:

1.  How do habitat requirements restrict what the biology/process tells us?

    1.  Baseline is the process model alone, then we see how limiting that to habitat types reduces area

        1.  This is how we've typically done things, as it picks up unknown requirements

        2.  But it is static and loses areas that may be becoming favourable

2.  How does process/biology restrict what we get from habitat?

    1.  Baseline is the habitat inundation model alone, then we see how requiring successful processes within that reduces area.

        1.  If doing a habitat-type focused analysis, the processes can *dramatically* limit the actual favourability

        2.  *expansion* from habitat is covered above where we compare the two independent models, here we just look at the reduction in area caused by the interaction with biology

Can make maps for all of this too, but not sure how useful they'll be.

## Germination and habitat

The area of germination favourability declines when it has to occur in the proper habitat type, and is typically, but not always lower than the total inundation within the habitat @fig-germ-interact-catch, @fig-germ-interact-basin.

First I plot just the raw results, and then I plot specific comparisons.

anae_ala is almost always highest, so we're not losing much if any germ habitat to the ala restriction. But see avoca, it does happen, indicating favourable germination conditions outside typical habitat types. We always lose a LOT to the habitat name (note log scale).

```{r}
#| label: fig-germ-interact-catch
#| fig-cap: Area favourable for each red gum germination alone and after clipping to 'habitat' defined both ways. The overall inundation of the habitat types is included as reference 'anae_ala' and 'anae_name'.
process_and_hab_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
germ_hab |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin

```{r}
#| label: fig-germ-interact-basin
#| fig-cap: Area favourable for each red gum germination alone and after clipping to 'habitat' defined both ways. The overall inundation of the habitat types is included as reference 'anae_ala' and 'anae_name'.
germ_hab_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

Now let's draw out specific comparisons in both directions.

How much area do we lose from process if we restrict by habitat? Here, we use the process-only germination as the baseline, and ask how much less area there is when we cut that to the ANAE types with their name or where they have ALA records. Specifically, this compares germ to germ_anae_ala and anae_name?

Do I want relative or the actual area?

```{r}
germ_compare_r <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germination', 'germination_ala', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germination',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

germ_compare_d <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germination', 'germination_ala', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germination',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'difference')
```

If we relativise to the germination stricture alone, we get the proportional loss in favourability due to habitat requirements @fig-germ-relative-catch, @fig-germ-relative-basin.

```{r}
#| label: fig-germ-relative-catch
#| fig-cap: Area favourable for red gum germination when both germination and habitat are considered, relativised to the germination favourability in the absence of a habitat requirement, thus showing proportional reduction in germination due to habitat requirements.
germ_compare_r |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
      scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

```{r}
germ_compare_d |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = difference_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
      scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin

```{r}
#| label: fig-germ-relative-basin
#| fig-cap: Area favourable for red gum germination when both germination and habitat are considered, relativised to the germination favourability in the absence of a habitat requirement, thus showing proportional reduction in germination due to habitat requirements.
germ_compare_r_basin <- germ_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('germination', 'germination_ala', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germination',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

germ_compare_r_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

How much do we lose from just looking at habitat inundation when we also ask if that inundation met germination conditions? Specifically, this compares the inundation in anae types to the germination stricture within that habitat type.

Thus, we flip that around to the inuns as baseline, what proportion of the inundated habitat is lost when we consider the biological processes *within those types*? We do it for both the named types and the ALA-selected.

```{r}
germ_inun_name_compare <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_name', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')
germ_anae_ala_compare <- germ_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_ala', 'germination_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')
```

Whether 'habitat' is determined by name or ALA records, there are *massive* drops in the area favourable within the wetland types when we require it to meet germination conditions @fig-name-germ-relative-basin, @fig-name-germ-relative-catch, @fig-ala-germ-relative-catch, @fig-ala-germ-relative-basin.

```{r}
#| label: fig-name-germ-relative-catch
#| fig-cap: Area favourable for red gum germination when both germination and habitat are considered, relativised to the habitat favourability of ANAE types described by the species in the absence of a germination requirement, thus showing proportional reduction in germination due to the biological germination requirements.
germ_inun_name_compare |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

```{r}
#| label: fig-ala-germ-relative-catch
#| fig-cap: Area favourable for red gum germination when both germination and habitat are considered, relativised to the habitat favourability of ANAE types with ALA records in the absence of a germination requirement, thus showing proportional reduction in germination due to the biological germination requirements.
germ_anae_ala_compare |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin

```{r}
#| label: fig-name-germ-relative-basin
#| fig-cap: Area favourable for red gum germination when both germination and habitat are considered, relativised to the habitat favourability of ANAE types described by the species in the absence of a germination requirement, thus showing proportional reduction in germination due to the biological germination requirements.
germ_inun_name_compare_basin <- germ_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_name', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

germ_inun_name_compare_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

```{r}
#| label: fig-ala-germ-relative-basin
#| fig-cap: Area favourable for red gum germination when both germination and habitat are considered, relativised to the habitat favourability of ANAE types with ALA records in the absence of a germination requirement, thus showing proportional reduction in germination due to the biological germination requirements.
germ_anae_ala_compare_basin <- germ_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_ala', 'germination_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

germ_anae_ala_compare_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

### Maps over the period

Get the relativisations for each catchment over the period. Do the mean over the period on the area, *then* relativise

```{r}
# Get the time-mean
# fastest to drop geometry and re-add

germ_period <- germ_hab |> 
  sf::st_drop_geometry() |>
  summarise(area = mean(area, na.rm = T),
            .by = c(ValleyName, stage, species)) |> 
  left_join(valleys) |> 
  st_as_sf()

hab2germ_period <- germ_period |>  
  filter(stage %in% c('germination', 'germination_ala', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'germination',
                                 group_cols = c('ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

germ2name_period <- germ_period |> 
  filter(stage %in% c('anae_name', 'germination_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

germ2ala_period <- germ_period |> 
  filter(stage %in% c('anae_ala', 'germination_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')
```

```{r}
# I want to facet, but the fill scales are too different and scales = free doesn't work.
name_germ_map <- hab2germ_period |> 
  # filter(species == 'red_gum' & stage %in% c('germination_name', 'germination_ala')) |> 
  filter(species == 'red_gum' & stage %in% c('germination_name')) |> 
ggplot(aes(fill = relative_area)) +
  geom_sf() +
  # facet_grid(.~stage, scales = 'free') +
  scale_fill_viridis_c(option = 'mako') +
  labs(fill = "Area relative\nto process-based") +
  ggtitle("Habitat name") +
  werptoolkitr::theme_werp_toolkit()

ala_germ_map <- hab2germ_period |> 
  # filter(species == 'red_gum' & stage %in% c('germination_name', 'germination_ala')) |> 
  filter(species == 'red_gum' & stage %in% c('germination_ala')) |> 
ggplot(aes(fill = relative_area)) +
  geom_sf() +
  # facet_grid(.~stage, scales = 'free') +
  scale_fill_viridis_c(option = 'mako') +
  labs(fill = "Area relative\nto process-based") +
  ggtitle("Habitat records") +
  werptoolkitr::theme_werp_toolkit()

germ_name_map <- germ2name_period |> 
  # filter(species == 'red_gum' & stage %in% c('germination_name', 'germination_ala')) |> 
  filter(species == 'red_gum' & stage %in% c('germination_name')) |> 
ggplot(aes(fill = relative_area)) +
  geom_sf() +
  # facet_grid(.~stage, scales = 'free') +
  scale_fill_viridis_c(option = 'mako') +
  labs(fill = "Area relative\nto habitat name") +
  ggtitle("Process-based") +
  werptoolkitr::theme_werp_toolkit()

germ_ala_map <- germ2ala_period |> 
  # filter(species == 'red_gum' & stage %in% c('germination_name', 'germination_ala')) |> 
  filter(species == 'red_gum' & stage %in% c('germination_ala')) |> 
ggplot(aes(fill = relative_area)) +
  geom_sf() +
  # facet_grid(.~stage, scales = 'free') +
  scale_fill_viridis_c(option = 'mako') +
  labs(fill = "Area relative\nto habitat records") +
  ggtitle("Process-based") +
  werptoolkitr::theme_werp_toolkit()

(name_germ_map + ala_germ_map) / (germ_name_map + germ_ala_map) +
  plot_annotation(tag_levels = 'a')
```

## Recruitment and habitat

Keeping this straight is tricky, but I'm stopping writing fig caps for now. It follows the same set of logical steps as germination alone

I could look at just seedling too, but this is already a TON

Again, start with just plotting the outcomes

```{r}
adult_germ_seed_hab |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin, also logged so we can see the data.

```{r}
adult_germ_seed_hab_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point()
```

Now the comparisons

What do we lose from the process-based strictures if we require them to occur in the habitat types?

```{r}
adult_germ_seed_compare_r <- adult_germ_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('recruitment', 'recruitment_ala', 'recruitment_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'recruitment',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_germ_seed_compare_d <- adult_germ_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('recruitment', 'recruitment_ala', 'recruitment_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'recruitment',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'difference')
```

This is almost all NaN because there's so little recruitment it's all divide-by-zero. Could add one, but the message is captured in the next one.

```{r}
adult_germ_seed_compare_r |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Here we can see that not much gets lost to the habitat requirements, because there's not much to lose. But it does happen in Avoca, further limiting the already-rare recruitment events if they are restricted to habitat.

```{r}
adult_germ_seed_compare_d |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = difference_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin has enough we can use the relative. Sort of.

```{r}

adult_germ_seed_compare_r_basin <- adult_germ_seed_hab_basin |> 
  #mutate(area = area + 1) |> # make it not NA
  sf::st_drop_geometry() |> 
  filter(stage %in% c('recruitment', 'recruitment_ala', 'recruitment_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'recruitment',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_germ_seed_compare_r_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

How much do we lose from just looking at habitat inundation when we also ask if that inundation met recruitment conditions? Specifically, this compares the inundation in anae types to the recruitment strictures within that habitat type.

Thus, we flip that around to the inuns as baseline, what proportion of the inundated habitat is lost when we consider the biological processes *within those types*? We do it for both the named types and the ALA-selected.

```{r}
adult_germ_seed_inun_name_compare <- adult_germ_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_name', 'recruitment_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_germ_seed_anae_ala_compare <- adult_germ_seed_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_ala', 'recruitment_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')
```

This is kind of silly, since the strictures are almost all basically 0, but it makes the point that we lose a LOT (all of the area). So the habitat inundation tells us nothing about seedlings, and if we base how good we think we're doing on habitat, it's completely wrong.

```{r}
adult_germ_seed_inun_name_compare |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

For the ALA, there *is* some data, but it's not possible to see on an unscaled 0-1 axis

```{r}
adult_germ_seed_anae_ala_compare |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
    scale_color_manual(values = stage_pal) +
  # scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName')
```

We could log it (see commented out bit above), or we could just say that by definition the habitat is a line at 1 since it's the reference, and just plot the habitat \* biology, which gets scaled automatically and makes the tiny fraction clear.

In fact, we could drop the upper two plots, and just plot the name and ala together on here, if we're super clear they've been referenced to different things (their respective habitat inundation). The name is still be very boring (but important), since it's always 0.

```{r}
adult_germ_seed_anae_ala_compare |> 
  bind_rows(adult_germ_seed_inun_name_compare) |> 
  filter(species == 'red_gum' & stage %in% c('recruitment_ala', 'recruitment_name')) |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
    scale_color_manual(values = stage_pal) +
  # scale_y_continuous(trans = 'log10') +
  facet_wrap('ValleyName') +
  labs(y = 'favourable area relative to\ninundation of respective habitat types')
```

Basin

```{r}
adult_germ_seed_inun_name_compare_basin <- adult_germ_seed_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_name', 'recruitment_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_germ_seed_anae_ala_compare_basin <- adult_germ_seed_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_ala', 'recruitment_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_germ_seed_anae_ala_compare_basin |> 
  bind_rows(adult_germ_seed_inun_name_compare_basin) |> 
  filter(species == 'red_gum' & stage %in% c('recruitment_ala', 'recruitment_name')) |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  geom_point() +
    scale_color_manual(values = stage_pal) +
  labs(y = 'favourable area relative to\ninundation of respective habitat types')
```

## Adults

Again, start with the overall outputs

```{r}
adult_hab |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() + 
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin, also logged so we can see the data.

```{r}
adult_hab_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point()
```

Now, how much area do we lose from process if we restrict by habitat? Here, we use the process-only adult as the baseline, and ask how much less area there is when we cut that to the ANAE types with their name or where they have ALA records.

Do I want relative or the actual area?

```{r}
adult_compare_r <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('adult', 'adult_ala', 'adult_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'adult',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_compare_d <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('adult', 'adult_ala', 'adult_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'adult',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'difference')
```

What fraction of the area of the process-based strictures alone is lost when they are restricted to specific habitat types? Well, this shows the proportion that remains.

```{r}
adult_compare_r |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
      scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

```{r}
adult_compare_d |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = difference_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
      scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin

```{r}

adult_compare_r_basin <- adult_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('adult', 'adult_ala', 'adult_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'adult',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_compare_r_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

How much do we lose from just looking at habitat inundation when we also ask if that inundation met adult conditions? Specifically, this compares the inundation in anae types to the adult stricture within that habitat type.

Thus, we flip that around to the inuns as baseline, what proportion of the inundated habitat is lost when we consider the biological processes *within those types*? We do it for both the named types and the ALA-selected.

The adults can have more favourable area than inundated area even when clipped to habitat type the habitat area is the area inundated that year, and adult condition can persist for many years. It tends to track with the rolling maximum inundation, and does not ever go over the total area of the relevant habitat type (i.e. we haven't just stuffed something up). See appendix.

```{r}
adult_inun_name_compare <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_name', 'adult_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_anae_ala_compare <- adult_hab |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_ala', 'adult_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('date', 'ValleyName', 'species'),
                                 values_col = 'area', comp_fun = 'relative')
```

Here, we have an interesting and counterintuitive result that there's actually MORE (often much more) favourable area in the adult stricture *even when cut to the ANAE type* than there is in the ANAE inundation. This is because an area can be favourable for adults without inundation that year- it just has to have been within the inter-event limit. So adult favourability falls off with time since maximum inundation. *See appendix*

```{r}
adult_inun_name_compare |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

```{r}
adult_anae_ala_compare |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = relative_area, color = stage)) +
  geom_line() + 
  scale_y_continuous() +
  scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin

```{r}

adult_inun_name_compare_basin <- adult_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_name', 'adult_name')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_name',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_inun_name_compare_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

```{r}
adult_anae_ala_compare_basin <- adult_hab_basin |> 
  sf::st_drop_geometry() |> 
  filter(stage %in% c('anae_ala', 'adult_ala')) |> 
  werptoolkitr::baseline_compare(compare_col = 'stage', base_lev = 'anae_ala',
                                 group_cols = c('date', 'species'),
                                 values_col = 'area', comp_fun = 'relative')

adult_anae_ala_compare_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area, color = stage)) +
  geom_line() +
    scale_color_manual(values = stage_pal) +
geom_point()
```

# Discussion

Biological processes are important- they're what determine where species actually can persist.

In some cases, habitat, particularly around key species, can be a useful shorthand. And put bounds on reasonable places to assess the biological processes, picking up covariates we might have missed, especially in something simple like strictures.

But relying solely on habitat is particularly dangerous- it does not capture whether conditions were actually favourable, particularly for sequential life cycles. And misses things like a major limitation of seedling survival, or in the opposite case, that conditions can be favourable for adults without inundation (or more generally, at longer timescales).

Moreover, with climate change, 'habitat type' as defined statically, will not stay the same, and we run the risk of missing and mis-modeling shifts.

Here, we see areas of congruence and areas of major discrepancy between process-based strictures and habitat-based locations, though they can inform each other. This leads to hypothesis generation (where might 'red gum' wetlands shift in the future, where should we look for red gum), and identifies critical periods for condition, whether or not they occur in the proper wetland type (seedling survival) that can be targeted by management.

# Appendices

## Adult overperformance

Why do the adults end up with more favourable area when clipped to the habitat types than the raw habitat types? Because adult favourability does not depend on yearly inundation, but only on some long return interval; i.e. there may not be any inundation in a given year, but that area is still favourable if it were inundated 8 years ago.

To see this, we could plot the maximum inundation each year, and we would see that the adult area tracks well with the maximum inundation within a species-specific x year lookback. *I haven't saved the max yearly inundation, but the mean. If we want that level of detail, I can tweak the outputs and re-run the strictures to also save the max to make this plot.* In the meantime, we can see that it is less than the total area of the anaes in each habitat type, and so we haven't just stuffed up the clipping.

We have extracted the total area of each wetland group, and we can use that to show that the adult area is always lower than the matching total habitat area, and so we're not generating area somehow.

So, the adult_name and adult_ala are always below the total available habitat in those groups. It's easies to see at the basin scale.

```{r}
adult_hab |> 
  filter(species == 'red_gum') |>
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() + 
  geom_hline(data = total_wetland_area |> 
              filter(species == 'red_gum'),
            aes(yintercept = total_area, color = stage),
            linetype = 'dashed') +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
  facet_wrap('ValleyName')
```

Basin, also logged so we can see the data.

```{r}
adult_hab_basin |> 
  filter(species == 'red_gum') |> 
ggplot(aes(x = year, y = area+1, color = stage)) +
  geom_line() +
  geom_hline(data = total_wetland_area_basin |> 
              filter(species == 'red_gum'),
            aes(yintercept = total_area, color = stage),
            linetype = 'dashed') +
  scale_y_continuous(trans = 'log10') +
    scale_color_manual(values = stage_pal) +
geom_point()
```

# Targeted Figures

## Each of the model types

Habitat

```{r}

# Should I facet? Or should I make each panel separately and stitch together with patchwork?
hab_maps <- inun_anae_types |> 
  group_by(ValleyName, stage, species) |> 
  summarise(area = mean(area, na.rm = TRUE))|>
  ungroup() |> 
  filter(species == 'red_gum') |> 
  mutate(clean_name = case_when(stage == 'anae_name' ~ 'Named wetland types',
                                stage == 'anae_ala' ~ 'Recorded wetland types')) |> 
  ggplot(aes(fill = log(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako', limits = (c(0, 22))) +
  facet_grid(.~clean_name)

hab_maps
```

## Process

```{r}
bio_maps <- all_process |> 
  group_by(ValleyName, stage, species) |> 
  summarise(area = mean(area, na.rm = TRUE))|>
  ungroup() |> 
  filter(species == 'red_gum' & stage %in% c('adult', 'adult_regen', 'recruitment')) |> 
  mutate(clean_name = case_when(stage == 'adult' ~ 'Adult',
                                stage == 'germination' ~ 'Germination',
                                stage == 'seedling' ~ 'Seedling',
                                stage == 'adult_regen' ~ 'Regeneration',
                                stage == 'recruitment' ~ 'Recruitment')) |> 
  ggplot(aes(fill = log(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako', limits = (c(0, 22))) +
  facet_grid(.~clean_name)

bio_maps
```

## Interactive

```{r}
inter_maps <- adult_germ_seed_hab |> 
  group_by(ValleyName, stage, species) |> 
  summarise(area = mean(area, na.rm = TRUE))|>
  ungroup() |> 
  filter(species == 'red_gum' & stage %in% c('recruitment_name', 'recruitment_ala')) |> 
  mutate(clean_name = case_when(stage == 'recruitment_name' ~ 'Recruitment and Named',
                                stage == 'recruitment_ala' ~ 'Recruitment and Recorded',
                                stage == 'recruitment' ~ 'Recruitment')) |> 
  ggplot(aes(fill = log(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako', limits = (c(0, 22))) +
  facet_grid(.~clean_name)

inter_maps
```

Paneling is super ugly.

```{r}
hab_maps +
  bio_maps +
  inter_maps +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides = 'collect')
```

Make in one go?

```{r}
full_compare <- all_process |>
  filter(stage %in% c('adult','adult_regen')) |> 
  bind_rows(adult_germ_seed_hab) |> 
  mutate(clean_name = case_when(stage == 'anae_name' ~ 'Named wetland types',
                                stage == 'anae_ala' ~ 'Recorded wetland types',
                                stage == 'adult' ~ 'Adult',
                                stage == 'germination' ~ 'Germination',
                                stage == 'seedling' ~ 'Seedling',
                                stage == 'adult_regen' ~ 'Regeneration',
                                stage == 'recruitment' ~ 'Recruitment',
                                stage == 'recruitment_name' ~ 'Recruitment and Named',
                                stage == 'recruitment_ala' ~ 'Recruitment and Recorded'))
```

```{r}
full_compare |> 
  group_by(ValleyName, clean_name, species) |> 
  summarise(area = mean(area, na.rm = TRUE))|>
  ungroup() |> 
  filter(species == 'red_gum') |> 
  ggplot(aes(fill = log(area + 1))) +
  geom_sf() + 
  scale_fill_viridis_c(option = 'mako') +
  facet_grid(.~clean_name) +
  werptoolkitr::theme_werp_toolkit(legend.position = 'bottom')
```
