---
title: "Area inundated"
format: html
editor: visual
---

## Calculating the area inundated in each ANAE

First, set directories and set up for parallel

```{r}
source('directorySet.R')
library(CC2)
```

```{r}
library(foreach)
library(doFuture)
library(progressr)
# make the handlers call in the console.
# handlers(global = TRUE)
# Not supposed to need this, but it seems to help
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per job, I think.

```{r}
if (parSet == 'local') {
  plan(multisession)
}

if (parSet == 'gandalf') {
  plan(list(tweak(batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 5,
                                 ntasks.per.node = 12, 
                                 mem = 1000,
                                 job.name = 'area_inundated')),
          multicore))
}
```

## Set the function

The data comes in in mm, and there are an awful lot of 1mm datapoints. Assume those are artifacts, so make a depth limit of 0.5 cm. Units of depth are in m. Following new conventions (dplyr \> 1.1), we hardcode area in not as an argument.

```{r}
areaInun05cm <- function(x) {
  sum(ifelse(x > 0.005, area, 0), na.rm = TRUE)
}
```

### Check what needs to happen

I should make this a cleaner function in eFlowEval once I confirm this approach works.

```{r}
# I've modified makeSHfails to give me a list
# I don't like the 'processed' on here, but it's hardcoded somewhere and I just need this to run.
runlist <- makeSHfails(outerDir = file.path(datOut, 'inundation'),
            summaryFuns = 'areaInun05cm',
            varName = 'areaInun05cm',
            nchunks = 100,
            lengthOrChunk = c('short', 'long'), # , 'long', 'chunk'
            runImmediate = FALSE,
            forceAllCatchments = TRUE,
            returnForR = TRUE, produce_sh = FALSE)
```

```{r}
# making a tibble eliminates some problematic loop nesting
# Run over the catchments and chunks 
runtib <- runlist |>  
  tibble::as_tibble() |> 
  tidyr::pivot_longer(cols = everything())
```

## Set up the runs

```{r}

# To test, cut down to only a few
runtib <- runtib[c(1:2, 401:402)]


# with runlist as a tibble, this could actually be furrr_imap.
with_progress({
  p <- progressor(steps = nrow(runtib))
  alltimes <- foreach(nl = 1:nrow(runtib), 
          .combine = rbind,
          .options.future = list(seed = TRUE,
                                 globals = structure(TRUE, add = "areaInun05cm"))) %dofuture% {
                                          
                                   w = runtib$name[nl]
                                   i = runtib$value[nl]
   
   inuntab <- processData(dataname = 'inundation',
                          data_dir = file.path(datDir,
                                               'Inundation_new',
                                               'data',
                                               'MDB_Water_Depth_v3.6_4326'),
                          poly_path = file.path(datOut, 'ANAEcatchment'),
                          summaryFun = 'areaInun05cm',
                          out_dir = datOut,
                          catchment = w,
                          thischunk = i)

   p(glue::glue('catchment {w} chunk {i} finished'))
   inuntab
      


}
})
```

```{r}
# y <- foreach(i = 1:3, .combine = rbind) %:%
#        foreach(j = 3:5, .combine = rbind, .options.future = list(seed = TRUE)) %dofuture% {
#          writeLines('test', paste0('test', as.character(i), '_', as.character(j), '.txt'))
#   data.frame(i = i, j = j, random = runif(n = 1L)) 
# }
```

### Timings

The timings are saved in alltimes

```{r}
alltimes
```

## Concatenate

We could do this automatically, but it's dangerous. Better to look and check.

```{r}
runlist_end <- makeSHfails(outerDir = file.path(datOut, 'inundation'),
            summaryFuns = 'areaInun05cm',
            varName = 'areaInun05cm',
            nchunks = 100,
            lengthOrChunk = c('short', 'long'), # , 'long', 'chunk'
            runImmediate = FALSE,
            forceAllCatchments = TRUE,
            returnForR = TRUE, produce_sh = FALSE)

if (is.null(runlist_end)) {
  cattime <- system.time(concatANAEchunks(
    outerDir = file.path(datOut,
                         'inundation'),
    summaryFuns = c('areaInun05cm')))
  print(cattime)
} else {
  print("Not all runs completed, did not concatenate")
}


```

### Error checks

There are errors that typically arise with old data and versions of sf that cause ANAE duplication. But safest to always check.

```{r}
if (is.null(runlist_end)) {
 check_aggs <- test_anae_agg(catchments = 'all', datDir = datOut, 
                            variableDir = 'inundation', 
                            summaryFun = 'areaInun05cm') 
 check_aggs
}

```

This should yield 0 rows unless there are unexpected errors and warnings.

```{r}
if (is.null(runlist_end)) {
  check_aggs |> filter(passfail != 'pass' & !grepl('Assigning based on position', passfail))
}

```
