---
title: "Bird breeding inundation"
format: html
editor: visual
---

## Calculating breeding inundation in each ANAE

Set directories and set up for parallel

```{r}
source('directorySet.R')
library(CC2)
library(sf)
library(foreach)
library(doFuture)
library(progressr)
doFuture::registerDoFuture()
```

This notebook will sometimes be run locally, but may be run on the HPC through purl, so set up the future plans appropriately.

Here, we set the local plan to a simple multisession, while the HPC sends the loops here to nodes, and the inner loops in rastPolyJoin should go to cores. This lets us change the slurm commands- time is minutes, ntasks.per.node is cores, and mem is per node, I think.

```{r}
if (parset == 'local') {
  plan(multisession)
}

if (parset == 'gandalf') {
  plan(list(tweak(future.batchtools::batchtools_slurm,
                template = "batchtools.slurm.tmpl",
                resources = list(time = 10,
                                 ntasks.per.node = 12, 
                                 mem = "70GB",
                                 job.name = 'bird_breeding')),
          multicore))
}
```

## Set the function

Water needs to be between 0.5 and 1.5m deep. The data comes in in mm, but gets changed to m for consistency inside process_data. Following new conventions (dplyr \> 1.1), we hardcode area in not as an argument.

```{r}
 areaBirdBreed <- function(x, limitShallow = 0.5, limitDeep = 1.5) {
      sum(ifelse(x >= limitShallow & x <= limitDeep, area, 0))
 }
```

There is a stricture here about time of year. I suppose for speed, I could only read in those inundation files. But it will be much more flexible to get the inundation assessment in all of them, and then use the breeding period as a stricture in the next step.

### Set up the chunks

The following is typically indexed to catchments, but we should be able to use any set of polygon-based groupings. Use the breeding polys created in [waterbird_breeding_polys.qmd](waterbird_breeding_polys.qmd).

```{r}
breeding_polys <- readRDS(file.path(datOut, 'waterbird_breeding', 'breeding_polys.rds'))
```

This just looks for a directory/file structure, so doesn't need the polys, just the names. Use the 'clean' wetland names without spaces.

```{r}
# I've modified makeSHfails to give me a list
# I don't like the 'processed' on here, but it's hardcoded somewhere and I just need this to run.
runlist <- chunks_to_process(out_dir = datOut,
                             dataname = 'inundation', 
                             summaryFun = 'areaBirdBreed',
                             nchunks = 100,
                             catchment = breeding_polys$wetland_clean,
                             returnForR = TRUE,
                             filetype = '.rds')
```

## Set up the runs

Send it the ANAEs we've cut down to the breeding polys (in ANAE_birdbreeding.qmd)

```{r}
# with runlist as a tibble, this could actually be furrr_imap.
with_progress({
  alltimes <- parallel_data(runframe = runlist,
                            dataname = 'inundation',
                          data_dir = file.path(datDir,
                                               'Inundation_new',
                                               'data',
                                               'MDB_Water_Depth_v3.6_4326'),
                          poly_path = file.path(datOut, 'ANAEbirdbreed'),
                          summaryFun = 'areaBirdBreed',
                          out_dir = datOut,
                          nchunks = 100)
})

```

### Timings

The timings are saved in alltimes

```{r}
alltimes
```

## Concatenate

We could do this automatically, but it's dangerous. Better to look and check.

```{r}
runlist_end <- chunks_to_process(out_dir = datOut,
                             dataname = 'inundation', 
                             summaryFun = 'areaBirdBreed',
                             nchunks = 100,
                             catchment = breeding_polys$wetland_clean,
                             returnForR = TRUE,
                             filetype = '.rds')

if (nrow(runlist_end) == 0) {
  cattime <- system.time(concat_chunks(out_dir = datOut,
                             dataname = 'inundation', 
                             summaryFun = 'areaBirdBreed'))
  print(cattime)
} else {
  print("Not all runs completed, did not concatenate")
}


```

### Error checks

There are errors that typically arise with old data and versions of sf that cause ANAE duplication. But safest to always check.

```{r}
if (is.null(runlist_end)) {
 check_aggs <- test_anae_agg(out_dir = datOut,
                             dataname = 'inundation', 
                             summaryFun = 'areaBirdBreed',
                             catchment = breeding_polys$wetland_clean,
                             filetype = '.rds') 
 check_aggs
}

```

This should yield 0 rows unless there are unexpected errors and warnings.

```{r}
if (is.null(runlist_end)) {
  check_aggs |> 
    dplyr::filter(passfail != 'pass' & 
                    !grepl('Assigning based on position', passfail))
}

```
