---
title: "Waterbird tests"
format: html
editor: visual
---

This file is just for sorting out issues and double checking things for the waterbirds.

## Intersecting with ANAEs

```{r}
library(ggplot2)
library(sf)
library(CC2)
```

This assumes I've run waterbird_breeding_polys.qmd to create the breeding polygons.
```{r}
breeding_polys <- readRDS(file.path(datOut, 'SRA',
                                    'waterbird_breeding',
                                    'breeding_polys.rds'))
```


How do we do the intersection with the anaes? Let's not do a complete intersection with a split, let's instead get all the anaes contained in or overlapping the edges of a unit.

First, let's check we do that correctly

```{r}
ggplot() +
  geom_sf(data = ltimNoNorth, aes(fill = ValleyName)) +
  #geom_sf_label(data = ltimNoNorth, aes(label = ValleyName)) +
  geom_sf(data = breeding_polys) + 
  geom_sf_text(data = breeding_polys, aes(label = Wetland))
```

That's hard to read, but what does Corop intersect? And how do we extract that quickly?

```{r}
corop <- breeding_polys |> 
  dplyr::filter(grepl('corop', Wetland, ignore.case = TRUE))
```

```{r}
st_intersection(corop, ltimNoNorth)
```

```{r}
ggplot() +
  geom_sf(data = ltimNoNorth |> dplyr::filter(grepl('Goul', ValleyName))) +
  geom_sf(data = corop)
```

### Bring in ANAEs

```{r}
goulanae <- readRDS(file.path(datOut, 'ANAEcatchment', 'Goulburn_ANAE.rds'))
```

```{r}
ggplot() +
  geom_sf(data = goulanae) +
  geom_sf(data = corop)
```

```{r}
cg_intersect <- st_intersection(goulanae, corop)
```

```{r}
ggplot() +
  geom_sf(data = corop, fill = 'forestgreen') +
  geom_sf(data = cg_intersect)
```

What about other st\_ functions

```{r}
st_covered_by(goulanae, corop) |> unlist() |> sum()
st_touches(corop, goulanae) |> unlist() |> sum()
```

Neither of those seems good.

```{r}
st_intersects(goulanae, corop) |> unlist() |> sum()
```

That's the same number as the intersection. The question though, is if some got chopped off by the intersection.

This only works this easily because we have a single second arg, otherwise we'd have a matrix.

```{r}
goulint <- st_intersects(goulanae, corop) |> 
  purrr::map_lgl(\(x) !rlang::is_empty(x))
```

```{r}
goulover <- goulanae[which(goulint), ]
```

```{r}
ggplot() +
  geom_sf(data = corop, fill = 'forestgreen') +
  geom_sf(data = goulover)
```

Now, which is the best way to go? If its just little river tails poking over, the intersection is probably better? Theoretically, the breeding_polys wouldn't miss important bits, so I think use that.
