---
title: "Aggregate"
format: html
editor: visual
---

```{r}
library(werptoolkitr)
#devtools::load_all('E:/Georgia/WERP_toolkit') 


library(dplyr)
library(sf)

# get directories
source('directorySet.R')
```

## Paths

I'm going to set this up to dump data to the QAEL WERP share for now. Unfortunately, that calls itself something different for each of us.

```{r}
qaelpath <- myhome
#qaelpath <- path.expand(qaelpath)
datDir <- file.path(qaelpath, "Deakin University/QAEL - MER/Model/dataBase")
datOut <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out")
project_dir <- file.path(datOut, 'werpstyle')
hydro_dir <- file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR_numeric_gauges')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output')

```

## MANUAL AGGREGATION - needed for timeseries

## RUN MANUAL

```{r}
  # GET Target frequencies from NSWEWR (could also use NSWEWR from EWR tool?)
 summarydf <- get_any_ewr_output(dir = ewr_results, type = "summary")
 annualdf <- get_any_ewr_output(dir = ewr_results, type = "yearly")
 
 
Target_frequencies <- summarydf |>
    dplyr::select(planning_unit_name, gauge, ewr_code, ewr_code_timing, target_frequency) |>
    dplyr::group_by(planning_unit_name, gauge, ewr_code, ewr_code_timing, target_frequency) |>
    dplyr::distinct() |>
    dplyr::ungroup()

  # Join target frequencies to annualdf
annualdf <- dplyr::left_join(annualdf, Target_frequencies,
    by = dplyr::join_by(ewr_code, ewr_code_timing, gauge, planning_unit_name),
    relationship = "many-to-many"
  )

year_roll <- 10
  # Frequency checks (ACHIEVEMENT test)
  if (year_roll > 1) {
    # Specific rolling time frame
    # calculate number of event years, frequency, and EWR pass/fail at defined (year_roll) year rolling time frames.
    # cease to flows are the inverse of success.
    annualdf_summary <- annualdf |>
      dplyr::group_by(scenario, planning_unit_name, gauge, ewr_code, ewr_code_timing) |>
      dplyr::arrange(scenario, planning_unit_name, gauge, ewr_code, ewr_code_timing, year) |>
      # defined n years
      dplyr::mutate(eventyears_per_n_years = purrr::reduce(purrr::map(1:(year_roll - 1), ~ lag(event_years, ., order_by = year)), `+`) + event_years) |>
      dplyr::mutate(frequency_per_n_years = (eventyears_per_n_years / year_roll) * 100) |>
      dplyr::mutate(frequency_check_n_years = ifelse(grepl("CF", ewr_code), frequency_per_n_years <= target_frequency,
        frequency_per_n_years >= target_frequency
      )) |>
      dplyr::ungroup()

    # ACHIEVEMENT test
    EWR_results_summary <- annualdf_summary |>
      dplyr::group_by(ewr_code, ewr_code_timing, gauge, scenario, planning_unit_name) |>
      dplyr::filter(!is.na(frequency_check_n_years)) |>
      # dplyr::summarise(ewr_achieved = sum(frequency_check_n_years) == dplyr::n()) |> # do all pass?
      dplyr::summarise(ewr_achieved = mean(frequency_check_n_years)) |> # what proportion passes?
      dplyr::mutate(ewr_achieved_timeframe = year_roll) |>
      dplyr::ungroup()
    }
  

  # change the logical to numeric to maintain generality with later functions
  EWR_results_summary$ewr_achieved <- as.numeric(EWR_results_summary$ewr_achieved)
  EWR_results_summary$scenario <- "Historical"

  write.csv(EWR_results_summary, file.path(project_dir, 'MANUAL', 'EWR_summary.csv'))
  
  #####
  #### FOR TIME SERIES
  
  annualdf$ewr_achieved <- as.numeric(annualdf$event_years)
  annualdf$scenario <- "Historical"
  write.csv(annualdf, file.path(project_dir, 'MANUAL', 'EWR_timeseries.csv'))
  
  

```

## Prep for aggregations

-   specific for SRA because gauges are separate csvs, and otherwise are treated like scenarios

```{r}

#FIXING GAUGES
#devtools::load_all('E:/Georgia/WERP_toolkit/R') 
# #NOT SURE HOW TO DO THIS
#temp_df <- get_ewr_output(dir = ewr_results)
# temp_df2 <- get_any_ewr_output(dir = ewr_results, type = 'yearly')
# 
# 
# gauge_EWRS <- sdl_EWRS_agg$ewr_code |>
#   filter(scenario != "MAX")|>
#   mutate(scenario = "Historical")
```

## Aggregation sequencing

-   Sequence (levels of each theme, space, time axis)

-   Aggregation functions at each step

-   Produces a list, with each sheet a step in the aggregation

```{r}
# !!!!!!!!!!!!!
# keep in mind gauges are separate csvs, and are being treated like scenarios 
# !!!!!!!!!!!!!
# the MAX creation doesnt work with this data set. max is only being made for one gauge.
# !!!!!!!!!!!!!


# NOTE: I've been moving to Target as an outcome, since there seems to be appetite to aggregate to the broad ecological groupings. It means we lose some granularity and can't get to the 5,10,20 year targets. I'll do that too and put it in an internal directory.
aggseq_simple <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units)

funseq_simple <- list("ArithmeticMean",
                      'ArithmeticMean') 

system.time(agged_data_simple <- read_and_agg(datpath = ewr_results, 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint,
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq_simple,
           funsequence = funseq_simple,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(agg_results, 'Simple_agg') ))

ewr_code_timing <- agged_data_simple$ewr_code_timing
ewr_code <- agged_data_simple$ewr_code
```

```{r}
aggseq <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units,
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_units,
               Specific_goal = c('env_obj', "Specific_goal"),
               Objective = c('Specific_goal', 'Objective'),
               target_5_year_2024 = c('Objective', 'target_5_year_2024'))


funseq <- list("ArithmeticMean", # changed from 'CompensatingFactor',
               'ArithmeticMean',
               'ArithmeticMean',
               'SpatialWeightedMean',
               'ArithmeticMean',
               'ArithmeticMean',
               'ArithmeticMean')

system.time(agged_data <- read_and_agg(datpath = ewr_results, 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq,
           funsequence = funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(agg_results, 'sdl_specific_goal_objective_agg')))
```

```{r}
target_aggseq <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units,
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_units,
               Specific_goal = c('env_obj', "Specific_goal"),
               Target = c('Specific_goal', 'Target'))

target_funseq <- list("ArithmeticMean", # changed from 'CompensatingFactor',
               'ArithmeticMean',
               'ArithmeticMean',
               'SpatialWeightedMean',
               'ArithmeticMean',
               'ArithmeticMean')

system.time(agged_data_tar <- read_and_agg(datpath = ewr_results, 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = target_aggseq,
           funsequence = target_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(agg_results, 'sdl_specific_goal_agg')))
```

```{r}
#Georgias version:
EWRs_aggseq <- list(
               ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units,
               sdl_units = sdl_units)

EWRs_funseq <- list(
              c('ArithmeticMean', "NumberOfValues", "Variance"), #aggregates ewr_code_timing to ewr_code
              c('ArithmeticMean', "NumberOfValues", "Sum"), #aggregate gauges to planning_unit
              c('ArithmeticMean', "NumberOfValues", "Sum")) #planning_unit gauges to sdl_units

system.time(agged_data_EWRs <- read_and_agg(datpath = ewr_results, 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = EWRs_aggseq,
           funsequence = EWRs_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(agg_results, 'sdl_EWRS_agg')))
```

```{r}
Theme_aggseq <- list(
               ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_units = planning_units,
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_units,
               Target = c('env_obj', 'Target'))

Theme_funseq <- list(
              c('ArithmeticMean', "NumberOfValues", "Variance"), #aggregates ewr_code_timing to ewr_code
              c('ArithmeticMean', "NumberOfValues", "Sum"), #aggregate gauges to planning_unit
              c('ArithmeticMean', "NumberOfValues", "Sum"), #ewr_code to env_obj              
              c('ArithmeticMean', "NumberOfValues", "Sum"), #planning_unit to sdl_units              
              c('ArithmeticMean', "NumberOfValues", "Sum")) #env_obj  to Target

system.time(agged_data_Theme <- read_and_agg(datpath = ewr_results, 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           # group_until = list(planning_unit_name = 'sdl_units', 
           #                      gauge = is_notpoint),
           #              pseudo_spatial = 'planning_units',
           auto_ewr_PU = TRUE,
           aggsequence = Theme_aggseq,
           funsequence = Theme_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(agg_results, 'sdl_target_agg')))
```

40 seconds

```         
#GD: user  system elapsed   128.84   12.03  264.08 
```
