---
title: "Comparer"
format: html
editor: visual
execute: 
  cache: true
---

```{r}
#| include: false
#| 

library(HydroBOT)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)

# get directories
source('directorySet.R')
```

## Paths

I'm going to set this up to dump data to the QAEL WERP share for now. Unfortunately, that calls itself something different for each of us.

```{r}
#| include: false
qaelpath <- myhome
#qaelpath <- path.expand(qaelpath)
datDir <- file.path(qaelpath, "Deakin University/QAEL - MER/Model/dataBase")
datOut <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out")
project_dir <- file.path(datOut, 'werpstyle')
hydro_dir <- file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR_numeric_gauges')
ewr_results <- file.path(project_dir, 'MANUAL')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output_numeric_gauges')

comp_results <- file.path(project_dir, 'comparer_output') 

data_path <- file.path(qaelpath, "Deakin University/QAEL - SRA - SRA/data_out/SRA_analysis/Final_datasets")
```

## Read in agged data

```{r}

#list.files(agg_results)
# sdl_EWRS_agg <- readRDS(file.path(agg_results, "sdl_EWRS_agg", 'achievement_aggregated.rds'))
# #sdl_specific_goal_agg <- readRDS(file.path(agg_results, "sdl_specific_goal_agg", 'achievement_aggregated.rds'))
# #sdl_specific_goal_objective_agg <- readRDS(file.path(agg_results, "sdl_specific_goal_objective_agg", 'achievement_aggregated.rds'))
# sdl_target_agg <- readRDS(file.path(agg_results, "sdl_target_agg", 'achievement_aggregated.rds'))
# # simple_agg <- readRDS(file.path(agg_results, "Simple_agg", 'achievement_aggregated.rds'))


Tagg_gauge_EWRversions <- read.csv(file.path(project_dir, 'MANUAL', 'EWR_summary.csv'))
Timeseries_gauge_EWRversions <- read.csv(file.path(project_dir, 'MANUAL', 'EWR_timeseries.csv'))

#filter EWRs == NA
Tagg_gauge_EWRversions <- filter(Tagg_gauge_EWRversions, !is.na(ewr_achieved))
Timeseries_gauge_EWRversions <- filter(Timeseries_gauge_EWRversions, !is.na(ewr_achieved))

#Clean ewr_code
Tagg_gauge_EWRversions$ewr_code <- sub("-", "_", Tagg_gauge_EWRversions$ewr_code)
Timeseries_gauge_EWRversions$ewr_code <- sub("-", "_", Timeseries_gauge_EWRversions$ewr_code)

#SWITCH CFs
Tagg_gauge_EWRversions <- Tagg_gauge_EWRversions |>
  mutate(ewr_achieved = case_when(ewr_code == "ALT" ~ 1-ewr_achieved,
                                  ewr_code == "CF" ~ 1-ewr_achieved,
                                  ewr_code == "CF1" ~ 1-ewr_achieved,
                                  ewr_code == "CF1_c_P" ~ 1-ewr_achieved,
                                  ewr_code == "CF1_c_S" ~ 1-ewr_achieved,
                                  .default = ewr_achieved))

Timeseries_gauge_EWRversions <- Timeseries_gauge_EWRversions |>
  mutate(ewr_achieved = case_when(ewr_code == "ALT" ~ 1-ewr_achieved,
                                  ewr_code == "CF" ~ 1-ewr_achieved,
                                  ewr_code == "CF1" ~ 1-ewr_achieved,
                                  ewr_code == "CF1_c_P" ~ 1-ewr_achieved,
                                  ewr_code == "CF1_c_S" ~ 1-ewr_achieved,
                                  .default = ewr_achieved))
```

## For joining space data and climate categories

```{r}
#Gauge points:
gauges_df <- get_ewr_gauges()|>
  #st_drop_geometry() |>
  mutate(OWNER = case_when(owner == "NSW - NSW Department of Industry – Lands and Water" ~ "NSW",
                           owner == "VIC - Department of Environment, Land, Water and Planning"~ "VIC",
                           owner == "SA - Department of Environment, Water and Natural Resources"~ "SA",
                           owner == "QLD - Department of Natural Resources, Mines and Energy"~ "QLD",
                           owner == NA ~ NA))

gauges_df_sld <- st_join(gauges_df, sdl_units)

#Climate categorgy data:
Climate_Categories <- read.csv(file.path(qaelpath, "Deakin University", "QAEL - SRA - SRA", "Climate_Categories_Coloured_2023.csv"), check.names = FALSE)

Climate_Categories <- Climate_Categories |>
  pivot_longer(cols = `Barwon-Darling`:`Total MDB`, names_to = "Climate_category.data", values_to = "Climate_Category")

Climate_Categories <- Climate_Categories |>
  mutate(Climate_Category = factor(Climate_Category, levels = c("Very Dry", "Dry", "Moderate", "Wet", "Very Wet")))

# read in the mapping of sdls to the climate category areas:
Climate_Category_to_polygons <- read.csv(file.path(qaelpath, "Deakin University", "QAEL - SRA - SRA", "Climate_Category_to_polygons.csv"))|>
  dplyr::select(Climate_category.data, SWSDLName)|>
  
  #Climate_Categories_sdl does not have categorys for SA, so should use 'Eastern Mt Lofty Ranges' for SA
  dplyr::mutate(Climate_category_area = case_when(SWSDLName == "South Australian Murray" ~ "Lower Murray",
                                                  SWSDLName == "Eastern Mount Lofty Ranges" ~ "Lower Murray",
                                           SWSDLName == "South Australian Non-Prescribed Areas" ~ "Lower Murray",
                                           SWSDLName == "Marne Saunders" ~ "Lower Murray",
                                           .default = Climate_category.data))|>
  filter(Climate_category_area != "")|>
  filter(SWSDLName != "")|>
  mutate(SWSDLName = case_when(SWSDLName == "Barwon-Darling Watercourse" ~ "Barwon–Darling Watercourse",
                               SWSDLName == "Barwon Darling Watercourse" ~ "Barwon–Darling Watercourse",
                               SWSDLName == "Macquarie-Castlereagh" ~ "Macquarie–Castlereagh",
                               SWSDLName == "Macquarie Castlereagh" ~ "Macquarie–Castlereagh",
                               SWSDLName == "Wimmera Mallee (Surface Water)" ~ "Wimmera–Mallee (Surface Water)",
                               SWSDLName == "Wimmera–Mallee (Surface Water)" ~ "Wimmera–Mallee (Surface Water)",
                               SWSDLName == "Condamine-Balonne" ~ "Condamine–Balonne",
                               SWSDLName == "Condamine Balonne" ~ "Condamine–Balonne",
                               .default = SWSDLName))

# Join polygon data	
Climate_Category_to_polygon_geometry <- left_join(Climate_Category_to_polygons, sdl_units, by = join_by(SWSDLName))
  #Climate_Categories_sdl does not have categorys for SA, so should use 'Eastern Mt Lofty Ranges' for SA

                                                    
# meld polygons
Climate_Category_geometry <- Climate_Category_to_polygon_geometry|>
  group_by(Climate_category_area) |>
  mutate(geometry = st_union(geometry),
         SWSDLName_all = paste(unique(SWSDLName), collapse = ";"),
         Climate_category.data = paste(unique(Climate_category.data), collapse = ""))

# join polygons to climate category data:
Climate_Categories_sdl <- left_join(Climate_Categories, Climate_Category_geometry, by = join_by(Climate_category.data)) |>
  rename(year = `Start of water Year`)

Climate_Categories_sdl



```

## For joining EWR groups and connectivity groups

```{r}
EWR_table <- get_ewr_table()
EWR_table <- left_join(EWR_table, gauges_df_sld, by = c("Gauge" = "gauge"))
EWR_table$ewr_code <- sub("_[^_]+$", "", EWR_table$Code)


EWRS_df <- Tagg_gauge_EWRversions |>
  distinct(ewr_code) |>
  mutate(ewr_group_temp1 = substr(ewr_code, start = 1, stop = 2)) |>
  mutate(ewr_group_temp2 = substr(ewr_code, start = 1, stop = 1)) |> #DODGY BUT WILL DO FOR NOW
  mutate(ewr_group = case_when(ewr_group_temp2 == "F" ~ ewr_group_temp2, 
                               ewr_group_temp1 == "W-" ~ "LF",
                               .default = ewr_group_temp1)) |>
  mutate(ewr_group = ifelse(is.na(ewr_group), ewr_group_temp1, ewr_group)) |>
  select(-ewr_group_temp1, -ewr_group_temp2)

List_EWRs <- read.csv(file.path(project_dir, "List_EWRs.csv"))

List_EWRs$ewr_code <- sub("-", "_", List_EWRs$ewr_code)
EWRS_df$ewr_code <- sub("-", "_", EWRS_df$ewr_code)


EWRS_df <- left_join(EWRS_df, List_EWRs, by = "ewr_code")


```

```{r}
#WORKING OUT WHICH EWRS are related to lateral connectivity and longitudinal connectivity
# EWR_table_def <- EWR_table |>
#   distinct(ewr_code)
# write.csv(EWR_table_def, file.path(project_dir, "List_EWRs_dontdelete.csv"))

unique(EWR_table$StateID)

Plot_EWRS_QLD_data <-  EWR_table |>
  #filter(StateID == "QLD")|>
  filter(ewr_code %in% c("IC1"))
VIC_gauges <- Plot_EWRS_QLD_data$Gauge         
         #, 'SF1_P', 'SF1_S', 'SF2','BK1_ds', 'BK2_ds', 'BK1_us', 'BK2_us','BK1', 'BK2_P', 'BK2_S',
          #           'dANA', 'NE', 'PP', 'rANA', 'DR1', 'DR2', 'FD1', 'FD2', 'FrC', 'FR1', 'LDF', 'WFT'))
#'CF_a', 'CF_b', 'CF_c', 'VF_a', 'VF_b', 'BF1_a', 'BF1_b', 'BF2_a', 'BF2_b', 'SF1_P', 'SF1_S', 'SF2', 'LF1_P', 'LF1_S', #'LF2', 'BK1_ds', 'BK2_ds', 'BK1_us', 'BK2_us', 'OB1', 'OB2_P', 'OB2_S', 'OB2_WHA_P', 'OB2_WHA_S', 'OB3', 'LF3', 'BK1', #'BK2_P', 'BK2_S', 'OB1_P', 'OB1_S', 'dANA', 'NE', 'PP', 'rANA', 'DR1', 'DR2', 'FD1', 'FD2', 'FrC', 'FR1', 'LDF', 'WFT'

temp <- filter(EWR_table, Gauge %in% VIC_gauges)

ggplot(data = filter(EWR_table, Gauge %in% VIC_gauges), 
       aes(x = Code, y = as.numeric(LevelThresholdMin), fill = Code, colour = Code))+
    geom_hline(data = Plot_EWRS_QLD_data, 
             aes(yintercept = as.numeric(LevelThresholdMin)))+#, colour = "black")+
  geom_point()+#, colour = "black")+
  geom_line()+#, colour = "black")+
  facet_grid(Gauge~., scales = "free_y")+
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = filter(EWR_table, Gauge %in% VIC_gauges), 
       aes(x = Code, y = as.numeric(FlowThresholdMin), fill = Code, colour = Code))+
    geom_hline(data = Plot_EWRS_QLD_data, 
             aes(yintercept = as.numeric(FlowThresholdMin)))+#, colour = "black")+
  geom_point()+#, colour = "black")+
  geom_line()+#, colour = "black")+
  facet_grid(Gauge~., scales = "free_y")+
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90))

ggplot(data = filter(EWR_table, Gauge %in% VIC_gauges), 
       aes(x = Code, y = as.numeric(FlowThresholdMax), fill = Code, colour = Code))+
    geom_hline(data = Plot_EWRS_QLD_data, 
             aes(yintercept = as.numeric(FlowThresholdMax)))+#, colour = "black")+
  geom_point()+#, colour = "black")+
  geom_line()+#, colour = "black")+
  facet_grid(Gauge~., scales = "free_y")+
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90))

EWR_table |>  
  filter(Gauge %in% VIC_gauges)|>
  select(ewr_code, FlowThresholdMin, FlowThresholdMax, LTWPShortName, StateID)


```

## SRA: prep - MANUAL

```{r}
#TIME AGGREGATED (Tagg):
## agregate to EWR codes
Tagg_gauge_EWR <- Tagg_gauge_EWRversions |>
  dplyr::group_by(dplyr::across(c(-ewr_achieved, -ewr_code_timing)))|>
  left_join(EWRS_df)|>
  left_join(gauges_df_sld, by = "gauge")

## agregate to EWR groups
Tagg_gauge_EWRgroups <- Tagg_gauge_EWR |>
  dplyr::group_by(dplyr::across(c(-ewr_achieved, -ewr_code)))|>
  dplyr::summarise(ewr_achieved = mean(ewr_achieved, na.rm = TRUE))

```

```{r}
#TIMESERIES - Individual EWRS
# GAUGE level

## agregate to EWR codes
Timeseries_gauge_EWR <- Timeseries_gauge_EWRversions |>
  #dplyr::group_by(dplyr::across(c(-ewr_achieved, -ewr_code_timing)))|> #didnt work - other variables relating to code_timing
   dplyr::group_by(year, ewr_code, scenario, gauge, planning_unit_name) |>
  dplyr::summarise(ewr_achieved = max(ewr_achieved, na.rm = TRUE)) |> #USING MAX
  left_join(EWRS_df, by = "ewr_code")

Timeseries_gauge_EWR <- left_join(Timeseries_gauge_EWR, gauges_df_sld, by = "gauge")

#gauge_EWRS_timeseries <- st_join(gauge_EWRS_timeseries, Climate_Categories)

#individual EWRs
Timeseries_gauge_EWR <- Timeseries_gauge_EWR |>
  ungroup() |>
  st_drop_geometry() |>
  select(-geometry, -planning_unit_name, -planningunitname, -ltwpshortname, -gaugetype, -site, -owner, -OWNER) 

#add polygons; 
Timeseries_gauge_EWR <- Timeseries_gauge_EWR |>
  left_join(Climate_Category_geometry, by = join_by(SWSDLID, SWSDLName, StateID))

#Then add climate categories (works better than doing both together):
Timeseries_gauge_EWR <- Timeseries_gauge_EWR |>
  left_join(Climate_Categories_sdl, by = join_by(year, SWSDLID, SWSDLName, StateID, Climate_category.data, Climate_category_area, geometry, SWSDLName_all))




```

```{r}
#TIMESERIES - GROUPED EWRS
##GAUGE level -  agregate to EWR groups
Timeseries_gauge_EWRgroup <- Timeseries_gauge_EWR |>
  dplyr::group_by(dplyr::across(c(-ewr_achieved, -ewr_code)))|>
  dplyr::summarise(ewr_achieved = mean(ewr_achieved, na.rm = TRUE))
```

```{r}
#TIMESERIES - GROUPED EWRS BY LONG and LATERAL cONNECTIVITY
#(does lat or long connectivity happen at any gauge?)
##GAUGE level -  agregate to EWR groups
Timeseries_gauge_LATERALgroup <- Timeseries_gauge_EWR |>
  dplyr::filter(Lateral_connectivity_including_SF == "Y")|>
  dplyr::select(-Lateral_connectivity_including_SF, -Lateral_connectivity_above_BK, -Lateral_connectivity_including_BK, -Longitudinal_connectivity_CF,
          -Longitudinal_connectivity_FD, -Notes, -Check, -LTWP)|>
  dplyr::group_by(dplyr::across(c(-ewr_achieved, - ewr_code, -ewr_group)))|>
  dplyr::summarise(ewr_achieved = max(ewr_achieved, na.rm = TRUE))

##GAUGE level -  agregate to EWR groups
Timeseries_gauge_LONGITUDINALgroup <- Timeseries_gauge_EWR |>
  dplyr::filter(Longitudinal_connectivity_CF == "Y" | Longitudinal_connectivity_FD == "Y") |>
  dplyr::select(-Longitudinal_connectivity_CF, -Longitudinal_connectivity_FD, -Lateral_connectivity_above_BK, -Lateral_connectivity_including_BK, -Lateral_connectivity_including_SF,
          -Notes, -Check, -LTWP)|>
  dplyr::group_by(dplyr::across(c(-ewr_achieved, - ewr_code, -ewr_group)))|>
  dplyr::summarise(ewr_achieved = max(ewr_achieved, na.rm = TRUE))


# Climate_category_area level
Timeseries_ClimateCategoryArea_LATERALgroup <- Timeseries_gauge_LATERALgroup |> 
  ungroup() |>
  dplyr::select(-gauge, -SWSDLID, -SWSDLName, -StateID, -Climate_category.data)|>
  dplyr::group_by(dplyr::across(c(-ewr_achieved)))|>
  dplyr::reframe(ewr_achieved = mean(ewr_achieved, na.rm = TRUE),
                 n_gauges = n())

# Climate_category_area level
Timeseries_ClimateCategoryArea_LONGITUDINALgroup <- Timeseries_gauge_LONGITUDINALgroup |> 
  ungroup() |>
  dplyr::select(-gauge, -SWSDLID, -SWSDLName, -StateID, -Climate_category.data)|>
  dplyr::group_by(dplyr::across(c(-ewr_achieved)))|>
  dplyr::reframe(ewr_achieved = mean(ewr_achieved, na.rm = TRUE),
                 n_gauges = n())

# basin level
Timeseries_Basin_LATERALgroup <- Timeseries_ClimateCategoryArea_LATERALgroup |> 
  ungroup() |>
  dplyr::select(-Climate_Category, -geometry, -SWSDLName_all, -Climate_category_area)|>
  dplyr::group_by(year)|>
  dplyr::reframe(ewr_achieved = mean(ewr_achieved, na.rm = TRUE),
                 n_gauges = sum(n_gauges),
                 n_climate_category_areas = n())|>
  dplyr::mutate(Climate_category.data = "Total MDB") |>
  left_join(Climate_Categories, by = c("Climate_category.data", "year" = "Start of water Year"))

# basin level
Timeseries_Basin_LONGITUDINALgroup <- Timeseries_ClimateCategoryArea_LONGITUDINALgroup |> 
  ungroup() |>
  dplyr::select(-Climate_Category, -geometry, -SWSDLName_all, -Climate_category_area)|>
  dplyr::group_by(year)|>
  dplyr::reframe(ewr_achieved = mean(ewr_achieved, na.rm = TRUE),
                 n_gauges = sum(n_gauges),
                 n_climate_category_areas = n())|>
  dplyr::mutate(Climate_category.data = "Total MDB") |>
  left_join(Climate_Categories, by = c("Climate_category.data", "year" = "Start of water Year"))

saveRDS(Timeseries_ClimateCategoryArea_LATERALgroup, file.path(data_path, "Timeseries_Valley_LATERALconnectivity.rds"))
saveRDS(Timeseries_ClimateCategoryArea_LONGITUDINALgroup, file.path(data_path, "Timeseries_Valley_LONGITUDINALconnectivity.rds"))

saveRDS(Timeseries_Basin_LATERALgroup, file.path(data_path, "Timeseries_Basin_LATERALconnectivity.rds"))
saveRDS(Timeseries_Basin_LONGITUDINALgroup, file.path(data_path, "Timeseries_Basin_LONGITUDINALconnectivity.rds"))
```

```{r}
# Time aggregation
Tagg_gauge_LATERALgroup <- Timeseries_gauge_LATERALgroup|>
  group_by(gauge)|>
  reframe(ewr_achieved_weighted = weighted.mean(ewr_achieved, year),
          ewr_achieved_unweighted = weighted.mean(ewr_achieved))|>
  left_join(gauges_df_sld, by = "gauge")

Tagg_gauge_ClimateCategories_LATERALgroup <- Timeseries_gauge_LATERALgroup|>
  group_by(gauge, Climate_Category)|>
  reframe(ewr_achieved_weighted = weighted.mean(ewr_achieved, year),
          ewr_achieved_unweighted = weighted.mean(ewr_achieved))|>
  left_join(gauges_df_sld, by = "gauge")

Tagg_ClimateCategoryArea_LATERALgroup <- Timeseries_ClimateCategoryArea_LATERALgroup |>
  group_by(Climate_category_area, geometry)|>
  reframe(ewr_achieved_weighted = weighted.mean(ewr_achieved, year),
          ewr_achieved_unweighted = weighted.mean(ewr_achieved))

Tagg_ClimateCategoryArea_ClimateCategories_LATERALgroup <- Timeseries_ClimateCategoryArea_LATERALgroup |>
  group_by(Climate_category_area, Climate_Category, geometry)|>
  reframe(ewr_achieved_weighted = weighted.mean(ewr_achieved, year),
          ewr_achieved_unweighted = weighted.mean(ewr_achieved))
  
Tagg_Basin_LATERALgroup <- Timeseries_Basin_LATERALgroup |>
  group_by(Climate_category.data)|>
  reframe(ewr_achieved_weighted = weighted.mean(ewr_achieved, year),
          ewr_achieved_unweighted = weighted.mean(ewr_achieved))
Tagg_Basin_LATERALgroup <- bind_cols(Tagg_Basin_LATERALgroup, basin)

Tagg_Basin_ClimateCategories_LATERALgroup <- Timeseries_Basin_LATERALgroup |>
  group_by(Climate_category.data, Climate_Category)|>
  reframe(ewr_achieved_weighted = weighted.mean(ewr_achieved, year),
          ewr_achieved_unweighted = weighted.mean(ewr_achieved))
Tagg_Basin_ClimateCategories_LATERALgroup <- bind_cols(Tagg_Basin_ClimateCategories_LATERALgroup, basin)



```

```{r}
#individual EWR
# Climate_category_area level
Timeseries_ClimateCategoryArea_EWR <- Timeseries_gauge_EWR |> 
  ungroup() |>
  dplyr::select(-gauge, -SWSDLID, -SWSDLName, -StateID, -Climate_category.data)|>
  dplyr::group_by(dplyr::across(c(-ewr_achieved)))|>
  dplyr::reframe(ewr_achieved = mean(ewr_achieved, na.rm = TRUE))

#EWR GROUP
# SWSDLName level
Timeseries_ClimateCategoryArea_EWRgroup <- Timeseries_ClimateCategoryArea_EWR |>
  dplyr::group_by(dplyr::across(c(-ewr_achieved, -ewr_code)))|>
  dplyr::summarise(ewr_achieved = mean(ewr_achieved, na.rm = TRUE))
```

```{r}
#Aggregating time
Tagg_ClimateCategoryArea_EWRgroup <- Timeseries_ClimateCategoryArea_EWRgroup |> 
  ungroup() |>
  dplyr::group_by(dplyr::across(c( -ewr_achieved, -year)))|>
  dplyr::reframe(ewr_achieved = mean(ewr_achieved, na.rm = TRUE),
                 n_years = n())
```

## Scenario subsets

```{r}
#| label: data-subsets
#| include: false

gauges_to_plot <- unique(Tagg_gauge_EWR$gauge)
#planning_units_to_plot <- unique(planning_unit_EWRS$PlanningUnitName)
#SWSDL_units_to_plot <- unique(sdl_EWRS$SWSDLName)

gauges_x_4 <- c("421001","418037","409017","419039","403230","407249","414203","409207","A4260505","A4260507","A4260509", "416201A")

```

## Palettes

#maybe make palette based on end of sys flow???

```{r}
#| label: palettes
#| include: false

# I'm adding these from Georgia as needed
# Trying to organise by the sort of palette we need for each

# Qualitative
pal_gauge <- stats::setNames(colorRampPalette(paletteer::paletteer_d('ggsci::nrc_npg'))(length(gauges_to_plot)), gauges_to_plot)
class(pal_gauge) <- 'colors'

#pal_planning_units <-  stats::setNames(colorRampPalette(paletteer::paletteer_d('impressionist.colors::la_recolte_des_foins_eragny'))(length(planning_units_to_plot)), planning_units_to_plot)
#class(pal_planning_units) <- 'colors'
  
# pal_SDL <-  stats::setNames(colorRampPalette(paletteer::paletteer_d('impressionist.colors::la_recolte_des_foins_eragny'))(length(SWSDL_units_to_plot)), SWSDL_units_to_plot)
# class(pal_SDL) <- 'colors'

# these have to use quantitative even though they're not, or we run out of colors.
pal_env = list(EB = 'grDevices::Grays',
                EF = 'grDevices::Purp',
                NF = 'grDevices::Mint',
                NV = 'grDevices::Burg',
                OS = 'grDevices::Blues 2',
                WB = 'grDevices::Peach')

# use the first level of each of those to make a named pal. I wish there were an easier way
pal_envgroup <- purrr::imap_chr(pal_env,
                                \(x,y) make_pal(levels = y, palette = x)) |> 
  HydroBOT:::as_colors()

# Quantitative- sequential achievement
pal_achieve <- 'grDevices::Blue-Yellow'

# quantitative- diverging achievement (e.g. relative to baseline)
pal_compare <- 'scico::bam'

# pal_scene <- make_pal(unique(scenarios$scenario),                       
#                       palette = "viridis::mako", #'ggsci::nrc_npg', 
#                       refvals = 'base', refcols = 'black')

pal_climate <-  stats::setNames(c("#ED2024", "#FAA41A", "#F6EB14", "#87CDE9", "#282A73"), levels(Climate_Categories$Climate_Category))
class(pal_climate) <- 'colors'


pal_year <-  stats::setNames(colorRampPalette(paletteer::paletteer_d('impressionist.colors::la_recolte_des_foins_eragny'))(length(unique(Climate_Categories$`Start of water Year`))), unique(Climate_Categories$`Start of water Year`))
class(pal_year) <- 'colors'
```

## Hydrographs

```{r}
#| label: fig-ewr-example
#| fig-cap: !expr glue::glue("EWR are illustrated at two example gauges ({paste0(gauges_to_plot, collapse = ' and ')}) on the historical base level (scenario E1) hydrographs. See @sec-ewr-table for a table.")

#Hydrographs- just read in the ones we use
scenehydros <- read_hydro(hydro_dir,
                          # scenariofilter = "historical_scale_rain_1_2_evap_1_0_licvolfactor_1_5_0",
                          long = TRUE, format = 'nc') 

#Scenario names have change - this is a work around. hopefully in future the metadata, hydrographs, and EWR outputs match.
scenehydros$scenario <- stringr::str_match(scenehydros$scenario, '(.*)_(.*)')[, -1][,1]

scenehydros <- left_join(scenehydros, scenarios, by = 'scenario')

# # This relies on the NSW ewr definitions. We could keep passing them around, but better to pull from py-ewr directly
pdi <- reticulate::import("py_ewr.data_inputs")

# The second is 'bad', so just get the first
ewrs_in_pyewr <- pdi$get_EWR_table()[[1]]

NSWEWR_gauge <- filter(ewrs_in_pyewr, Gauge %in% gauges_to_plot) |>
  tidyr::separate_wider_delim(cols = Code, delim = '_',
                              names = c("Code", "Timing"),
                              too_few = 'align_start',
                              too_many = 'merge') |>
  rename(gauge = Gauge) |>
  group_by(gauge) %>%
  distinct(Code, .keep_all = TRUE) |>
  mutate(FlowThresholdMin = as.numeric(FlowThresholdMin)) |>
  arrange(FlowThresholdMin) %>%
  mutate(Date = seq(from = max(scenehydros$Date),
                    to = min(scenehydros$Date),
                    length.out = n())) %>%
  ungroup()

```

## bar plots - climate-comparison

```{r}
#| label: fig-sdl-comparison

# Scenario comparison for different Sustainable Diversion Limit areas. This example shows the mean proportion of environmental watering requirements (EWRs) that are achieved under each scenario for each SDL unit. This approach illuminates broad-brush differences between scenarios and geographic locations, but does not address which EWRs may be more important to environmental assets or which assets are more sensitive to particular scenarios. Climate scenarios and adaptation options as in @tbl-scenarios. Panels a and b illustrate the same data with a emphasizing quantititive differences and b emphasizing spatial patterns.

#| message: false

# The bars
sdl_achieve_bars_climate_nonrounding <- sdl_units_nonrounding |> 
  filter(scenario != "MAX") |> 
  mutate(scenario = paste0(licvolfactor)) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = 'Proportion\nEWR achieved',
                x_col = 'scenario',
                x_lab = 'Adaptation option scenario (Change in Licence volume)',
                colorset = 'names_climate_scenario',
                color_lab = 'Climate scenario:',
                pal_list = pal_climate_scenario  |> setNames(stringr::str_replace(names(pal_climate_scenario ), '–', '-\n')),
                position = 'dodge',
                setLimits = c(0,1)) +
  # guides(fill = guide_legend(nrow=2, label.position = 'top')) +
  theme(legend.position = 'bottom')



#MANUAL_sdl_achieve_bars_climate_nonrounding + 

sdl_achieve_bars_climate_nonrounding 

ggsave(plot = sdl_achieve_bars_climate_nonrounding, filename = file.path(comp_results, "sdl_achieve_bars_climate_nonrounding.tiff"), device = "tiff",
       width = 7, height = 6)
```

## SRA: tile plots - individual EWRs per gauge

```{r}

Plot_EWRs_per_gauge1 <- ggplot(data = Tagg_gauge_EWR, 
       aes(x = ewr_code, y = gauge))+
  geom_tile(aes(fill = ewr_achieved), colour = "black")+
  #geom_text(aes(label = n))+
  facet_grid(OWNER~., scales = "free", space = "free")+
  paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  theme_werp_toolkit()+
  labs(x = "EWR", y = "Gauge", fill = "Proportion \nEWR achieved")+
  theme(axis.text.x = element_text(angle = 90))

ggsave(plot = Plot_EWRs_per_gauge1, filename = file.path(comp_results, paste0("EWRs_per_gauge_STATE", Sys.Date(), ".tiff")), device = "tiff",
       width = 10, height = 10)

Plot_EWRs_per_gauge1


```

## SRA: tile plots - EWR groups per gauge

```{r}
Plot_EWRgroups_per_gauge <- ggplot(data = gauge_EWR_groups, 
       aes(x = ewr_group, y = gauge))+
  geom_tile(aes(fill = ewr_achieved), colour = "black")+
  #geom_text(aes(label = n))+
  facet_grid(OWNER~., scales = "free", space = "free")+
  paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  theme_werp_toolkit()+
  labs(x = "EWR", y = "Gauge", fill = "Proportion \nEWR achieved")+
  theme(axis.text.x = element_text(angle = 90))

ggsave(plot = Plot_EWRgroups_per_gauge, filename = file.path(comp_results, paste0("EWRgroups_per_gauge_STATE", Sys.Date(), ".tiff")), device = "tiff",
       width = 10, height = 10)

Plot_EWRgroups_per_gauge
```

## SRA: Time series - LATERAL connectivity

```{r}

Plot_LATERALgroups_per_gauge_timeseries <- ggplot(data = Timeseries_gauge_LATERALgroup, 
       aes(x = year, y = ewr_achieved, colour = Climate_Category))+
  geom_point()+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area)+
  #paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  theme_werp_toolkit()+
  labs(x = "Year", fill = "Gauge", y = "Lateral connectivity \nEWR achieved")+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylim(0,1)+ xlim(1900,NA)

Plot_LATERALgroups_per_gauge_timeseries

ggsave(plot = Plot_LATERALgroups_per_gauge_timeseries, filename = file.path(comp_results, paste0("Plot_Timeseries1900_gauge_LATERAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 10, height = 10)

Plot_LATERALgroups_per_gauge_timeseries <- ggplot(data = Timeseries_gauge_LATERALgroup, 
       aes(x = year, y = ewr_achieved, colour = Climate_Category))+
  geom_point()+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area)+
  #paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  theme_werp_toolkit()+
  labs(x = "Year", fill = "Gauge", y = "Lateral connectivity \nEWR achieved")+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylim(0,1)+ xlim(1983,NA)

Plot_LATERALgroups_per_gauge_timeseries

ggsave(plot = Plot_LATERALgroups_per_gauge_timeseries, filename = file.path(comp_results, paste0("Plot_Timeseries1983_gauge_LATERAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 10, height = 10)

```

## SRA: Time series - LONGITUDINAL connectivity

```{r}

Plot_LONGITUDINALgroups_per_gauge_timeseries <- ggplot(data = Timeseries_gauge_LONGITUDINALgroup, 
       aes(x = year, y = ewr_achieved, colour = Climate_Category))+
  geom_point()+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area)+
  #paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  theme_werp_toolkit()+
  labs(x = "Year", fill = "Gauge", y = "Longitudinal connectivity \nEWR achieved")+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylim(0,1)+ xlim(1900,NA)

Plot_LONGITUDINALgroups_per_gauge_timeseries

ggsave(plot = Plot_LONGITUDINALgroups_per_gauge_timeseries, filename = file.path(comp_results, paste0("Plot_Timeseries1900_gauge_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 10, height = 10)

Plot_LONGITUDINALgroups_per_gauge_timeseries <- ggplot(data = Timeseries_gauge_LONGITUDINALgroup, 
       aes(x = year, y = ewr_achieved, colour = Climate_Category))+
  geom_point()+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area)+
  #paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  theme_werp_toolkit()+
  labs(x = "Year", fill = "Gauge", y = "Longitudinal connectivity \nEWR achieved")+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylim(0,1)+ xlim(1983,NA)

Plot_LONGITUDINALgroups_per_gauge_timeseries

ggsave(plot = Plot_LONGITUDINALgroups_per_gauge_timeseries, filename = file.path(comp_results, paste0("Plot_Timeseries1983_gauge_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 10, height = 10)
```

## SRA: Time series - LATERAL connectivity

```{r}

Plot_Timeseries_ClimateCategoryArea_LATERAL <- ggplot(data = Timeseries_ClimateCategoryArea_LATERALgroup, 
       aes(x = year, y = ewr_achieved))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  geom_smooth()+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Proportion of gauges \nwith lateral connectivity EWR occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ xlim(1900,NA)

Plot_Timeseries_ClimateCategoryArea_LATERAL

ggsave(plot = Plot_Timeseries_ClimateCategoryArea_LATERAL, filename = file.path(comp_results, paste0("Plot_Timeseries1900_ClimateCategoryArea_LATERAL_trend", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)

Plot_Timeseries_ClimateCategoryArea_LATERAL <- ggplot(data = Timeseries_ClimateCategoryArea_LATERALgroup, 
       aes(x = year, y = ewr_achieved))+
  #geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Proportion of gauges \nwith lateral connectivity EWR occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ xlim(1983,NA)

Plot_Timeseries_ClimateCategoryArea_LATERAL

ggsave(plot = Plot_Timeseries_ClimateCategoryArea_LATERAL, filename = file.path(comp_results, paste0("Plot_Timeseries1983_ClimateCategoryArea_LATERAL_trend", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Time series - LONGITUDINAL connectivity

```{r}


Plot_Timeseries_ClimateCategoryArea_LONGITUDINAL <- ggplot(data = Timeseries_ClimateCategoryArea_LONGITUDINALgroup, 
       aes(x = year, y = ewr_achieved))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
    geom_smooth(colour = "grey20", linewidth = 0.5)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Proportion of gauges \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ xlim(1900,NA)

Plot_Timeseries_ClimateCategoryArea_LONGITUDINAL

ggsave(plot = Plot_Timeseries_ClimateCategoryArea_LONGITUDINAL, filename = file.path(comp_results, paste0("Plot_Timeseries1900_ClimateCategoryArea_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)


Plot_Timeseries_ClimateCategoryArea_LONGITUDINAL <- ggplot(data = Timeseries_ClimateCategoryArea_LONGITUDINALgroup, 
       aes(x = year, y = ewr_achieved))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Proportion of gauges \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ xlim(1983,NA)

Plot_Timeseries_ClimateCategoryArea_LONGITUDINAL

ggsave(plot = Plot_Timeseries_ClimateCategoryArea_LONGITUDINAL, filename = file.path(comp_results, paste0("Plot_Timeseries1983_ClimateCategoryArea_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Time series - BASIN - LATERAL connectivity

```{r}
Plot_Timeseries_Basin_LATERAL <- ggplot(data = Timeseries_Basin_LATERALgroup, 
       aes(x = year, y = ewr_achieved))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  
        geom_smooth(
    data = filter(Timeseries_Basin_LATERALgroup, year >= 2012), 
       aes(x = year, y = ewr_achieved, linetype = Climate_Category), method = "lm",
    colour = "red", linewidth = 0.5)+
  
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Proportion of gauges with\n lateral connectivity\n EWR achieved")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)+ xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL

ggsave(plot = Plot_Timeseries_Basin_LATERAL, filename = file.path(comp_results, paste0("Plot_Timeseries_Basin_LATERAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Time series - BASIN - LONGITUDINAL connectivity

```{r}
Plot_Timeseries_Basin_LONGITUDINAL <- ggplot(data = Timeseries_Basin_LONGITUDINALgroup, 
       aes(x = year, y = ewr_achieved))+
  #geom_line(colour = "grey80")+

  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
    geom_smooth(colour = "grey20", linewidth = 0.5)+
    #geom_smooth(aes(colour = Climate_Category), linewidth = 0.5, se = F)+
  
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+  
      geom_smooth(
    data = filter(Timeseries_Basin_LONGITUDINALgroup, year >= 2012), 
       aes(x = year, y = ewr_achieved), method = "lm",
    colour = "red", linewidth = 0.5)+
  
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Proportion of gauges with\n longitudinal connectivity\n EWR achieved")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1) + 
  xlim(1900,NA)

Plot_Timeseries_Basin_LONGITUDINAL

ggsave(plot = Plot_Timeseries_Basin_LONGITUDINAL, filename = file.path(comp_results, paste0("Plot_Timeseries_Basin_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## IS SCALING

```{r}
Timeseries_Basin_LATERALgroup_SCALED <- Timeseries_Basin_LATERALgroup |>
  ungroup()|>
  mutate(ewr_achieved_TotalScaled  = (ewr_achieved-0)/(1-0),
         ewr_achieved_ObsScaled    = (ewr_achieved-min(ewr_achieved))/(max(ewr_achieved)-min(ewr_achieved))
         ) |>
  group_by(Climate_Category)|>
  mutate(ewr_achieved_YrTypeScaled = (ewr_achieved-min(ewr_achieved))/(max(ewr_achieved)-min(ewr_achieved)),
         ) |>
  mutate(ewr_achieved_IS = (ewr_achieved_TotalScaled*0.3)+(ewr_achieved_ObsScaled*0.4)+(ewr_achieved_YrTypeScaled*0.3))
         
Timeseries_Basin_LONGITUDINALgroup_SCALED <- Timeseries_Basin_LONGITUDINALgroup |>
ungroup()|>
    mutate(ewr_achieved_TotalScaled = (ewr_achieved-0)/(1-0),
         ewr_achieved_ObsScaled = (ewr_achieved-min(ewr_achieved))/(max(ewr_achieved)-min(ewr_achieved))
         ) |>
  group_by(Climate_Category)|>
  mutate(ewr_achieved_YrTypeScaled = (ewr_achieved-min(ewr_achieved))/(max(ewr_achieved)-min(ewr_achieved)),
         ) |>
  mutate(ewr_achieved_IS = (ewr_achieved_TotalScaled*0.3)+(ewr_achieved_ObsScaled*0.4)+(ewr_achieved_YrTypeScaled*0.3))


# Timeseries_Basin_LONGITUDINALgroup_SCALED_temp <- Timeseries_Basin_LONGITUDINALgroup |>
#   filter(Climate_Category == "Very Wet") |>
#   mutate(ewr_achieved_YrTypeScaled = ewr_achieved-min(ewr_achieved)/(max(ewr_achieved)-min(ewr_achieved)))|>
#   mutate(ewr_achieved_YrTypeScaled2 = (ewr_achieved-min(ewr_achieved))/(max(ewr_achieved)-min(ewr_achieved)))



```

## SRA: Time series - BASIN - LATERAL connectivity - IS

```{r}
Plot_Timeseries_Basin_LATERAL_IS <- ggplot(data = Timeseries_Basin_LATERALgroup_SCALED, 
       aes(x = year, y = ewr_achieved_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  
    geom_smooth(
    data = filter(Timeseries_Basin_LATERALgroup_SCALED, year >= 2012), 
       aes(x = year, y = ewr_achieved_IS), method = "lm",
    colour = "red", linewidth = 0.5)+
  
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS <- ggplot(data = Timeseries_Basin_LATERALgroup_SCALED, 
       aes(x = year, y = ewr_achieved_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  
    geom_smooth(
    data = filter(Timeseries_Basin_LATERALgroup_SCALED, year >= 2012), 
       aes(x = year, y = ewr_achieved_IS), method = "lm",
    colour = "red", linewidth = 0.5)+
  
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LATERAL_IS

ggsave(plot = Plot_Timeseries_Basin_LATERAL_IS, filename = file.path(comp_results, paste0("Plot_Timeseries_Basin_LATERAL_IS", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Time series - BASIN - LONGITUDINAL connectivity - IS

```{r}
Plot_Timeseries_Basin_LONGITUDINAL_IS <- ggplot(data = Timeseries_Basin_LONGITUDINALgroup_SCALED, 
       aes(x = year, y = ewr_achieved_IS))+
  geom_line(colour = "grey80")+
  geom_point(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  geom_smooth(colour = "grey20", linewidth = 0.5)+
  
  geom_smooth(
    data = filter(Timeseries_Basin_LONGITUDINALgroup_SCALED, year >= 2012), 
       aes(x = year, y = ewr_achieved_IS), method = "lm",
    colour = "red", linewidth = 0.5)+
  
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Lateral connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)

Plot_Timeseries_Basin_LONGITUDINAL_IS <- ggplot(data = Timeseries_Basin_LONGITUDINALgroup_SCALED, 
       aes(x = year, y = ewr_achieved_TotalScaled))+
  #geom_line(colour = "grey80")+
    geom_point(aes(x = year, y = ewr_achieved, colour = Climate_Category), shape = 5)+#, colour = "black")+               #empty diamond
    geom_point(aes(x = year, y = ewr_achieved_TotalScaled, colour = Climate_Category), shape = 15)+#, colour = "black")+  #fillted square
    geom_point(aes(x = year, y = ewr_achieved_ObsScaled, colour = Climate_Category), shape = 6)+#, colour = "black")+     #empty triangle
    geom_point(aes(x = year, y = ewr_achieved_YrTypeScaled, colour = Climate_Category), shape = 17)+#, colour = "black")+ #filled triangle
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #geom_smooth(colour = "grey20", linewidth = 0.5)+
  
  #geom_smooth(
  #  data = filter(Timeseries_Basin_LONGITUDINALgroup_SCALED, year >= 2012), 
  #     aes(x = year, y = ewr_achieved_IS), method = "lm",
  #  colour = "red", linewidth = 0.5)+
  
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "Year", colour = "SWC", y = "Longitudinal connectivity IS")+
  theme(axis.text.x = element_text(angle = 90))+
  #ylim(0,1)+ 
  xlim(1900,NA)

ggsave(plot = Plot_Timeseries_Basin_LONGITUDINAL_IS, filename = file.path(comp_results, paste0("Plot_Timeseries_Basin_LONGITUDINAL_IS", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

```{r}
plot_this <- Plot_Timeseries_Basin_LATERAL / Plot_Timeseries_Basin_LONGITUDINAL + plot_layout(guides = "collect")

ggsave(plot = plot_this, filename = file.path(comp_results, paste0("Plot_Timeseries1900_Basin_LONG_and_LAT_TREND", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

```{r}
plot_this <- Plot_Timeseries_Basin_LATERAL_IS / Plot_Timeseries_Basin_LONGITUDINAL_IS + plot_layout(guides = "collect")

ggsave(plot = plot_this, filename = file.path(comp_results, paste0("Plot_Timeseries1900_Basin_LONG_and_LAT_IS_TREND", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Boxplot - climate categories - LATERAL connectivity

```{r}
boxPlot_Timeseries_ClimateCategoryArea_LATERALgroup <- ggplot(data = Timeseries_ClimateCategoryArea_LATERALgroup, 
       aes(x = Climate_Category, y = ewr_achieved))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Proportion of gauges \nwith lateral connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

boxPlot_Timeseries_ClimateCategoryArea_LATERALgroup

ggsave(plot = boxPlot_Timeseries_ClimateCategoryArea_LATERALgroup, filename = file.path(comp_results, paste0("Boxplot_Timeseries_ClimateCategoryArea_LATERALgroup", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)

```

## SRA: Boxplot - climate categories - LONGITUDINAL connectivity

```{r}
boxPlot_Timeseries_ClimateCategoryArea_LONGITUDINAL <- ggplot(data = Timeseries_ClimateCategoryArea_LONGITUDINALgroup, 
       aes(x = Climate_Category, y = ewr_achieved))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Proportion of gauges \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

boxPlot_Timeseries_ClimateCategoryArea_LONGITUDINAL

ggsave(plot = boxPlot_Timeseries_ClimateCategoryArea_LONGITUDINAL, filename = file.path(comp_results, paste0("Boxplot_Timeseries_ClimateCategoryArea_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Boxplot - climate categories - LATERALconnectivity - BASIN

```{r}
boxPlot_Timeseries_Basin_LATERAL <- ggplot(data = Timeseries_Basin_LATERALgroup, 
       aes(x = Climate_Category, y = ewr_achieved))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Proportion of XX \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

boxPlot_Timeseries_Basin_LATERAL

ggsave(plot = boxPlot_Timeseries_Basin_LATERAL, filename = file.path(comp_results, paste0("Boxplot_Timeseries_Basin_LATERAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## SRA: Boxplot - climate categories - LONGITUDINAL connectivity - BASIN

```{r}
boxPlot_Timeseries_Basin_LONGITUDINAL <- ggplot(data = Timeseries_Basin_LONGITUDINALgroup, 
       aes(x = Climate_Category, y = ewr_achieved))+
  geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Proportion of XX \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(0,1)

boxPlot_Timeseries_Basin_LONGITUDINAL

ggsave(plot = boxPlot_Timeseries_Basin_LONGITUDINAL, filename = file.path(comp_results, paste0("Boxplot_Timeseries_Basin_LONGITUDINAL", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## TRENDS

```{r}

#SPAMM


Climate_category_areaS <- unique(Timeseries_ClimateCategoryArea_LONGITUDINALgroup$Climate_category_area)
Climate_category_areaS <- Climate_category_areaS[-12]#minus paroo
Climate_category_areaS <- Climate_category_areaS[-2]#minus paroo 

Trend_df <- data.frame(Climate_category_area = Climate_category_areaS,
                       ar1 = NA,
                       se = NA,
                       slope = NA,
                       n_years = NA)

for(i in 1:length(Climate_category_areaS)){

  data <- Timeseries_ClimateCategoryArea_LONGITUDINALgroup |>
    filter(Climate_category_area == Climate_category_areaS[i])|>
    filter(year >= 1983)
  
  #DUMMY data
  #data <- data.frame(ewr_achieved = 1:100 + runif(100),
  #                   year = 1901:2000)
  tryCatch({  
  data_ts <- ts(data$ewr_achieved, start = min(data$year),frequency = 1,end = max(data$year))
  data_diff <- diff(data_ts,1)

  plot(data_ts)
  plot(data_diff)

  Result <-arima(data_diff, order=c(1, 1, 0), method = "CSS")
  Result
  
  Trend_data <- ts(predict(Result,10)$pred)
  plot(Trend_data)
  data_trend <- data.frame(ewr_achieved = Trend_data[1:10],
                     year = (max(data$year)+1):(max(data$year)+10))
    
    
  lm_Result <- lm(ewr_achieved ~ year, data = data_trend)
  summary(lm_Result)

 Trend_df$ar1[i] <- Result$coef[1]
 Trend_df$se[i] <- sqrt(diag(vcov(Result))) 
  
  Trend_df$slope[i] <-   lm_Result$coefficients[2]}, error=function(e){})
  Trend_df$n_years[i] <-   nrow(filter(data, !is.na(ewr_achieved)))
}


ggplot(data = Trend_df, 
       aes(x = Climate_category_area, y = ar1))+
  geom_point(aes(x = Climate_category_area, y = ar1, alpha = n_years), colour = "blue")+
  geom_errorbar(aes(ymin = ar1-se, ymax = ar1+se))+
  #geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  #scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  #facet_wrap(~Climate_category_area, scales = "free_y", ncol = 3)+
  geom_point()+
  theme_werp_toolkit()+
  #labs(x = "SWC", colour = "SWC", y = "Proportion of gauges \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))#+
  #ylim(-0.05,0.05)
```

```{r}
#CANT DO THIS FO RINDIVIDUAL CLIMATE CATEGORIES 
Climate_category_areaS <- unique(Timeseries_ClimateCategoryArea_LONGITUDINALgroup$Climate_category_area)
Climate_categoryS <- unique(Timeseries_ClimateCategoryArea_LONGITUDINALgroup$Climate_Category)

Climate_category_areaS <- Climate_category_areaS[-12]#minus paroo


Trend_df <- data.frame(Climate_category_area = rep(Climate_category_areaS, 5),
                       Climate_category = sort(rep(Climate_categoryS, 12)),
                       ar1 = NA,
                       se = NA,
                       slope = NA,
                       n = NA)


for(i in 1:nrow(Trend_df)){

  start <- Timeseries_ClimateCategoryArea_LONGITUDINALgroup |>
    filter(Climate_category_area == Trend_df$Climate_category_area[i] & Climate_Category == Trend_df$Climate_category[i])
  start_year <- min(start$year)
  fin_year <- max(start$year)
  
  data <- Timeseries_ClimateCategoryArea_LONGITUDINALgroup |>
    filter(Climate_category_area == Trend_df$Climate_category_area[i])|>
    filter(year >= start_year & year <= fin_year)|>
    mutate(ewr_achieved = ifelse(Climate_Category == Trend_df$Climate_category[i], ewr_achieved, NA))|>
    filter(year >= 1983)
  
  #DUMMY data
  #data <- data.frame(ewr_achieved = 1:100 + runif(100),
  #                   year = 1901:2000)
   tryCatch({ 
  data_ts <- ts(data$ewr_achieved, start = min(data$year),frequency = 1,end = max(data$year))
  data_diff <- diff(data_ts,1)

  #plot(data_ts)
  #plot(data_diff)


  Result <-arima(data_diff,order=c(1,1,0), method = "CSS")
  Trend_data <- ts(predict(Result,10)$pred)
  plot(Trend_data)
  data_trend <- data.frame(ewr_achieved = Trend_data[1:10],
                     year = (max(data$year)+1):(max(data$year)+10))
    
    
  lm_Result <- lm(ewr_achieved ~ year, data = data_trend)
  summary(lm_Result)

  Trend_df$ar1[i] <- Result$coef[1]
  Trend_df$se[i] <- sqrt(diag(vcov(Result))) 
  
  Trend_df$slope[i] <-   lm_Result$coefficients[2]}, error=function(e){})
  
  Trend_df$n[i] <-   nrow(filter(data, !is.na(ewr_achieved)))
}


ggplot(data = Trend_df, 
       aes(x = Climate_category_area, y = slope))+
  geom_point(aes(x = Climate_category_area, y = ar1), colour = "blue")+
  geom_errorbar(aes(ymin = ar1-se, ymax = ar1+se))+
  #geom_boxplot(aes(colour = Climate_Category))+#, colour = "black")+
  #scale_colour_manual(values = pal_climate, aesthetics = "colour") +
  facet_wrap(~Climate_category)+
  geom_point()+
  theme_werp_toolkit()+
  labs(x = "SWC", colour = "SWC", y = "Proportion of gauges \nwith longitudinal connectivity EWRs occuring")+
  theme(axis.text.x = element_text(angle = 90))#+
  #ylim(-0.05,0.05)
```

## EWRs for target groups -

NEXT - maybe just a line for hte max scenario? to make sure the scale includes the max?

```{r}
## | label: fig-obj_in_groups
## | fig-cap: "Proportion of EWRs achieved for each environmental objective, grouped into broader environmental groups (EF = Priority Ecosystem Function, NF = Native Fish, NV = Native Vegetation, OS = Other Species, WB = Waterbirds). This view provides an assessment of the performance of individual environmental objectives, as well as how those contribute to the overall sensitivity of the broader groups across space. Not all EWR are applicable in all locations and there are not equal number of EWR in each category. The MAX column illustrates the total number of EWRs for reference, with each black box showing the situation where all EWRs contributing to an Environmental Objective are met. Where the max column does not exist, those objectives are not relevant to that particular planning unit. This illustration includes three climate scenarios: A (0.5x), E (historical base level/no change), and I (2x) and three adaptation options 1 (no adaptation), 2 (+250 ML/d), and 3 (+6500 ML/d)"
## | message: false
## | warning: false

obj_in_groups <- sdl_objectives_nonrounding |>
  ungroup()|>
  dplyr::filter(scenario != "MAX") |> 
  dplyr::filter(names_climate_scenario %in% MDBA_comparison)|>
  #filter(env_group != 'EB') |> # There's only one, this is just distracting.
  #clean the names
  mutate(scenario = paste0(licvolfactor),
        SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n')) |>
  #rename(env_obj2 = env_obj)|>
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "EWR achievement\n (summed proportion of objectives)",
                x_lab = "Climate & adaptation option scenario", 
                colorgroups = 'env_group',
                colorset = 'env_obj',
                pal_list = pal_env,
                color_lab = "Envionmental objectives",
                facet_col = 'names_MDBA_climate_scenario',
                facet_row = 'env_group',
                #sceneorder = sceneorder
                )+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  guides(fill=guide_legend(ncol=3))+
  facet_grid(env_group~names_MDBA_climate_scenario, scales = "free")

#   ggplot2::geom_hline(aes(yintercept = sum(n_ewr_code)),
#                     colour = "black", linetype = "longdash") 

#obj_in_groups

# obj_in_groups <- obj_in_groups +
#   ggplot2::theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
#   scale_y_continuous(n.breaks = 3)+
#   scale_x_discrete(labels= c(scenario_labels_to_plot, "MAX"))

# ADD IN MAX: #Line ON TOP AT END
Max_summary <- sdl_objectives_nonrounding |>
  filter(scenario == "MAX")|>
  group_by(env_group)|>
  summarise(ewr_achieved = sum(ewr_achieved))

obj_in_groups_MAXline <- obj_in_groups + 
  ggplot2::geom_hline(data = Max_summary, 
                    aes(yintercept = ewr_achieved),
                    colour = "black", linetype = "longdash") 

obj_in_groups_MAXline

ggsave(plot = obj_in_groups_MAXline, filename = file.path(comp_results, paste0("EWRs_for_target_groups_MAX ", Sys.Date(), ".tiff")), device = "tiff",
       width = 7, height = 5)

```

## Dry_comparison

```{r}
Dry_comparison_plot <- sdl_objectives_nonrounding |>
  ungroup()|>
  dplyr::mutate(licvolfactor = factor(licvolfactor))|>
  dplyr::mutate(licvolfactor = factor(licvolfactor, levels = rev(levels(licvolfactor))))|>
  #dplyr::filter(scenario != "MAX") |> 
  dplyr::filter(names_climate_scenario %in% Dry_comparison) |>
  dplyr::mutate(scenario = factor(names_MDBA_climate_scenario_long, levels = c("Historical climate", "Dry climate change")), 
        SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n')) |>
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "EWR achievement\n (summed proportion of objectives)",
                x_lab = "Climate & adaptation option scenario", 
                colorgroups = 'env_group',
                colorset = 'env_obj',
                pal_list = pal_env,
                color_lab = "\n \n \n \n \n \n \nEnvironmental objectives",
                facet_col = 'names_climate_scenario',
                facet_row = 'env_group',
                #sceneorder = sceneorder
                )+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  guides(fill=guide_legend(ncol=3))+
  facet_grid(env_group~licvolfactor, scales = "free")

# ADD IN MAX: #Line ON TOP AT END
Max_summary <- sdl_objectives_nonrounding |>
  filter(scenario == "MAX")|>
  group_by(env_group)|>
  summarise(ewr_achieved = sum(ewr_achieved))

Dry_comparison_plot_MAXline <- Dry_comparison_plot + 
  ggplot2::geom_hline(data = Max_summary, 
                    aes(yintercept = ewr_achieved),
                    colour = "black", linetype = "longdash") 

Dry_comparison_plot_MAXline
ggsave(plot = Dry_comparison_plot_MAXline, file.path(comp_results, paste0("Dry_comparison ", Sys.Date(), ".tiff")), device = "tiff",
       width = 7, height = 6)
```

## Wet_comparison

```{r}
Wet_comparison_plot <- sdl_objectives_nonrounding |>
  ungroup()|>
  dplyr::mutate(licvolfactor = factor(licvolfactor))|>
  dplyr::mutate(licvolfactor = factor(licvolfactor, levels = rev(levels(licvolfactor))))|>
  #dplyr::filter(scenario != "MAX") |> 
  dplyr::filter(names_climate_scenario %in% Wet_comparison) |>
  dplyr::mutate(scenario = factor(names_MDBA_climate_scenario_long, levels = c("Historical climate", "Wet climate change")), 
        SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n')) |>
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "EWR achievement\n (summed proportion of objectives)",
                x_lab = "Climate & adaptation option scenario", 
                colorgroups = 'env_group',
                colorset = 'env_obj',
                pal_list = pal_env,
                color_lab = "\n \n \n \n \n \n \nEnvironmental\n objectives",
                facet_col = 'names_climate_scenario',
                facet_row = 'env_group',
                #sceneorder = sceneorder
                )+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  guides(fill=guide_legend(ncol=3))+
  facet_grid(env_group~licvolfactor, scales = "free")

# ADD IN MAX: #Line ON TOP AT END
Max_summary <- sdl_objectives_nonrounding |>
  filter(scenario == "MAX")|>
  group_by(env_group)|>
  summarise(ewr_achieved = sum(ewr_achieved))

Wet_comparison_plot_MAXline <- Wet_comparison_plot + 
  ggplot2::geom_hline(data = Max_summary, 
                    aes(yintercept = ewr_achieved),
                    colour = "black", linetype = "longdash") 

Wet_comparison_plot_MAXline
ggsave(plot = Wet_comparison_plot_MAXline, filename = file.path(comp_results, paste0("Wet_comparison",  Sys.Date(), ".tiff")), device = "tiff",
       width = 7, height = 6)
```

## Median_comparison

```{r}
Median_comparison_plot <- sdl_objectives_nonrounding |>
  ungroup()|>
  dplyr::mutate(licvolfactor = factor(licvolfactor))|>
  dplyr::mutate(licvolfactor = factor(licvolfactor, levels = rev(levels(licvolfactor))))|>
  #dplyr::filter(scenario != "MAX") |> 
  dplyr::filter(names_climate_scenario %in% Median_comparison) |>
  dplyr::mutate(scenario = factor(names_MDBA_climate_scenario_long, levels = c("Historical climate", "Median climate change")), 
        SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n')) |>
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "EWR achievement\n (summed proportion of objectives)",
                x_lab = "Climate & adaptation option scenario", 
                colorgroups = 'env_group',
                colorset = 'env_obj',
                pal_list = pal_env,
                color_lab = "\n \n \n \n \n \n \nEnvironmental objectives",
                facet_col = 'names_climate_scenario',
                facet_row = 'env_group',
                #sceneorder = sceneorder
                )+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  guides(fill=guide_legend(ncol=3))+
  facet_grid(env_group~licvolfactor, scales = "free")

# ADD IN MAX: #Line ON TOP AT END
Max_summary <- sdl_objectives_nonrounding |>
  filter(scenario == "MAX")|>
  group_by(env_group)|>
  summarise(ewr_achieved = sum(ewr_achieved))

Median_comparison_plot_MAXline <- Median_comparison_plot + 
  ggplot2::geom_hline(data = Max_summary, 
                    aes(yintercept = ewr_achieved),
                    colour = "black", linetype = "longdash") 

Median_comparison_plot_MAXline
ggsave(plot = Median_comparison_plot_MAXline, filename = file.path(comp_results, paste0("Median_comparison", Sys.Date(), ".tiff")), device = "tiff",
       width = 7, height = 6)
```

## MDBA_comparison

```{r}
 sdl_objectives_nonrounding2 <- sdl_objectives_nonrounding |>
   #did this to order NF10,but it shouldnt be there any way, at some point it will be though
   dplyr::mutate(env_obj = ordered(env_obj, levels = c(
    'EF1', 'EF2', 'EF3', 'EF3a', 'EF3b', 'EF4', 'EF5', 'EF6', 'EF7', 'NF', 'NF1',  'NF2', 'NF3', 'NF4', 'NF5', 'NF6', 'NF7', 'NF8', 'NF9', 'NF10', 'NV1', 'NV2', 'NV3', 'NV4', 'NV4a', 'NV4b', 'NV4c', 'NV4d', 'NV4e', 'NV4f', 'OS1', 'OS2', 'OS4', 'WB1', 'WB2', 'WB3', 'WB4', 'WB5')))|> #is losing 'NF' here a problem 
  dplyr::arrange(env_obj) #|>
   
  #  #dumb work arround until we fix problem with planning unit join
  # dplyr::filter(env_obj %in% SWSDLName_objectives)


MDBA_comparison_plot <- sdl_objectives_nonrounding2 |>
  ungroup()|>
  dplyr::mutate(licvolfactor = factor(licvolfactor))|>
  dplyr::mutate(licvolfactor = factor(licvolfactor))|>
  #dplyr::mutate(licvolfactor = factor(licvolfactor, levels = rev(levels(licvolfactor))))|>
  #dplyr::filter(scenario != "MAX") |> 
  dplyr::filter(names_climate_scenario %in% MDBA_comparison) |>
  dplyr::mutate(scenario = names_MDBA_climate_scenario_long, 
        SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n')) |>
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "EWR achievement\n (summed proportion of objectives)",
                x_lab = "Climate & adaptation option scenario", 
                colorgroups = 'env_group',
                colorset = 'env_obj',
                pal_list = pal_env,
                color_lab = "\n \n \n \n \n \n \nEnvironmental objectives",
                facet_col = 'names_climate_scenario',
                facet_row = 'env_group',
                #sceneorder = sceneorder
                )+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  guides(fill=guide_legend(ncol=3))+
  facet_grid(env_group~licvolfactor, scales = "free") + 
  scale_y_continuous(breaks= scales::breaks_pretty())

# ADD IN MAX: #Line ON TOP AT END
Max_summary <- sdl_objectives_nonrounding2 |>
  filter(scenario == "MAX")|>
  group_by(env_group)|>
  summarise(ewr_achieved = sum(ewr_achieved))

MDBA_comparison_plot_MAXline <- MDBA_comparison_plot + 
  ggplot2::geom_hline(data = Max_summary, 
                    aes(yintercept = ewr_achieved),
                    colour = "black", linetype = "longdash") 

MDBA_comparison_plot_MAXline
ggsave(plot = MDBA_comparison_plot_MAXline, filename = file.path(comp_results, paste0("MDBA_comparison", Sys.Date(), ".tiff")), device = "tiff",
       width = 7, height = 6)
```

## End of system flows - adaptation comparison

the current scenarios overlap a lot - but this may be a useful plot with other scenarios.

```{r}
#| label: fig-difference-baseline
#| fig-cap: "Quantitative scenario comparison for Native Fish objectives for three SDL units. Scenarios defined here as the difference in mean flow (GL) from the baseline historical scenario (E1). A key message here is that the lines are not smooth- EWR achievement is not simply a function of the amount of water. Instead, the 'adaptation' options, particularly the '2' scenarios of adding 250 ML/d of water, have disproportionately large impact (steep slopes). Shading indicates different environmental objectives within the native fish target group. This illustration includes three climate scenarios: A (0.5x), E (historical base level/no change), and I (2x) and three adaptation options 1 (no adaptation), 2 (+250 ML/d), and 3 (+6500 ML/d)."
#| message: false

scenarios_end_sys <- sdl_objectives_nonrounding |>
  dplyr::filter(names_climate_scenario %in% MDBA_comparison) |>
  dplyr::filter(scenario != "MAX") |>
  mutate(scenario = names_scenario) |> 
  group_by(scenario, env_group) |>
  mutate(y = 0.45,
         'ewr_achieved' = 0.3,
         pointgroup = 1)

gl_difference <- sdl_objectives_nonrounding |>
  dplyr::filter(scenario != "MAX") |>
    dplyr::filter(names_climate_scenario %in% MDBA_comparison) |>
   mutate(scenario = names_scenario) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "Proportion EWR achieved",
                x_col = "End sys",
                x_lab = "End of system flow (GL)",
               colorgroups = 'env_group',
               colorset = 'env_obj',
               pal_list = pal_env,
                # base_lev = 'E1',
                # comp_fun = 'difference',
               # group_cols = c('env_obj'),
                color_lab = "Envionmental objectives",
                facet_row = 'env_group',
                facet_col = '.'
                ) +
  ylim(0,1) +
  geom_vline(mapping = aes(xintercept = `End sys`),
             colour = "black", linetype = "solid")+
    guides(colour=guide_legend(ncol=3))+
  facet_grid(env_group~.)

# gl_difference + 
#   geom_text(data = scenarios_end_sys, mapping = aes(label = scenarios_end_sys$scenario, x = scenarios_end_sys$`End sys`, y = scenarios_end_sys$y), size = 3, angle = 90)

header_difference <-  scenarios |> 
    dplyr::filter(names_climate_scenario %in% MDBA_comparison) |>
    dplyr::filter(scenario != "MAX") |>
  mutate(scenario = names_scenario) |> 
  ggplot(aes(x = `End sys`,
             y = 1)) +
  geom_text(mapping = aes(label = scenario), size = 2.5, angle = 90) +
  theme_werp_toolkit(legend.position = "none", axis.title=element_blank(),
                     axis.text=element_blank(), axis.ticks=element_blank())+
  theme(plot.margin = margin(b = 2))+
  expand_limits(y = c(-6,8))

# put those together
Plot_EndOfSysFlows1 <- header_difference + gl_difference + 
  patchwork::plot_layout(ncol = 1, heights = c(7,15), guides = "collect") + 
  theme(legend.position = "right")

ggsave(plot = Plot_EndOfSysFlows1, filename = file.path(comp_results, paste0("Objectives_EndOfSysFlows_adaptation_comparison",Sys.Date(),".tiff")), device = "tiff",
       width = 7, height = 4)

```

## End of system flows - climate comparison

```{r}

scenarios_end_sys <- filter(sdl_objectives_nonrounding, names_climate_scenario %in% MDBA_comparison) |>
  group_by(scenario, env_group) |>
  mutate(y = 0.45,
         'ewr_achieved' = 0.3,
         pointgroup = 1,
         scenario = names_MDBA_climate_scenario)

gl_difference <- sdl_objectives_nonrounding |>
  dplyr::filter(names_climate_scenario %in% MDBA_comparison) |>
  mutate(scenario = names_MDBA_climate_scenario) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "Proportion EWR achieved",
                x_col = "End sys",
                x_lab = "End of system flow (GL)",
                colorgroups = 'env_group',
                colorset = 'env_obj',
                pal_list = pal_env,
                # base_lev = 'E1',
                # comp_fun = 'difference',
                #group_cols = c('env_obj'),
                color_lab = "Envionmental objectives",
                facet_row = 'env_group'
                #facet_col = '.'
                ) +
  ylim(0,1) +
  geom_vline(alpha = 0.5, mapping = aes(xintercept = `End sys`),
             colour = "black", linetype = "solid")+
  facet_grid(env_group~.)+
    guides(colour=guide_legend(ncol=3))+
  theme(plot.margin = margin(t = 0))

# gl_difference + 
#   geom_text(data = scenarios_end_sys, mapping = aes(label = scenarios_end_sys$scenario, x = scenarios_end_sys$`End sys`, y = scenarios_end_sys$y), size = 3, angle = 90)

header_difference <-  scenarios |> 
  filter(names_climate_scenario %in% MDBA_comparison) |> 
  filter(licvolfactor == 1.0)|>
  mutate(scenario = names_MDBA_climate_scenario) |> 
  ggplot(aes(x = `End sys`,
             y = 1)) +
  geom_text(mapping = aes(label = scenario), size = 2.5, angle = 90) +
  theme_werp_toolkit(legend.position = "none", axis.title=element_blank(),
                     axis.text=element_blank(), axis.ticks=element_blank())+
  theme(plot.margin = margin(b = 2))+
  expand_limits(y = c(-5,7))

# put those together
Plot_EndOfSysFlows <- header_difference + gl_difference + 
  patchwork::plot_layout(ncol = 1, heights = c(5,15), guides = "collect") + 
  theme(legend.position = "right")

ggsave(plot = Plot_EndOfSysFlows, filename = file.path(comp_results, paste0("Objectives_EndOfSysFlows_climate_comparison",Sys.Date(),".tiff")), device = "tiff",
       width = 7, height = 4)
Plot_EndOfSysFlows
```

## End of system flows - median climate adaptation comparison

```{r}
scenarios_end_sys <- sdl_objectives_nonrounding |>
  dplyr::filter(names_climate_scenario %in% MDBA_comparison[1]) |>
  dplyr::filter(scenario != "MAX") |>
  mutate(scenario = names_scenario) |> 
  group_by(scenario, env_group) |>
  mutate(y = 0.45,
         'ewr_achieved' = 0.3,
         pointgroup = 1)

gl_difference <- sdl_objectives_nonrounding |>
  dplyr::filter(scenario != "MAX") |>
    dplyr::filter(names_climate_scenario %in% MDBA_comparison[1]) |>
   mutate(scenario = names_scenario) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "Proportion EWR achieved",
                x_col = "End sys",
                x_lab = "End of system flow (GL)",
               colorgroups = 'env_group',
               colorset = 'env_obj',
               pal_list = pal_env,
                # base_lev = 'E1',
                # comp_fun = 'difference',
               # group_cols = c('env_obj'),
                color_lab = "Envionmental objectives",
                facet_row = 'env_group',
                facet_col = '.'
                ) +
  ylim(0,1) +
  geom_vline(mapping = aes(xintercept = `End sys`),
             colour = "black", linetype = "solid")+
    guides(colour=guide_legend(ncol=3))+
  facet_grid(env_group~.)

header_difference <-  scenarios |> 
    dplyr::filter(names_climate_scenario %in% MDBA_comparison[1]) |>
    dplyr::filter(scenario != "MAX") |>
  mutate(scenario = names_scenario) |> 
  ggplot(aes(x = `End sys`,
             y = 1)) +
  geom_text(mapping = aes(label = scenario), size = 2.5, angle = 90) +
  theme_werp_toolkit(legend.position = "none", axis.title=element_blank(),
                     axis.text=element_blank(), axis.ticks=element_blank())+
  theme(plot.margin = margin(b = 2))+
  expand_limits(y = c(-6,8))

# put those together
Plot_EndOfSysFlows3 <- header_difference + gl_difference + 
  patchwork::plot_layout(ncol = 1, heights = c(7,15), guides = "collect") + 
  theme(legend.position = "right")

ggsave(plot = Plot_EndOfSysFlows3, filename = file.path(comp_results, paste0("Objectives_EndOfSysFlows_MedianClimate_adaptation_comparison",Sys.Date(),".tiff")), device = "tiff",
       width = 7, height = 4)
```

## End of system flows - Dry climate adaptation comparison

```{r}
scenarios_end_sys <- sdl_objectives_nonrounding |>
  dplyr::filter(names_climate_scenario %in% MDBA_comparison[2]) |>
  dplyr::filter(scenario != "MAX") |>
  mutate(scenario = names_scenario) |> 
  group_by(scenario, env_group) |>
  mutate(y = 0.45,
         'ewr_achieved' = 0.3,
         pointgroup = 1)

gl_difference <- sdl_objectives_nonrounding |>
  dplyr::filter(scenario != "MAX") |>
    dplyr::filter(names_climate_scenario %in% MDBA_comparison[2]) |>
   mutate(scenario = names_scenario) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "Proportion EWR achieved",
                x_col = "End sys",
                x_lab = "End of system flow (GL)",
               colorgroups = 'env_group',
               colorset = 'env_obj',
               pal_list = pal_env,
                # base_lev = 'E1',
                # comp_fun = 'difference',
               # group_cols = c('env_obj'),
                color_lab = "Envionmental objectives",
                facet_row = 'env_group',
                facet_col = '.'
                ) +
  ylim(0,1) +
  geom_vline(mapping = aes(xintercept = `End sys`),
             colour = "black", linetype = "solid")+
    guides(colour=guide_legend(ncol=3))+
  facet_grid(env_group~.)

header_difference <-  scenarios |> 
    dplyr::filter(names_climate_scenario %in% MDBA_comparison[2]) |>
    dplyr::filter(scenario != "MAX") |>
  mutate(scenario = names_scenario) |> 
  ggplot(aes(x = `End sys`,
             y = 1)) +
  geom_text(mapping = aes(label = scenario), size = 2.5, angle = 90) +
  theme_werp_toolkit(legend.position = "none", axis.title=element_blank(),
                     axis.text=element_blank(), axis.ticks=element_blank())+
  theme(plot.margin = margin(b = 2))+
  expand_limits(y = c(-6,8))

# put those together
Plot_EndOfSysFlows4 <- header_difference + gl_difference + 
  patchwork::plot_layout(ncol = 1, heights = c(7,15), guides = "collect") + 
  theme(legend.position = "right")

ggsave(plot = Plot_EndOfSysFlows4, filename = file.path(comp_results, paste0("Objectives_EndOfSysFlows_DryClimate_adaptation_comparison",Sys.Date(),".tiff")), device = "tiff",
       width = 7, height = 4)
```

## Heatmap -Qual

```{r}
#| label: build-heatmaps
# Use the Target here to get to the big groups

# qualitative axes
qual_heatmap <- sdl_target_nonrounding |>
  dplyr::filter(scenario != 'MAX') |> 
  dplyr::filter(!is.na(Target)) |> 
  dplyr::filter(names_climate_scenario %in% MDBA_comparison)|>
  # clean names
  mutate(scenario = names_scenario, 
         #SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n'),
         Target = stringr::str_replace(Target, 'Priority e', 'E')) |>
  
  
qual_heatmap_plot <- qual_heatmap|>  
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = "Proportion EWR achieved",
                y_col = 'licvolfactor', 
                y_lab = 'Adaptation option',
                x_col = 'names_MDBA_climate_scenario', 
                x_lab = 'Climate scenario',
                plot_type = 'heatmap',
                colorset = 'ewr_achieved',
                pal_list = pal_achieve,
                facet_row = 'env_group',
                facet_col = '.')
```

```{r}


# Quantitative axes- it's more informative, but uglier
quant_heatmap <- sdl_target_nonrounding |>
  dplyr::filter(scenario != 'MAX') |> 
  dplyr::filter(!is.na(Target)) |> 
  dplyr::filter(names_climate_scenario %in% MDBA_comparison)|>
  # clean names
  mutate(scenario = names_scenario, 
         #SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n'),
         Target = stringr::str_replace(Target, 'Priority e', 'E')) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = 'Condition',
                y_col = 'flow_addition', 
                y_lab = 'Flow addition',
                x_col = 'flow_multiplier', 
                x_lab = "Flow multiplier",
                plot_type = 'heatmap',
                transy = 'log10',
                transx = 'log10',
                colorset = 'ewr_achieved',
                pal_list = 'grDevices::Viridis',
                facet_row = 'Target',
                facet_col = 'SWSDLName',
                setLimits = c(0,1))

# interpolated raster- just one argument different
  # THe spacing is too uneven though
quant_interp_heatmap <- sdl_target_nonrounding |>
  dplyr::filter(adapt_code %in% c(1,2,3) &
                  scenario != 'MAX') |> # max isn't really relevant here
  dplyr::filter(!is.na(Target)) |> 
  dplyr::filter(names_climate_scenario %in% MDBA_comparison)|>
  # clean names
  mutate(scenario = paste0(climate_code, adapt_code), 
         SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n'),
         Target = stringr::str_replace(Target, 'Priority e', 'E'),
         adapt_code = as.character(adapt_code)) |>
  mutate(flow_addition = flow_addition + 1) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = 'Condition',
                y_col = 'flow_addition', 
                y_lab = 'Flow addition',
                x_col = 'flow_multiplier', 
                x_lab = "Flow multiplier",
                plot_type = 'heatmap',
                transy = 'log10',
                transx = 'log10',
                colorset = 'ewr_achieved',
                pal_list = 'grDevices::Viridis',
                facet_row = 'Target',
                facet_col = 'SWSDLName',
                setLimits = c(0,1),
                contour_arglist = list(interpolate = TRUE))

# This would be better if we had a more even and tighter set of scenarios
  contour_heatmap <- agged_data_pooled_ewrs$Target |>
  dplyr::filter(adapt_code %in% c(1,2,3) &
                  scenario != 'MAX') |> # max isn't really relevant here
  dplyr::filter(!is.na(Target)) |> 
  dplyr::filter(names_climate_scenario %in% MDBA_comparison)|>
  # clean names
  mutate(scenario = paste0(climate_code, adapt_code), 
         SWSDLName = stringr::str_replace(SWSDLName, '–', '-\n'),
         Target = stringr::str_replace(Target, 'Priority e', 'E'),
         adapt_code = as.character(adapt_code)) |>
  mutate(flow_addition = flow_addition + 1) |> 
  plot_outcomes(outcome_col = 'ewr_achieved',
                outcome_lab = 'Condition',
                y_col = 'flow_addition', 
                y_lab = 'Flow addition',
                x_col = 'flow_multiplier', 
                x_lab = "Flow multiplier",
                plot_type = 'heatmap',
                transy = 'log10',
                transx = 'log10',
                colorset = 'ewr_achieved',
                pal_list = 'grDevices::Viridis',
                facet_row = 'Target',
                facet_col = 'SWSDLName',
                setLimits = c(0,1),
                contour_arglist = list()
  )
```

```{r}
# Quantitative axes- it's more informative, but uglier
quant_heatmap <- agg_envgroup_sdl_to_plot |>
  dplyr::filter(names_climate_scenario %in% MDBA_comparison) |>
  dplyr::filter(env_group != 'EB') |> 
  mutate(scenario = paste0("SE",scale_evap, "_LV",licvolfactor)) |> 
  ggplot(aes(x = `End sys`, y = `GS Irrig`, fill = ewr_achieved)) + 
  geom_raster(interpolate = TRUE) + # OR geom_point
  geom_point(mapping = aes(colour = ewr_achieved), shape = 15, size = 6) +
  facet_grid(. ~ env_group) +
  theme_werp_toolkit() +
  paletteer::scale_fill_paletteer_c('grDevices::Viridis', limits = c(0,1)) +
  paletteer::scale_colour_paletteer_c('grDevices::Viridis', limits = c(0,1)) #+
  #labs(x = "Flow multiplier", y = "Flow addition", fill = "Condition")# +
  # scale_y_continuous(trans = 'log10') + 
  # scale_x_continuous(trans = 'log10')
quant_heatmap
```

```{r}
#| label: fig-contour
#| fig-cap: Condition results visualised as a surface with the two scenario definitions on the axes. This approach allows visualising changes in outcome as the result of multiple axes on which scenarios might differ. These axes might be different aspects of scenario creation (as here), or they might be different axes describing the outcome of scenarios (e.g. two different hydrometrics such as mean flow and flow variance)

# This would be better if we had a more even and tighter set of scenarios
contour_heatmap <- agg_envgroup_sdl_to_plot |>
  dplyr::filter(scenario %in% scenarios_scale_evap_climate_comp) |>
  dplyr::filter(env_group != 'EB') |> 
  mutate(scenario = paste0("SE",scale_evap, "_LV",licvolfactor)) |> 
  ggplot(aes(x = `End sys`, y = `GS Irrig`, z = ewr_achieved)) + 
  geom_tile() + # OR geom_point
  facet_grid(. ~ env_group) +
  geom_contour_filled(breaks = seq(0, 1, 0.1)) + 
  theme_werp_toolkit() 

# This is for Galen's reference for developing the function, I think- overlay points and change the fill ramp

# Changing the fill for geom_contour_filled needs bins. The easiest way to make that work from a continuous scale is to get the colors and then use manual.
binpal <- paletteer::paletteer_c('grDevices::Plasma', n = 10)

contour_point_heatmap <- contour_heatmap +
  # Change the fill scale
  scale_fill_manual(values = binpal) +
  # ideally, we'd use the same color ramp and fill these points with a black circle around them. But that conflicts with the binned fill for the contour
  # geom_point(shape = 21, color = 'black')
  geom_point(mapping = aes(color = ewr_achieved)) +
  paletteer::scale_color_paletteer_c('grDevices::Viridis')

contour_heatmap
contour_point_heatmap
```

## MAP

```{r}
ggplot(data = Tagg_ClimateCategoryArea_ClimateCategories_LATERALgroup,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = ewr_achieved_weighted))+
  geom_sf(data = Tagg_gauge_ClimateCategories_LATERALgroup,  aes(geometry = geometry, colour = ewr_achieved_weighted))+ 
  #geom_sf_text(aes(label = Climate_category_area), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_color_paletteer_c('grDevices::Viridis')+
  paletteer::scale_fill_paletteer_c('grDevices::Viridis')+
  labs(fill = "Proportion of gauges with\n longitudinal connectivity\n EWR achieved", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

ggplot(data = Tagg_Basin_ClimateCategories_LATERALgroup ,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = ewr_achieved_weighted))+
  geom_sf(data = Tagg_gauge_ClimateCategories_LATERALgroup,  aes(geometry = geometry, colour = ewr_achieved_weighted))+ 
  #geom_sf_text(aes(label = Climate_category_area), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_color_paletteer_c('grDevices::Viridis')+
  paletteer::scale_fill_paletteer_c('grDevices::Viridis')+
  labs(fill = "Proportion of gauges with\n longitudinal connectivity\n EWR achieved", y = "", x = "", colour = "") +
  facet_wrap(~Climate_Category)

ggplot(data = Tagg_ClimateCategoryArea_LATERALgroup,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = ewr_achieved_weighted))+
  
  geom_sf(data = Tagg_gauge_LATERALgroup,  aes(geometry = geometry, colour = ewr_achieved_weighted))+ 
  geom_sf_text(aes(label = Climate_category_area), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_color_paletteer_c('grDevices::Viridis')+
  paletteer::scale_fill_paletteer_c('grDevices::Viridis')+
  labs(fill = "Proportion of gauges with\n longitudinal connectivity\n EWR achieved", y = "", x = "", colour = "") 
  #geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))

ggplot(data = Tagg_Basin_LATERALgroup,  
       aes(geometry = geometry)) +
  geom_sf(aes(fill = ewr_achieved_weighted))+
  
  geom_sf(data = Tagg_gauge_LATERALgroup,  aes(geometry = geometry, colour = ewr_achieved_weighted))+ 
  #geom_sf_text(aes(label = Climate_category_area), colour = "red", size = 3)+
  theme_werp_toolkit() +
  paletteer::scale_color_paletteer_c('grDevices::Viridis')+
  paletteer::scale_fill_paletteer_c('grDevices::Viridis')+
  labs(fill = "Proportion of gauges with\n longitudinal connectivity\n EWR achieved", y = "", x = "", colour = "") 
  #geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))

```

```{r}
# The map


ggplot(data = Climate_Category_geometry,  aes(geometry = geometry)) +
  geom_sf()+
  geom_sf_text(data = Climate_Category_geometry, aes(label = Climate_category_area))+
  geom_sf(data = gauges_df_sld,  aes(geometry = geometry), colour = "red")+ #ALL GAUGES, TWO DONT RUN THORUGH EWR TOOL
  geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))

plot1 <- ggplot(data = Climate_Category_geometry,  aes(geometry = geometry)) +
  geom_sf(aes(colour = Climate_category_area))+
  geom_sf_text(data = Climate_Category_geometry, aes(label = Climate_category_area, colour = Climate_category_area))+
  geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))+ 
  theme(legend.position = "none")

plot2 <- ggplot()+#data = Climate_Category_geometry,  aes(geometry = geometry)) +
  #geom_sf(aes(colour = Climate_category_area))+
  #geom_sf_text(data = Climate_Category_geometry, aes(label = Climate_category_area, colour = Climate_category_area))+
  #geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))+
  geom_sf(data = sdl_units,  aes(geometry = geometry, fill = SWSDLName, colour = SWSDLName), alpha = 0.1)+ 
  geom_sf_text(data = filter(sdl_units), aes(label = SWSDLName, colour = SWSDLName))+
  theme(legend.position = "none")

plot3 <- ggplot(data = Climate_Category_geometry,  aes(geometry = geometry)) +
  #geom_sf(aes(colour = Climate_category_area))+
  #geom_sf_text(data = Climate_Category_geometry, aes(label = Climate_category_area, colour = Climate_category_area))+
  geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))+
  geom_sf(data = cewo_valleys,  aes(geometry = geometry, fill = ValleyName, colour = ValleyName), alpha = 0.1)+ 
  geom_sf_text(data = cewo_valleys, aes(label = ValleyName, colour = ValleyName))+
  theme(legend.position = "none")

plot4 <- ggplot(data = Climate_Category_geometry,  aes(geometry = geometry)) +
  #geom_sf(aes(colour = Climate_category_area))+
  #geom_sf_text(data = Climate_Category_geometry, aes(label = Climate_category_area, colour = Climate_category_area))+
  geom_sf(data = gauge_EWR_groups,  aes(geometry = geometry))+
  geom_sf(data = resource_plan_areas,  aes(geometry = geometry, fill = SWWRPANAME, colour = SWWRPANAME), alpha = 0.1)+ 
  geom_sf_text(data = resource_plan_areas, aes(label = SWWRPANAME, colour = SWWRPANAME))+
  theme(legend.position = "none")

suppressWarnings(print(
plot1 + plot4 + theme(legend.position = "none")
))
suppressWarnings(print(
plot2 + plot4 + theme(legend.position = "none")
))

suppressWarnings(print(
plot3 + plot4 + theme(legend.position = "none")
))

sdl_units <- sdl_units
```
