---
title: "Testing gauge files"
format: html
editor: visual
---

## Uneven gauge dates

When working with historical data, we often have gauges with uneven ranges. The (maybe) safest way to handle this is to put each in a separate file, so the directory looks like scenario_name/gauge1.csv, scenario_name/gauge2.csv, etc. That runs each as a separate scenario. I've done a fair amount of wrangling of directories and output to make that work, but it's still a hassle sometimes.

So here, I want to check that if I smash them together for the maximum date range (leaving NA in various places) it gives the same thing. That's more in the spirit of what the EWR tool expects, anyway.

So, the question is, do we get the same results both ways?

```{r}
library(HydroBOT)
library(sf)
library(dplyr)
# get directories
source('directorySet.R')
```

Directories

```{r}
# Outer directory for project data
project_dir <- file.path(datOut, 'werpstyle')

hydro_dir <- file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR')

# Outer directory for project data
smoosh_dir <- file.path(datOut, 'werpsmoosh')

hydrosmoosh_dir <- file.path(smoosh_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewrsmoosh_results <- file.path(smoosh_dir, 'module_output', 'EWR')
```

Now, we don't want to do any aggregations at all. Just read in the EWR data as-is and see if it's the same

```{r}
ewr_separate <- get_ewr_output(ewr_results)
ewr_smoosh <- get_ewr_output(ewrsmoosh_results)
```

Hmm. Those are totally different

```{r}
ewr_separate
ewr_smoosh
```

```{r}
separate_summary <- get_any_ewr_output(ewr_results, type = 'summary')
smoosh_summary <- get_any_ewr_output(ewrsmoosh_results, type = 'summary')
```

```{r}
separate_summary
smoosh_summary
```

```{r}
separate_yearly <- get_any_ewr_output(ewr_results, type = 'yearly')
smoosh_yearly <- get_any_ewr_output(ewrsmoosh_results, type = 'yearly')
```

```{r}
separate_yearly |> 
  dplyr::arrange(gauge, planning_unit_name, year, ewr_code)
smoosh_yearly |> 
  dplyr::arrange(gauge, planning_unit_name, year, ewr_code)
```

Event_years looks ok, lots of the frequency calcs are off because they compare to the whole span.
